% !TEX root = ../main.tex
\section{Sympathy} \label{sec::sympathy}
\textbf{TODO}.

When you choose any school from the Flamespeaking school, you learn the control flames cantrip (see page \pageref{spell::controlflames}).
You also gain the ability to learn any spell from this doctrine following the normal rules for spellcasting.

\subsection*{Flamespeaking} \label{ssec::flamespeaking}
    \DndDropCapLine{}{I see your future, mantled in ash.}

    The seers of Viphoger are said to be blessed by the gods, granted special sight that sees past our world, into the stars of Nyx and beyond.
    Even novice seers are able to glimpse the weave of fate, seeing the connections of destiny that bind us all.
    With proper training, years of practice, and a bit of intuition, the best soothsayers can foretell every possible future, not just those most likely.

    Flamespeakers are special seers, blessed by Purphoros, god of the forge.
    Through the god's divine power, they are able to see portents in the curlk of smoke, the flicker of flames, and the patterns of ash.

    \subsubsection{Flickering Future}
        With the exception of those blessed by Keranos, god of insight, or Klothys, god of destiny, the powers of a seer depend very little on which god they've received their sight from.
        The only variation is often in what they are able to see from their future --- or example, seers blessed by Erebos are usually haunted by visions of death, while those blessed by Nylea might know exactly when and where to find the quarry of their hunt.

        Most seers receive their portents by sight, in moments when their eyes look beyond, to the weave of fate, and follow the tangled lines therein.
        The flamespeakers of Purphoros are different in that they are unable to see the weave directly, but instead view it in every spark and ember of fire.
        For them, fire and desinty are inextricable, one and the same, with the weave of destiny imprinted onto a fundamental force of the world.

    \subsubsection{Twist the Lines}
        While the method with which they view the future is novel, what truly sets the flamespeakers apart is their ability to twist and tangle the pieces of the weave that they can see.
        Like many of Purphoros' priests, the flamespeakers are vessels for the god's power, granting them control over fire in its many forms.
        But for the flamespeakers, control of fire means a control of destiny.

        The flamespeakers are able to change the future as they see in the ashes.
        It requires great effort on their part, and the changes are rarely more than minor, but it can be done all the same.
        For this reason, the flamespeakers are highly sought after, especially by those who have been informed of a terrible fate destined to befall themselves or a loved one.

    \subsubsection{Spellcasting School}
        As with all sympathy spellcasting schools, flamespeakers need a medium to redirect heat.
        For them, this is done via blowpipes, the most essential component of a set of glassblower's tools.
        While not all flamespeakers are master glassblowers, they all know at least a small bit of the craft.

        In combat, flamespeakers usually wield their metallic blowpipes as quarterstaffs, acting as both a weapon and a spellcasting focus.
        Additionally, most also carry a firetrap, a spherical glass container they can heat to extreme temperatures with little effort. % Tubtsughak in Avshenese.
        Firetraps are used to fuel sympathy spells and enhance their effects.

        When you choose this spellcasting school, you learn the produce flame (see page \pageref{spell::produceflame}) cantrip, as well as the whispering ember spell \pageref{spell::whisperingember}.
