% !TEX root = ../main.tex
\section{Sympathy}
\subsection*{Mediums}
    \DndSpellHeader{Heat Link: Ember \label{spell::ember}}
        {Sympathy medium}
        {2 actions}
        {12 mt.}
        {S}
        {Up to an hour}
        You produce a lingering ember that tethers to a point of your choice within range.
        The ember can lie on a point ocuppied by another creature, stays in position for the spell's duration, and is visible.
        Other creatures can snuff out the flame by covering it in water or by enclosing it on a closed volume of medium or lesser size.
        You can have a number of embers active at the same time equal to your spellcasting ability modifier.

        Using an action, you can affect an ember in one of the following ways:
        \begin{itemize}
            \item \textbf{Move}.
            You move the ember up to 6 meters to a point within range.
            \item \textbf{Snuff Out}.
            You harmlessly snuff out the ember.
            \item \textbf{Explode}.
            The ember explodes, harming any creature(s) in the same space that the ember is.
            The creature(s) must succeed on a Dexterity saving throw or take 1d10 fire damage.
            This damage increases by 1d8 when you reach 5th level (2d10), 11th level (3d10), and 17th level (4d10).
        \end{itemize}
    \DndSpellHeader{Heat Link: Firetrap \label{spell:firetrap}}
        {Flamespeaker medium}
        {2 actions}
        {Self}
        {S}
        {Until dispelled}
        You produce a lingering ember inside a firetrap you are carrying.
        This flame can be used to cast any sympathy spell as if it were a normal ember, but it doesn't count towards your total number of embers.
        You can move the ember outside the firetrap as if it were a normal ember, but it explodes at the end of your turn without requiring an action from you.
    \DndSpellHeader{Electric Link: Charge \label{spell::charge}}
        {Sympathy medium}
        {1 action}
        {12 mt.}
        {S}
        {Up to an hour}
        You add a charge to a creature or object within range.
        A creature or object can have a total number of charges lesser or equal to your spellcasting ability modifier + your spellcasting proficiency bonus, but an arbitrary number of creatures can have charges at the same time.
        A creature can lose its charges only by being affected by certain sympathy spells, as specified in the spells' descriptions.

        Using two actions, you can affect a charged creature or object in one of the following ways:
        \begin{itemize}
            \item \textbf{Attract}.
            You cause the creature or object to be attracted to the closest metal object it is not wearing or carrying.
            The creature must succeed on a Strength saving throw or be moved a number of meters equal to the number of charges it has towards the object.
            Creatures of size Large or larger make this roll with advantage.
            Objects automatically roll a number equal to their weight (in kg) divided by 5.
            \item \textbf{Discharge}.
            You cause the creature to violently discharge, causing it to lose all charges.
            The creature must succeed on a Constitution saving throw or take 1d6 lightning damage plus 1d6 lightning damage for each charge it loses in this way.
            This spell's base damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).
            \item \textbf{Repel}.
            You cause two charged creatures or objects to be repelled from each other.
            Creatures must succeed on a Strength saving throw or be moved a number of meters equal to half the sum of the number of charges the two creatures have (rounded down).
            Creatures of size Large or larger make this roll with advantage.
            Objects automatically roll a number equal to their weight (in kg) divided by 5.
        \end{itemize}
    \DndSpellHeader{Similarity Link: Tether \label{spell::tether}}
        {Sympathy medium}
        {1 action}
        {12 mt.}
        {S}
        {Up to an hour}
        You create a sympathetic link to a creature or object within range, linking it to all other creatures and objects already affected by this spell.
        You can maintain a link between a number of creatures and objects equal to your spellcasting ability modifier (minimum of 2).
        When a creature dies, its link is automatically broken.

        Using two actions, you can affect all linked creatures and objects in one of the following ways:
        \begin{itemize}
            \item \textbf{Disconnect}.
            You break the link, freeing all affected creatures.
            \item \textbf{Harm}.
            Any time one of the linked creatures takes damage until the end of your next turn, all other creatures take 1d4 force damage (roll once for all creatures).
            \item \textbf{Ward}.
            All creatures can roll a d4 and add the number rolled to one saving throw of their choice before the end of your next turn.
        \end{itemize}
\subsection*{Spells}
\subsubsection{Heat Link}
    \DndSpellHeader{Condense I: Fog Cloud \label{spell::fogcloud}}
        {Sympathy spell - 2 spell points}
        {1 action}
        {24 meters}
        {S, M (a drop of water)}
        {up to 1 hour}
        You create a 2-meter-radius sphere of fog centered on an ember within range.
        The sphere spreads around corners, and its area is heavily obscured.
        It lasts for the duration, until a wind of moderate or greater speed disperses it, or until you choose to end the effect as a free action.

        You can consume up to 8 additional spell points to increase the range of this spell by 1 meter for each spell point beyond 2.
        In addition, you can use another action and consume 2 additional spell points to heat the fog.
        When a creature enters the spell's area for the first time on a turn or starts its turn there, that creature takes 1d8 fire damage.
    \DndSpellHeader{Condense II: Steam Burst \label{spell::steamburst}}
        {Sympathy spell - 3 spell points}
        {2 actions}
        {30 meters}
        {S, M (a pint of water)}
        {Instantaneous}
        You burst an ember into an eruption of steam.
        Every creature within 2 meters of the ember must make a Strength saving throw.
        A target takes 4d6 fire damage and is pushed 2 meters away from the ember on a failed save.
        On a successful save, the creature takes half damage and isn't pushed.

        You can consume up to 7 additional spell points to increase the damage by 1d6 for each point used.
        In addition, you can consume another action and 2 additional spell points to increase the number of meters a creature is pushed by 2.
    \DndSpellHeader{Drain I: Frostbite \label{spell::frostbite}}
        {Sympathy spell - 2 spell points}
        {2 actions}
        {24 meters}
        {S, M (a snowflake)}
        {Instantaneous}
        You drain heat out of one creature within 3 meters of one ember.
        The target must make a Constitution saving throw.
        On a failed save, the target takes 2d8 cold damage, and it has disadvantage on the next weapon attack roll it makes before the end of its next turn.

        You can consume up to 8 additional spell points to increase the damage by 1d8 for each point used.
        In addition, you can use another action and consume 2 additional spell points to prevent the creature from healing until the start of your next turn.
    \DndSpellHeader{Drain II: Freezing Sphere \label{spell::freezingsphere}}
        {Sympathy spell - 9 spell points}
        {2 actions}
        {30 meters}
        {S, M (a fistful of snow)}
        {Instantaneous}
        You turn an ember into an icy kernel about the size of a sling stone, which is cool to the touch.
        The kernel shatters when it impacts a surface, exploding into a 6-meter-radius sphere.
        Each creature in the area must make a Constitution saving throw.
        On a failed save, a creature takes 10d6 cold damage.
        On a successful save, it takes half as much damage.

        If the globe strikes a body of water or a liquid that is principally water (not including water-based creatures), it freezes the liquid to a depth of 15 cm over an area 6 meters square.
        This ice lasts for 1 minute.
        Creatures that were swimming on the surface of frozen water are trapped in the ice.
        A trapped creature can use an action to make a Strength check against your spell save DC to break free.

        You can consume up to 3 additional spell points to increase the damage by 1d6 for each spell point.
        In addition, you can consume another action and 3 additional spell points to cause any creature that fails the saving throw to be slowed.
        Slowed creatures can only take 2 actions during their next turn.
    \DndSpellHeader{Explode I: Fireball \label{spell::fireball}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {24 meters}
        {V, S}
        {Instantaneous}
        You cause a bright streak to flash from an ember you choose within range, which then blossoms with a low roar into an explosion of flame.
        Each creature in a 4-meter-radius sphere centered on that point must make a Dexterity saving throw.
        A target takes 8d6 fire damage on a failed save, or half as much damage on a successful one.

        The fire spreads around corners.
        It ignites flammable objects in the area that aren't being worn or carried.

        You can consume up to 6 additional spell points to increase the damage by 1d6 for each spell point used.
        In addition, you can consume another action and 3 additional spell points to cause all creatures that failed the saving throw to be pulled 2 meters towards the center of the fireball.
    \DndSpellHeader{Explode II: Fire Storm \label{spell::firestorm}}
        {Sympathy spell - 10 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Instantaneous}
        You manifest a storm made up of sheets of roaring flame to appear in all embers within range.
        The area of each storm consists of 3-meter cubes.
        A creature in an area overlaping two cubes is subjected to the effect only once.

        Each creature in the area must make a Dexterity saving throw.
        It takes 7d10 fire damage on a failed save, or half as much damage on a successful one.

        The fire damages objects in the area and ignites flammable objects that aren't being worn or carried.

        You can use another action and consume 3 additional spell points to cause the storms to linger until the start of your next turn.
        When a creature enters the spell's area for the first time on a turn or starts its turn there, that creature takes 2d10 fire damage.
    \DndSpellHeader{Heat I: Heat Metal \label{spell::heatmetal}}
        {Sympathy spell - 3 spell points}
        {2 actions}
        {24 meters}
        {S, M (a piece of metal)}
        {Concentration, up to 1 minute}
        You cause a metal object within range to glow red-hot.
        You cause the object to glow red-hot.
        You or the targetted object must be within 3 meters of an ember.
        Any creature in physical contact with the object takes 2d8 fire damage when you cast the spell.
        Until the spell ends, you can use another action on each of your subsequent turns to cause this damage again.

        If a creature is holding or wearing the object and takes the damage from it, the creature must succeed on a Constitution saving throw or drop the object if it can.
        If it doesn't drop the object, it has disadvantage on attack rolls and ability checks until the start of your next turn.

        You can consume up to 7 spell points to increase the damage by 1d8 for each additional spell point consume.
        Additionally, you can use another action and consume 3 additional spell points to target a non-metallic object with this spell.
    \DndSpellHeader{Heat II: Immolation \label{spell::immolation}}
        {Sympathy spell - 7 spell points}
        {2 actions}
        {30 meters}
        {S, M (an piece taken from the target creature)}
        {Concentration, up to 1 minute}
        You cause flames to wreathe one creature you can see within range.
        You or the creature must be standing within 3 meters of an ember.

        The target must make a Constitution saving throw.
        It takes 8d6 fire damage on a failed save, or half as much damage on a successful one.
        The target also burns for the spell's duration.
        The burning target sheds bright light in a 6-meter radius and dim light for an additional 6 meters.
        At the end of each of its turns, the target repeats the saving throw.
        It takes 4d6 fire damage on a failed save.

        You can consume up to 4 spell points to increase the initial damage by 1d6 for each additional spell point consumed.
    \DndSpellHeader{Radiance I: Light \label{spell::light}}
        {Sympathy spell - 0 spell points}
        {1 action}
        {24 meters}
        {V, S}
        {1 hour}
        Using an action, you cause an ember within range to shed a warm, bright light in a 4-meter radius and dim light for an additional 4 meters.
        Completely covering the ember with something opaque blocks the light.
        The spell ends if you cast it again or dismiss it as an action.
    \DndSpellHeader{Radiance II: Brilliance \label{spell::brilliance}}
        {Sympathy spell - 5 spell points}
        {1 actions}
        {30 meters}
        {V, S}
        {1 hour}
        You cause an ember affected by the Light spell to quickly increase in brightness.
        It emits a bright light in a 12-meter radius and sheds dim light for an additional 12 meters.

        Completely covering the ember with an opaque object, such as a bowl or a helm, blocks the light.

        When you cast this spell, you can use another action and consume 2 additional spell points to cause the light to spark fiercely upon being cast.
        Any creature (excluding you) in a 12-meter radius of the ember must roll a Constitution saving throw.
        On a failed save, a creature becomes blinded until the end of your next turn.
    \DndSpellHeader{Rebuke I: Scold \label{spell::scold}}
        {Sympathy spell - 2 spell points}
        {1 reaction, which you take in response to being damaged by a creature within 24 meters of you that you can see}
        {24 meters}
        {V, S}
        {Instantaneous}
        You cause an ember to dart towards the creature that damaged you, surrounding it by hellish flames.
        The creature must make a Dexterity saving throw.
        It takes 2d10 fire damage on a failed save, or half as much damage on a successful one.

        You can consume up to 8 spell points to increase the damage dealt by 1d10 for each additional spell point consumed.
    \DndSpellHeader{Rebuke II: Fire Shield \label{spell::fireshield}}
        {Sympathy spell - 6 spell points}
        {2 actions}
        {Self}
        {V, S}
        {10 minutes}
        You cause an ember to dart towards you, wreathing your body in thin and wispy flames.
        The flames shed a bright light in a 2-meter radius and dim light for an additional 2 meters.
        You can end the spell early by using an action to return the ember to its normal form.

        The flames provide you with a warm shield or a chill shield, as you choose.
        The warm shield grants you resistance to cold damage, and the chill shield grants you resistance to fire damage.

        You cannot use the ember to cast other spells while it acts as a shield.

        In addition, whenever a creature within a meter of you hits you with a melee attack, the shield erupts with flame.
        The attacker takes 2d8 fire damage from a warm shield, or 2d8 cold damage from a cold shield.

        By using another action and consuming 3 additional spell points, you can cause an ember to target another creature within 24 meters of you, causing this same effect on it instead of you.
    \DndSpellHeader{Screaming Bead \label{spell::screamingbead}}
        {Flamespeaker signature spell - 2 spell points}
        {2 actions}
        {30 meters}
        {S, M (a firetrap)}
        {Up to 24 hours}
        You cause an ember within range to turn into a glowing yellow bead.
        When you end the spell, the bead blossoms with a low roar into an explosion of flame that spreads around corners.
        Each creature in a 4-meter-radius sphere centered on that point must make a Dexterity saving throw.
        A creature takes fire damage equal to the total accumulated damage on a failed save, or half as much damage on a successful one.

        The spell's base damage is 2d6.
        If at the end of your turn the bead has not yet detonated, the bead grows slightly and the damage increases by 2d6.
        The maximum number of damage dice of this spell is equal to your level.
        When the spell reaches this damage, the bead stops growing.

        The bead sheds a bright light up to a radius equal to 1/4ths its number of damage dice in meters and dim light up to double that distance.

        The fire damages objects in the area and ignites flammable objects that aren't being worn or carried.

        This spell consumes two spell points when you cast it, and one additional spell point for each two damage dice added to it (one additional point at 4d6, another at 6d6, etc).
    \DndSpellHeader{Sear I: Searing Smite \label{spell::searingsmite}}
        {Sympathy spell - 2 spell points}
        {1 action}
        {24 meters}
        {V}
        {Concentration, up to 1 minute}
        You cause an ember within 3 meters of a creature to infuse its weapon.
        The next time it hits a creature with a weapon attack during the spell's duration, the weapon flares with white-hot intensity.
        The attack deals an extra 1d6 fire damage to the target and causes it to ignite in flames.
        At the start of each of its turns until the spell ends, the target must make a Constitution saving throw.
        On a failed save, it takes 1d6 fire damage.
        On a successful save, the spell ends.
        If the target or a creature within a meter of it uses two actions to put out the flames, or if some other effect douses the flames (such as the target being submerged in water), the spell ends.

        You can consume up to 8 spell points with when you cast this spell, increasing the initial extra damage by 1d6 for each additional spell point consumed.
        In addition, you can consume a spell point each time the target rolls the Constitution saving throw to force it to roll with disadvantage.
    \DndSpellHeader{Sear II: Flame Arrows \label{spell::flamearrows}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {24 meters}
        {S, M (An arrow or bolt)}
        {Concentration, up to 1 hour}
        You infuse a container holding ammunition with an ember within 3 meters of you.
        When a target is hit by a ranged weapon attack using a piece of ammunition drawn from the container, the target takes an extra 1d6 fire damage.
        The spell ends on a piece of ammunition when it hits or misses, and the spell ends when twelve pieces of ammunition have been drawn from the container.

        You can consume up to 6 additional spell points to increase the number of pieces of ammunition infused by two for each point.
        When an infused munition is shot, you can use your reaction and one spell point to move an ember to the location where it hits, dealing 2d6 additional fire damage to the target.
    \DndSpellHeader{Warmth I: Burn Wounds \label{spell::burnwounds}}
        {Sympathy spell - 2 spell points}
        {2 actions}
        {24 meters}
        {S, M (a piece of cloth)}
        {Instantaneous}
        You heal a creature within 3 meters of an ember.
        The creature regains a number of hit points equal to 1d8 + your spellcasting ability modifier.

        You can consume up to 8 additional spell points when you cast this spell, healing the target 1d8 hit points for each spell point consumed.
        In addition, you can use another action and consume 1 spell point to end the frightened condition on the target.
    \DndSpellHeader{Warmth II: Aura of Vitality \label{spell::auraofvitality}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Concentration, up to 1 minute}
        You cause healing energy to radiate from an ember within range with a 3-meter radius.
        Until the spell ends, you can use an action to cause one creature in the aura (including you) to regain 2d6 hit points.
        You can heal a creature using this effect only once during your turn.

        When you heal a creature with this spell, you can choose to consume 1 spell point to give the creature resistance against fire or cold damage (your choice) until the start of your next turn.
\subsubsection{Electric Link}
    \DndSpellHeader{Alacrity I: Stride \label{spell::stride}}
        {Sympathy spell - 2 spell points}
        {1 action}
        {24 meters}
        {V, S}
        {1 hour}
        Choose a charged creature within range.
        The creature's movement speed is increased by one meter for each charge it has for the duration of the spell.
        In addition, the creature's jump distance is tripled for the duration.

        If the creature is lifted off the ground via any method, it loses this benefit.

        You can use up to 8 additional spell points, increasing the number of creatures affected by the spell by 1 for each spell points consumed.
    \DndSpellHeader{Alacrity II: Haste \label{spell::haste}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Up to 1 minute}
        Choose a charged creature within range.
        That creature gains a +2 bonus to AC, advantage on Dexterity saving throws, gains an additional action on each of its turns, and its multiple attack penalty is reduced by 1.

        Every turn the target is affected by this spell it loses one charge.
        The spell ends when the creature drops to zero charges.

        When the spell ends, the target can't move or take actions until after its next turn, as a wave of lethargy sweeps over it.
    \DndSpellHeader{Bolt I: Lightning \label{spell::lightning}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {20-meter line}
        {V, S}
        {Instantaneous}
        A stroke of lightning forming a line 20 meters long and 1 meter wide blasts out from you, aiming a charged creature of your choice.
        Each creature in the line must make a Dexterity saving throw.
        A creature takes 8d6 lightning damage on a failed save, or half as much damage on a successful one.

        The lightning ignites flammable objects in the area that aren't being worn or carried.

        You can consume up to 6 additional spell points when you cast this spell, increasing the damage by 1d6 for each additional point.
        In addition, you can use another action and spend 2 additional spell points to discharge all affected creature, dealing an additional 1d6 lightning damage for each lost charge.
    \DndSpellHeader{Bolt II: Chain Lightning \label{spell::chainlightning}}
        {Sympathy spell - 9 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Instantaneous}
        You create a bolt of lightning that arcs toward a target of your choice that you can see within range.
        Bolts then leap from that target to all creatures with at least one charge within 6 meters of the first target.
        A target can be a creature or an object and can be targeted by only one of the bolts.

        A target must make a Dexterity saving throw.
        The target takes 10d8 lightning damage on a failed save, or half as much damage on a successful one.

        You can consume up to 3 spell points to increase the range of the leaping bolts by 3 meters for each additional spell point consumed.
        In addition, you can use another action and spend 3 spell points to discharge all affected creatures, dealing an additional 1d8 lightning damage for each lost charge.
    \DndSpellHeader{Deviate I: Deflect \label{spell::deflect}}
        {Sympathy spell - 2 spell points}
        {1 reaction, which you take in response to being attacked}
        {Self}
        {V}
        {Instantaneous}
        You impose disadvantage on an attack made against you using a weapon made of metal, like an arrow or a sword.

        You can consume 1 additional spell point to use this spell against an attack made with a non-metallic weapon.
    \DndSpellHeader{Deviate II: Eject \label{spell::eject}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {Self (15-meter sphere)}
        {V}
        {Concentration, up to 1 minute}
        You cause a strong magnetic push or pull (your choice) to emanate from you.
        Each creature with at least one charge that starts its turn inside a 15-meter sphere centered on you must succeed on a Strength saving throw or be pushed or pulled 3 meters from you in a straight line pointed towards you.
        Creatures with 3 or more charges make this roll with disadvantage.

        In addition, moving through the charged sphere is hard, and any charged creature inside it has its movement speed halved.

        As an action on each of your turns before the spell ends, you can change the direction of the force.
    \DndSpellHeader{Field I: Call Lightning \label{spell::calllightning}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {24 meters}
        {V, S}
        {Concentration, up to 10 minutes}
        You charge an circular area of ground with a 12-meter radius.
        The spell fails if there is no direct access to the sky above the area.

        On each of your turns until the spell ends, you can use an action to call down lightning towards a creature or object with at least one charge.
        Each creature within 1 meter of the targetted point must make a Dexterity saving throw.
        A creature takes 3d10 lightning damage on a failed save, or half as much damage on a successful one.
        You can call down lightning in this way only once per turn.

        If you are outdoors in stormy conditions when you cast this spell, the spell's damage increases by 1d10.

        You can consume up to 12 additional spell points when casting this spell, increasing the damage done by each lightning strike by 1d10 for each 2 extra spell points used in this way.
        In addition, by consuming 2 spell points, you can use another action to call down one subsequent lightning strike during your turn.
    \DndSpellHeader{Field II: Storm Sphere \label{spell::stormsphere}}
        {Sympathy spell - 6 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Concentration, up to 1 minute}
        A 4-meter-radius sphere of whirling air springs into existence, centered on a point you choose within range.
        The sphere remains for the spell's duration.
        Each creature in the sphere when it appears or that ends its turn there must succeed on a Strength saving throw or take 2d6 bludgeoning damage.
        The sphere's space is difficult terrain.

        Until the spell ends, you can use an action on each of your turns to cause a bolt of lightning to leap from the center of the sphere toward one charged creature you choose within 12 meters of the center.
        Make a ranged spell attack.
        You have advantage on the attack roll if the target is in the sphere.
        On a hit, the target takes 4d6 lightning damage.
        You can use this effect only once per turn.
        When using this attack, you can consume 3 spell points to cause the attack to target all charged creatures within range.

        Creatures within 6 meters of the sphere have disadvantage on Wisdom (Perception) checks made to listen.

        You can consume up to 5 additional spell points when casting the spell, increasing the damage for each of its effects by 1d6 for each spell point consumed.
    \DndSpellHeader{Jolt I: Thunderwave \label{spell::thunderwave}}
        {Sympathy spell - 2 spell points}
        {2 actions}
        {24 meters (3-meter cube)}
        {V, S}
        {Instantaneous}
        A wave of thunderous force sweeps out from you or a charged creature of your choice within range.
        Each creature in a 3-meter cube originating from the target (excluding the target) must make a Constitution saving throw.
        On a failed save, a creature takes 2d8 thunder damage and is pushed 2 meters away from the target.
        On a successful save, the creature takes half as much damage and isn't pushed.

        In addition, unsecured objects that are completely within the area of effect are automatically pushed 2 meters away from you by the spell's effect, and the spell emits a thunderous boom audible out to 60 meters.

        You can consume up to 8 additional spell points, increasing the damage by 1d8 for each spell point used.
        In addition, you can use another action and consume 3 additional spell points to cause all creatures that fail the saving throw to lose their movement speed until the start of your next turn.
    \DndSpellHeader{Jolt II: Lightning Arrow \label{spell::lightningarrow}}
        {Sympathy spell - 5 spell points}
        {1 action}
        {12 meters}
        {V, S}
        {Concentration, up to 1 minute}
        You apply a charge on a piece of ammunition or thrown weapon.
        The next time this object is used to make a ranged weapon attack during the spell's duration, it transforms into a bolt of lightning.
        The attack roll is made as normal.
        The target takes 4d8 lightning damage on a hit, or half as much damage on a miss, instead of the weapon's normal damage.

        Whether the attack hits or misses, each creature within 2 meters of the target must make a Dexterity saving throw.
        Each of these creatures takes 2d8 lightning damage on a failed save, or half as much damage on a successful one.

        The piece of ammunition or weapon then returns to its normal form.

        You can consume up to 6 additional spell points, increasing the damage for both effects by 1d8 for each spell point consumed.
        In addition, you can use another action and consume 4 additional spell points to cause all creatures that fail the save to be paralyzed until the start of the attacker's next turn.
    \DndSpellHeader{Overload I: Spray \label{spell::spray}}
        {Sympathy spell - 2 spell points}
        {2 actions}
        {Self (3-meter cone)}
        {V, S}
        {1 round}
        You overcharge all charged creatures in a 3-meter cone in front of you.
        All creatures affected by this spell are blinded until the end of your next turn.
        Creatures with 3 or more charges must succeed on a Constitution saving throw.
        On a failed save, they are also paralyzed for the duration.
    \DndSpellHeader{Overload II: Hold \label{spell::hold}}
        {Sympathy spell - 7 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Concentration, up to 1 minute}
        Choose a charged creature that you can see within range.
        The target must succeed on a Constitution saving throw or be paralyzed for the duration.
        At the end of each of its turns, the target can make another Constitution saving throw.
        On a success, the spell ends on the target.

        You can use up to 12 additional spell points when you cast this spell, affecting another charged creature within range for each 3 additional spell points.
    \DndSpellHeader{Spark I: Booming Blade \label{spell::boomingblade}}
        {Sympathy spell - 0 spell points}
        {1 action}
        {12 meters}
        {V}
        {1 round}
        You apply one charge on a metallic weapon or piece of ammunition.
        The weapon discharges on a successful attack against a target, adding a charge to it.

        In addition to the attack's normal effects, the attack deals an extra 1d8 thunder damage on a hit.
        This damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).

        If the attacked creature moves before the start of your next turn, you can use your reaction to cause it to violently discharge.
        The creature takes 1d8 lightning damage plus an extra 1d8 lightning damage for each charge lost in this way.
        This effect's base damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).

        Additionally, you can
    \DndSpellHeader{Spark II: Electric Arc \label{spell::electricarc}}
        {Sympathy spell - 0 spell points}
        {2 actions}
        {3 meters}
        {V, S}
        {Instantaneous}
        You create an arc of lightning that strikes one creature of your choice that you can see within 3 meters of you.
        The target must succeed on a Dexterity saving throw, taking 1d10 lightning damage on a failed save.
        This damage increases by 1d10 when you reach 5th level (2d10), 11th level (3d10), and 17th level (4d10).
        In addition, this attack applies a charge on the target.

        If the creature moves before the start of your next turn, you can use your reaction to cause the creature to violently discharge.
        The creature takes 1d8 lightning damage plus an extra 1d8 lightning damage for each charge lost in this way.
        This effect's base damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).
    \DndSpellHeader{Stride I: Misty Step \label{spell::mistystep}}
        {Sympathy spell - 3 spell points}
        {1 actions}
        {Self meters}
        {V}
        {Instantaneous}
        You teleport up to 6 meters to an unoccupied space that you can see.
        You must have at least one charge to use this spell.
    \DndSpellHeader{Stride II: Thunder Step \label{spell::thunderstep}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {18 meters}
        {V}
        {Instantaneous}
        You teleport yourself to an unoccupied space you can see within range.
        Immediately after you disappear, a thunderous boom sounds, and each creature within 2 meters of the space you left must make a Constitution saving throw, taking 3d10 thunder damage on a failed save, or half as much damage on a successful one.
        The thunder can be heard from up to 60 meters away.

        You can bring along objects as long as their weight doesn't exceed what you can carry.
        You can also teleport one willing creature of your size or smaller who is carrying gear up to its carrying capacity.
        The creature must be within 1 meter of you when you cast this spell, and there must be an unoccupied space within 1 meter of your destination space for the creature to appear in; otherwise, the creature is left behind.

        You must have at least 3 charges to use this spell.

        You can consume up to 6 additional spell points when you cast this spell, increasing the damage dealt by 1d10 for each point.
\subsubsection{Similarity Link}
    \DndSpellHeader{Compress I: Sinkhole \label{spell::sinkhole}}
        {Sympathy spell - 6 spell points}
        {2 actions}
        {24 meters}
        {S, M (a piece of rock)}
        {Instantaneous}
        All linked creatures are pushed by a tremendous force towards the middle point between all of them.
        Each creature must make a Strength saving throw.
        On a failed save, the creature takes 5d10 force damage and is pulled up to 4 meters in a straight line toward this point (even if that point is in the air).
        On a successful save, the creature takes half as much damage and isn't pulled.

        You can consume up to 5 additional spell points when you cast this spell, increasing the damage dealt by 1d10 per spell point.
        In addition, you can use another action and consume 2 spell points to move the middle point to the location of one of the linked creatures.
    \DndSpellHeader{Compress II: Ravenous Void \label{spell::ravenousvoid}}
        {Sympathy spell - 13 spell points}
        {3 actions}
        {50 meters}
        {S, M (a chunk of iron)}
        {Concentration, up to 1 minute}
        You create a 4-meter-radius sphere of destructive force at the middle point between all linked creatures.
        For the spell's duration, the sphere and any space within 20 meters of it is difficult terrain to all linked creatures.

        A linked creature that starts its turn within 20 meters of the sphere must succeed on a Strength saving throw or be pulled straight toward the sphere's center, ending in an unoccupied space as close to the center as possible.
        A creature that enters the sphere for the first time on a turn or starts its turn there takes 5d10 force damage and is restrained until it is no longer in the sphere.
        If the sphere is in the air, the restrained creature hovers inside the sphere.
        A creature can use two actions to make a Strength check against your spell save DC, ending this restrained condition on itself or another creature in the sphere that it can reach.
    \DndSpellHeader{Conformation I: Aqueous Form \label{spell::aqueousform}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {24 meters}
        {S, M (a pint of water)}
        {Concentration, up to 1 hour}
        You transform a willing linked creature into a pool of water.
        It returns to its true form after 1 hour, if it becomes incapacitated or dies, or if you lose concentration.

        The creature is under the following effects while in this form:
        \subparagraph{Liquid Movement}
        It has a swimming speed of 6 meters.
        It can move over or through other liquids.
        It can enter and occupy the space of another creature.
        It can rise up to its normal height, and it can pass through even Tiny openings.
        It extinguish flames in any space it enters.

        \subparagraph{Watery Resilience}
        It has resistance to bludgeoning, piercing, and slashing damage.
        It also has advantage on Strength, Dexterity, and Constitution saving throws.

        \subparagraph{Limitations}
        It can't talk, attack, cast spells, or activate items.
        Any objects it was carrying or wearing melds into its new form and are inaccessible, though it continues to be affected by anything it's wearing, such as armor.

        By spending up to 15 additional spell points, you can affect up to 6 linked creatures with this spell, using 3 spell points for each creature beyond the first.
    \DndSpellHeader{Conformation II: Investiture \label{spell::investiture}}
        {Sympathy spell - 9 spell points}
        {2 actions}
        {30 meters}
        {S, M (a stone or a shard of ice)}
        {Concentration, up to 10 minutes}
        You choose a linked creature within range, riming its body in stone or ice, depending on the material component used.

        While under investiture of stone, the creature gains the following benefits:
        \begin{itemize}
            \item It gains resistance to bludgeoning, piercing, and slashing damage.
            \item It can use two actions to create a small earthquake on the ground in a 3-meter radius centered on it.
            Other creatures on that ground must succeed on a Dexterity saving throw or be knocked prone.
            \item It can move across difficult terrain made of earth or stone without spending extra movement.
            It can move through solid earth or stone as if it was air and without destabilizing it, but it can't end your movement there.
            If it does so, it is ejected to the nearest unoccupied space, the spell ends, and it is stunned until the end of its next turn.
        \end{itemize}

        While under investiture of ice, the creature gains the following benefits:
        \begin{itemize}
            \item It is immune to cold damage and has resistance to fire damage.
            \item It can move across difficult terrain created by ice or snow without spending extra movement.
            \item The ground in a 2-meter radius around it is icy and is difficult terrain for creatures other than it.
            The radius moves with it.
            \item It can use two actions to create a 3-meter cone of freezing wind extending from its outstretched hand in a direction it chooses.
            Each creature in the cone must make a Constitution saving throw.
            A creature takes 4d6 cold damage on a failed save, or half as much damage on a successful one.
            A creature that fails its save against this effect has its speed halved until the start of the creature's next turn.
        \end{itemize}

        By spending up to 25 additional spell points, you can affect up to 6 linked creatures with this spell, using 5 spell points for each creature beyond the first.
    \DndSpellHeader{Cosanguinity I: Locate \label{spell::locate}}
        {Sympathy spell - 3 spell points}
        {2 actions}
        {---}
        {M (a part of a creature, such as hair or a nail)}
        {Up to 24 hours}
        You can track the creature from which the material component of this spell came from.
        You sense the direction to the creature's location, as long as it is in any location besides Nyx.
    \DndSpellHeader{Cosanguinity II: Effigy \label{spell::effigy}}
        {Sympathy spell - 5 spell points}
        {1 action}
        {12 meters}
        {S, M (a part of a creature, such as hair or a nail)}
        {Up to 1 hour}
        You create a similarity link to the creature from which the material component of this spell came from.
        All saving throws the creature makes against your sympathy spells are made with disadvantage.
        For all other purposes, this link behaves the same as the one produced by the Tether spell.
    \DndSpellHeader{Kinesis I: Catapult \label{spell::catapult}}
        {Sympathy spell - 2 spell points}
        {1 action}
        {24 meters}
        {S}
        {Instantaneous}
        Choose one object with which you are linked that weighs 3 kg or less within range.
        The object flies in a straight line up to 18 meters in a direction you choose before falling to the ground, stopping early if it impacts against a solid surface.
        If the object would strike a creature, that creature must make a Dexterity saving throw.
        On a failed save, the object strikes the target and stops moving.
        When the object strikes something, the object and what it strikes each take 3d6 bludgeoning damage.

        You can consume up to 8 additional spell points when casting this spell.
        The maximum weight of the objects that you can target with this spell increases by 3 kg, and the damage increases by 1d6, for each spell point above the first two.
    \DndSpellHeader{Kinesis II: Remote Movement \label{spell::remotemovement}}
        {Sympathy spell - 7 spell points}
        {2 actions}
        {30 meters}
        {S}
        {Concentration, up to 10 minutes}
        You gain the ability to move or manipulate linked creatures or objects by thought.
        When you cast the spell, and using two actions each round for the duration, you can exert your will on one linked creature or object that you can see within range, causing the appropriate effect below.
        You can affect the same target round after round, or choose a new one at any time.
        If you switch targets, the prior target is no longer affected by the spell.

        \subparagraph{Creature}
        You can try to move a Huge or smaller creature.
        Make an ability check with your spellcasting ability contested by the creature's Strength check.
        If you win the contest, you move the creature up to 6 meters in any direction, including upward but not beyond the range of this spell.
        Until the end of your next turn, the creature is restrained in your grip.
        A creature lifted upward is suspended in mid-air.
        On subsequent rounds, you can use your actions to attempt to maintain your grip on the creature by repeating the contest.

        \subparagraph{Object}
        You can try to move an object that weighs up to 500 kg.
        If the object isn't being worn or carried, you automatically move it up to 6 meters in any direction, but not beyond the range of this spell.
        If the object is worn or carried by a creature, you must make an ability check with your spellcasting ability contested by that creature's Strength check.
        If you succeed, you pull the object away from that creature and can move it up to 6 meters in any direction but not beyond the range of this spell.

        You can exert fine control on objects with your grip, such as manipulating a simple tool, opening a door or a container, stowing or retrieving an item from an open container, or pouring the contents from a vial.
    \DndSpellHeader{Pressure I: Pulse Wave \label{spell::pulsewave}}
        {Sympathy spell - 5 spell points}
        {2 actions}
        {Self (6-meter cone)}
        {S}
        {Instantaneous}
        You create intense pressure, unleash it in a 6-meter cone, and decide whether the pressure pulls or pushes linked creatures and objects.
        Each creature in that cone must make a Constitution saving throw.
        A creature takes 6d6 force damage on a failed save, or half as much damage on a successful one.
        Every creature that fails the save is either pulled 3 meters toward you or pushed 3 meters away from you, depending on the choice you made for the spell.

        In addition, unsecured linked objects that are completely within the cone are likewise pulled or pushed 3 meters.

        You can consume up to 6 spell points when you cast this spell, increasing the damage by 1d6 and the distance pulled or pushes by 1 meter for each additional point.
    \DndSpellHeader{Pressure II: Radiating Pressure \label{spell::radiatingpressure}}
        {Sympathy spell - 7 spell points}
        {2 actions}
        {Self (6-meter radius)}
        {S}
        {Instantaeous}
        You strike the ground, creating a burst of pressure that ripples outward from you.
        Each linked creature within 6 meters of you must succeed on a Constitution saving throw or take 5d6 thunder damage, as well as 5d6 force, and be knocked prone.
        A creature that succeeds on its saving throw takes half as much damage and isn't knocked prone.

        You can consume up to 4 spell points to increase the damages done by 1d6 each for each additional point consumed.
    \DndSpellHeader{Sprite I: Faerie Fire \label{spell::faeriefire}}
        {Sympathy spell - 2 spell points}
        {2 actions}
        {24 meters}
        {S}
        {Concentration, up to 1 minute}
        You choose one linked creature or object within range.
        Until the spell ends, the creature or object sheds bright light in a 4-meter radius and dim light for an additional 4 meters.
        The light can be colored as you like.
        Completely covering the target with something opaque blocks the light.
        The spell ends if you cast it again or dismiss it as an action.

        If you target a creature or an object held or worn by a hostile creature, that creature must succeed on a Dexterity saving throw to avoid the spell.
        Any attack made against an affected creature has advantage if the attacker can see it, and the affected creature or object can't benefit from being invisible.

        You can consume up to 8 additional spell points to affect up to 8 additional linked creatures or object with this spell, 1 point per creature or object.
    \DndSpellHeader{Sprite II: Wall of Light \label{spell::walloflight}}
        {Sympathy spell - 7 spell points}
        {2 actions}
        {30 meters}
        {S}
        {Concentration, up to 10 minutes}
        A shimmering wall of bright light appears between two linked creatures or objects you choose within range.
        The wall is 2 meters high, and 1 meter thick.
        The wall blocks line of sight, but creatures and objects can pass through it.
        It emits bright light out to 24 meters and dim light for an additional 24 meters.

        When the wall appears, each creature in its area (excluding the sources of the wall) must make a Constitution saving throw.
        On a failed save, a creature takes 4d8 radiant damage, and it is blinded for 1 minute.
        On a successful save, it takes half as much damage and isn't blinded.
        A blinded creature can make a Constitution saving throw at the end of each of its turns, ending the effect on itself on a success.

        A creature that ends its turn in the wall's area takes 4d8 radiant damage.

        You can use up to 4 spell points when you cast this spell, increasing the damage by 1d8 for each additional point.
        In addition, you can use another action and 3 spell points to cause the spell to also affect both source points.
    \DndSpellHeader{Transference I: Shared Essence \label{spell::sharedessence}}
        {Sympathy spell - 6 spell points}
        {2 actions}
        {24 meters}
        {V, S}
        {Concentration, up to 1 hour}
        All linked creatures must make a Constitution saving throw, with disadvantage if they are within 6 meters of any other linked creature.
        Any creature can willingly fail the save.
        If a creature succeeds on the save, it is unaffected by the spell, but remains linked for all other purposes.

        When damage or healing is dealt to one of the creatures tethered by this spell, it is instead divided between all of them.
        If one of the creatures dies, the other creatures remain affected.
    \DndSpellHeader{Transference II: Life Ceding \label{spell::lifeceding}}
        {Sympathy spell - 6 spell points}
        {2 actions}
        {30 meters}
        {S, M (a drop of blood)}
        {Instantaneous}
        You transfer life from one tethered creature to mend another's injuries.
        A linked creature of your choice takes 4d8 necrotic damage, and another linked creature of your choice regains a number of hit points equal to the damage taken.

        You can consume up to 5 additional spell points, increasing the damage and healing dealt by 1d8 for each spell point used.
        In addition, you can consume another action and 2 spell points to transfer the hit points between all other linked creatures.
        You choose how many hit points are transfered to each.
    \DndSpellHeader{Weight I: Feather Fall \label{spell::featherfall}}
        {Sympathy spell - 2 spell points}
        {1 reaction, which you take when you or a creature within 24 meters of you falls}
        {24 meters}
        {S, M (a small feather or a rock)}
        {1 minute}
        Choose any number of linked creatures within range.
        A falling creature's rate of descent slows to 12 meters per round until the spell ends.
        If the creature lands before the spell ends, it takes no falling damage and can land on its feet, and the spell ends for that creature.

        You can consume up to 6 additional spell points when you cast this spell, allowing you to target one non-linked creature for each spell point used.
    \DndSpellHeader{Weight II: Adjust Density \label{spell::adjustdensity}}
        {Sympathy spell - 0 spell points}
        {2 actions}
        {30 meters}
        {S}
        {Concentration, up to 1 minute}
        You can alter the weight of all linked objects and creatures.

        For up to one minute, you produce one of the following effects on the targets:
        \subparagraph{Lighten}
        The weight of the target is halved.
        Its speed is increased by 2 meters, it can jump twice as far as normal, and it has disadvantage on Strength checks and Strength saving throws.
        \subparagraph{Burden}
        The weight of the target is doubled.
        Its speed is reduced by 2 meters, and it has advantage on Strength checks and Strength saving throws.
        \subparagraph{Crush}
        The weight of the target is quadrupled.
        The creature's speed is halved, and it must roll a Constitution saving throw at the start of each of its turns.
        On a failed save, it takes 1d8 force damage.
