% !TEX root = ../main.tex
\section{Miscellaneous Spells}
This section contains spells not directly related to any school, like the innate magic from oths and zaloths and spells so commonplace that any spellcaster can learn them.

% \subsection*{Racial Spells}
%     % TODO. Update all these spells here to acommodate the action-magic relation.
%     \DndSpellHeader{Light \label{spell::light}} % Moonborn Oths.
%         {Moonborn cantrip}
%         {1 action}
%         {Touch}
%         {M (a firefly or a gram of silver moss)}
%         {1 hour}
%         You touch one object that is no larger than 2 meters in any dimension.
%         Until the spell ends, the object sheds bright light in a 9-meter radius and dim light for an additional 6 meters.
%         The light is of a pale blue color.
%         Completely covering the object with something opaque blocks the light.
%         The spell ends if you cast it again or dismiss it as an action.
%
%         If you target an object held or worn by a hostile creature, that creature must succeed on a Dexterity saving throw to avoid the spell.
%     \DndSpellHeader{Faerie Fire \label{spell::faeriefire}} % Moonborn Oths.
%         {Moonborn 1st-level spell}
%         {1 action}
%         {Self}
%         {S (forewings)}
%         {1 minute}
%         You flutter your forewings, spreading a blue dust into the air.
%         Each object in a 9-meter radius around you is outlined in a pale blue light.
%         Any creature in the area when the spell is cast is also outlined in the light.
%         For the duration, objects and affected creatures shed dim light in a 6-meter radius.
%
%         Any attack roll against an affected creature or object has advantage if the attacker can see it, and the affected creature or object can't benefit from being invisible.
%
%         A creature can try to shake off the dust as an action by succeeding on a Dexterity saving throw.
%         The dust stops glowing after a minute.
%     \DndSpellHeader{Glitterdust \label{spell::glitterdust}} % Moonborn Oths.
%         {Moonborn 2nd-level spell}
%         {1 action}
%         {Self}
%         {S (hindwings)}
%         {1 minute}
%         You flutter your hindwings, spreading a white dust into the air.
%         A cloud of golden particles covers everyone and everything within a 3-meter radius around you.
%         All creatures and objects within the area are covered by the dust, which cannot be removed and continues to sparkle until it fades.
%
%         For the duration, any target covered by the dust has disadvantage on Dexterity (Stealth) checks, and gains no benefit from being invisible.
%
%         Each creature targeted must succeed on a Wisdom saving throw or become blinded for the duration.
%         The creature can repeat its saving throw at the end of each of its turns, ending the blindness on a success.
%     \DndSpellHeader{Dancing Lights \label{spell::dancinglights}} % Chu'ash Oths.
%         {Chu'ash cantrip}
%         {1 action}
%         {24 meters}
%         {M (a firefly or a gram of silver moss)}
%         {1 hour}
%         You create up to four torch-sized pale blue orbs within range that hover in the air for the duration.
%         You can also combine the four lights into one glowing object vaguely resembling a creature of Medium size.
%         Each light sheds dim light in a 6-meter radius.
%
%         As a bonus action on your turn, you can move the lights up to 12 meters to a new spot within range.
%         A light must be within 4 meters of another light created by this spell, and a light winks out if it exceeds the spell's range.
%     \DndSpellHeader{Color Spray \label{spell::colorspray}} % Chu'ash Oths.
%         {Chu'ash 1st-level spell}
%         {1 action}
%         {Self (9-meter cone)}
%         {S (hindwings)}
%         {1 round}
%         A dazzling array of flashing, pale-colored light springs from your hindwings.
%         Roll a number of d10s equal to double your total number of hit dice; the total is how many hit points of creatures this spell can effect.
%         Creatures in a 9-meter cone originating from you are affected in a ascending order of their current hit points (ignoring unconscious creatures and creatures that can't see).
%
%         Starting with the creature that has the lowest current hit points, each creature affected by this spell is blinded until the end of your next turn.
%         Subtract each creature's hit points from the total before moving on to the creature with the next lowest hit points.
%         A creature's hit points must be equal to or less than the remaining total for that creature to be affected.
%     \DndSpellHeader{Blur \label{spell::blur}} % Chu'ash Oths.
%         {Chu'ash 2nd-level spell}
%         {1 action}
%         {Self}
%         {S (forewings)}
%         {Concentration, up to 1 minute}
%         You flutter your forewings in a frantic manner, lifting a refracting golden dust around you.
%         Your body becomes blurred, shifting and wavering to all who can see you.
%         For the duration, any creature has disadvantage on attack rolls against you.
%         An attacker is immune to this effect if it doesn't rely on sight, as with blindsight, or can see through illusions, as with truesight.
\subsection*{Cantrips}
    \DndSpellHeader{Bewitchery \label{spell::bewitchery}}
        {Miscellaneous cantrip}
        {2 actions}
        {6 meters}
        {V}
        {Up to 1 minute}
        You manifest a minor wonder, a sign of strange power, within range.
        You create one of the following magical effects within range:
        \begin{itemize}
            \item Your voice booms up to three times as loud as normal for 1 minute.
            \item You cause flames to flicker, brighten, dim, or change color for 1 minute.
            \item You cause harmless tremors in the ground for 1 minute.
            \item You create an instantaneous sound that originates from a point of your choice within range, such as a rumble of thunder, the cry of a raven, or ominous whispers.
            \item You instantaneously cause an unlocked door or window to fly open or slam shut.
            \item You alter the appearance of your eyes for 1 minute.
        \end{itemize}
        If you cast this spell multiple times, you can have up to three of its 1-minute effects active at a time, and you can dismiss such an effect as an action.
    \DndSpellHeader{Mage Hand \label{spell::magehand}}
        {Miscellaneous cantrip}
        {2 actions}
        {6 meters}
        {V, S}
        {1 minute}
        An invisible force only you can perceive appears at a point you choose within range.
        You can manipulate this force as if it was a floating hand.
        The hand lasts for the duration or until you dismiss it as an action.
        The hand vanishes if it is ever more than 6 meters away from you or if you cast this spell again.

        You can use an action to control the hand.
        You can use the hand to manipulate an object, open an unlocked door or container, stow or retrieve an item from an open container, or pour the contents out of a vial.
        You can move the hand up to 6 meters each time you use it.

        The hand can't attack, activate magic items, or carry more than 5 kilograms.
    \DndSpellHeader{Prestidigitation \label{spell::prestidigitation}}
        {Miscellaneous cantrip}
        {2 actions}
        {2 meters}
        {V, S}
        {Up to 1 hour}
        This spell is a minor magical trick that novice spellcasters use for practice.
        You create one of the following magical effects within range:
        \begin{itemize}
            \item You create an instantaneous, harmless sensory effect, such as a shower of sparks, a puff of wind, faint musical notes, or an odd odor.
            \item You instantaneously light or snuff out a candle, a torch, or a small campfire.
            \item You instantaneously clean or soil an object no larger than 30 liters.
            \item You chill, warm, or flavor up to 30 liters of nonliving material for 1 hour.
            \item You make a color, a small mark, or a symbol appear on an object or a surface for 1 hour.
            \item You create a nonmagical trinket or an illusory image that can fit in your hand and that lasts until the end of your next turn.
        \end{itemize}
        If you cast this spell multiple times, you can have up to three of its non-instantaneous effects active at a time, and you can dismiss such an effect using two actions.
\subsection*{1st-level Spells}
    \DndSpellHeader{Charm Person \label{spell::charmperson}}
        {1st-level miscellaneous}
        {2/3 actions}
        {6 meters}
        {V, S}
        {1 hour}
        You attempt to charm a humanoid you can see within range.
        It must make a Wisdom saving throw, and does so with advantage if you or your companions are fighting it.
        If it fails the saving throw, it is charmed by you until the spell ends or until you or your companions do anything harmful to it.
        The charmed creature regards you as a friendly acquaintance.
        When the spell ends, the creature knows it was charmed by you.

        If you cast this spell using 3 actions, the target can't make the Wisdom saving throw with advantage, even if you or your companions are fighting it.

        \paragraph{At Higher Levels}
        When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
        The creatures must be within 6 meters of each other when you target them.
    \DndSpellHeader{Mage Armor \label{spell::magearmor}}
        {1st-level miscellaneous}
        {1 action}
        {Touch}
        {V, S, M (a piece of cured leather)}
        {8 hours}
        You touch a willing creature who isn't wearing armor, and a protective magical force surrounds it until the spell ends.
        The target's base AC becomes 13 + its Dexterity modifier.
        The spell ends if the target dons armor or if you dismiss the spell as an action.
    \DndSpellHeader{Shield \label{spell::shield}}
        {1st-level miscellaneous}
        {1 reaction, which you take when you are hit by an attack}
        {Self}
        {V, S}
        {1 round}
        An invisible barrier of magical force appears and protects you.
        Until the start of your next turn, you have a +5 bonus to AC, including against the triggering attack.
