% !TEX root = ../main.tex
\section{Sympathy} \label{sec::sympathy}
% Red tide, fire, explode
% SCHOOLS: !Queish, Eljur, !Flamespeaking

Born from the red tide, the sympathy doctrine focuses on tethering links, the exchange of properties, and the redirection of energy.
Oft called Sympathists, sympathy spellcasters establish sympathetic links of different kinds between objects and creatures, altering the world around them through these.
These links can be of three natures: heat, electric, and similarity.

\subparagraph{Heat Link}
    (see page \pageref{medium::ember}).
    Sympathy spellcasters can quickly produce great surges of energy around them, but these are useless without a spark to ignite them.
    Heat links are floating embers which act as these sparks.

\subparagraph{Electric Link}
    (see page \pageref{medium::charge}).
    In contrast with fire, sympathists don't require a spark to manifest energy in its most pure form: electricity.
    Nonetheless, without a charge to guide lightning, it just takes the shortest route towards the ground.
    Sympathists use electric links to apply these charges to creatures and objects around them, enabling them to direct lightning at foes and allies alike.

\subparagraph{Similarity Link}
    (see page \pageref{medium::tether}).
    Unlike other sympathetic mediums, similarity links connect creatures and objects to exchange properties between them.
    A sympathist can tether these links to, for example, increase the weight of a creature, change its form, levitate it, etc.

\subsection*{Flamespeaking} \label{ssec::flamespeaking}
    \textit{I see your future, mantled in ash.}

    The seers of Viphoger are said to be blessed by the gods, granted special sight that sees past our world, into the stars of Nyx and beyond.
    Even novice seers are able to glimpse the weave of fate, seeing the connections of destiny that bind us all.
    With proper training, years of practice, and a bit of intuition, the best soothsayers can foretell every possible future, not just those most likely.

    Flamespeakers are special seers, blessed by Purphoros, god of the forge.
    Through the god's divine power, these sympathists are able to see portents in the curl of smoke, the flicker of flames, and the patterns of ash.
    They access sympathy through glassblowing, diving Purphoros' will through the heat of the glass.

    When you choose this spellcasting school, you learn the \textbf{Firetrap} heat link (see page \pageref{medium::firetrap}), as well as the \textbf{Screaming Bead} spell (see page \pageref{spell::screamingbead}).
    Neither the medium nor the spell count towards your known mediums and spells.

    % \subsubsection{Flickering Future}
    %     With the exception of those blessed by Keranos, god of insight, or Klothys, god of destiny, the powers of a seer depend very little on which god they've received their sight from.
    %     The only variation is often in what they are able to see from their future --- for example, seers blessed by Erebos are usually haunted by visions of death, while those blessed by Nylea might know exactly when and where to find the quarry of their hunt.
    %
    %     Most seers receive their portents by sight, in moments when their eyes look beyond, to the weave of fate, and follow the tangled lines therein.
    %     The flamespeakers of Purphoros are different in that they are unable to see the weave directly, but instead view it in every spark and ember of fire.
    %     For them, fire and destiny are inextricable, one and the same, with the weave of destiny imprinted onto a fundamental force of the world.
    %
    % \subsubsection{Twist the Lines}
    %     While the method with which they view the future is novel, what truly sets the flamespeakers apart is their ability to twist and tangle the pieces of the weave that they can see.
    %     Like many of Purphoros' priests, the flamespeakers are vessels for the god's power, granting them control over fire in its many forms.
    %     But for the flamespeakers, control of fire means a control of destiny.
    %
    %     The flamespeakers are able to change the future as they see in the ashes.
    %     It requires great effort on their part, and the changes are rarely more than minor, but it can be done all the same.
    %     For this reason, the flamespeakers are highly sought after, especially by those who have been informed of a terrible fate destined to befall themselves or a loved one.

\subsection*{Skycalling} \label{ssec::skycalling}
    \textit{Faced by a herald of the storm, your fate now lies in Keranos' hands.}

    Intrinsecally connected to the ash storm from which they were born, the zaloth have always had some capacity to control lightning.
    Early sympathists noticed that this link was sympathetic in nature, and copied it by applying electric links to gemstones.
    The Skycallers spellcasting school was born from these efforts.

    Skycallers have a unique understanding of the skies and the thunder that inhabits therein, drawing their power from the mighty Keranos.
    Their spellcasting acts to honor their god, embodying the fury of the storm as they gain insight from each spell cast.

    When you choose this spellcasting school, you learn the \textbf{Dry Air} electric link (see page \pageref{medium::dryair}), as well as the \textbf{Skycall} spell (see page \pageref{spell::skycall}).
    Neither the medium nor the spell count towards your known mediums and spells.

\subsection*{Frithbinder} \label{ssec::frithbinder}
    \textit{}

    Frithlings are small, inky humanoids that represent different aspects of nature.
    Thought to be older than the gods, they have been the subject of study for sympathists from even before The Schism.
    These studies led to the birth of the Frithbinders, a spellcasting school dedicated to the employment of frithlings to aid in Sympathy spellcasting.

    Frithbinders do not follow the teachings of any god in particular, but rather praise nature itself.
    These sympathists are not concerned about society's goals, and most are deemed outcasts due to their views.
    They access sympathy through the humble art of cobbling, allowing up to two accompanying frithlings to live as close to the ground as possible, taking shelter in the frithbinder's shoes.

    When you choose this spellcasting school, you learn the \textbf{Frithbind} similarity link (see page \pageref{medium::frithbind}), as well as the \textbf{Guided Strike} spell (see page \pageref{spell::guidedstrike}).
    Neither the medium nor the spell count towards your known mediums and spells.

\newpage
