% !TEX root = ../main.tex
\chapter{Yuadrem} \label{ch::yuadrem}

\DndDropCapLine{B}{efore all other races, the tall kin}
stood, and created both conscience and sentience.
Also known as ets, the tall ones are a species with a history so old that their origin is muddied in rumors and myth.
While their intentions were mysterious, it is believed that they created the first kins.

Ets were obsessed with the preservation of the self and of their species.
They cured all ailments from illness and age, and we capable of molding their own flesh.
While the tall kin are long gone now, remains of their stone dwellings can be found all around Yuadrem.
Even above the wall of ice and stone and below the canopies of the elderberry wilds, their ruins stand strong and immutable.

Either by accident or conscious decision, the ets created the first four kins: the hardy gats, the mobile irds, the wise oths, and the playful marsets.
Ever haunted by the fear of death, the tall kin assigned each race a different task.
To search for the Lung of Ur, a relic of great importance to the ets.

Gats were created with the shape of goats by the indigo school of thought of Thul-yharch.
Adaptable and hardy, they were tasked with digging and searching the deepest caverns and ravines.

A product of the red school of Zyl'rech, irds were made in the image of birds.
They soared the skies along with their creators, surveying land and ocean with unparalleled efficiency.

The gold school of Tosh Drieln produced the arboreal marsets in the image of marmosets.
Their duty was to explore the deep reaches of forest and jungle, where the foliage was too dense to be seen from the high skies.

% Tol, yua'kch szua-tlekeloo
Finally, the oths were created by the enigmatic Tol, a schoolless et that disappeared long before the rest of its kin.
Educated and ingenious, they worked day and night recording and strategizing.
They coordinated the efforts of their siblings, making sure that no region was explored twice.

Either by design or by accident, all these newborn kins were unable to retain their sentience by themselves.
This ability was only conserved via a special token: the qualar.
Qualars are small totems made from bone and a strange black liquid known as qual ichor, obsessively crafted by the tireless et Ctereth.

Anybody who doesn't keep a qualars in its possession will lose their sentience over the course of a few weeks.
If its unable to obtain a new one, the poor creature will eventually be reduced to a ``lost one'', a shell of their former self.
A lost one's mind is partially lost, as they lose their sentience.
They are perfectly capable of abstract thought and able to understand their surroundings.
They are, however, incapable of perceiving themselves as something separated from the environment, and forever roam with empty minds.

During their search, the roaming marsets discovered two new kins from the Drejeck rainforests, the naenks and tsaneks.
Born of mold and fungi, these two were surprisingly not created by the tall kin, but by a conscious tree, Tekatsae.

The ets' obsession grew as did the vigor of their search.
This eventually coalesced as the eruption of the spire, an age-defining event known as the Schism.
This catastrophe swiftly ended the life of the ets, bringing with it decades of darkness and winter.
This defines the year 0 After the Schism --- or 0 AS.
The event was followed by a 40 year famine.

However, the strength of the event also created the sizzling gate, which is a hole to an outside plane only known as the outer lands.
This gate brought forth horrid creatures known as the blueblood beasts.
These fiends are terrifying abominations that hunt fauna and kin alike.

But not all beings that came from the outer lands were terrible.
Three foreigner kins also arrived from the gate: the adventurous tortles, the ingenious umans, and the violent grungs.
Quickly dragged to a raging ash storm, these creatures were forced to find home in a torn world.
While they eventually managed to live among the locals, their connection to the outer lands brings them problems to this date.
They are hunted by blueblood beasts and dark scholars, both permanently seeking their outsider blood.

Four years after the Schism, the zaloth arrived.
The zaloth are creatures born from storm, given conscience in strange circumstances.
They instinctively gathered qualar from the burning Jan'krug, living in the ruins after the fires subsided.
Eventually, they descended into the lacerated lands of Yuadrem.

Decades later, the last of the et-created kins was discovered: the quies.
Obedient and vigorous, the quies acted as servants to carry out the few duties their masters couldn't do.

Strangely enough, both foreigner and orphan kins require qualar to retain their sentience.
Lost ones of every race can be found in Yuadrem.
This suggests that the objects are related to the nature of sentience itself, rather than being a restriction imposed by the tall kin.

\input{01yuadrem/01qualars}
\input{01yuadrem/02tides}
\input{01yuadrem/10continent}
\input{01yuadrem/20cultures}
\input{01yuadrem/30history}
