\chapter{Equipment} \label{ch::equipment}
\section{Starting Equipment} \label{sec::starting}
\section{Currency \& Trade Goods} \label{sec::currency}
Fob: copper coin, least value. Translate to ``common''.
Agnoma: nickel coin, worth 100 fobs. Named after Agnomakhos, the original et ruler of Mephetis.

% ORIG LIST OF ADVENTURING GEAR
% Abacus	2 gp	2 lb.
% Ammunition
% Arrows (20)	1 gp	1 lb.
% Blowgun needles (50)	1 gp	1 lb.
% Crossbow bolts (20)	1 gp	1½ lb.
% Sling bullets (20)	4 cp	1½ lb.
% Arcane focus
% Crystal	10 gp	1 lb.
% Orb	20 gp	3 lb.
% Rod	10 gp	2 lb.
% Staff	5 gp	4 lb.
% Wand	10 gp	1 lb.
% Backpack	2 gp	5 lb.
% Ball bearings (bag of 1,000)	1 gp	2 lb.
% Barrel	2 gp	70 lb.
% Basket	4 sp	2 lb.
% Bedroll	1 gp	7 lb.
% Bell	1 gp	—
% Blanket	5 sp	3 lb.
% Block and tackle	1 gp	5 lb.
% Book	25 gp	5 lb.
% Bottle, glass	2 gp	2 lb.
% Bucket	5 cp	2 lb.
% Caltrops (bag of 20)	1 gp	2 lb.
% Candle	1 cp	—
% Case, crossbow bolt	1 gp	1 lb.
% Case, map or scroll	1 gp	1 lb.
% Chain (10 feet)	5 gp	10 lb.
% Chalk (1 piece)	1 cp	—
% Chest	5 gp	25 lb.
% Clothes, common	5 sp	3 lb.
% Clothes, costume	5 gp	4 lb.
% Clothes, fine	15 gp	6 lb.
% Clothes, traveler's	2 gp	4 lb.
% Component pouch	25 gp	2 lb.
% Crowbar	2 gp	5 lb.
% Druidic focus
% Sprig of mistletoe	1 gp	—
% Totem	1 gp	—
% Wooden staff	5 gp	4 lb.
% Yew wand	10 gp	1 lb.
% Fishing tackle	1 gp	4 lb.
% Flask or tankard	2 cp	1 lb.
% Grappling hook	2 gp	4 lb.
% Hammer	1 gp	3 lb.
% Hammer, sledge	2 gp	10 lb.
% Healer's Kit	5 gp	3 lb.
% Holy symbol
% Amulet	5 gp	1 lb.
% Emblem	5 gp	—
% Reliquary	5 gp	2 lb.
% Holy water (flask)	25 gp	1 lb.
% Hourglass	25 gp	1 lb.
% Hunting trap	5 gp	25 lb.
% Ink (1-ounce bottle)	10 gp	—
% Ink pen	2 cp	—
% Jug or pitcher	2 cp	4 lb.
% Kit, climber's	25 gp	12 lb.
% Kit, disguise	25 gp	3 lb.
% Kit, forgery	15 gp	5 lb.
% Kit, herbalism	5 gp	3 lb.
% Kit, healer's	5 gp	3 lb.
% Kit, mess	2 sp	1 lb.
% Kit, poisoner's	50 gp	2 lb.
% Ladder (10-foot)	1 sp	25 lb.
% Lamp	5 sp	1 lb.
% Lantern, bullseye	10 gp	2 lb.
% Lantern, hooded	5 gp	2 lb.
% Lock	10 gp	1 lb.
% Magnifying glass	100 gp	—
% Manacles	2 gp	6 lb.
% Mirror, steel	5 gp	1/2 lb.
% Paper (one sheet)	2 sp	—
% Parchment (one sheet)	1 sp	—
% Pick, miner's	2 gp	10 lb.
% Piton	5 cp	1/4 lb.
% Poison, basic (vial)	100 gp	—
% Pole (10-foot)	5 cp	7 lb.
% Pot, iron	2 gp	10 lb.
% Potion of healing	50 gp	1/2 lb.
% Pouch	5 sp	1 lb.
% Quiver	1 gp	1 lb.
% Ram, portable	4 gp	35 lb.
% Rations (1 day)	5 sp	2 lb.
% Robes	1 gp	4 lb.
% Rope, hempen (50 feet)	1 gp	10 lb.
% Rope, silk (50 feet)	10 gp	5 lb.
% Sack	1 cp	1/2 lb.
% Scale, merchant's	5 gp	3 lb.
% Sealing wax	5 sp	—
% Shovel	2 gp	5 lb.
% Signal whistle	5 cp	—
% Signet ring	5 gp	—
% Spellbook	50 gp	3 lb.
% Spikes, iron (10)	1 gp	5 lb.
% Spyglass	1,000 gp	1 lb.
% Tent, two-person	2 gp	20 lb.
% Tinderbox	5 sp	1 lb.
% Torch	1 cp	1 lb.
% Vial	1 gp	—
% Waterskin	2 sp	5 lb. (full)
% Whetstone	1 cp	1 lb.


\section{Items} \label{sec::items}
\subsection*{Armor and Shields} \label{ssec::armor}
% https://2e.aonprd.com/Armor.aspx
% https://2e.aonprd.com/Shields.aspx
\subsection*{Brews} \label{ssec::brews}
% brew of heroism
% brew of letargy
% Revivify spell
% \paragraph{Brew of Speed} % Haste
\subsection*{Potions} \label{ssec::potions}
% NOTE: Costs could be a bit prohibitive. Check if it's a good idea to reduce them.
\begin{DndTable}[width=\linewidth, header=Potions]{llll}
    \textbf{Item}              & \textbf{Rarity} & \textbf{Cost} & \textbf{Weigtht} \\
    Acid (Vial)                & Common          & 250 agnomas   & --- \\
    Alchemist's Fire (Flask)   & Common          & 500 agnomas   & 0.5 kg. \\
    Antitoxin (Vial)           & Common          & 500 agnomas   & --- \\
    Caustic Brew (Flask)       & Common          & 250 agnomas   & 0.5 kg. \\
    Oil (Flask)                & Common          &   1 agnoma    & 0.5 kg. \\
    Perfume (Vial)             & Common          &  50 agnomas   & --- \\
    Potion of Healing (Flask)  & Common          & 500 agnomas   & 0.5 kg. \\
    Potion of Sickness (Flask) & Common          & 250 agnomas   & 0.5 kg. \\
    Soap                       & Common          &   2 fobs      & --- \\
    Bottled Acid Arrow (Flask)        & Uncommon & 1,000 agnomas & 0.5 kg. \\
    Oil of Slipperiness (Vial)        & Uncommon & 1,500 agnomas & --- \\
    Potion of Greater Healing (Flask) & Uncommon & 1,000 agnomas & 0.5 kg. \\
    Potion of Resistance (Flask)      & Uncommon & 1,000 agnomas & 0.5 kg. \\
    Bottled Fire (Flask)               & Rare    & 10,000 agnomas & 0.5 kg. \\
    Elixir of Health (Flask)           & Rare    & 10,000 agnomas & 0.5 kg. \\
    Flask of Mass Healing (Flask)      & Rare    & 10,000 agnomas & 0.5 kg. \\
    Oil of Burning (Vial)              & Rare    & 10,000 agnomas & --- \\
    Potion of Aqueous Form (Vial)      & Rare    & 10,000 agnomas & --- \\
    Potion of Superior Healing (Flask) & Rare    & 10,000 agnomas & 0.5 kg. \\
    Bottled Blight (Vial)              & Very Rare & 100,000 agnomas & --- \\
    Flask of Weakness (Flask)          & Very Rare & 100,000 agnomas & 0.5 kg. \\
    Healing Cloud (Flask)              & Very Rare & 100,000 agnomas & 0.5 kg. \\
    Liquid Death (Flask)               & Very Rare & 100,000 agnomas & 0.5 kg. \\
    Oil of Immolation (Vial)           & Very Rare & 100,000 agnomas & --- \\
    Oil of Sharpness (Vial)            & Very Rare & 100,000 agnomas & --- \\
    Potion of Contagion (Flask)        & Very Rare & 100,000 agnomas & 0.5 kg. \\
    Potion of Supreme Healing (Flask)  & Very Rare & 100,000 agnomas & 0.5 kg. \\
    Bottled Tizerus (Flask)            & Legendary & 500,000 agnomas & 0.5 kg. \\
    Potion of Condensated Life (Flask) & Legendary & 500,000 agnomas & 0.5 kg. \\
    Potion of Regeneration (Vial)      & Legendary & 500,000 agnomas & --- \\
    Vial of Pain (Vial)                & Legendary & 500,000 agnomas & ---
\end{DndTable}

% Common - Level 1 spells, DC 10, +1.
\paragraph{Acid (Vial)}
    As an action, you can splash the contents of this vial onto a creature within 1.5 meters of you or throw the vial up to 6 meters, shattering it on impact.
    In either case, make a ranged attack against a creature or object, treating the acid as an improvised weapon.
    On a hit, the target takes 2d6 acid damage.
\paragraph{Alchemist's Fire (Flask)}
    This sticky, adhesive fluid ignites when exposed to air.
    As an action, you can throw this flask up to 6 meters, shattering it on impact.
    Make a ranged attack against a creature or object, treating the alchemist's fire as an improvised weapon.
    On a hit, the target takes 1d4 fire damage at the start of each of its turns.
    A creature can end this damage by using its action to make a DC 10 Dexterity check to extinguish the flames.
\paragraph{Antitoxin (Vial)}
    A creature that drinks this vial of liquid gains advantage on saving throws against poison for 1 hour.
    It confers no benefit to undead or constructs.
\paragraph{Caustic Brew (Flask)} % Tasha's Caustic Brew
    Upon being shaken and breaking, this flask explodes in a radius of 3 meters.
    Each creature in the cloud must succeed on a DC 10 Dexterity saving throw or be covered in acid for a minute or until a creature uses two actions to scrape or wash the acid off itself or another creature.
    A creature covered in the acid takes 2d4 acid damage at start of each of its turns.
\paragraph{Oil (Flask)}
    As an action, you can splash the oil in this flask onto a creature within 1.5 meters of you or throw it up to 6 meters, shattering it on impact.
    Make a ranged attack against a target creature or object, treating the oil as an improvised weapon.
    On a hit, the target is covered in oil.
    The oil dries after one minute, and for this duration the target gains vulnerability to fire damage.
    You can also pour a flask of oil on the ground to cover a 1.5-meter-square area, provided that the surface is level.
    If lit, the oil burns for 2 rounds and deals 5 fire damage to any creature that enters the area or ends its turn in the area.
    A creature can take this damage only once per turn.
\paragraph{Potion of Healing (Flask)}
    You regain 2d4 + 2 hit points when you drink this potion.
    The potion's red liquid glimmers when agitated.
\paragraph{Potion of Sickness (Flask)} % Ray of sickness.
    Upon breaking, a raw of sickening greenish energy lashes out toward the closest creature within 18 meters.
    The target takes 2d8 poison damage and must make a Constitution saving throw with DC 10.
    On a failed save, it is also poisoned until the end of your next turn.
% Uncommon - level 2 spells, DC 12, +2.
\paragraph{Bottled Acid Arrow (Flask)} % Melf's acid arrow.
    Upon being opened, a shimmering green arrow streaks from the bottle opening in a line and bursts in a spray of acid.
    Make attack against a target within 27 meters.
    On a hit, the target takes 4d4 acid damage immediately and 2d4 acid damage at the end of its next turn.
    On a miss, the arrow splashes the target with acid for half as much of the initial damage and no damage at the end of its next turn.
\paragraph{Oil of Slipperiness (Vial)} % Freedom of Movement + Grease
    This sticky black unguent is thick and heavy in the container, but it flows quickly when poured.
    The oil can cover a Medium or smaller creature, along with the equipment it's wearing and carrying (one additional vial is required for each size category above Medium).
    Applying the oil takes 10 minutes.

    The affected creature's movement is unaffected by difficult terrain for 8 hours, and spells and other magical effects can neither reduce the target's speed nor cause the target to be paralyzed or restrained for the same duration.
    The target can also spend 1.5 meters of movement to automatically escape from nonmagical restraints, such as manacles or a creature that has it grappled.
    Finally, being underwater imposes no penalties on the target's movement or attacks.

    Alternatively, the oil can be poured on the ground as two actions, where it covers a 3-meter square.
    Slick grease covers the ground in the square which is turned into difficult terrain for 8 hours.
    Each creature standing in the area when you pour the liquid must succeed on a Dexterity saving throw or fall prone.
    A creature that enters the area or ends its turn there must also succeed on a Dexterity saving throw or fall prone.
\paragraph{Potion of Greater Healing (Flask)}
    You regain 4d4 + 4 hit points when you drink this potion.
    The potion's red liquid glimmers when agitated.
\paragraph{Potion of Resistance (Flask)}
    This potion comes in 5 flavors.
    When you drink this potion, you gain resistance to the potion's damage type for 1 hour.
    The damage types available are acid, cold, fire, lightning, or thunder.
% Rare - level 3 spells, DC 14, +3.
\paragraph{Bottled Fire (Flask)} % Fireball.
    Upon breaking, a bright spark blossoms with a low roar into an explosion of flame.
    Each creature in a 6-meter-radius sphere centered on that point must make a Dexterity saving throw with DC 14.
    A target takes 8d6 fire damage on a failed save, or half as much damage on a successful one.

    The fire spreads around corners.
    It ignites flammable objects in the area that aren't being worn or carried.
\paragraph{Elixir of Health (Flask)}
    When you drink this potion, it cures any disease afflicting you, and it removes the blinded, deafened, paralyzed, and poisoned conditions.
    The clear red liquid has tiny bubbles of light in it.
\paragraph{Flask of Mass Healing (Flask)} % Mass healing word.
    Upon breaking, all creatures within a 6-meter radius regain hit points equal to 1d4 + 3.
    This potion has no effect on undead or constructs.
\paragraph{Oil of Burning (Vial)} % Flame arrows.
    This brown sticky oil quickly heats up when accelerated.
    By drenching an arrow or bolt in the oil as an action, the piece of ammunition gains an additional 1d6 fire damage on hit.
    The oil evapores on a piece of ammunition when it hits or misses.
    Using two actions, you can pour the liquid into up to twelve pieces of ammunition at once.
\paragraph{Potion of Aqueous Form (Vial)}
    When you drink this potion, you transform into a pool of water.
    You return to your true form after 10 minutes or if you are incapacitated or die.
    You're under the following effects while in this form:
    \begin{itemize}
        \item \textbf{Liquid Movement.} You have a swimming speed of 9 meters.
        You can move over or through other liquids.
        You can enter and occupy the space of another creature.
        You can rise up to your normal height, and you can pass through even Tiny openings.
        You extinguish nonmagical flames in any space you enter.
        \item \textbf{Watery Resilience.} You have resistance to physical damage.
        You also have advantage on Strength, Dexterity, and Constitution saving throws.
        \item \textbf{Limitations}. You can't talk, attack, cast spells, or activate magic items.
        Any objects you were carrying or wearing meld into your new form and are inaccessible, though you continue to be affected by anything you're wearing, such as armor.
    \end{itemize}
\paragraph{Potion of Superior Healing (Flask)}
    You regain 8d4 + 8 hit points when you drink this potion. The potion's red liquid glimmers when agitated.
% Very Rare - level 4 and 5 spells, DC 16, +4.
\paragraph{Bottled Blight (Vial)} % 5th-level Blight.
    Upon being opened, this bottle releases a sickening gas that drains moistury and vitality.
    The gas fills a 1.5-meter square before dispersing.

    Any creature standing in this square must make a DC 16 Constitution saving throw.
    It takes 9d8 necrotic damage on a failed save, or half as much damage on a successful one.
    This potion has no effect on undead or constructs.

    If you target a plant creature or a magical plant, it makes the saving throw with disadvantage, and the potion deals maximum damage to it.

    If you target a nonmagical plant that isn't a creature, such as a tree or shrub, it doesn't make a saving throw, it simply withers and dies.
\paragraph{Flask of Weakness (Flask)} % Elemental Bane.
    This flask comes in 5 flavors: acid, cold, fire, lightning, and thunder.
    Upon being opened, this flask releases a noxious gas in a 10-meter square.
    Any creature who breathes the gas must succeed on a DC 16 Constitution saving throw or be affected by a weakening effect for a minute.
    The first time each turn the affected creature takes damage of the potion's type, the target takes an extra 2d6 damage of the type.
    Moreover, the target loses any resistance to that damage until the effect ends.
\paragraph{Healing Cloud (Flask)} % Mass Cure Wounds.
    Upon being opened, this potion releases a wave of healing energy in the form of a flowery smell.
    Any creature standing in a 9-meter radius sphere centered on the potion's location regains hit points equal to 3d8 + 4.
    This potion has no effect on undead or constructs.
\paragraph{Liquid Death (Flask)} % Cloudkill.
    Upon breaking, this flask releases a 6-meter radius sphere of poisonous, yellow-green fog.
    The fog spreads around corners.
    It lasts for 10 minutes or until strong wind disperses the fog, ending the effect.
    Its area is heavily obscured.

    When a creature enters the fog's area for the first time on a turn or starts its turn there, that creature must make a DC 16 Constitution saving throw.
    The creature takes 5d8 poison damage on a failed save, or half as much damage on a successful one.
    Creatures are affected even if they hold their breath or don't need to breathe.

    % The fog moves 3 meters away from you at the start of each of your turns, rolling along the surface of the ground.
    % The vapors, being heavier than air, sink to the lowest level of the land, even pouring down openings.
\paragraph{Oil of Immolation (Vial)} % Immolation.
    Upon being opened, the vial explodes into all consuming flames in a 1.5-meter radius sphere.
    Any creature within this sphere is wreathed by flames.
    It must make a DC 16 Dexterity saving throw.
    It takes 8d6 fire damage on a failed save, or half as much damage on a successful one.
    On a failed save, the target also burns for 1 minute.
    The burning target sheds bright light in a 9-meter radius and dim light for an additional 9 meters.
    At the end of each of its turns, the target repeats the saving throw.
    It takes 4d6 fire damage on a failed save, and the effect ends on a successful one.
    These flames can't be extinguished by other means.

    If damage from this spell kills a target, the target is turned to ash.
\paragraph{Oil of Sharpness (Vial)}
    This clear, gelatinous oil sparkles with tiny, ultrathin silver shards.
    The oil can coat one slashing or piercing weapon or up to 5 pieces of slashing or piercing ammunition.
    Applying the oil takes 1 minute.
    For 1 hour, the coated item has a +3 bonus to attack and damage rolls.
\paragraph{Potion of Contagion (Flask)} % Contagion.
    This flask inflicts disease, and comes in 6 flavors, detailed below.
    A creature touched by the contents of this flask is poisoned.

    At the end of each of the poisoned target's turns, the target must make a DC 16 Constitution saving throw.
    If the target succeeds on three of these saves, it is no longer poisoned, and the effect ends.
    If the target fails three of these saves, the target is no longer poisoned, but is infected by the potion's disease.
    The target is subjected to the disease for the a full week.

    Since this spell induces a natural disease in its target, any effect that removes a disease or otherwise ameliorates a disease's effects apply to it.

    \paragraph{Blinding Sickness} Pain grips the creature's mind, and its eyes turn milky white.
    The creature has disadvantage on Wisdom checks and Wisdom saving throws and is blinded.
    \paragraph{Filth Fever} A raging fever sweeps through the creature's body.
    The creature has disadvantage on Strength checks, Strength saving throws, and attack rolls that use Strength.
    \paragraph{Fleshrot} The creature's flesh decays.
    The creature has disadvantage on Charisma checks and vulnerability to all damage.
    \paragraph{Mindfire} The creature's mind becomes feverish.
    The creature has disadvantage on Intelligence checks and Intelligence saving throws, and the creature behaves as if under the effects of the confusion spell during combat.
    \paragraph{Seizure} The creature is overcome with shaking.
    The creature has disadvantage on Dexterity checks, Dexterity saving throws, and attack rolls that use Dexterity.
    \paragraph{Slimy Doom} The creature begins to bleed uncontrollably.
    The creature has disadvantage on Constitution checks and Constitution saving throws.
    In addition, whenever the creature takes damage, it is stunned until the end of its next turn.
\paragraph{Potion of Supreme Healing (Flask)}
    You regain 10d4 + 20 hit points when you drink this potion.
    The potion's red liquid glimmers when agitated.
% Legendary - level 6 and 7 spells, DC 18, +5
\paragraph{Bottled Tizerus (Flask)} % Delayed Blast Fireball
    This flask contains a tiny spark, patiently waiting to be awakened.
    You can shake the bottle to activate this spark.
    For the following minute, the bead continues to grow ever more violent.
    Upon breaking or when the minute passes, it blossoms with a low roar into an explosion of flame that spreads around corners.
    Each creature in a 6-meter radius sphere centered on that point must make a DC 18 Dexterity saving throw.
    A creature takes fire damage equal to the total accumulated damage on a failed save, or half as much damage on a successful one.

    The potions's base damage is 12d6.
    If at the end of your turn the bead has not yet detonated, the damage increases by 1d6.

    The glowing bead can be taken from the flask without causing it to explode.
    The creature touching it must make a DC 12 Dexterity saving throw.
    On a failed save, the spark erupts in flame.
    On a successful save, the creature can throw the bead up to 12 meters.
    When it strikes a creature or a solid object, the bead explodes.

    The fire damages objects in the area and ignites flammable objects that aren't being worn or carried.
\paragraph{Potion of Condensated Life (Flask)} % Heal
    Upon drinking, a surge of energy washes through the creature, causing it to regain 80 hit points.
    This potion also ends blindness, deafness, and any diseases affecting the target.
    This spell has no effect on constructs or undead.
\paragraph{Potion of Regeneration (Vial)} % Regenerate
    This potion's contents stimulate a creature's natural healing ability.
    The target regains 4d8 + 15 hit points.
    Lasting for an hour, the target regains 1 hit point at the start of each of its turns (10 hit points each minute).

    The target's severed body members (fingers, legs, tails, and so on), if any, are restored after 2 minutes.
    Any bodypart larger than a finger causes the creature to suffer one level of exhaustion upon regeneration.
\paragraph{Vial of Pain (Vial)} % Harm
    This vial contains a virulent disease which harms any creature who touches its contents.
    The target must make a DC 18 Constitution saving throw.
    On a failed save, it takes 14d6 necrotic damage, or half as much damage on a successful save.
    The damage can't reduce the target's hit points below 1.
    If the target fails the saving throw, its hit point maximum is reduced for 1 hour by an amount equal to the necrotic damage it took.
    Any effect that removes a disease allows a creature's hit point maximum to return to normal before that time passes.
\section{Weapons} \label{sec::weapons}
% SPECIAL WEAPONS:
% * Huge Krudzal weapons used to fight giants
% * Drer fire weapons
% * Sulia's large blast weapons (cannons and large handcannons)
% * Kaldrathal's more refined flintlock pistols
% * Mercury weapons from frostburn umans

% heavy shields grant +3 AC and half cover against ranged attacks, but impose a movement speed debuff:
% tower shield: +3 AC, -10 movement speed
% bulwark: +4 AC, -20 movement speed

% WEAPON CATEGORIES:
% Knives:
%   simple    : dagger (L) 1d4, throwing dagger (L) 1d4, kukri 1d6 (only when thrown, less range)
%   1-handed  : parrying dagger 1
% Straight Swords:
%   simple    : shortsword 1d6
%   1-handed  : broadsword (H) 1d8, backsword 1d8
%   versatile : bastard sword 1d8-1d10
%   2-handed  : longsword 1d10, claymore (H) 1d12, zweihander (H) 2d6, flamberge (H) 1d10, greatsword (H) 2d6
% Curved Swords:
%   simple    : sickle (L) 1d4, cutlass 1d6
%   1-handed  : scimitar (L) 1d6, sabre 1d8, khopesh 1d6
%   versatile : falchion (H) 1d8-1d10
%   2-handed  : katana 1d10, double-bladed scimitar 2d4
% Light Swords:
%   simple    : mail breaker 1d4
%   1-handed  : rapier 1d8, estoc/tuck 1d8, basket hilted sword 1d8
% Axes:
%   simple    : handaxe (L) 1d6
%   versatile : battleaxe 1d8-1d10, broad axe 1d8-1d10 (H)
%   2-handed  : bearded axe 1d10, greataxe (H) 1d12
% Hammer:
%   simple    : club (L) 1d4, light hammer (L) 1d4, mace 1d6
%   1-handed  : warhammer 1d8-1d10, boomerang 1d4
%   2-handed  : greatclub (H) 1d8, maul (H) 2d6, lucerne 1d10
% Pick:
%   simple    : kama (L) 1d6
%   1-handed  : war pick 1d8
%   2-handed  : horseman's pick 1d10
% Staves:
%   simple    : quarterstaff 1d6-1d8
% Spears:
%   simple    : javelin 1d6, trident 1d6-1d8
%   versatile : spear 1d8-1d10, lance 1d12
%   2-handed  : pike (H) 1d10
% Halberds:
%   2-handed  : glaive (H) 1d10, poleaxe (H) 1d10, lucerne (H) 1d0
% Flails:
%   1-handed  : nunchaku (L) 1d4, ball-and-chain 1d6
% Whip:
%   1-handed  : whip 1d4, bullwhip (1d4 slashing but 6m reach), qilinbian (1d6 slashing, finesse, reach - 6mt)
% Bow:
%   2-handed  : shortbow 1d6, composite bow 1d8, longbow (H) 1d8, yumi (H) 1d10 - disadvantage on less than 6 meters
% Crossbow:
%   1-handed  : hand crossbow (L) R1 1d6
%   2-handed  : light crossbow R1 1d8, repeating crossbow R3 1d8, heavy crossbow (H) R1 1d10
% Pistol:
%   1-handed  : flintlock R1 1d10, pistol (change name) R4 1d8
% Musket:
%   2-handed  : musket R1 1d12
% "Newer" Firearms:
%   1-handed  : palm pistol (L) R1 1d8, pepperbox R6 1d10
%   2-handed  : blunderbuss R1 2d8, bad news R1 2d12
% Fire-breathers (Drer) - misfiring damages you:
%   1-handed  : bomb 3d6
%   2-handed  : firelance 1d12, hand mortar 2d8, flamespewer 1d6*
% Giant-slayers (Krudzal) - no extra attack:
%   2-handed  : dreihander 2d12, greatmaul 4d6, greatchisel 2d8*, hand ballista 2d10
%       dreihander    - https://mortalshell.wiki.fextralife.com/Martyr's+Blade
%       greatmaul     - https://mortalshell.wiki.fextralife.com/Smoldering+Mace
%       greatchisel   - https://mortalshell.wiki.fextralife.com/Hammer+and+Chisel
%       hand ballista - https://mortalshell.wiki.fextralife.com/Ballistazooka - action to shoot, action to reload
% Trick weapons: take 3 or 4 from here https://bloodborne.wiki.fextralife.com/Weapons.
% Exotic:
%   1-handed  :
%   versatile :
%   2-handed  : swordspear* (H) 1d10
%   ranged    : blowgun 1, net -
% Special (no specific talents, generally used for flavor):
%   simple    : shortspear 1d6, dart 1d4, sling 1d4
% Footnotes:
% * swordspears are essentially fancy glaive, but require proficiency with spears and swords due to having a different combat style.

% Take firearms from https://www.dndbeyond.com/subclasses/gunslinger .

\subsection*{Armor Properties} \label{ssec::armorproperties}
    \subparagraph{Bulwark} The armor covers you so completely that your movement is hindered.
    You do not add your Dexterity modifier to Dexterity saving throws.

    \subparagraph{Chain} The armor is so flexible that it bends under strong blows, absorbing some of their strength.
    You gain resistance to the damage made by critical hits from bludgeoning, slashing, an piercing damage.

    \subparagraph{Cloth} This armor is light and comfortable.
    You can rest normally while wearing it.

    \subparagraph{Composite} The numerous overlapping pieces of this armor protect you from piercing attacks.
    You gain resistance to piercing damage.

    \subparagraph{Leather} The thick second skin of the armor disperses blunt force.
    You gain resistance to bludgeoning damage.

    \subparagraph{Noisy} The armor is also loud and likely to alert others of your presence, giving you disadvantage on Dexterity (Stealth) checks.

    \subparagraph{Plate} The sturdy plate provides no purchase for a cutting edge.
    You gain resistance to slashing damage.

\subsection*{Weapon Properties} \label{ssec::weaponproperties}
    \subparagraph{Ammunition} You can use a weapon that has the ammunition property to make a ranged attack only if you have ammunition to fire from the weapon.
    Each time you attack with the weapon, you expend one piece of ammunition.
    Drawing the ammunition from a quiver, case, or other container is part of the attack.
    Loading a one-handed weapon requires a free hand.
    At the end of the battle, you can recover half your expended ammunition by taking a minute to search the battlefield.

    If you use a weapon that has the ammunition property to make a melee attack, you treat the weapon as an improvised weapon.
    A sling must be loaded to deal any damage when used in this way.

    \subparagraph{Explosive} Upon a hit, everything within 5 ft of the target must make a Dexterity saving throw (DC equal to 8 + your proficiency bonus + your Dexterity modifier) or suffer 1d8 fire damage.
    If the weapon misses, the ammunition fails to detonate, or bounces away harmlessly before doing so.

    \subparagraph{Great} This weapon requires the Great Weapon User 1 feat to use.

    \subparagraph{Heavy} Creatures that are Small or Tiny have disadvantage on attack rolls with heavy weapons.
    A heavy weapon's size and bulk make it too large for a Small or Tiny creature to use effectively.

    \subparagraph{Loading} Because of the time required to load this weapon, you can fire only one piece of ammunition from it when you use an action, bonus action, or reaction to fire it, regardless of the number of attacks you can normally make.

    \subparagraph{Misfiring} Whenever you make an attack roll, and the dice roll is equal to or lower than the weapon’s Misfire score, the weapon misfires.
    The attack misses, and the weapon cannot be used again until you spend an action to try and repair it.
    To repair your weapon, you must make a successful Tinker’s Tools check (DC equal to 8 + misfire score).
    If your check fails, the weapon is broken and must be mended out of combat at a quarter of its cost.
    Creatures who use a weapon without being proficient increase its misfire score by 1.

    \subparagraph{Reloading} The weapon can be fired a number of times equal to its Reload score before you must spend 1 attack or 1 action to reload.
    You must have one free hand to reload the weapon.

    \subparagraph{Trick} This weapon requires the Flexible Fighter 1 feat to use.
    These weapons can be transformed into alternate forms and have different capabilities in this transformed state.
    The weapons have two values for damage and properties, one for their normal form, and one for the transformed one.

    \subparagraph{Two-Handed} This weapon requires two hands to use.
    This property is relevant only when you attack with the weapon, not when you simply hold it.

\subsection*{Ammunition} \label{ssec::ammunition}

\section{Adventuring Gear} \label{sec::adventuring}
% NOTE: Coating a weapon or 3 pieces of ammunition in poison costs two actions.
\section{Tools} \label{sec::tools}
\section{Mounts and Vehicles} \label{sec::adventuring}
\section{Qualars \& Trinkets} \label{sec::trinkets}
