% !TEX root = ../main.tex
\section*{Ammunition} \label{sec::ammunition}
\begin{table*}[b]%
    \begin{DndTable}[width=\linewidth, header=Ammunition]{Xcccccc}
        \textbf{Item} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
        Arrow                       & Mundane   &  1 &     15 fobs    & WOO    & 25 gr  & PHB 150 \\
        Arrows (20)                 & Mundane   & 18 &      1 agnoma  & WOO    & 0.5 kg & PHB 150 \\
        Blowgun Needle              & Mundane   &  1 &     15 fobs    & WOO    & 25 gr  & PHB 150 \\
        Blowgun Needles (20)        & Mundane   & 18 &      1 agnoma  & WOO    & 0.5 kg & PHB 150 \\
        Crossbow Bolt               & Mundane   &  1 &     15 fobs    & WOO    & 50 gr  & PHB 150 \\
        Crossbow Bolts (20)         & Mundane   & 18 &      1 agnoma  & WOO    & 1 kg   & PHB 150 \\
        Sling Bullet                & Mundane   &  1 &     15 fobs    & WOO    & 50 gr  & PHB 150 \\
        Sling Bullets (20)          & Mundane   & 18 &      1 agnoma  & WOO    & 1 kg   & PHB 150 \\
        Crossbow Bolt Case          & Plain     &  1 &      3 agnomas & CAR    & 0.5 kg & PHB 151 \\
        Quiver                      & Plain     &  1 &      3 agnomas & LEA    & 0.5 kg & PHB 153 \\
        Bullet                      & Common    &  1 &     30 agnomas & TIN    & 100 g  & DMG 268 \\
        Bullets (10)                & Common    &  8 &    100 agnomas & TIN    & 1 kg   & DMG 268 \\
        +1 Ammunition (20)          & Uncommon  &  4 &    300 agnomas & $\ast$ & $\ast$ & DMG 150 \\
        Barbed Ammunition (20)      & Uncommon  &  4 &    300 agnomas & $\ast$ & $\ast$ & ---     \\
        Destructive Ammunition (20) & Uncommon  &  4 &    300 agnomas & $\ast$ & $\ast$ & XGE  78 \\
        Nylea's Quiver              & Uncommon  &  8 &    500 agnomas & LEA    & 1 kg   & DMG 189 \\
        Reinforced Ammunition (20)  & Uncommon  &  4 &    300 agnomas & $\ast$ & $\ast$ & XGE 139 \\
        Walloping Ammunition (20)   & Uncommon  &  4 &    300 agnomas & $\ast$ & $\ast$ & XGE 139 \\
        +2 Ammunition (20)          & Rare      &  4 &  3,000 agnomas & $\ast$ & $\ast$ & DMG 150 \\
        Cacophonous Ammunition      & Rare      &  1 &  1,500 agnomas & $\ast$ & $\ast$ & ---     \\
        Fulgurating Ammunition (5)  & Rare      &  1 &  1,500 agnomas & $\ast$ & $\ast$ & MOT 198 \\
        Stunning Ammunition (5)     & Rare      &  1 &  1,500 agnomas & $\ast$ & $\ast$ & MOT 198 \\
        +3 Ammunition (20)          & Very Rare &  4 & 30,000 agnomas & $\ast$ & $\ast$ & DMG 150 \\
        Slaying Ammunition (4)      & Very Rare &  4 & 30,000 agnomas & $\ast$ & $\ast$ & DMG 152
    \end{DndTable}
\end{table*}

$\ast$ \textit{Required tool and weight depends on the type of ammunition.}

\paragraph{+1/+2/+3 Ammunition}
    You have a +1/+2/+3 bonus to attack and damage rolls made with this piece of ammunition.
    These pieces of ammunition break normally.
\paragraph{Barbed Ammunition}
    A creature attacked by a piece of barbed ammunition takes 1d4 necrotic damage at the beginning of its next turn.
    This effect doesn't stack.
\paragraph{Cacophonous Ammunition}
    Upon landing, a wave of thunderous force sweeps out from this projectile.
    Each creature in a 3-meters sphere originating from its landing location must make a DC 13 Constitution saving throw, taking 2d8 thunder damage and being pushed 2 meters away on a failed save.
    Unsecured objects that are completely within the area of effect are automatically pushed 2 meters away from the landing location.

    In addition, if you hit a creature with this projectile it must succeed on a DC 13 Constitution saving throw, taking 3d10 lightning damage on a failed save, or half as much damage on a successful save.

    This piece of ammunition breaks upon landing.
\paragraph{Crossbow Bolt Case}
    This wooden case can hold up to twenty crossbow bolts.
\paragraph{Destructive Ammunition}
    Coated with heavy steel, this piece of ammunition is unusually effective when used to break objects.
    Whenever a piece of destructive ammunition hits an object, the hit is a critical hit.
\paragraph{Fulgurating Ammunition}
    On a hit, this projectile deals an extra 2d8 lightning damage to its target.
    All other creatures within 2 meters of the target must each succeed on a DC 15 Constitution saving throw or take 1d8 thunder damage.
\paragraph{Quiver}
    A quiver can hold up to 20 arrows.
\paragraph{Nylea's Quiver}
    This quiver seems to be larger on the inside than what it looks from the outside.
    Each of the quiver's three compartments allows the quiver to hold numerous items while never weighing more than 1 kg.
    The shortest compartment can hold up to sixty arrows, bolts, or similar objects.
    The midsize compartment holds up to eighteen javelins or similar objects.
    The longest compartment holds up to six long objects, such as bows, quarterstaffs, or spears.

    You can draw any item the quiver contains as if doing so from a regular quiver or scabbard.
\paragraph{Reinforced Ammunition}
    This piece of ammunition doesn't break when used in combat.
    It can however be broken by succeeding on a DC 15 Athletics check.
\paragraph{Slaying Ammunition}
    A slaying ammunition is a specially designed weapon meant to slay a particular kind of creature.
    If a creature belonging to the type, race, or group associated with a slaying ammunition takes damage from it, the creature must make a DC 17 Constitution saving throw, taking an extra 6d10 piercing damage on a failed save, or half as much extra damage on a successful one.

    Once an arrow of slaying deals its extra damage to a creature, it breaks.
\paragraph{Stunning Ammunition}
    On a hit, this projectile deals an extra 1d10 force damage, and the target must roll a DC 13 Constitution saving throw, becoming stunned until the end of your next turn on a failed save.
\paragraph{Walloping Ammunition}
    This ammunition packs a wallop.
    A creature hit by the ammunition must succeed on a DC 10 Strength saving throw or be knocked prone.
\newpage~\newpage
