% !TEX root = ../main.tex
\subsection*{Brews} \label{ssec::brews}
The prices listed for brews are for a small keg, which fits 8 tankards worth of brew.
Divide this by 8 for the price of a tankard, or by 16 for the price of a cup.
Prices consider only the brew itsel, not the medium of transportation.

It takes one minute to drink a brew and gain its benefits, which can be done at the end of a short rest.
A creature cannot benefit from more than one brew at the same time.
% After drinking a brew a creature rolls a DC 8 Constitution saving throw.
% On a failure, it empties the content of the brew

\begin{DndTable}[width=\linewidth, header=Potions]{llll}
    \textbf{Item}                      & \textbf{Rarity} & \textbf{Cost}  & \textbf{Weigtht} \\
    Ale                                & Common          &     2 agnomas  &  4 kg.   \\
    Ale of Heroism                     & Common          &   500 agnomas  &  4 kg.   \\
    Barrel                             & Common          &    20 agnomas  & 35 kg.   \\
    Common Wine                        & Common          &    32 agnomas  &  4 kg.   \\
    Dozing Wine                        & Common          &   500 agnomas  &  4 kg.   \\
    Exalted Beer                       & Common          &   500 agnomas  &  4 kg.   \\
    Expeditious Brew                   & Common          &   500 agnomas  &  4 kg.   \\
    Fine Wine                          & Common          & 1,600 agnomas  &  4 kg.   \\
    Full Keg                           & Common          &    15 agnomas  & 15 kg.   \\
    Laughing Ale                       & Common          &   500 agnomas  &  4 kg.   \\
    Small Keg                          & Common          &    10 agnomas  &  2 kg.   \\
    Tankard                            & Common          &     2 fobs     &  0.5 kg. \\
    Beer of Vitality                   & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Brew of Absorption                 & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Brew of Giant's Strength           & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Calming Wine                       & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Dead Man's Ale                     & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Madman Wine                        & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Speaker's Whiskey                  & Uncommon        & 2,000 agnomas  &  4 kg.   \\
    Thassa's Mockery                   & Uncommon        & 2,000 agnomas  &  4 kg.   \\
\end{DndTable}



\paragraph{Ale of Heroism} % Heroism
    This ale is honey-flavored, reminding you of those most important to you.
    A creature who drinks this is imbued with bravery.
    For an hour, the creature is immune to being frightened and gains 1 temporary hit point at the start of each of its turns.
    After the hour passes, the creature loses all temporary hit points gained from this brew.
\paragraph{Dozing Wine} % Sleep
    This wine is so comforting that it sends creatures into slumber.
    Any creature who drinks this must succeed on a DC 10 Constitution saving throw.
    On a failure, the creature falls unconscious for an hour, until the sleeper takes damage, or someone uses an action to shake or slap the sleeper awake.
\paragraph{Exalted Beer} % Bless
    The sweet flavor of this beer truly is a blessing.
    After drinking it, the creature can add a d4 to any attack roll or saving throw it makes for one hour.
\paragraph{Expeditious Brew} % Expeditious Retreat
    This brew feels like caustic acid falling through your throat.
    After drinking it, the creature gains a bonus of 3 meters to its movement speed for one hour.
\paragraph{Laughing Brew} % Tasha's Hideous Laughter
    This fuzzy and bubbly drink seems to vibrate with astounding speed.
    After drinking it, the creature perceives everything as hilariously funny and falls into fits of laughter.
    The creature must succeed on a DC 10 Wisdom saving throw or fall prone, becoming incapacitated and unable to stand up for up to an hour.
    A creature with an Intelligence score of 4 or less isn't affected.

    At the end of each of its turns, and each time it takes damage, the target can make another DC 10 Wisdom saving throw.
    The target has advantage on the saving throw if it's triggered by damage.
    On a success, the effect ends.
% UNCOMMON - 2nd level spells, DC 12, +2
\paragraph{Beer of Vitality} % Aid
    This beer emboldens creatures with toughness and resolve.
    The drinker's hit point maximum and current hit points increase by 5 for 8 hours.
\paragraph{Brew of Absorption} % Absorb Elements + Dragon's breath of the absorbed element
    This drink seems to remain in your throat after drinking it, ready to return to the world on command.
    When the drinker takes acid, cold, fire, lightning, or poison damage within 8 hours of drinking the brew, it can use its reaction to gain resistance against the attack.
    As part of the same reaction, it can then exhale energy in a 4.5 meter cone.
    Each creature in the area must make a DC 12 Dexterity saving throw, taking 3d6 damage of the absorbed type on a failed save, or half as much damage on a successful one.
    The drinker can only use this ability once during the brew's duration.
\paragraph{Brew of Giant Strength}
    This brew's transparent liquid has floating in it a sliver of fingernail from a cyclops.
    When you drink it, your Strength score changes to 21 for 1 hour.
    The potion has no effect on you if your Strength is equal to or greater than that score.
\paragraph{Calming Wine} % Calm Emotions
    This wine's fruity flavor seems to calm emotions on command.
    Any creature who drinks this rolls a DC 12 Charisma saving throw.
    A creature can choose to fail this saving throw if it wishes.
    If a creature fails, two effects occur with a duration of an hour:
    \begin{itemize}
        \item Any effect causing a target to be charmed or frightened is suppressed.
        When this effect ends, any suppressed effect resumes, provided that its duration has not expired in the meantime.
        \item The target feels indifferent about creatures that it is hostile toward.
        This indifference ends if the target is attacked or harmed by a spell or if it witnesses any of its friends being harmed.
        When the effect ends, the creature becomes hostile again, unless the DM rules otherwise.
    \end{itemize}
\paragraph{Dead Man's Ale} % Blindness/Deafness
    This brew looks like common ale, hiding a terrible effect within.
    After drinking it, the creature rolls a DC 12 Constitution saving throw.
    If it fails, the target is blinded for an hour.
\paragraph{Madman Wine} % Crown of Madness
    This wine looks normal, but has a somewhat odd flavor.
    A creature who drinks this must succeed on a DC 12 Wisdom saving throw or become charmed for a minute.
    While charmed, madness glows in the creature's eyes.

    The charmed creature must use its action before moving on each of its turns to make a melee attack against a creature other than itself within 1.5 meters of it chosen randomly.
    If no creatures are within reach, it moves towards the closest creature to attack it.

    The target can make a DC 12 Wisdom saving throw at the end of each of its turns.
    On a success, the effect ends.
\paragraph{Speaker's Whiskey} % Zone of Truth on a target
    This strong whiskey seems to pick at your brain, forcing you to feel remorse about your misdeeds.
    Any creature who drinks this must make a DC 12 Charisma saving throw.
    On a failed save, a creature can't speak a deliberate lie for an hour.
    A skilled brewer knows whether each creature succeeds or fails on its saving throw.

    An affected creature is aware of the effect and can thus avoid answering questions to which it would normally respond with a lie.
    Such creatures can be evasive in its answers as long as it remains within the boundaries of the truth.
\paragraph{Thassa's Mockery} % Water Breathing
    This transparent vodka has fish scales floating in it, which must be drinked with the brew to gain its effect.
    This drinks grants a creature the ability to breathe underwater for 8 hours.
    Affected creatures also retain their normal mode of respiration.
% RARE - 3rd level spells, DC 14, +3
Breathkiller % Stinking Cloud
Brew of Clairvoyance
Brew of Invulnerability
Brew of Letargy % Slow
Brew of Maximum Power
Mindblower % Speak with Plants + Hallucinatory Terrain
Soulcatcher % Revivify
% VERY RARE - 4-5th level spells, DC 16, +4
Brew of Confusion % Confusion
Brew of Vitality % Potion of Vitality
Brew of Speed % Haste
Dead Raiser % Raise Dead
Ioun's Heavy Hitter % Random Ioun strong --- randomized when drinking.
Kickstarter % Awaken
Kyrzin's Ooze % Kyrzin's Ooze
% LEGENDARY - 6-7th level spells, DC 18, +5
Dancer's Whiskey % Otto's Irresistible Dance
Groundhshaker % Investiture of Stone
Seer's Vodka % True Seeing
Stoner % Flesh to Stone
