% !TEX root = ../main.tex
\section{Clothing} \label{sec::clothing}
    \begin{table*}[b]%
        \begin{DndTable}[width=\linewidth, header=Clothing and Accessories]{Xlccccc}
            \textbf{Item} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            \multicolumn{7}{l}{\hspace{0.5cm}\textit{Clothes}} \\
            Common Clothes           & Mundane   & 8 &      50 fobs    & WEA & 1.5 kg & PHB   150 \\
            Costume Clothes          & Plain     & 3 &       5 agnomas & WEA & 2 kg   & PHB   150 \\
            Robes                    & Plain     & 1 &       1 agnoma  & WEA & 2 kg   & PHB   150 \\
            Traveler's Clothes       & Plain     & 1 &       2 agnomas & WEA & 2 kg   & PHB   150 \\
            Warm Clothing            & Plain     & 8 &      10 agnomas & WEA & 2.5 kg & IDRotF 20 \\
            Boots of False Tracks    & Common    & 8 &     100 agnomas & COB & 1 kg   & XGE   136 \\
            Fine Clothes             & Common    & 1 &      30 agnomas & WEA & 3 kg   & PHB   150 \\
            Boggart Boots            & Uncommon  & 8 &     500 agnomas & COB & ---    & DMG   155 \\
            Boots of Springing       & Uncommon  & 8 &     500 agnomas & COB & ---    & DMG   156 \\
            Winter Boots             & Uncommon  & 8 &     500 agnomas & COB & ---    & DMG   156 \\
            Boots of Speed           & Rare      & 8 &   5,000 agnomas & COB & ---    & DMG   155 \\
            \multicolumn{7}{l}{\hspace{0.5cm}\textit{Accessories}} \\
            Athlete's Gloves         & Uncommon  & 8 &     500 agnomas & LEA & ---    & DMG   172 \\
            Bracers of Archery       & Uncommon  & 8 &     500 agnomas & LEA & ---    & DMG   156 \\
            Cloak of Protection      & Uncommon  & 8 &     500 agnomas & LEA & ---    & DMG   159 \\
            Cloak of Stealth         & Uncommon  & 8 &     500 agnomas & LEA & ---    & DMG   158 \\
            Cloak of Thassa          & Uncommon  & 8 &     500 agnomas & LEA & ---    & DMG   159 \\
            Gloves of Snaring        & Uncommon  & 8 &     500 agnomas & WEA & ---    & DMG   172 \\
            Eyes of Charming         & Uncommon  & 8 &     500 agnomas & GLA & ---    & DMG   168 \\
            Eyes of Minute Seeing    & Uncommon  & 8 &     500 agnomas & GLA & ---    & DMG   168 \\
            Eyes of the Eagle        & Uncommon  & 8 &     500 agnomas & GLA & ---    & DMG   168 \\
            Hat of Disguise          & Uncommon  & 8 &     500 agnomas & LEA & ---    & DMG   173 \\
            Helm of Communication    & Uncommon  & 8 &     500 agnomas & JEW & ---    & DMG   174 \\
            Mask of Adaptation       & Uncommon  & 8 &     500 agnomas & WEA & ---    & DMG   182 \\
            Thieves' Gloves          & Uncommon  & 8 &     500 agnomas & WEA & ---    & DMG   172 \\
            Belt of Giant's Strength & Rare      & 8 &   5,000 agnoams & LEA & ---    & DMG   155 \\
            Bracers of Defense       & Rare      & 8 &   5,000 agnomas & LEA & ---    & DMG   156 \\
            Cape of the Mountebank   & Rare      & 8 &   5,000 agnomas & WEA & ---    & DMG   157 \\
            Cloak of Displacement    & Rare      & 8 &   5,000 agnomas & LEA & ---    & DMG   158 \\
            Cloak of Marsetkind      & Rare      & 8 &   5,000 agnomas & LEA & ---    & DMG   159 \\
            Living Gloves            & Rare      & 6 &   4,000 agnomas & ALC & ---    & ERLW  278 \\
            Watchful Helm            & Rare      & 8 &   5,000 agnomas & JEW & ---    & CM    183 \\
            Cloak of Arasta          & Very Rare & 8 &  50,000 agnomas & LEA & ---    & DMG   158 \\
            % Helm of Fiend Command    & Very Rare & 8 &  50,000 agnomas & SMI & 1 kg   & BGDIA 223 \\
            Illusionist's Bracers    & Very Rare & 8 &  50,000 agnoams & JEW & ---    & GGR   178 \\
            Wings of Flying          & Very Rare & 8 &  50,000 agnomas & LEA & ---    & DMG   214 \\
            Cloak of Invisibility    & Legendary & 8 & 250,000 agnomas & LEA & ---    & DMG   158 \\
            \multicolumn{7}{l}{\hspace{0.5cm}\textit{Jewelry}} \\
            Amulet                   & Plain     & 3 &       5 agnomas & JEW & 0.5 kg & PHB   151 \\
            Signet Ring              & Plain     & 3 &       5 agnomas & JEW & ---    & PHB   150 \\
            Amulet of the Closed Eye & Uncommon  & 8 &     500 agnomas & JEW & 0.5 kg & DMG   150 \\
            Brooch of Shielding      & Uncommon  & 8 &     500 agnomas & GLA & ---    & DMG   156 \\
            Periapt of Health        & Uncommon  & 8 &     500 agnomas & JEW & 0.5 kg & DMG   184 \\
            Amulet of Health         & Rare      & 8 &   5,000 agnomas & JEW & 0.5 kg & DMG   150 \\
            Necklace of Fireballs    & Rare      & 8 &   5,000 agnomas & JEW & 0.5 kg & DMG   182 \\
            Ring of Animal Influence & Rare      & 8 &   5,000 agnomas & JEW & ---    & DMG   189 \\
            Ring of Evasion          & Rare      & 8 &   5,000 agnomas & JEW & ---    & DMG   191 \\
            Ring of Resistance       & Rare      & 8 &   5,000 agnomas & JEW & ---    & DMG   192 \\
            Ring of Salvation        & Rare      & 8 &   5,000 agnomas & JEW & ---    & EGW   269 \\
            Ring of Spell Storing    & Rare      & 8 &   5,000 agnomas & JEW & ---    & DMG   192 \\
            Ring of the Ram          & Rare      & 8 &   5,000 agnomas & JEW & ---    & DMG   193 \\
            Ring of Spell Turning    & Legendary & 8 & 250,000 agnomas & JEW & ---    & DMG   193 \\
            Talisman of the Sphere   & Legendary & 8 & 250,000 agnoams & JEW & 0.5 kg & DMG   207 \\
            \multicolumn{7}{l}{\hspace{0.5cm}\textit{Qualars}} \\
            Qualar of Mind Shielding & Uncommon  & 8 &     500 agnomas & WOO & ---    & DMG   191 \\
            Qualar of Thoughts       & Uncommon  & 8 &     500 agnomas & WOO & ---    & DMG   181 \\
            Qualar of Truth Telling  & Uncommon  & 8 &     500 agnomas & WOO & ---    & WDH   192 \\
            Qualar of Intellect      & Rare      & 8 &   5,000 agnomas & WOO & ---    & DMG   173
        \end{DndTable}
    \end{table*}

Hat of Disguise	Uncommon	Wondrous Item	LEAD

    \paragraph{Amulet of Health $\odot$}
        While wearing this amulet, your Constitution ability score increases by 4, up to a limit of 24.
    \paragraph{Amulet of the Closed Eye $\odot$}
        While you are wearing this amulet, you can't be targeted by scrying magic or be perceived by any incorporeal sensors.
    \paragraph{Athlete's Gloves $\odot$}
        While wearing these gloves, climbing and swimming don't cost you extra movement, and you gain a +5 bonus to Strength (Athletics) checks made to climb or swim.
    \paragraph{Belt of Giant's Strength $\odot$}
        While wearing this belt, your Strength ability score increases by 4, up to a limit of 24.
    \paragraph{Boggart Boots}
        While you wear these boots, your steps make no sound, regardless of the surface you are moving across. You also have advantage on Dexterity (Stealth) checks that rely on moving silently.
    \paragraph{Boots of False Tracks}
        By using two actions to adjust the soles, you can adjust the size and shape of your tracks to make them look like those of a wild animal.
    \paragraph{Boots of Speed $\odot$}
        While you wear these boots, you can use an action and click the boots' heels together.
        If you do, the boots double your walking speed, and any creature that makes an opportunity attack against you has disadvantage on the attack roll.
        If you click your heels together again, you end the effect.

        When the boots' property has been used for a total of 10 minutes, the boots ceases to function until you finish a short rest.
    \paragraph{Boots of Springing $\odot$}
        While you wear these boots, your walking speed becomes 6 meters, unless your walking speed is higher, and your speed isn't reduced if you are encumbered or wearing heavy armor.
        In addition, you can jump three times the normal distance, though you can't jump farther than your remaining movement would allow.
    \paragraph{Bracers of Archery $\odot$}
        While wearing these bracers, you gain a +2 bonus to damage rolls on ranged attacks made with weapons of the bow and crossbow types.
    \paragraph{Bracers of Defense $\odot$}
        While wearing these bracers, you gain a +2 bonus to AC if you are wearing no armor and using no shield.
    \paragraph{Brooch of Shielding $\odot$}
        While wearing this brooch, you have resistance against force damage.
    \paragraph{Cape of the Mountebank}
        This cape smells faintly of brimstone.
        While wearing it, you can use it to teleport up to 100 meters using two actions.

        You can bring along objects as long as their weight doesn't exceed what you can carry.
        You can also bring one willing creature of your size or smaller who is carrying gear up to its carrying capacity.
        The creature must be within a meter of you when you cast this spell.

        If you would arrive in a place already occupied by an object or a creature, you and any creature traveling with you each take 4d6 force damage, and the spell fails to teleport you.

        This property of the cape can't be used again until the next dawn.

        When you disappear, you leave behind a cloud of smoke, and you appear in a similar cloud of smoke at your destination.
        The smoke lightly obscures the space you left and the space you appear in, and it dissipates at the end of your next turn. A light or stronger wind disperses the smoke.
    \paragraph{Cloak of Arasta $\odot$}
        This fine garment is made of black silk interwoven with faint silvery threads.
        While wearing it, you gain the following benefits:
        \begin{itemize}
            \item You have resistance to poison damage.
            \item You have a climbing speed equal to your walking speed.
            \item You can move up, down, and across vertical surfaces and upside down along ceilings, while leaving your hands free.
            \item You can't be caught in webs of any sort and can move through webs as if they were difficult terrain.
            \item You can use an action to cast the web spell (save DC 13).
            The web created by the spell fills twice its normal area.
            Once used, this property of the cloak can't be used again until the next dawn.
        \end{itemize}
    \paragraph{Cloak of Displacement $\odot$}
        While you wear this cloak, it projects an illusion that makes you appear to be standing in a place near your actual location, causing any creature to have disadvantage on attack rolls against you.
        If you take damage, the property ceases to function until the start of your next turn.
        This property is suppressed while you are incapacitated, restrained, or otherwise unable to move.
    \paragraph{Cloak of Invisibility $\odot$}
        While wearing this cloak, you can pull its hood over your head to cause yourself to become invisible.
        While you are invisible, anything you are carrying or wearing is invisible with you.
        You become visible when you cease wearing the hood.
        Pulling the hood up or down requires an action.

        Deduct the time you are invisible, in increments of 1 minute, from the cloak's maximum duration of 2 hours.
        After 2 hours of use, the cloak ceases to function.
        For every uninterrupted period of 12 hours the cloak goes unused, it regains 1 hour of duration.
    \paragraph{Cloak of Marsetkind $\odot$}
        While wearing this cloak, you have advantage on Dexterity (Stealth) checks.
        In an area of dim light or darkness, you can grip the edges of the cloak with both hands and use it to fly at a speed of 8 meters.
        If you ever fail to grip the cloak's edges while flying in this way you lose this flying speed.
    \paragraph{Cloak of Protection $\odot$}
        You gain a +1 bonus to AC and saving throws while you wear this cloak.
    \paragraph{Cloak of Stealth $\odot$}
        While you wear this cloak with its hood up, Wisdom (Perception) checks made to see you have disadvantage, and you have advantage on Dexterity (Stealth) checks made to hide, as the cloak's color shifts to camouflage you.
        Pulling the hood up or down requires an action.
    \paragraph{Cloak of Thassa $\odot$}
        While wearing this cloak with its hood up, you can breathe underwater, and you have a swimming speed of 12 meters.
        Pulling the hood up or down requires an action.
    \paragraph{Eyes of Charming $\odot$}
        These crystal lenses fit over the eyes.
        They have 3 charges.
        While wearing them, you can expend 1 charge as an action to cast the charm person spell (see page \pageref{spell::charmperson}) with a save DC of 13 on a humanoid within 6 meters of you, provided that you and the target can see each other.
        The lenses regain all expended charges daily at dawn.
    \paragraph{Eyes of Minute Seeing}
        These crystal lenses fit over the eyes.
        While wearing them, you can see much better than normal out to a range of 30 cm.
        You have advantage on Intelligence (Investigation) checks that rely on sight while searching an area or studying an object within that range.
    \paragraph{Eyes of the Eagle $\odot$}
        These crystal lenses fit over the eyes.
        While wearing them, you have advantage on Wisdom (Perception) checks that rely on sight.
        In conditions of clear visibility, you can make out details of even extremely distant creatures and objects as small as 60 cm. across.
    \paragraph{Gloves of Snaring $\odot$}
        These gloves seem to almost meld into your hands when you don them.
        When a ranged weapon attack hits you while you're wearing them, you can use your reaction to reduce the damage by 1d10 + your Dexterity modifier, provided that you have a free hand.
        If you reduce the damage to 0, you can catch the missile if it is small enough for you to hold in that hand.
    \paragraph{Hat of Disguise $\odot$}
        While wearing this hat, you can use two actions to cast the disguise self spell from it at will.
        The spell ends if the hat is removed.
    \paragraph{Helm of Communication $\odot$}
        Wearing this copper helm brings the constant sensation of a light breeze on the wearer's head.
        While wearing this helm, you can use two actions to cast the detect thoughts spell (save DC 13) from it.
        As long as you maintain concentration on the spell, you can use an action to send a message to a creature you are focused on.
        It can reply --- using an action to do so --- while your focus on it continues.

        While focusing on a creature with detect thoughts, you can use an action to cast the suggestion spell (save DC 13) from the helm on that creature.
        Once used, the suggestion property can't be used again until the next dawn.
    % \paragraph{Helm of Fiend Command $\odot$}
    %     While wearing this bulky, eyelass helmet, you can see out of it as though you weren't wearing it.
    %     In addition, you know the exact location and type of all fiends within a kilometer of you.
    %     You can telepathically communicate with a fiend within range, or you can broadcast your thoughts to all fiends within range.
    %     The fiends receiving your broadcasted thoughts have no special means of replying to them.
    %
    %     The helm has 3 charges.
    %     Using two actions, you can expend 1 charge to cast dominate monster with save DC 21, which affects fiends only.
    %     If a fiend can see you when you cast this spell on it, the fiend knows you tried to charm it.
    %     The helm regains all its charges 24 hours after its last charge is expended.
    \paragraph{Illusionist's Bracers $\odot$}
        While wearing these intricate bracers, whenever you cast a cantrip, you can use an action on the same turn to cast that cantrip a second time.
        You can do this only once per turn.
    \paragraph{Living Gloves $\odot$}
        These symbiotic gloves --- made of thin chitin and sinew --- pulse with a life of their own.
        To attune to them, you must wear them for the entire attunement period, during which the gloves bond with your skin.

        While attuned to these gloves, you double your proficiency bonus with one of the following proficiencies (your choice when you attune to the gloves):
        \begin{itemize}
            \item Sleight of Hand,
            \item thieves' tools,
            \item one kind of artisan's tools of your choice, or
            \item one kind of musical instrument of your choice.
        \end{itemize}

        \paragraph{Symbiotic Nature}
        The gloves can't be removed from you while you're attuned to them, and you can't voluntarily end your attunement to them.
        The only way to end your attunement to the gloves is by pouring Oozekiller (see page \pageref{item::oozekiller}) on them, which destroys the gloves.
    \paragraph{Mask of Adaptation $\odot$}
        While wearing this necklace, you can breathe normally in any environment, and you have advantage on saving throws made against harmful gases and vapors (such as cloudkill and stinking cloud effects, and inhaled poisons).
    \paragraph{Periapt of Health}
        You have advantage on saving throws made to avoid contracting a disease while you wear this pendant.
        If you are infected with a disease, the effects of the disease are slower, and the time it takes for its effect to take place are doubled.
    \paragraph{Qualar of Mind Shielding $\odot$}
        While carrying this qualar, you are immune to magic that allows other creatures to read your thoughts, determine whether you are lying, know your tidal alignment, or know your creature type.
        Creatures can telepathically communicate with you only if you allow it.
    \paragraph{Qualar of Intellect $\odot$}
        While wearing this qualar, your Intelligence ability score increases by 4, up to a limit of 24.
    \paragraph{Qualar of Thoughts $\odot$}
        The qualar has 3 charges.
        While wearing it, you can use two actions and expend 1 charge to cast the detect thoughts spell with save DC 13 from it.
        The qualar regains 1d3 expended charges daily at dawn.
    \paragraph{Qualar of Truth Telling $\odot$}
        While wearing this ring, you have advantage on Wisdom (Insight) checks to determine whether someone is lying to you.
    \paragraph{Necklace of Fireballs}
        This necklace has 1d6 + 3 beads hanging from it. You can use an action to detach a bead and throw it up to 12 meters away.
        When it reaches the end of its trajectory, the bead detonates as a 3rd-level fireball spell with save DC 15.

        You can hurl multiple beads, or even the whole necklace, as one action.
        When you do so, increase the level of the fireball by 1 for each bead beyond the first.
    \paragraph{Ring of Animal Influence}
        This bone ring has 3 charges, and it regains 1d3 expended charges daily at dawn.
        While wearing the ring, you can use an action to expend 1 of its charges to cast one of the following spells with save DC 13:
        \begin{itemize}
            \item Animal friendship,
            \item Fear, targeting only beasts that have an Intelligence of 3 or lower.
        \end{itemize}
    \paragraph{Ring of Evasion $\odot$}
        This ring has 3 charges, and it regains 1d3 expended charges daily at dawn.
        When you fail a Dexterity saving throw while wearing it, you can use your reaction to expend 1 of its charges to succeed on that saving throw instead.
    \paragraph{Ring of Resistance $\odot$}
        You have resistance to one damage type while wearing this ring.
        The gem in the ring indicates the type.
        \begin{DndTable}[width=\linewidth, header=Resistance Gems]{cll}
            \textbf{d10} & \textbf{Damage Type} & \textbf{Gem} \\
            1            & Acid                 & Pearl        \\
            2            & Cold                 & Tourmaline   \\
            3            & Fire                 & Garnet       \\
            4            & Force                & Sapphire     \\
            5            & Lightning            & Citrine      \\
            6            & Necrotic             & Jet          \\
            7            & Poison               & Amethyst     \\
            8            & Psychic              & Jade         \\
            9            & Radiant              & Topaz        \\
            10           & Thunder              & Spinel
        \end{DndTable}
    \paragraph{Ring of Salvation $\odot$}
        If you die while wearing this gray crystal ring, it breathes life back to you, waking you up.
        You have a number of hit points equal to 3d6 + your Constitution modifier.
        If your hit point maximum is lower than the number of hit points you regain, your hit point maximum rises to a similar amount.
        If you have any levels of exhaustion, reduce your level of exhaustion by 1.
        Once the ring is used, it turns to dust and is destroyed.
    \paragraph{Ring of Spell Storing $\odot$}
        This ring stores spells cast into it, holding them until the attuned wearer uses them.
        The ring can store up to 5 levels worth of spells at a time.

        Any creature can cast a spell of 1st through 5th level into the ring by touching the ring as the spell is cast.
        The spell has no effect, other than to be stored in the ring.
        If the ring can't hold the spell, the spell is expended without effect.
        The level of the slot used to cast the spell determines how much space it uses.

        While wearing this ring, you can cast any spell stored in it.
        The spell uses the slot level, spell save DC, spell attack bonus, and spellcasting ability of the original caster, but is otherwise treated as if you cast the spell.
        The spell cast from the ring is no longer stored in it, freeing up space.
    \paragraph{Ring of Spell Turning $\odot$}
        While wearing this ring, you have advantage on saving throws against any spell that targets only you (not in an area of effect).
        In addition, if you roll a 20 for the save and the spell is 7th level or lower, the spell has no effect on you and instead targets the caster, using the slot level, spell save DC, attack bonus, and spellcasting ability of the caster.
    \paragraph{Ring of the Ram $\odot$}
        This ring has 3 charges, and it regains 1d3 expended charges daily at dawn.
        While wearing the ring, you can use an action to expend 1 to 3 of its charges to attack one creature you can see within 12 meters of you.
        The ring produces a spectral ram's head and makes its attack roll with a +7 bonus.
        On a hit, for each charge you spend, the target takes 2d10 force damage and is pushed 1 meter away from you.

        Alternatively, you can expend 1 to 3 of the ring's charges as an action to try to break an object you can see within 12 meters of you that isn't being worn or carried.
        The ring makes a Strength check with a +5 bonus for each charge you spend.
    \paragraph{Talisman of the Sphere $\odot$}
        When you make an Intelligence (Arcana) check to control a sphere of annihilation while you are holding this talisman, you double your proficiency bonus on the check.
        In addition, when you start your turn with control over a sphere of annihilation, you can use an action to levitate it 2 meters plus a number of additional meters equal to 2 times your Intelligence modifier.
    \paragraph{Thieves' Glovers}
        These gloves are invisible while worn.
        While wearing them, you gain a +5 bonus to Dexterity (Sleight of Hand) checks and Dexterity checks made to pick locks.
    \paragraph{Warm Clothing}
        This outfit consists of a heavy fur coat or cloak over layers of wool clothing, as well as a fur-lined hat or hood, goggles, and fur-lined leather boots and gloves.

        As long as this clothing remains dry, its wearer automatically succeeds on saving throws against the effects of extreme cold.
    \paragraph{Watchful Helm $\odot$}
        While you wear this helm, you gain a +1 bonus to AC and remain aware of your surroundings even while you're asleep, and you have advantage on Wisdom (Perception) checks that rely on sight.
    \paragraph{Wings of Flying $\odot$}
        While wearing this cloak, you can use two actions to sprout bird wings on your back.
        This effect lasts for one hour or until you use an action to end it.
        The wings give you a flying speed of 12 meters.
        When they disappear, you can't use them again for 1d12 hours.
    \paragraph{Winter Boots $\odot$}
        These furred boots are snug and feel quite warm.
        While you wear them, you gain the following benefits:
        \begin{itemize}
            \item You have resistance to cold damage.
            \item You ignore difficult terrain created by ice or snow.
            \item You can tolerate temperatures as low as -50 degrees Celsius without any additional protection.
            If you wear heavy clothes, you can tolerate temperatures as low as -70 degrees Celsius.
        \end{itemize}
\newpage~\newpage
