% !TEX root = ../main.tex
\subsection*{Glass Items} \label{ssec::glassitems}
\begin{table*}[b]%
    \begin{DndTable}[width=\linewidth, header=Brews]{Xlccccc}
        \textbf{Item} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
        Blowpipe                     & Common    & 1 &      20 agnomas & SMI       & 1 kg.   & --- \\
        Orb                          & Common    & 1 &      20 agnomas & GLA       & 1.5 kg. & PHB 151 \\
        Brooch of Shielding          & Uncommon  &  &     500 agnomas & GLA       & ---     & --- \\
        Decanter of Endless Water    & Uncommon  &  &     500 agnomas & GLA       & 2 kg.   & --- \\
        Eversmoking Bottle           & Uncommon  &  &     500 agnomas & GLA       & 0.5 kg. & --- \\
        Eyes of Charming             & Uncommon  &  &     500 agnomas & GLA       & ---     & --- \\
        Eyes of Minute Seeing        & Uncommon  &  &     500 agnomas & GLA       & ---     & --- \\
        Eyes of the Eagle            & Uncommon  &  &     500 agnomas & GLA       & ---     & --- \\
        Firetrap                     & Uncommon  &  &     500 agnomas & GLA       & 1 kg.   & --- \\
        Goggles of Night             & Uncommon  &  &     500 agnomas & GLA + TIN & ---     & --- \\
        Bowl of Commanding Water     & Rare      &  &   5,000 agnomas & GLA       & 1.5 kg. & --- \\
        Censer of Controlling Air    & Rare      &  &   5,000 agnomas & GLA       & 0.5 kg. & --- \\
        Crystal Ball                 & Rare      &  &   5,000 agnomas & GLA       & 1.5 kg. & --- \\
        Rod of Leadership            & Rare      &  &   5,000 agnomas & GLA       & 1 kg.   & --- \\
        Crystalline Chronicle        & Very Rare &  &  50,000 agnomas & GLA       & 1.5 kg. & --- \\
        Frithling Glass Home         & Very Rare &  &  50,000 agnomas & GLA       & 0.5 kg. & --- \\
        Crystal of Absorption        & Very Rare &  &  50,000 agnomas & GLA       & 1 kg.   & --- \\
        Rod of Alertness             & Very Rare &  &  50,000 agnomas & GLA       & 1 kg.   & --- \\
        Shard of Nuagal              & Very Rare &  &  50,000 agnomas & GLA       & 1 kg.   & --- \\
        Crystal Ball of Mind Reading & Legendary &  & 150,000 agnomas & GLA       & 1.5 kg. & --- \\
        Crystal Ball of Telepathy    & Legendary &  & 150,000 agnomas & GLA       & 1.5 kg. & --- \\
        Crystal Ball of True Seeing  & Legendary &  & 150,000 agnomas & GLA       & 1.5 kg. & --- \\
        Rod of Might                 & Legendary &  & 250,000 agnomas & GLA       & 1.5 kg. & ---
    \end{DndTable}
\end{table*}

\paragraph{Blowpipe}
    Metal blowpipes are of higher quality than the common blowpipe contained in a set of glassblower's tools, and can be used as a quarterstaff.
    In addition, a flamespeaker can use a good quality blowpipe as an arcane focus.
\paragraph{Orb}
    A crystal orb of high value.
\paragraph{Bowl of Commanding Water}
    While this bowl is filled with water, you can use two action to speak the bowl's command word and summon a water elemental, as if you had cast the conjure elemental spell (see page \pageref{spell::conjureelemental}), requiring concentration.
    The bowl can't be used this way again until the next dawn.

    The bowl is about 30 centimeters in diameter and half as deep.
    It weighs 1.5 kg. and holds about 12 liters.
\paragraph{Brooch of Shielding $\odot$}
    While wearing this brooch, you have resistance against force damage.
\paragraph{Censer of Controlling Air}
    While incense is burning in this censer, you can use two actions to speak the censer's command word and summon an air elemental, as if you had cast the conjure elemental spell (see page \pageref{spell::conjureelemental}), requiring concentration.
    The censer can't be used this way again until the next dawn.

    This 15-centimeter-wide, 30-centimeter-high vessel resembles a chalice with a decorated lid.
    It weighs 0.5 kg.
\paragraph{Crystal Ball $\odot$}
    Made by wandering zaloths, this item is infused with their strange magic.

    This crystal ball is about 15 centimeters in diameter.
    While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.
\paragraph{Crystalline Chronicle $\odot$}
    Made by wandering zaloths, this item is infused with their strange magic.

    An etched crystal sphere the size of a grapefruit hums faintly and pulses with irregular flares of inner light.
    The crystal contains the following spells: detect thoughts (see page \pageref{spell::detectthoughts}), intellect fortress (see page \pageref{spell::intellectfortress}), Rary's telepathic bond (see page \pageref{spell::rarystelepathicbond}), sending (see page \pageref{spell::sending}), telekinesis (see page \pageref{spell::telekinesis}), Tasha's mind whip (see page \pageref{spell::tashasmindwhip}), and Tenser's floating disk (see page \pageref{spell::tensersfloatingdisc}).
    While attuned to this item you know all these spells, and your knowledge of them fades when you end your attunement with it.

    While you are holding the crystal, you can use it as a spellcasting focus for these spells, and you know the mage hand (see page \pageref{spell::magehand}), mind sliver (see page \pageref{spell::mindsliver}), and message (see page \pageref{spell::message}) cantrips if you don't already know them.

    The crystal has 3 charges, and it regains 1d3 expended charges daily at dawn.
    You can use the charges to cast a spell given by this item without verbal, somatic, or material components of up to 100 gp value.
\paragraph{Crystal Ball of Mind Reading $\odot$}
    Made by wandering zaloths, this item is infused with their strange magic.

    This crystal ball is about 15 centimeters in diameter.
    While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.

    You can use an action to cast the detect thoughts spell (see page \pageref{spell::detectthoughts}) with a save DC of 17 while you are scrying with the crystal ball, targeting creatures you can see within 30 feet of the spell's sensor.
    You don't need to concentrate on this detect thoughts to maintain it during its duration, but it ends if scrying ends.
\paragraph{Crystal Ball of Telepathy $\odot$}
    Made by wandering zaloths, this item is infused with their strange magic.

    This crystal ball is about 15 centimeters in diameter.
    While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.

    While scrying with the crystal ball, you can communicate telepathically with creatures you can see within 6 meters of the spell's sensor.
    You can also use an action to cast the suggestion spell (see page \pageref{spell::suggestion}) with save DC 17 through the sensor on one of those creatures.
    You don't need to concentrate on this suggestion to maintain it during its duration, but it ends if scrying ends.
    Once used, the suggestion power of the crystal ball can't be used again until the next dawn.
\paragraph{Crystal Ball of True Seeing $\odot$}
    Made by wandering zaloths, this item is infused with their strange magic.

    This crystal ball is about 15 centimeters in diameter.
    While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.

    While scrying with the crystal ball, you have truesight with a radius of 24 meters centered on the spell's sensor.
\paragraph{Crystal of Absorption $\odot$}
    Designed by zaloths, this item is infused with their strange magic.

    While holding this crystal, you can use your reaction to absorb a spell that is targeting only you and not with an area of effect.
    The absorbed spell's effect is canceled, and the spell's energy --- not the spell itself --- is stored in the crystal.
    The energy has the same level as the spell when it was cast.
    The crystal can absorb and store up to 50 levels of energy over the course of its existence.
    Once the crystal absorbs 50 levels of energy, it can't absorb more.
    If you are targeted by a spell that the crystal can't store, the crystal has no effect on that spell.

    When you become attuned to the crystal, you know how many levels of energy the crystal has absorbed over the course of its existence, and how many levels of spell energy it currently has stored.

    If you are a spellcaster holding the crystal, you can convert energy stored in it into spell points to cast spells you know.
    You create a number of spell points equal to the level of energy the crystal has stored instead of your normal spell points, but otherwise cast the spell as normal.
    For example, you can use 5 levels stores in the crystal to cast a 3rd level spell.

    A newly found crystal has 1d10 levels of spell energy stored in it already.
    A crystal that can no longer absorb spell energy and has no energy remaining becomes nonmagical.
\paragraph{Decanter of Endless Water}
    This decanter can contain up to 8 liters of water, which is compressed to extreme lengths when inside.
    Upon being opened, a 6-meter long geyser gushes forth from the decanter.
    As an action while holding the decanter, you can aim the geyser at a creature you can see within 6 meters of you.
    The target must succed on a DC 12 Strength saving throw or take 1d4 bludgeoning damage and fall prone.
    Instead of a creature, you can target an object that isn't being worn or carried and that weighs no more than 100 kg.
    The object is either knocked over or pushed up to 3 meters away from you.

    To use this ability the decanter must be filled with water, a process that takes half a minute.
\paragraph{Eversmoking Bottle}
    Smoke leaks from the lead-stoppered mouth of this glass bottle, which weighs 0.5 kg.
    When you use two actions to remove the stopper, a cloud of thick smoke pours out in a 12-meter radius from the bottle.
    The cloud's area is heavily obscured.
    Each minute the bottle remains open and within the cloud, the radius increases by 2 meters until it reaches its maximum radius of 24 meters.

    The cloud persists as long as the bottle is open.
    Closing the bottle requires an action.
    Once the bottle is closed, the cloud disperses after 10 minutes.
    A moderate wind can also disperse the smoke after 1 minute, and a strong wind can do so after 1 round.
\paragraph{Eyes of Charming $\odot$}
    These crystal lenses fit over the eyes.
    They have 3 charges.
    While wearing them, you can expend 1 charge as an action to cast the charm person spell (see page \pageref{spell::charmperson}) with a save DC of 13 on a humanoid within 6 meters of you, provided that you and the target can see each other.
    The lenses regain all expended charges daily at dawn.
\paragraph{Eyes of Minute Seeing}
    These crystal lenses fit over the eyes.
    While wearing them, you can see much better than normal out to a range of 30 cm.
    You have advantage on Intelligence (Investigation) checks that rely on sight while searching an area or studying an object within that range.
\paragraph{Eyes of the Eagle $\odot$}
    These crystal lenses fit over the eyes.
    While wearing them, you have advantage on Wisdom (Perception) checks that rely on sight.
    In conditions of clear visibility, you can make out details of even extremely distant creatures and objects as small as 60 cm. across.
\paragraph{Firetrap}
    A firetrap is an spherical glass container about the size of a bottle.
    A flamespeaker can use a firetrap as a spellcasting focus, and is a required component to cast the whispering ember spell (see page \pageref{spell::whisperingember}).
\paragraph{Frithling Glass Home} % TODO. Base frithlings in Chwingas.
    This colored glass bottle weights 0.5 kg.
    The bottle can serve as a comfortable home for up to 8 frithlings (see page \pageref{creature::frithling}) as long as the frithlings get along with each other.
    The frithlings are thankful towards you for giving them a home and taking them in your adventures, and can perform tasks asked by you within their ability, and will ocassionally give you favors or gifts for your friendship.
    The frithlings need to eat and drink, each consuming 1/8th of the rations and doses of water that a normal-sized humanoid needs.

    If you fail to provide the frithlings basic needs or constantly put them in danger they will abandon you, usually without warning.
\paragraph{Goggles of Night}
    While wearing these dark lenses, you have darkvision out to a range of 12 meters.
    If you already have darkvision, wearing the goggles increases its range by 12 meters.
\paragraph{Rod of Alertness $\odot$}
    This glass rod has a flanged head and the following properties.
    \begin{itemize}
        \item \textbf{Alertness}
        While holding the rod, you have advantage on Wisdom (Perception) checks and on rolls for initiative.
        \item \textbf{Protective Aura} Using two actions, you can plant the haft end of the rod in the ground, whereupon the rod's head sheds bright light in a 12-meter radius and dim light for an additional 12 meters.
        While in that bright light, you and any creature that is friendly to you gain a +1 bonus to AC and saving throws and can sense the location of any invisible hostile creature that is also in the bright light.
        The rod's head stops glowing and the effect ends after 10 minutes, or when a creature uses an action to pull the rod from the ground.
        This property can't be used again until the next dawn.
    \end{itemize}
\paragraph{Rod of Leadership $\odot$}
    Said to be designed by king Olag the Immortal for the military, this rod can command respect from anyone around you.
    You can use two actions to present the rod and command obedience from each creature of your choice that you can see within 24 meters of you.
    Each target must succeed on a DC 15 Wisdom saving throw or be charmed by you for 8 hours.
    While charmed in this way, the creature regards you as its trusted leader.
    If harmed by you or your companions, or commanded to do something contrary to its nature, a target ceases to be charmed in this way.
    The rod can't be used again until the next dawn.
\paragraph{Rod of Might $\odot$} % TODO. Changes pending.
    % TODO. Add some lore.
    This glass rod has a straight and unassuming shape, and it functions as a mace that grants a +3 bonus to attack and damage rolls made with it.
    An item of intricate design, you can transform this mace into three different forms using an action.
    As another action you can transform the rod back to its original form or to another of its special forms.
    \begin{itemize}
        \item \textbf{Spear}.
        The rod's head folds down, a spear point springs from the rod's tip, and the rod's handle lengthens into a 1.8-meter haft, transforming the rod into a spear that grants a +3 bonus to attack and damage rolls made with it.
        \item \textbf{Ladder}.
        The rod transforms into a climbing pole up to 10 meters long, as you specify.
        In surfaces as hard as granite, a spike at the bottom and three hooks at the top anchor the pole.
        Horizontal bars 8 centimeters long fold out from the sides, 30 centimeters apart, forming a ladder.
        The pole can bear up to 2,000 kg.
        More weight or lack of solid anchoring causes the rod to revert to its normal form.
        \item \textbf{Ram}.
        The rod transforms into a handheld battering ram and grants its user a +10 bonus to Strength checks made to break through doors, barricades, and other barriers.
        \item \textbf{Compass}.
        The rod assumes or remains in its normal form and indicates magnetic north (Nothing happens if this function of the rod is used in a location that has no magnetic north).
    \end{itemize}

    In addition, you can add one of the following effect to this rod's attacks by expending an action:
    \begin{itemize}
        \item \textbf{Drain Life}.
        When you hit a creature with a melee attack using the rod, you can force the target to make a DC 17 Constitution saving throw.
        On a failure, the target rakes an extra 4d6 necrotic damage, and you regain a number of hit points equal to half that necrotic damage.
        This property can't be used again until the next dawn.
        \item \textbf{Paralyze}.
        When you hit a creature with a melee attack using the rod, you can force the target to make a DC 17 Strength saving throw.
        On a failure, the target is paralyzed for 1 minute.
        The target can repeat the saving throw at the end of each of its turns, ending the effect on a success.
        This property can't be used again until the next dawn.
        \item \textbf{Terrify}. % TODO. Change this effect.
        While holding the rod, you can use an action to force each creature you can see within 6 meters of you to make a DC 17 Wisdom saving throw.
        On a failure, a target is frightened of you for 1 minute.
        A frightened target can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success.
        This property can't be used again until the next dawn.
    \end{itemize}
\paragraph{Shard of Nuagal}
    The origins of these shards are unknown, and only a master glassblower can evoke the following effects from it.

    While holding this shard, you can use an action to activate it.
    The shard then instantly transports you and up to 199 other willing creatures you can see to an island in Nuagal, the blue moon.
    The island is a tranquil garden, and contains enough water and food to sustain its visitors.

    For each hour spent in the island, a visitor regains hit points as if it had spent 1 hit die.
    Visitors remain in the island for up to 6 days.

    When the time runs out or you use an action to end it, all visitors reappear in the location they occupied when you activated the shard, or an unoccupied space nearest that location.
    The shard loses its power when it is used in this way.
\paragraph{Vial}
    A vial can hold about 0.1 liters.
