% !TEX root = ../main.tex
\subsection*{Mounts and Vehicles} \label{ssec::mountsandvehicles}
\subsubsection{Mounts}
    Mounting or dismounting a creature requires two actions.

    \begin{table*}[t]%
        \begin{DndTable}[width=\linewidth, header=Adventuring Gear]{Xlcccc}
            \textbf{Mount} & \textbf{Rarity} & \textbf{Speed} & \textbf{Carrying Capacity} & \textbf{Total Cost} & \textbf{Source} \\
            Beakdog       & Common   & 10 mt & 100 kg &  50 agnomas & --- \\
            Donkey        & Common   &  8 mt & 210 kg &   8 agnomas & PHB 157 \\
            Draft Horse   & Common   &  8 mt & 270 kg &  25 agnomas & PHB 157 \\
            Mastiff       & Common   &  8 mt & 100 kg &  25 agnomas & PHB 157 \\
            Mule          & Common   &  8 mt & 210 kg &   8 agnomas & PHB 157 \\
            Pony          & Common   &  8 mt & 110 kg &  30 agnomas & PHB 157 \\
            Riding Horse  & Common   & 12 mt & 240 kg &  75 agnomas & PHB 157
            Elephant      & Uncommon &  8 mt & 660 kg & 200 agnomas & PHB 157 \\
            Elk Bird      & Uncommon & 12 mt & 150 kg & 250 agnomas & --- \\
        \end{DndTable}
    \end{table*}

    % TODO. Add ``bestiary'' entries for all of these.

\subsubsection{Vehicles \& Harnesses}
    \begin{table*}[t]%
        \begin{DndTable}[width=\linewidth, header=Vehicles, Tack, and Harness]{Xlccccc}
            \textbf{Vehicle} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            Barding            & $\ast$   & $\ast$ & $\ast$      & $\ast$ & $\ast$   & PHB 157 \\
            Stabling (per day) & ---      & ---    &     50 fobs    & --- & ---      & PHB 157 \\
            Cart               & Plain    & 13     &     15 agnomas & CAR & 100 kg   & PHB 157 \\
            Pack Saddle        & Plain    &  3     &      5 agnomas & LEA &   7.5 kg & PHB 157 \\
            Riding Saddle      & Plain    &  8     &     10 agnomas & LEA &  12.5 kg & PHB 157 \\
            Saddlebags         & Plain    &  2     &      4 agnomas & LEA &   4 kg   & PHB 157 \\
            Military Saddle    & Common   &  1     &     30 agnomas & LEA &  15 kg   & PHB 157 \\
            Exotic Saddle      & Common   &  4     &     60 agnomas & LEA &  20 kg   & PHB 157 \\
            Carriage           & Common   &  8     &    100 agnomas & CAR & 300 kg   & PHB 157 \\
            Chariot            & Common   & 13     &    150 agnomas & CAR &  50 kg   & PHB 157 \\
            Rowboat            & Common   &  3     &     50 agnomas & CAR &  50 kg   & DMG 119 \\
            Wagon              & Common   &  2     &     35 agnomas & CAR & 200 kg   & PHB 157 \\
            Keelboat           & Uncommon & 58     &  3,000 agnomas & CAR & ---      & DMG 119 \\
            Galley             & Rare     & 58     & 30,000 agnomas & CAR & ---      & DMG 119 \\
            Longship           & Rare     & 18     & 10,000 agnomas & CAR & ---      & DMG 119 \\
            Sailing Ship       & Rare     & 18     & 10,000 agnomas & CAR & ---      & DMG 119 \\
            Warship            & Rare     & 48     & 25,000 agnomas & CAR & ---      & DMG 119
        \end{DndTable}
    \end{table*}

    \paragraph{Barding}
        Barding is armor designed to protect an animal's head, neck, chest, and body.
        Any type of armor shown on the armor tables in this chapter can be purchased as barding.
        The cost is four times the equivalent armor made for umanoids, and it weighs twice as much.
    \paragraph{Exotic Saddle}
        An exotic saddle is required for riding any aquatic or flying mount.
    \paragraph{Galley}
        A galley has a speed of 6 km/h, and a carrying capacity of 150 tons.
        It requires a crew of 80 to run effectively, and it has an AC of 15, HP of 500, and a damage threshold of 20.
    \paragraph{Keelboat}
        A keelboat has a speed of 1.5 km/h, and a carrying capacity of half a ton plus 6 passengers at most.
        It requires a crew of 1, and it has an AC of 15, HP of 100, and a damage threshold of 10.

        Keelboats and rowboats are used on lakes and rivers.
        If going downstream, add the speed of the current (typically 5 kilometers per hour) to the speed of the vehicle.
        These vehicles can't be rowed against any significant current, but they can be pulled upstream by draft animals on the shores.
    \paragraph{Longship}
        A longship has a speed of 5 km/h, and a carrying capacity of 10 tons plus a cargo of 150 passengers.
        It requires a crew of 40, and it has an AC of 15, HP of 300, and a damage threshold of 15.
    \paragraph{Military Saddle}
        A military saddle braces the rider, helping you keep your seat on an active mount in battle.
        It gives you advantage on any check you make to remain mounted.
    \paragraph{Rowboat}
        A rowboat has a speed of 2.5 km/h, and a carrying capacity of 3 passengers at most.
        It requires a crew of 1, and it has an AC of 11, and HP of 50.

        Keelboats and rowboats are used on lakes and rivers.
        If going downstream, add the speed of the current (typically 5 kilometers per hour) to the speed of the vehicle.
        These vehicles can't be rowed against any significant current, but they can be pulled upstream by draft animals on the shores.
        A rowboat weighs 50 kilograms, in case adventurers carry it over land.
    \paragraph{Sailing Ship}
        A sailing ship has a speed of 3 km/h, and a carrying capacity of 100 tons plus a cargo of 20 passengers.
        It requires a crew of 20, and it has an AC of 15, HP of 300, and a damage threshold of 15.
    \paragraph{Warship}
        A warship has a speed of 4 km/h, and a carrying capacity of 200 tons plus a cargo of 60 passengers.
        It requires a crew of 60, and it has an AC of 15, HP of 500, and a damage threshold of 20.
