% !TEX root = ../main.tex
\subsection*{Supplies and Gear} \label{ssec::suppliesandgear}
\subsubsection{Adventuring Gear}
    \begin{table*}[t]%
        \begin{DndTable}[width=\linewidth, header=Adventuring Gear]{Xlccccc}
            \textbf{Item} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            Basket                & Mundane & 6   &  40 fobs    & WEA &  1 kg   & PHB 153 \\
            Blanket               & Mundane & 8   &  50 fobs    & WEA &  1.5 kg & PHB 150 \\
            Bucket                & Mundane & 1   &   5 fobs    & CAR &  1 kg   & PHB 153 \\
            Candle                & Mundane & --- &   1 fob     & --- & ---     & PHB 151 \\
            Chalk                 & Mundane & --- &   1 fob     & --- & ---     & PHB 150 \\
            Ink Pen               & Mundane & 1   &   2 fobs    & TIN & ---     & PHB 150 \\
            Iron Spike            & Mundane & 1   &  10 fobs    & SMI &  0.2 kg & PHB 150 \\
            Ladder                & Mundane & 1   &  10 fobs    & CAR & 12.5 kg & PHB 150 \\
            Lamp                  & Mundane & 8   &  50 fobs    & TIN &  0.5 kg & PHB 152 \\
            Abacus                & Plain   & 1   &   2 agnomas & CAR &  1 kg   & PHB 150 \\
            Backpack              & Plain   & 1   &   2 agnomas & LEA &  2.5 kg & PHB 153 \\
            Ball Bearings (1,000) & Plain   & 1   &   1 agnomas & SMI &  1 kg   & PHB 151 \\
            Bedroll               & Plain   & 1   &   1 agnoma  & WEA &  3.5 kg & PHB 150 \\
            Bell                  & Plain   & 1   &   1 agnoma  & SMI & ---     & PHB 150 \\
            Block and Tackle      & Plain   & 1   &   1 agnoma  & TIN &  2.5 kg & PHB 151 \\
            Bullseye Lantern      & Plain   & 8   &  10 agnomas & TIN &  1 kg   & PHB 152 \\
            Caltrops (20)         & Plain   & 1   &   1 agnoma  & SMI &  1 kg   & PHB 151 \\
            Chest                 & Plain   & 3   &   5 agnomas & CAR & 12.5 kg & PHB 153 \\
            Crowbar               & Plain   & 1   &   2 agnomas & SMI &  2.5 kg & PHB 151 \\
            Fishing Tackle        & Plain   & 1   &   1 agnoma  & TIN &  2 kg   & PHB 151 \\
            Grappling Hook        & Plain   & 1   &   2 agnomas & SMI &  2 kg   & PHB 150 \\
            Hammer                & Plain   & 1   &   1 agnoma  & SMI &  1.5 kg & PHB 150 \\
            Hempen Rope           & Plain   & --- &   1 agnoma  & --- &  5 kg   & PHB 153 \\
            Hooded Lantern        & Plain   & 3   &   5 agnomas & TIN &  1 kg   & PHB 152 \\
            Hunting Trap          & Plain   & 3   &   5 agnomas & TIN & 12.5 kg & PHB 152 \\
            Ink (0.025 lt.)       & Plain   & --- &  10 agnomas & --- & ---     & PHB 150 \\
            Iron Pot              & Plain   & 1   &   2 agnomas & SMI &  5 kg   & PHB 153 \\
            Lock                  & Plain   & 8   &  10 agnomas & TIN &  0.5 kg & PHB 152 \\
            Manacles              & Plain   & 1   &   2 agnomas & TIN &  3 kg   & PHB 152 \\
            Map or Scroll Case    & Plain   & 1   &   1 agnoma  & LEA &  0.5 kg & PHB 151 \\
            Merchant's Scale      & Plain   & 3   &   5 agnomas & TIN &  1.5 kg & PHB 153 \\
            Miner's Pick          & Plain   & 1   &   2 agnomas & SMI &  5 kg   & PHB 150 \\
            Book                  & Common  & 1   &  25 agnomas & CAL &  2.5 kg & PHB 151 \\
            Hourglass             & Common  & 1   &  25 agnomas & GLA &  0.5 kg & PHB 150 \\
            Magnifying Glass      & Common  & 8   & 100 agnomas & GLA & ---     & PHB 152 \\
        \end{DndTable}
    \end{table*}

    \paragraph{Basket}
        A basket holds 60 liters or 20 kg of gear.
    \paragraph{Block and Tackle}
        A set of pulleys with a cable threaded through them and a hook to attach to objects, a block and tackle allows you to hoist up to four times the weight you can normally lift.
    \paragraph{Book}
        A book might contain poetry, historical accounts, information pertaining to a particular field of lore, diagrams and notes on gat contraptions, or just about anything else that can be represented using text or pictures.
    \paragraph{Bucket}
        A bucket holds 12 liters.
    \paragraph{Bullseye Lantern}
        A bullseye lantern casts bright light in a 12-meter cone and dim light for an additional 12 meters.
        Once lit, it burns for 6 hours on a flask of oil.
    \paragraph{Caltrops}
        As two action, you can spread a single bag of caltrops to cover a 1-meter-square area.
        Any creature that enters the area must succeed on a DC 15 Dexterity saving throw or stop moving and take 1 piercing damage.
        Until the creature regains at least 1 hit point, its walking speed is reduced by 2 meters.
        A creature moving through the area at half speed doesn't need to make the saving throw.
    \paragraph{Candle}
        For 1 hour, a candle sheds bright light in a 1-meter radius and dim light for an additional meter.
    \paragraph{Chest}
        A chest holds 350 liters of gear.
    \paragraph{Crowbar}
        Using a crowbar grants advantage to Strength checks where the crowbar's leverage can be applied.
    \paragraph{Fishing Tackle}
        This kit includes a wooden rod, silken line, corkwood bobbers, steel hooks, lead sinkers, velvet lures, and narrow netting.
    \paragraph{Hempen Rope}
        Rope, whether made of hemp or silk, has 2 hit points and can be burst with a DC 17 Strength check.
    \paragraph{Hooded Lantern}
        A hooded lantern casts bright light in a 6-meter radius and dim light for an additional 6 meters.
        Once lit, it burns for 6 hours on a flask of oil.
        Using two actions, you can lower the hood, reducing the light to dim light in a 1-meter radius.
    \paragraph{Hunting Trap}
        When you use two actions to set it, this trap forms a saw-toothed steel ring that snaps shut when a creature steps on a pressure plate in the center.
        The trap is affixed by a heavy chain to an immobile object, such as a tree or a spike driven into the ground.
        A creature that steps on the plate must succeed on a DC 13 Dexterity saving throw or take 1d4 piercing damage and stop moving.
        Thereafter, until the creature breaks free of the trap, its movement is limited by the length of the chain (typically less than a meter long).
        A creature can use two actions to make a DC 13 Strength check, freeing itself or another creature within its reach on a success.
        Each failed check deals 1 piercing damage to the trapped creature.
    \paragraph{Iron Pot}
        An iron pot holds 4 liters of liquid.
    \paragraph{Lamp}
        A lamp casts bright light in a 3-meter radius and dim light for an additional 6 meters.
        Once lit, it burns for 6 hours on a flask of oil.
    \paragraph{Lock}
        A key is provided with the lock.
        Without the key, a creature proficient with thieves' tools can pick this lock with a successful DC 15 Dexterity check.
        Your DM may decide that better locks are available for higher prices.
    \paragraph{Magnifying Glass}
        This lens allows a closer look at small objects.
        It is also useful as a substitute for flint and steel when starting fires.
        Lighting a fire with a magnifying glass requires light as bright as sunlight to focus, tinder to ignite, and about 5 minutes for the fire to ignite.
        A magnifying glass grants advantage on any ability check made to appraise or inspect an item that is small or highly detailed.
    \paragraph{Manacles}
        These metal restraints can bind a Small or Medium creature.
        Escaping the manacles requires a successful DC 20 Dexterity check.
        Breaking them requires a successful DC 20 Strength check.
        Each set of manacles comes with one key.
        Without the key, a creature proficient with thieves' tools can pick the manacles' lock with a successful DC 15 Dexterity check.
        Manacles have 15 hit points.
    \paragraph{Map or Scroll Case}
        This cylindrical leather case can hold up to ten rolled-up sheets of paper or five rolled-up sheets of parchment.

\subsubsection{Trade Goods} \label{ssec::tradegoods}
    \begin{table*}[t]%
        \begin{DndTable}[width=\linewidth, header=Trade Goods]{Xlccccc}
            \textbf{Item} & \textbf{Rarity} & \textbf{Total Cost} & \textbf{Weight} & \textbf{Source} \\
            Chicken                  & Mundane  &   2 fobs    & ---  & PHB 157 \\
            Flour                    & Mundane  &   4 fobs    & 1 kg & PHB 157 \\
            Canvas (1 sq. mt.)       & Mundane  &  10 fobs    & ---  & PHB 157 \\
            Iron                     & Mundane  &  20 fobs    & 1 kg & PHB 157 \\
            Cotton Cloth (1 sq. mt.) & Mundane  &  50 fobs    & ---  & PHB 157 \\
            Cooper                   & Plain    &   1 agnoma  & 1 kg & PHB 157 \\
            Goat                     & Plain    &   1 agnoma  & ---  & PHB 157 \\
            Ginger                   & Plain    &   2 agnomas & 1 kg & PHB 157 \\
            Cinnamon                 & Plain    &   4 agnomas & 1 kg & PHB 157 \\
            Linen (1 sq. mt.)        & Plain    &   5 agnomas & ---  & PHB 157 \\
            Cloves                   & Plain    &   6 agnomas & 1 kg & PHB 157 \\
            Cow                      & Common   &  10 agnomas & ---  & PHB 157 \\
            Gold                     & Uncommon & 100 agnomas & 1 kg & PHB 157 \\
        \end{DndTable}
    \end{table*}
