% !TEX root = ../main.tex
\subsection*{Weapons} \label{ssec::weapons}
% SPECIAL WEAPONS:
% * Huge Krudzal weapons used to fight giants
% * Drer fire weapons
% * Sulia's large blast weapons (cannons and large handcannons)
% * Kaldrathal's more refined flintlock pistols
% * Mercury weapons from frostburn umans

% heavy shields grant +3 AC and half cover against ranged attacks, but impose a movement speed debuff:
% tower shield: +3 AC, -10 movement speed
% bulwark: +4 AC, -20 movement speed

% WEAPON CATEGORIES:
% Knives:
%   simple    : dagger (L) 1d4, throwing dagger (L) 1d4, kukri 1d6 (only when thrown, less range)
%   1-handed  : parrying dagger 1
% Straight Swords:
%   simple    : shortsword 1d6
%   1-handed  : broadsword (H) 1d8, backsword 1d8
%   versatile : bastard sword 1d8-1d10
%   2-handed  : longsword 1d10, claymore (H) 1d12, zweihander (H) 2d6, flamberge (H) 1d10, greatsword (H) 2d6
% Curved Swords:
%   simple    : sickle (L) 1d4, cutlass 1d6
%   1-handed  : scimitar (L) 1d6, sabre 1d8, khopesh 1d6
%   versatile : falchion (H) 1d8-1d10
%   2-handed  : katana 1d10, double-bladed scimitar 2d4
% Light Swords:
%   simple    : mail breaker 1d4
%   1-handed  : rapier 1d8, estoc/tuck 1d8, basket hilted sword 1d8
% Axes:
%   simple    : handaxe (L) 1d6
%   versatile : battleaxe 1d8-1d10, broad axe 1d8-1d10 (H)
%   2-handed  : bearded axe 1d10, greataxe (H) 1d12
% Hammer:
%   simple    : club (L) 1d4, light hammer (L) 1d4, mace 1d6
%   1-handed  : warhammer 1d8-1d10, boomerang 1d4
%   2-handed  : greatclub (H) 1d8, maul (H) 2d6, lucerne 1d10
% Pick:
%   simple    : kama (L) 1d6
%   1-handed  : war pick 1d8
%   2-handed  : horseman's pick 1d10
% Staves:
%   simple    : quarterstaff 1d6-1d8
% Spears:
%   simple    : javelin 1d6, trident 1d6-1d8
%   versatile : spear 1d8-1d10, lance 1d12
%   2-handed  : pike (H) 1d10
% Halberds:
%   2-handed  : glaive (H) 1d10, poleaxe (H) 1d10, lucerne (H) 1d0
% Flails:
%   1-handed  : nunchaku (L) 1d4, ball-and-chain 1d6
% Whip:
%   1-handed  : whip 1d4, bullwhip (1d4 slashing but 6m reach), qilinbian (1d6 slashing, finesse, reach - 6mt)
% Bow:
%   2-handed  : shortbow 1d6, composite bow 1d8, longbow (H) 1d8, yumi (H) 1d10 - disadvantage on less than 4 meters
% Crossbow:
%   1-handed  : hand crossbow (L) R1 1d6
%   2-handed  : light crossbow R1 1d8, repeating crossbow R3 1d8, heavy crossbow (H) R1 1d10
% Pistol:
%   1-handed  : flintlock R1 1d10, pistol (change name) R4 1d8
% Musket:
%   2-handed  : musket R1 1d12
% "Newer" Firearms:
%   1-handed  : palm pistol (L) R1 1d8, pepperbox R6 1d10
%   2-handed  : blunderbuss R1 2d8, bad news R1 2d12
% Fire-breathers (Drer) - misfiring damages you:
%   1-handed  : bomb 3d6
%   2-handed  : firelance 1d12, hand mortar 2d8, flamespewer 1d6*
% Giant-slayers (Krudzal) - no extra attack:
%   2-handed  : dreihander 2d12, greatmaul 4d6, greatchisel 2d8*, hand ballista 2d10
%       dreihander    - https://mortalshell.wiki.fextralife.com/Martyr's+Blade
%       greatmaul     - https://mortalshell.wiki.fextralife.com/Smoldering+Mace
%       greatchisel   - https://mortalshell.wiki.fextralife.com/Hammer+and+Chisel
%       hand ballista - https://mortalshell.wiki.fextralife.com/Ballistazooka - action to shoot, action to reload
% Trick weapons: take 3 or 4 from here https://bloodborne.wiki.fextralife.com/Weapons.
% Exotic:
%   1-handed  :
%   versatile :
%   2-handed  : swordspear* (H) 1d10
%   ranged    : blowgun 1, net -
% Special (no specific talents, generally used for flavor):
%   simple    : shortspear 1d6, dart 1d4, sling 1d4
% Footnotes:
% * swordspears are essentially fancy glaive, but require proficiency with spears and swords due to having a different combat style.

% Take firearms from https://www.dndbeyond.com/subclasses/gunslinger .

\subsection*{Weapon Properties} \label{ssec::weaponproperties}
    \subparagraph{Ammunition}
        You can use a weapon that has the ammunition property to make a ranged attack only if you have ammunition to fire from the weapon.
        Each time you attack with the weapon, you expend one piece of ammunition.
        Drawing the ammunition from a quiver, case, or other container is part of the attack.
        Loading a one-handed weapon requires a free hand.
        At the end of the battle, you can recover half your expended ammunition by taking a minute to search the battlefield.

        If you use a weapon that has the ammunition property to make a melee attack, you treat the weapon as an improvised weapon.
        A sling must be loaded to deal any damage when used in this way.
    \subparagraph{Explosive}
        Upon a hit, everything within 1 meter of the target must make a Dexterity saving throw (DC equal to 8 + your proficiency bonus + your Dexterity modifier) or suffer 1d8 fire damage.
        If the weapon misses, the ammunition fails to detonate, or bounces away harmlessly before doing so.
    \subparagraph{Finesse}
        When making an attack with a finesse weapon, you use your choice of your Strength or Dexterity modifier for the attack and damage rolls.
        You must use the same modifier for both rolls.
    \subparagraph{Heavy}
        Creatures that are Small or Tiny have disadvantage on attack rolls with heavy weapons.
        A heavy weapon's size and bulk make it too large for a Small or Tiny creature to use effectively.

        In addition, the multiple attack penalty is increased to 6 for weapons with this property.
    \subparagraph{Light}
        A light weapon is small and easy to handle, making it ideal for use when fighting with two weapons.

        In addition, the multiple attack penalty is reduced to 4 for weapons with this property.
    \subparagraph{Loading}
        After attacking with this weapon, you need to use one action to reload it before attacking again.
        You must have one free hand to reload the weapon.
    \subparagraph{Misfiring}
        Whenever you make an attack roll, and the dice roll is equal to or lower than the weapon’s misfire score, the weapon misfires.
        The attack misses, and the weapon cannot be used again until you spend two actions to try and repair it.
        To repair your weapon, you must make a successful Tinker’s Tools check (DC equal to 8 + the weapon's misfire score).
        If your check fails, the weapon is broken and must be mended as part of a long rest at a quarter of its cost.
        Creatures who use a weapon without being proficient increase its misfire score by 1.
    \subparagraph{Range}
        A weapon that can be used to make a ranged attack has a range in parentheses after the ammunition or thrown property.
        The range lists two numbers.
        The first is the weapon’s normal range in meters, and the second indicates the weapon’s long range.
        When attacking a target beyond normal range, you have disadvantage on the attack roll.
        You can’t attack a target beyond the weapon’s long range.
    \subparagraph{Reach}
        This weapon adds 1 meters to your reach when you attack with it, as well as when determining your reach for opportunity attacks with it.
    \subparagraph{Reloading}
        The weapon can be fired a number of times equal to its reload score before you must spend one action to reload it.
        You must have one free hand to reload the weapon.
    \subparagraph{Special}
        A weapon with the special property has unusual rules governing its use, explained in the weapon’s description (see ``Special Weapons'' later in this section).
    \subparagraph{Thrown}
        If a weapon has the thrown property, you can throw the weapon to make a ranged attack.
        If the weapon is a melee weapon, you use the same ability modifier for that attack roll and damage roll that you would use for a melee attack with the weapon.
        For example, if you throw a handaxe, you use your Strength, but if you throw a dagger, you can use either your Strength or your Dexterity, since the Dagger has the finesse property.
    % \subparagraph{Trick}
        % This weapon requires the Flexible Fighter 1 feat to use.
        % These weapons can be transformed into alternate forms and have different capabilities in this transformed state.
        % The weapons have two values for damage and properties, one for their normal form, and one for the transformed one.
    \subparagraph{Two-Handed}
        This weapon requires two hands to attack with it.
        This property is relevant only when you attack with the weapon, not when you simply hold it.
    \subparagraph{Versatile}
        This weapon can be used with one or two hands.
        A damage value in parentheses appears with the property --- the damage when the weapon is used with two hands to make a melee attack.

\subsection*{Improvised Weapons} \label{ssec::improvisedweapons}
    Sometimes characters don't have their weapons and have to attack with whatever is at hand.
    An improvised weapon includes any object you can wield in one or two hands, such as broken glass, a table leg, a frying pan, a wagon wheel, or a dead creature.

    Often, an improvised weapon is similar to an actual weapon and can be treated as such.
    For example, a table leg is akin to a club.
    At the DM's option, a character proficient with a weapon can use a similar object as if it were that weapon and use their proficiency bonus with that weapon.

    An object that bears no resemblance to a weapon deals 1d4 damage (the DM assigns a damage type appropriate to the object).
    If a character uses a ranged weapon to make a melee attack, or throws a melee weapon that does not have the thrown property, it also deals 1d4 damage.
    An improvised thrown weapon has a normal range of 4 meters and a long range of 12 meters.
