% !TEX root = ../main.tex
\subsubsection{Acrobat} \label{feat::acrobat}
\small{\textcolor{gray}{Acrobatics}}

\normalsize
You've had an exceptional flexibility from a very young age.
By regular training you maintain this ability, aware of its usefulness in your adventuring life.
\paragraph{RANK 1} You are proficient with the Acrobatics skill.
\paragraph{RANK 2} You can make a running long jump or a running high jump after moving only 1.5 meters on foot, rather than 3 meters.
\paragraph{RANK 3} Moving through difficult terrain costs you no extra movement.

% ============================================================================== %
\subsubsection{Actor} \label{feat::actor}
\small{\textcolor{gray}{Performer}}

\normalsize
You master performance so that you can command any stage.
\paragraph{REQUIREMENTS} Performer 3.
\paragraph{RANK 1} You double your proficiency modifier in the Performance skill.
\paragraph{RANK 2} You have advantage on Charisma (Deception) and Charisma (Performance) checks when trying to pass yourself off as a different person.
\paragraph{RANK 3} Increase your Charisma score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Aerialist} \label{feat::aerialist}
\small{\textcolor{gray}{Acrobatics}}

\normalsize
High above the ground, you defy falls to earth on a daily basis.
\paragraph{REQUIREMENTS} Acrobat 3.
\paragraph{RANK 1} You double your proficiency modifier in the Acrobatics skill.
\paragraph{RANK 2} Your walking speed increases by 1.5 meters.
Additionally, you gain a climbing speed and a swimming speed equal to your walking speed.
\paragraph{RANK 3} You learn the Light as a Feather technique.

% ============================================================================== %
\subsubsection{Animal Handler} \label{feat::animalhandler}
\small{\textcolor{gray}{Animal Handling}}

\normalsize
Ever since you were a kid, you've always surrounded yourself with animals, pets or otherwise.
Animals are calmer when they're around you, and you yourself get the same feeling when around them.
\paragraph{RANK 1} You are proficient with the Animal Handling skill.
\paragraph{RANK 2} Animals naturally trust you, and you don't need to perform any check to calm an animal or monster that is not already violent toward you.
\paragraph{RANK 3} You learn the Beast Command technique.

% ============================================================================== %
\subsubsection{Armed Fighter} \label{feat::armedfighter}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
No one learned how to use a sword without first swinging a stick.
\paragraph{RANK 1} You are proficient with simple weapons.
\paragraph{RANK 2} You can attack twice, instead of once, whenever you take the Attack action on your turn.
\paragraph{RANK 3} You learn one technique of your choice between Bonk, Block, Buttstroke, Feint, Lunge, Parry, Pushing Attack, Protect, Quick Draw, Riposte, Rush, Sweep, and Trip.

% ============================================================================== %
\subsubsection{Armor Breaker} \label{feat::armorbreaker}
\small{\textcolor{gray}{Strength}}

\normalsize
You use your extensive knowledge of heavy armor to improve your effectiveness against it, turning your bludgeoning attacks into devastating metal bending strikes.
\paragraph{REQUIREMENTS} Hammer Adept 2 and Heavily Armored 1.
\paragraph{RANK 1} You can use the Bonk technique as an opportunity attack.
\paragraph{RANK 2} When fighting a target with plate armor or natural armor, you get a +2 bonus to your melee attacks with hammers.
\paragraph{RANK 3} You learn the Fell Strike technique.

% ============================================================================== %
\subsubsection{Athlete} \label{feat::athlete}
\small \textcolor{gray}{Athletics}

\normalsize
You begin your day by training, pushing the limits of your body ever so slightly.
\paragraph{RANK 1} You are proficient with the Athletics skill.
\paragraph{RANK 2} When you are prone, standing up uses only 1.5 meters of your movement.
\paragraph{RANK 3} You count as if you were one size larger for the purpose of determining your carrying capacity.

% ============================================================================== %
\subsubsection{Axe Adept} \label{feat::axeadept}
\small{\textcolor{gray}{Strength}}

\normalsize
More than a simple tool, you master the use of axes in combat.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with axes.
\paragraph{RANK 2} While wielding an axe, you get advantage on your attack rolls with the Disarm action when forcing your target to drop a shield.
\paragraph{RANK 3} You learn the Rush technique.

% ============================================================================== %
\subsubsection{Ball-and-Chain Master} \label{feat::ballandchainmaster}
\small{\textcolor{gray}{Strength}}

\normalsize
Your increased awareness works in tandem to your flail mastery, allowing you to hit enemies behind obstacles and shields.
\paragraph{REQUIREMENTS} Flail Adept 2 and Insightful 2.
\paragraph{RANK 1} When you use a ball-and-chain, its damage die changes from a d6 to a d8.
\paragraph{RANK 2} When you hit with an opportunity attack using a ball-and-chain, the target must succeed on a Strength saving throw (DC 8 + your proficiency bonus + your Strength modifier) or be knocked prone.
\paragraph{RANK 3} You learn the Shield Sweep technique.

% ============================================================================== %
\subsubsection{Bent Blade Master} \label{feat::bentblademaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your extreme skill with curved swords allows you to cut through flesh with effectiveness and ease.
\paragraph{REQUIREMENTS} Curved Sword Adept 2 and Quick Fingers 2.
\paragraph{RANK 1} While you're wielding at least one curved sword and a creature gets an attack of opportunity on you, they attack with disadvantage.
\paragraph{RANK 2} You get a +2 bonus to your melee weapon attack damage with curved blades.
This extra damage is nullified against targets with chainmail, plate armor, or natural armor.
\paragraph{RANK 3} You learn the Shield Sweep technique.

% ============================================================================== %
\subsubsection{Blade \& Board} \label{feat::bladeandboard}
\small{\textcolor{gray}{Strength}}

\normalsize
You know the perfect balance between defense and attack, making you a formidable foe in melee combat.
\paragraph{REQUIREMENTS} Straight Blade Adept 2 and Shield Training 2, or Axe Adept 2 and Shield Training 2.
\paragraph{RANK 1} When you're wielding a slashing weapon and a shield, you gain a +1 to AC and to your attack damage.
\paragraph{RANK 2} While you're wielding a shield and a creature misses you with a melee attack, you can use your reaction to attack it with a melee attack.
\paragraph{RANK 3} You learn the Bash technique.

% ============================================================================== %
\subsubsection{Blade Breaker} \label{feat::bladebreaker}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You know that the perfect counter against any sword is simply a long pole.
\paragraph{REQUIREMENTS} Staff Fighter 2.
\paragraph{RANK 1} Staves have the Reach property when wielded by you.
\paragraph{RANK 2} You have advantage on the Disarm action and the Parry technique against creatures using any type of sword.
\paragraph{RANK 3} While using a polearm, you can use the Disarm action as your opportunity attack.

% ============================================================================== %
\subsubsection{Blowgun Adept} \label{feat::blowgunadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
While unconventional, you understand the effectiveness of the blowgun when remaining hidden is of the essence.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} You are proficient with blowguns.
\paragraph{RANK 2} You gain a +1 bonus to attack rolls with a blowgun.
Additionally, attacking with a blowgun at long range doesn't impose disadvantage on your ranged weapon attack rolls.
\paragraph{RANK 3} When you hit with a blowgun while hidden, your location is not revealed.

% ============================================================================== %
\subsubsection{Blunt Thrower} \label{feat::bluntthrower}
\small{\textcolor{gray}{Strength}}

\normalsize
You take advantage of the raw practicality of a good hammer, and not even faraway foes can escape the wrath of its face.
\paragraph{REQUIREMENTS} Hammer Adept 2 and Thrown Weapon Master 2.
\paragraph{RANK 1} You don't provoke opportunity attacks when picking weapons up from the floor.
\paragraph{RANK 2} When you hit a creature with an thrown bludgeoning weapon, you divide its moving speed by half (rounded up) during its next turn.
This effect does not stack.
\paragraph{RANK 3} You learn the Hammer Fling technique.

% ============================================================================== %
\subsubsection{Blunt Master} \label{feat::bluntmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your staff is an extension of your body, and it has become an essential part of your movement and defense.
\paragraph{REQUIREMENTS} Staff Fighter 2 and Unarmed Artist 2.
\paragraph{RANK 1} As a bonus action, you can use your staff to propel yourself into the air, making a high jump up to your Dexterity modifier times 1.5 meters.
Additionally, if you have moved at least 3 meters during this round, you can jump in a straight line up to a distance equal to your Dexterity modifier times 3 meters.
\paragraph{RANK 2} You gain a +1 bonus to your AC while using a staff.
Additionally, if you use the weapon with two hands you gain another +1 bonus to your AC.
\paragraph{RANK 3} You learn the Defensive Stance technique.

% ============================================================================== %
\subsubsection{Bow Adept} \label{feat::bowadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
While a long list of new ranged weapons have recently appeared, you know that nothing beats the long range of the traditional bow.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with bows.
\paragraph{RANK 2} After you successfully hit a target with a melee attack using your bow, that creature can't make opportunity attacks against you until the start of your next turn.
\paragraph{RANK 3} You learn the Quick Draw technique.

% ============================================================================== %
\subsubsection{Buckler Training} \label{feat::bucklertraining}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Small shields are much more than a weaker version of the standard shields.
They allow you to remain mobile while still providing a solid defense against even the fastest assailants.
\paragraph{RANK 1} You gain proficiency with light shields.
\paragraph{RANK 2} In combat, you can don or doff a light shield as the free object interaction of your turn.
\paragraph{RANK 3} You learn the Parry technique.

% ============================================================================== %
\subsubsection{Bullet Tinkerer} \label{feat::bullettinkerer}
\small{\textcolor{gray}{Science}}

\normalsize
Firearm ammunition is near impossible to find or purchase in most parts of Yuadrem.
Due to this, learning how to craft it yourself is an essential aspect for using firearms.
\paragraph{REQUIREMENTS} Musket Adept 2 and Educated 2, or Pistol Adept 2 and Educated 2.
\paragraph{RANK 1} You can craft ammunition using a set of Tinker's Tools at half the cost.
\paragraph{RANK 2} If you roll a misfire, you can use your reaction to roll a d20 with disadvantage.
If the number rolled is higher than the weapon's misfire score, the weapon does not misfire.
\paragraph{RANK 3} You learn the Violent Shot technique.

% ============================================================================== %
\subsubsection{Cognizant} \label{feat::cognizant}
\small{\textcolor{gray}{History}}

\normalsize
From background or perchance you've been given a privileged access to books and teaching thorough your life.
\paragraph{RANK 1} You are proficient with the History skill.
\paragraph{RANK 2} You have advantage on any Intelligence (History) checks to recall information of your kin and your country of origin.
\paragraph{RANK 3} You learn the Wizened Advice technique.

% ============================================================================== %
\subsubsection{Combat Improviser} \label{feat::combatimproviser}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Anything can be your weapon.
If you can grab it, you can swing it.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} You are proficient with improvised weapons.
An improvised weapon is anything that is somewhat similar to a simple weapon.
\paragraph{RANK 2} After rolling for initiative, you make your first attack with an improvised weapon at advantage.
\paragraph{RANK 3} You learn one technique of your choice between Bonk, Block, Buttstroke, Feint, Lunge, Parry, Pushing Attack, Protect, Quick Draw, Riposte, Rush, Sweep, and Trip.

% ============================================================================== %
\subsubsection{Covered Shooter} \label{feat::coveredshooter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You know that stealth and range go hand in hand.
\paragraph{REQUIREMENTS} Bow Adept 2 and Sly 2.
\paragraph{RANK 1} If you miss with a ranged attack with a bow or thrown weapon while hidden, the attack doesn't reveal your location, and you remain hidden.
\paragraph{RANK 2} You can treat ranged attack damage die rolls of 1 as 2.
\paragraph{RANK 3} You learn or improve the Sneak Attack technique.

% ============================================================================== %
\subsubsection{Crossbow Adept} \label{feat::crossbowadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are learned with the use of crossbow, and can use it proficiently both for hunting and combat.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with crossbows.
\paragraph{RANK 2} You can change the loading quality of crossbows to reloading.
% You can ignore the loading quality of crossbows.
\paragraph{RANK 3} You learn the Buttstroke technique.

% ============================================================================== %
\subsubsection{Crossbow Expert} \label{feat::crossbowexpert}
\small{\textcolor{gray}{Dexterity}}

\normalsize
While muskets and pistols have largely replaced the old weapons of warfare, you prefer a weapon that won't blow up on your hand every so often.
\paragraph{REQUIREMENTS} Crossbow Adept 2 and Quick Fingers 2.
\paragraph{RANK 1} Being within 1.5 meters of a hostile creature doesn't impose disadvantage on your ranged attack rolls.
Additionally, you don't provoke attacks of opportunity when using the Attack action with a ranged weapon when within the reach of a creature.
\paragraph{RANK 2} You get a +2 bonus to damage rolls when attacking a creature within 1.5 meters of you with a crossbow.
\paragraph{RANK 3} You learn the Prepared Shot technique.

% ============================================================================== %
\subsubsection{Crusher} \label{feat::crusher}
\small{\textcolor{gray}{Strength}}

\normalsize
You are practiced in the art of crushing your enemies.
\paragraph{REQUIREMENTS} Proficiency with at least two martial bludgeoning weapon types.
\paragraph{RANK 1} Once per turn, when you hit a creature with an attack that deals bludgeoning damage, you can move it 1.5 meters to an unoccupied space, provided that the target is no more than one size larger than you.
\paragraph{RANK 2} Increase your Strength by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Whack technique.

% ============================================================================== %
\subsubsection{Curved Sword Adept} \label{feat::curvedswordadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You forfeited the piercing capacity of the straight blades to maximize your deadliness against the unarmored.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with curved swords.
\paragraph{RANK 2} While wielding a curved sword, you get advantage on your attack rolls with the Disarm action when forcing your target to drop a weapon.
\paragraph{RANK 3} You learn the Parry technique.

% ============================================================================== %
\subsubsection{Cutthroat} \label{feat::cutthroat}
\small{\textcolor{gray}{Dexterity}}

\normalsize
A master at concealing your dagger, you act quick and strike hard in combat.
\paragraph{REQUIREMENTS} Dagger Savant 2.
\paragraph{RANK 1} You have advantage on any check to conceal a small weapon on your person.
\paragraph{RANK 2} You gain a +2 bonus to initiative. % when wielding a light weapon.
\paragraph{RANK 3} You gain or improve the Sneak Attack technique.

% ============================================================================== %
