% !TEX root = ../main.tex
\subsubsection{Giant Slayer} \label{tal::giantslayer}
\small{\textcolor{gray}{Strength}}

\normalsize
Partaking or not in Krudzal's Eternal War, you use your incredible strength to wield their massive weapons.
\paragraph{REQUIREMENTS} Strength 16. Great Weapon User 2.
\paragraph{RANK 1} You are able to use Krudzal's giant-slayers.
\paragraph{RANK 2} You gain a +1 bonus to damage rolls with weapons with the Great property.
\paragraph{RANK 3} When fighting with a melee giant-slayer, you can attack up to three creatures in range with one attack.
Additionally, you can reload the hand ballista as a bonus action instead of an action.

% ============================================================================== %
\subsubsection{Glaive Master} \label{tal::glaivemaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Different than the common polearm, you know how deadly a glaive can be in capable hands.
\paragraph{REQUIREMENTS} Halberd Adept 2.
\paragraph{RANK 1} When you use a glaive, its damage die changes from a d10 to a d12.
\paragraph{RANK 2} The glaive has the finesse property for you.
\paragraph{RANK 3} When you miss an attack, you can attempt to strike your enemy with the rondel of your glaive as a free action.
On a hit, the target takes 1d4 + your Strength modifier bludgeoning damage.
You can do this once per turn.

% ============================================================================== %
\subsubsection{Grappler} \label{tal::grappler}
\small{\textcolor{gray}{Strength}}

\normalsize
You've developed the skills necessary to hold your own in close-quarters grappling.
\paragraph{REQUIREMENTS} Pugilist 2.
\paragraph{RANK 1} You have advantage on attack rolls against creatures you are grappling.
\paragraph{RANK 2} You benefit from three-quarters cover while you grapple a creature of a size equal or greater than yours.
\paragraph{RANK 3} You learn the Pin technique.

% ============================================================================== %
\subsubsection{Great Weapon User} \label{tal::greatweaponuser}
\small{\textcolor{gray}{Strength}}

\normalsize
You've learned to put the weight of a weapon to your advantage, letting its momentum empower your strikes.
\paragraph{REQUIREMENTS} Strength 13. Armed Fighter 2.
\paragraph{RANK 1} You can use weapons with the great property.
Some of these, like the zweihander and the greataxe, also require you to have proficiency with the corresponding weapon type.
\paragraph{RANK 2} On your turn, when you score a critical hit with a melee weapon or reduce a creature to 0 hit points with one, you can make one melee weapon attack as a bonus action.
\paragraph{RANK 3} You learn the Reckless Strike technique.

% ============================================================================== %
\subsubsection{Greatshield Training} \label{tal::greatshieldtraining}
\small{\textcolor{gray}{Strength}}

\normalsize
When it comes to protecting your life or that of others, you know that size matters.
\paragraph{REQUIREMENTS} Shield Training 1.
\paragraph{RANK 1} You gain proficiency with heavy shields
\paragraph{RANK 2} Creatures standing behind you get three-fourths cover against ranged attacks.
\paragraph{RANK 3} You learn the Protect technique.

% ============================================================================== %
\subsubsection{Gunner} \label{tal::gunner}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Being a new breed of weapon, firearms are constantly subject to change and refinement.
New weapons appear by the minute, and you are an expert at experimenting with them.
\paragraph{REQUIREMENTS} Pistol Adept 2 and Musket Adept 2.
\paragraph{RANK 1} As long as you can examine the weapon for 30 seconds, you are proficient with any kind of firearm, even if it is new or experimental.
\paragraph{RANK 2} Your firearm attacks score a critical hit on a roll of 19-20.
\paragraph{RANK 3} You learn the Reckless Shot technique.

% ============================================================================== %
\subsubsection{Haggler} \label{tal::haggler}
\small{\textcolor{gray}{Persuasion}}

\normalsize
Your abilities at haggling and persuading are known in your local markets, and you are both feared and revered by merchants and traders.
\paragraph{REQUIREMENTS} Persuasive 3.
\paragraph{RANK 1} You double your proficiency modifier in the Persuasion skill.
\paragraph{RANK 2} Your well-honed haggling skills allow you to shave off 10\% off the price of anything, even if you fail a Charisma (Persuasion) check.
\paragraph{RANK 3} Increase your Charisma score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Halberd Adept} \label{tal::halberdadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You know that both farmers and nobles use halberds as their weapon of choice for a reason.
\paragraph{REQUIREMENTS} Armed Fighter 2 and Staff Fighter 2.
\paragraph{RANK 1} You are proficient with the many varieties of halberds.
\paragraph{RANK 2} When a creature within 1.5 meters of you makes an attack against a target other than you, you can use your reaction to make a melee weapon attack against the attacking creature.
\paragraph{RANK 3} You learn the Trip technique.

% ============================================================================== %
\subsubsection{Hammer Adept} \label{tal::hammeradept}
\small{\textcolor{gray}{Strength}}

\normalsize
If a hammer will do, why complicate things?
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You gain proficiency with hammer weapons.
\paragraph{RANK 2} If you use the Help action to aid an ally's melee attack while you're wielding a hammer weapon, you knock the target's shield aside momentarily.
In addition to the ally gaining advantage on the attack roll, the ally gains a bonus to the roll equal to the shield's AC bonus.
\paragraph{RANK 3} You learn the Bonk technique.

% ============================================================================== %
\subsubsection{Hand Crossbow Master} \label{tal::handcrossbowmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You can equip, load, and shoot a hand crossbow in an instant, and with deadly effect.
\paragraph{REQUIREMENTS} Crossbow Adept 2.
\paragraph{RANK 1} You can reload a hand crossbow or one-handed firearm without having a free hand.
\paragraph{RANK 2} You can ignore the loading (or reloading) quality of hand crossbows.
\paragraph{RANK 3} You can don and you can doff a one-handed ranged weapon as your free object interaction during your turn.
The two actions don't need to be done in tandem - for example, you can don a hand crossbow, shoot an arrow, and doff it during one turn.

% ============================================================================== %
\subsubsection{Heavily Armored} \label{tal::heavilyarmored}
\small{\textcolor{gray}{Strength}}

\normalsize
You are trained to use heavy armor.
\paragraph{REQUIREMENTS} Moderately Armored 1.
\paragraph{RANK 1} You gain proficiency with heavy armor.
\paragraph{RANK 2} Equipped heavy armor and metal accessories only add half their weight to your encumbrance.
\paragraph{RANK 3} Increase your Strength by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Heavy Armor Master} \label{tal::heavyarmormaster}
\small{\textcolor{gray}{Strength}}

\normalsize
You can use your armor to deflect strikes that would easily kill others.
\paragraph{REQUIREMENTS} Heavily Armored 2 and Athletics 2.
\paragraph{RANK 1} Your hit point maximum increases by an amount equal to your number of hit dice.
Whenever you earn a hit die thereafter, your hit point maximum increases by an additional 1 hit point.
\paragraph{RANK 2} While you are wearing heavy armor, piercing and slashing damage that you take is reduced by 3.
\paragraph{RANK 3} You learn the Defend technique.

% ============================================================================== %
\subsubsection{Heavy Lifter} \label{tal::heavylifter}
\small{\textcolor{gray}{Strength}}

\normalsize
You can easily lift and hurl objects that others can barely move.
\paragraph{REQUIREMENTS} Combat Improviser 2 and Thrown Weapon Master 2.
\paragraph{RANK 1} You can hurl any object or creature you can carry or grapple as you would an improvised weapon.
If you hurl a creature, both it and the target of your attack take 1d6 + your Strength modifier bludgeoning damage.
\paragraph{RANK 2} You count as if you were one size larger for the purpose of determining your carrying capacity.
\paragraph{RANK 3} You learn the Suplex technique.

% ============================================================================== %
\subsubsection{Heavy-Weight Combatant} \label{tal::heavyweightcombatant}
\small{\textcolor{gray}{Athletics}}

\normalsize
You can use the weight of your body and your armor to greatly aid you in combat.
\paragraph{REQUIREMENTS} Heavily Armored 2 and Pugilist 2.
\paragraph{RANK 1} If you are wearing metal gauntlets, your unarmed strike uses a d6 + your Strength modifier for damage.
\paragraph{RANK 2} While you are wearing heavy armor, you roll with advantage when taking the Shove action.
You also roll Strength (Athletics) with advantage when you are targeted by a Shove action.
\paragraph{RANK 3} You have learned to strategically position the crevices in your armor to hurt creatures too close to you.
When you grapple a creature, the target takes 1d6 piercing damage if your grapple check succeeds.
If another creature grapples you, they take 1d6 piercing damage.
If you start your turn grappling or being grappled by a creature, it takes 1d6 piercing damage.

% ============================================================================== %
\subsubsection{Historian} \label{tal::historian}
\small{\textcolor{gray}{History}}

\normalsize
Your extensive knowledge in the social sciences allows you to understand people, societies, and history with ease.
\paragraph{REQUIREMENTS} Cognizant 3.
\paragraph{RANK 1} You double your proficiency modifier in the History skill.
\paragraph{RANK 2} You can accurately recall anything you have seen or heard within the past month.
\paragraph{RANK 3} Increase your Intelligence score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Horse Killer} \label{tal::horsekiller}
\small{\textcolor{gray}{Animal Handling}}

\normalsize
Mounts are one of the most common advantages in war, so you've learned to deal with them appropriately.
\paragraph{REQUIREMENTS} Spear Adept 2 and Animal Handler 2.
\paragraph{RANK 1} You can always target a rider's mount with an attack made with a spear, even if the rider can normally deflect this attack to it.
\paragraph{RANK 2} You have a +2 to your attack rolls made against mounts.
\paragraph{RANK 3} You learn the Charge Stopper technique.

% ============================================================================== %
\subsubsection{Immovable Object} \label{tal::immovableobject}
\small{\textcolor{gray}{Strength}}

\normalsize
You are an obstacle.
\paragraph{REQUIREMENTS} Greatshield Training 2.
\paragraph{RANK 1} Creatures can't use a Tumble action to move through your space.
Additionally, you have advantage on Strength (Athletics) checks against being shoved or pushed.
\paragraph{RANK 2} While using a heavy shield, you get three-fourths cover against ranged attacks.
Additionally, you can duck behind your shield as a reaction, granting you full cover against ranged attacks until the start of your next turn.
\paragraph{RANK 3} The movement speed debuff from using a tower shield is halved for you.

% ============================================================================== %
\subsubsection{Inquisitive} \label{tal::inquisitive}
\small{\textcolor{gray}{Investigation}}

\normalsize
No detail can miss your analytical mind.
Your extensive experience and awareness means you can always tell when something's amiss.
\paragraph{RANK 1} You are proficient with the Investigation skill.
\paragraph{RANK 2} Your inquisitiveness allows you to tell when you are missing a detail or clue in a situation, even after a failed roll.
This doesn't allow you to roll again, but the lingering uneasiness stays in your mind.
\paragraph{RANK 3} You can take the Search action as a bonus action.

% ============================================================================== %
\subsubsection{Insightful} \label{tal::insightful}
\small{\textcolor{gray}{Insight}}

\normalsize
Either by primal intuition or extensive knowledge, you are always in complete awareness of your surroundings.
It's very rare for you to be surprised, and getting lost is something that simply does not happen to you.
\paragraph{RANK 1} You are proficient with the Insight skill.
\paragraph{RANK 2} You always know which way is north, and you always know the number of hours left before the next sunrise or sunset.
\paragraph{RANK 3} You have advantage on Wisdom (Perception) and Intelligence (Investigation) checks made to detect the presence of secret doors and traps.

% ============================================================================== %
\subsubsection{Insistent Fighter} \label{tal::insistentfighter}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You always maintain your foes at a cozy distance by masterfully manipulating your halberd.
\paragraph{REQUIREMENTS} Halberd Adept 2 and Observant 2.
\paragraph{RANK 1} Creature's provoke opportunity attacks from you even if they take the Disengage action before leaving your reach.
\paragraph{RANK 2} When you hit a creature with an opportunity attack, the creature's speed becomes 0 for the rest of the turn.
\paragraph{RANK 3} Your reach for opportunity attacks with polearms is of at least 3 meters.
Additionally, if you do hit a creature with an opportunity attack, you can choose to pull it towards you by 1.5 meters.

% ============================================================================== %
