% !TEX root = ../main.tex
\subsubsection{Kama Master} \label{tal::kamamaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
From among the common people weapon, you specialize in the use of the kama.
\paragraph{REQUIREMENTS} Pick Adept 2.
\paragraph{RANK 1} When you use a kama, its damage die changes from a d6 to a d8
\paragraph{RANK 2} When you successfully attack a foe with a piercing attack using your kama, you also deal 1d4 slashing damage, unmodified by your dexterity.
\paragraph{RANK 3} You can use the Trip technique as part of an opportunity attack.

% ============================================================================== %
\subsubsection{Knowledgeable} \label{tal::knowledgeable}
\small{\textcolor{gray}{Science}}

\normalsize
Your extensive knowledge in the natural sciences gives you access to a plethora of explanations to the phenomena of the world.
\paragraph{REQUIREMENTS} Educated 3.
\paragraph{RANK 1} You double your proficiency modifier in the Science skill.
\paragraph{RANK 2} You learn the Identify technique.
\paragraph{RANK 3} Increase your Intelligence score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Liar} \label{tal::liar}
\small{\textcolor{gray}{Deception}}

\normalsize
You can easily lie to someone to their face without batting an eye.
While you might not always be proud of this skill, you can't deny that it's saved you in countless situations.
\paragraph{RANK 1} You are proficient with the Deception skill.
\paragraph{RANK 2} When you fail to convince someone with a lie, it'll still take them one turn to realize you're lying, provided the lie isn't something absurd.
\paragraph{RANK 3} You learn the Mimic technique.

% ============================================================================== %
\subsubsection{Light Armor Master} \label{tal::lightarmormaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You make effective use of the increased mobility that comes from the use of light armor.
\paragraph{REQUIREMENTS} Lightly Armored 2.
\paragraph{RANK 1} You can use the Dodge action even if you speed is 0.
\paragraph{RANK 2} If you aren't incapacitated, you can add a +2 bonus to any Dexterity saving throw you make against a spell or other harmful effect that targets only you.
\paragraph{RANK 3} Your learn the Lunge technique.

% ============================================================================== %
\subsubsection{Light Sword Adept} \label{tal::lightswordadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Focused on piercing throw your opponent's armor, you've learned the art of fighting with light swords.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with light swords.
\paragraph{RANK 2} When you are wielding a light sword in one hand and no other weapons, you gain a +2 bonus to damage rolls with that weapon.
\paragraph{RANK 3} You learn the Riposte technique.

% ============================================================================== %
\subsubsection{Lightly Armored} \label{tal::lightlyarmored}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You are trained in the use of light armor.
\paragraph{RANK 1} You gain proficiency with light armor.
\paragraph{RANK 2} Equipped light armor and cloth accessories don't add to your encumbrance.
\paragraph{RANK 3} Increase your Dexterity by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Linguist} \label{tal::linguist}
\small{\textcolor{gray}{Languages}}

\normalsize
Your extensive knowledge in tongues is manifested in an enhanced ability recognizing languages and inventing codes of your own.
\paragraph{RANK 1} You are proficient in the Languages skill.
\paragraph{RANK 2} You have advantage on Charisma (Languages) checks to determine the language that a creature is speaking.
\paragraph{RANK 3} You can ably create ciphers.
Others can't decipher a code you create unless you teach them or they succeed on an Intelligence check (DC equal to your Intelligence score + your proficiency bonus).

% ============================================================================== %
\subsubsection{Lip-reader} \label{tal::lipreader}
\small{\textcolor{gray}{Languages}}

\normalsize
You have an uncanny capacity with languages and understanding speakers even without actually hearing them.
\paragraph{REQUIREMENTS} Linguist 3.
\paragraph{RANK 1} You double your proficiency modifier in the Languages skill.
\paragraph{RANK 2} If you see a creature's mouth while it is speaking a language you understand, you can interpret what it's saying by reading its lips.
\paragraph{RANK 3} Increase your Charisma score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Longsword Master} \label{tal::longswordmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Your proficiency with the longsword is unparalleled, and you regularly prove to your foes that the old sword is as valid today as it was on its golden age.
\paragraph{REQUIREMENTS} Straight Sword Adept 2.
\paragraph{RANK 1} When you use a longsword, its damage die changes from a d10 to a d12.
\paragraph{RANK 2} When a creature misses you with a melee weapon attack, you can roll to use the Disarm action on it as your reaction.
\paragraph{RANK 3} When you use the Block technique and an attack misses you, you can use the Riposte technique without using your reaction.

% ============================================================================== %
