% !TEX root = ../main.tex
\subsubsection{Maiming Strikes} \label{tal::maimingstrikes}
\small{\textcolor{gray}{Strength}}

\normalsize
Your increased proficiency cleaving through wood and stone translates to devastating attacks against flesh and bone.
\paragraph{REQUIREMENTS} Axe Adept 2 and Pick Adept 2.
\paragraph{RANK 1} The last attack you make with the Attack action is rolled with advantage if you hit the target at least once in your turn.
\paragraph{RANK 2} When a creature rolls on the minor \& major injury charts from one of your attacks, they roll with advantage.
\paragraph{RANK 3} You learn the Cleave technique.

% ============================================================================== %
\subsubsection{Medic} \label{tal::medic}
\small{\textcolor{gray}{Medicine}}

\normalsize
You mastered the physician's arts, and are able to heal any wound or bruise with ease.
\paragraph{REQUIREMENT} Mender 3.
\paragraph{RANK 1} You double your proficiency modifier in the Medicine skill.
\paragraph{RANK 2} When you heal a creature by any means, the creature regains additional hit points equal to 2 + your proficiency modifier.
\paragraph{RANK 3} Increase your Wisdom score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Medium Armor Master} \label{tal::mediumarmormaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You have extensively practiced moving in medium armor, and make skilled use of its adaptive capabilities.
\paragraph{REQUIREMENTS} Moderately Armored 2.
\paragraph{RANK 1} Wearing medium armor doesn't impose disadvantage on your Dexterity (Stealth) checks.
\paragraph{RANK 2} When you wear medium armor, you can add 3, rather than 2, to your AC if you have a Dexterity of 16 or higher.
\paragraph{RANK 3} While wearing medium armor, you may add half your proficiency bonus, rounded down, to Strength, Dexterity, and Constitution saving throws that don't already include your proficiency bonus.

% ============================================================================== %
\subsubsection{Medium Haft Master} \label{tal::mediumhaftmaster}
\small{\textcolor{gray}{Strength}}

\normalsize
Why learn how to fight with a sword when your tools will do the job?
\paragraph{REQUIREMENTS} Axe Adept 2, Hammer Adept 2, and Pick Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with axes, hammers, and picks.
\paragraph{RANK 2} You can treat any weapon as if it had the Heavy property.
\paragraph{RANK 3} You learn the Shield Break technique.

% ============================================================================== %
\subsubsection{Menacing} \label{tal::menacing}
\small{\textcolor{gray}{Intimidation}}

\normalsize
With good reason or not, people have always been a bit fearful of you.
Your menacing appearance has permitted you to bypass consequence in many situations, allowing you to lead a carefree lifestyle.
\paragraph{RANK 1} You are proficient with the Intimidation skill.
\paragraph{RANK 2} People are naturally more careful around you, and you can get away with petty crimes without repercussion from the law.
\paragraph{RANK 3} You learn the Taunt technique.

% ============================================================================== %
\subsubsection{Mender} \label{tal::mender}
\small{\textcolor{gray}{Medicine}}

\normalsize
You have a natural affinity to healing.
You are uncomfortable with the thought of a friend suffering, and your dedication to mending wounds is valued by anyone around you.
\paragraph{RANK 1} You are proficient with the Medicine skill.
\paragraph{RANK 2} When you successfully stabilize a dying creature, that creature also regains 1 hit point.
\paragraph{RANK 3} During a short rest, you can clean and bind the wounds of up to six willing beasts and humanoids.
Make a DC 15 Wisdom (Medicine) check for each creature.
On a success, if a creature spends a Hit Die during this rest, that creature can forgo the roll and instead regain the maximum number of hit points the die can restore.
A creature can do so only once per rest, regardless of how many Hit Dice it spends.

% ============================================================================== %
\subsubsection{Mobile} \label{tal::mobile}
\small{\textcolor{gray}{Acrobatics}}

\normalsize
You are exceptionally speedy and agile.
\paragraph{REQUIREMENTS} Lightly Armored 2 and Acrobat 2.
\paragraph{RANK 1} When you use the Dash action, difficult terrain doesn't cost you extra movement.
\paragraph{RANK 2} When you make a melee attack against a creature, you don't provoke opportunity attacks from that creature for the rest of the turn, whether you hit or not.
\paragraph{RANK 3} Your speed increases by 3 meters.

% ============================================================================== %
\subsubsection{Moderately Armored} \label{tal::moderatelyarmored}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You are trained in the use of medium armor, be it leather, chain, or plate.
\paragraph{REQUIREMENTS} Lightly Armored 1.
\paragraph{RANK 1} You gain proficiency with medium armor.
\paragraph{RANK 2} Equipped medium armor and leather or chain accessories don't add to your encumbrance.
\paragraph{RANK 3} Increase your Strength or Dexterity by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Modern Soldier} \label{tal::modernsoldier}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Always up-to-date, you are ready to fight your foes with both a melee and a ranged weapon.
\paragraph{REQUIREMENTS} Straight Sword Adept 2 and Crossbow Adept 2.
\paragraph{RANK 1} When you use the Attack action and attack with a one-handed weapon, you can use your bonus action to attack with a hand crossbow or loaded firearm you are holding.
\paragraph{RANK 2} When using a backsword or a sabre on one hand and your other hand is free, you can hold the back of the blade with your free hand to increase its cutting power.
You add a +2 to your melee weapon attack damage while wielding your weapon in this way.
\paragraph{RANK 3} You learn the Visceral Attack technique.

% ============================================================================== %
\subsubsection{Musket Adept} \label{tal::musketadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Quickly picking up on new trends, you gambled on muskets and their stopping power early on.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with muskets.
\paragraph{RANK 2} While you have a two-handed firearm equipped, you have advantage on rolls against effects that would move you.
\paragraph{RANK 3} You learn the Buttstroke technique.

% ============================================================================== %
\subsubsection{Naturalist} \label{tal::naturalist}
\small{\textcolor{gray}{Nature}}

\normalsize
Your appreciation for nature has led you to attain an extensive categorical knowledge of plants and animals, giving you a great talent at recognizing and identifying them.
\paragraph{RANK 1} You are proficient with the Nature skill.
\paragraph{RANK 2} Provided you are familiar with the local flora and fauna from experience or a guide, you don't need to make an ability check to identify common plants, fungi, animals, and insects.
\paragraph{RANK 3} Your group can't become lost except by magical means.

% ============================================================================== %
\subsubsection{Observant} \label{tal::observant}
\small{\textcolor{gray}{Perception}}

\normalsize
Easily distracted, you are always attentive of the details in your surroundings.
\paragraph{RANK 1} You are proficient with the Perception skill.
\paragraph{RANK 2} You can easily spot a person you know in a crowd or an object you're familiar with among many.
\paragraph{RANK 3} Being in a lightly obscured area doesn't impose disadvantage on your Wisdom (Perception) checks if you can both see and hear.

% ============================================================================== %
