% !TEX root = ../main.tex
\subsubsection{Sharpshooter} \label{tal::sharpshooter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You can strike a foe with an arrow or bullet no matter where they are in the battlefield.
\paragraph{REQUIREMENTS} Bow Adept 2 or Musket Adept 2.
\paragraph{RANK 1} If you do not move during your turn, you can make an additional ranged weapon attack as a bonus action.
\paragraph{RANK 2} Both your normal and long ranges are multiplied by 1.5 for all ranged weapons..
\paragraph{RANK 3} Whenever you have advantage on a ranged attack roll using Dexterity, you can reroll one of the dice once.

% ============================================================================== %
\subsubsection{Shield Master} \label{tal::shieldmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You know that fighting to the death leads to a short life.
You trust your shield with your life, and you are an expert at avoiding death.
\paragraph{REQUIREMENTS} Shield Training 2.
\paragraph{RANK 1} If you aren't incapacitated, you can add your shield's AC bonus to any Dexterity saving throw you make against a spell or other harmful effect that targets only you.
\paragraph{RANK 2} If you are subjected to an effect that allows you to make a Dexterity saving throw to take only half damage, you can use your reaction to take no damage if you succeed on the saving throw, interposing your shield between yourself and the source of the effect.
\paragraph{RANK 3} When you use the Shove action or the Push technique with your shield, you can choose to force the Prone condition on your target instead of pushing it.

% ============================================================================== %
\subsubsection{Shield Training} \label{tal::shieldtraining}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Your prefer to live a long life, and choose to carry your trusty shield with you at all times.
\paragraph{RANK 1} You gain proficiency with medium shields.
\paragraph{RANK 2} In combat, you can don or doff a medium shield as a bonus action instead of an action.
\paragraph{RANK 3} You learn the Push technique.

% ============================================================================== %
\subsubsection{Shooter} \label{tal::shooter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You have mastered ranged weapons and can make shots that others find impossible.
\paragraph{REQUIREMENTS} Proficiency with at least two martial ranged weapon types.
\paragraph{RANK 1} Your ranged attacks ignore half cover and three-quarters covers.
\paragraph{RANK 2} Increase your Dexterity by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Leg Shot technique.

% ============================================================================== %
\subsubsection{Silver-tongued} \label{tal::silvertongued}
\small{\textcolor{gray}{Deception}}

\normalsize
You develop your conversational skill to better deceive others.
\paragraph{REQUIREMENTS} Liar 3.
\paragraph{RANK 1} You double your proficiency modifier in the Deception skill.
\paragraph{RANK 2} You learn the Deceive technique.
\paragraph{RANK 3} Increase your Charisma score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Skulker} \label{tal::skulker}
\small{\textcolor{gray}{Stealth}}

\normalsize
You are expert at slinking through shadows.
\paragraph{REQUIREMENTS} Sly 3.
\paragraph{RANK 1} You double your proficiency modifier in the Stealth skill.
\paragraph{RANK 2} Making a melee or range attack alerts your target, but doesn't immediately reveal your position.
\paragraph{RANK 3} You gain or improve the Sneak Attack technique.

% ============================================================================== %
\subsubsection{Slasher} \label{tal::slasher}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Your experience with blades has taught you where to cut to have the greatest results.
\paragraph{REQUIREMENTS} Proficiency with at least two martial slashing weapon types.
\paragraph{RANK 1} Once per turn when you hit a creature with an attack that deals slashing damage, you can reduce the speed of the target by 3 meters until the start of your next turn.
\paragraph{RANK 2} Increase your Strength or Dexterity by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Grievous Wound technique.

% ============================================================================== %
\subsubsection{Sly} \label{tal::sly}
\small{\textcolor{gray}{Stealth}}

\normalsize
One with shadows, you can always escape from the most unfavorable situations.
You have a natural ease melding with the dark, and intuitively know how to avoid making any noise.
\paragraph{RANK 1} You are proficient with the Stealth skill.
\paragraph{RANK 2} You can try to hide when you are lightly obscured from the creature from which you are hiding.
\paragraph{RANK 3} You gain advantage on any Dexterity (Stealth) check if you move no more than half your speed on the same turn.

% ============================================================================== %
\subsubsection{Sniper} \label{tal::sniper}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Learned in the use of most ranged weapons, you are an expert at piercing foes from afar.
\paragraph{REQUIREMENTS} Bow Adept 2, Crossbow Adept 2, and Musket Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with bows, crossbows, pistols, and muskets.
\paragraph{RANK 2} Attacking at long range doesn't impose disadvantage on your ranged weapon attack rolls.
\paragraph{RANK 3} You learn the Hemorrhaging Attack technique.

% ============================================================================== %
\subsubsection{Spear Adept} \label{tal::spearadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Trained in the art of the spear, you know that nothing beats a long pole with a pointy end.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with spears.
\paragraph{RANK 2} Spears have the finesse property for you.
\paragraph{RANK 3} You learn the Feint technique.

% ============================================================================== %
\subsubsection{Staff Fighter} \label{tal::stafffighter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You have mastered the nuances of fighting with a staff.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} The staff counts as a finesse weapon for you.
\paragraph{RANK 2} While wielding a staff, you can use your bonus action to give yourself advantage on your next Dexterity (Acrobatics) or Strength (Athletics) check related to climbing, jumping, or otherwise bypassing obstacles.
This benefit lasts until the end of your turn.
\paragraph{RANK 3} You learn the Sweep technique.

% ============================================================================== %
\subsubsection{Stone Piercer} \label{tal::stonepiercer}
\small{\textcolor{gray}{Strength}}

\normalsize
You know that the difference between piercing stone and crushing bone lies only in the morals of the aggressor.
\paragraph{REQUIREMENTS} Pick Adept 2 and Athlete 2.
\paragraph{RANK 1} You double your damage dice against objects and structures while attacking with a pick.
Additionally, you have advantage on checks made with a climber's kit and pitons.
\paragraph{RANK 2} When you score a critical hit that deals piercing damage to a creature, you can roll one additional damage die when determining the extra piercing damage the target takes.
\paragraph{RANK 3} You learn the Injure technique.

% ============================================================================== %
\subsubsection{Straight Sword Adept} \label{tal::straightswordadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You are proficient with the traditional fighting style of straight swords.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with straight swords.
\paragraph{RANK 2} When you are wielding a straight sword in one hand and no other weapons, you gain a +1 to AC.
% As a free action at the start of your turn, you can choose to reduce your chance to hit by 2, while increasing your AC by 1 until the start of your next turn.
\paragraph{RANK 3} You learn the Block technique.

% ============================================================================== %
\subsubsection{Survivor} \label{tal::survivor}
\small{\textcolor{gray}{Survival}}

\normalsize
As if raised by wolves, you are a natural survivor in the most harsh of circumstances.
Your enviable endurance and experience allows you to be particularly effective at building shelter, purifying water, and foraging food.
\paragraph{RANK 1} You are proficient with the Survival skill.
\paragraph{RANK 2} When you forage, you find twice as much food as you normally would.
\paragraph{RANK 3} You have advantage on Wisdom (Survival) checks made to track creatures.

% ============================================================================== %
\subsubsection{Sword Master} \label{tal::swordmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You have an insight unique to those who master the many types of swords.
Your skill with the long blades is unparalleled, and your resoluteness in combat scares even the bravest of warriors.
\paragraph{REQUIREMENTS} Straight Sword Adept 2, Curved Sword Adept 2, and Light Sword Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with swords.
\paragraph{RANK 2} When you make an opportunity attack with a sword, you have advantage on the attack roll.
\paragraph{RANK 3} You learn the Parrying Stance technique.

% ============================================================================== %
\subsubsection{Swashbuckler} \label{tal::swashbuckler}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Like modern fighters, you mix your combat style with both melee and ranged attacks.
However, you gain the upper hand on them by adding a fair share of cheap tactics to this mix.
\paragraph{REQUIREMENTS} Curved Sword Adept 2 and Crossbow Adept 2, or Light Sword Adept 2 and Crossbow Adept 2.
\paragraph{RANK 1} When you use the Attack action and attack with a one-handed weapon, you can use a bonus action to attack with a hand crossbow or a loaded firearm you are holding.
\paragraph{RANK 2} During your turn, if you make a melee attack against a creature, that creature can't make opportunity attacks against you for the rest of your turn.
\paragraph{RANK 3} You learn the Cheap Shot technique.

% ============================================================================== %
\subsubsection{Theologian} \label{tal::theologian}
\small{\textcolor{gray}{Religion}}

\normalsize
Your extensive study of religion and the tides rewards you with many benefits.
\paragraph{REQUIREMENTS} Pious 3.
\paragraph{RANK 1} You double your proficiency modifier in the Religion skill.
\paragraph{RANK 2} You have advantage on Charisma (Persuasion) and Charisma (Deception) checks against creatures of your same tide.
You must know the tide of the creature to get this benefit.
\paragraph{RANK 3} Increase your Intelligence score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Thrown Weapon Master} \label{tal::thrownweaponmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Born with quick fingers and good aim, you're an expert at piercing your enemies with thrown objects.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} Attacking at long range doesn't impose disadvantage on your thrown weapon attack rolls.
\paragraph{RANK 2} When you throw a thrown weapon as an attack roll, you can draw another thrown weapon freely.
\paragraph{RANK 3} You learn the Quick Draw technique.

% ============================================================================== %
\subsubsection{Tracker} \label{tal::tracker}
\small{\textcolor{gray}{Survival}}

\normalsize
You have spent enough time hunting to hone your skill to a venerable level.
\paragraph{REQUIREMENTS} Survivor 3.
\paragraph{RANK 1} You double your proficiency modifier in the Survival skill.
\paragraph{RANK 2} You learn the Mark technique.
\paragraph{RANK 3} Increase your Wisdom score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Tree Feller} \label{tal::treefeller}
\small{\textcolor{gray}{Strength}}

\normalsize
Nature is your foe, and you use your broad axe to fell both trees and foes.
\paragraph{REQUIREMENTS} Axe Adept 2.
\paragraph{RANK 1} When you use a broad axe, its damage die changes from a d8 to a d10, and from a d10 to a d12 when wielded with two hands.
\paragraph{RANK 2} While wielding a broad axe, you deal double damage to structures and items.
\paragraph{RANK 3} Whenever you hit a plant or a plant creature with a slashing weapon, the target takes an additional 2 slashing damage.

% ============================================================================== %
\subsubsection{Two-weapon Master} \label{tal::twoweaponmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your ability to wield two weapons is unparalleled, and you can surprise any foe with your quick steps and unrelenting strikes.
\paragraph{REQUIREMENTS} Dexterity 16. Dual Wielder 2.
\paragraph{RANK 1} You can use use two-weapon fighting even when the one-handed melee weapons you are wielding aren't light.
\paragraph{RANK 2} You gain a +1 bonus to AC while you are wielding a separate melee weapon in each hand.
\paragraph{RANK 3} You can add your ability modifier to the damage of the bonus attack of your two-weapon fighting action.

% ============================================================================== %
\subsubsection{Unarmed Artist} \label{tal::unarmedartist}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are a painter.
Your hands are your brush, your opponent your canvas.
\paragraph{RANK 1} Your unarmed strike uses a d4 + your Dexterity modifier for damage.
You can only use this ability if you're not using a fist weapon.
\paragraph{RANK 2} When you use the Attack action, you can make an unarmed strike as a bonus action.
\paragraph{RANK 3} You get access to one Martial Arts technique of your choice.
You may buy this rank again to attain new Martial Arts techniques as long as you have not learned all available techniques.

% ============================================================================== %
\subsubsection{Unarmored} \label{tal::unarmored}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your extensive physical training allows to forfeit armor when fighting.
Your body is the only armor you need.
\paragraph{REQUIREMENTS} Acrobat 2 and Athlete 2.
\paragraph{RANK 1} As long as you are not wearing any armor, your speed increases by 3 meters.
\paragraph{RANK 2} If you are subjected to an effect that allows you to make a Dexterity saving throw to take only half damage, you can use your reaction to take no damage if you succeed on the saving throw, and half damage if you fail.
You only get this bonus while wearing no armor or light armor.
\paragraph{RANK 3} You learn the Rush technique.

% ============================================================================== %
