\subsubsection{Way of the Fist} \label{tal::wayofthefist}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Either by meditative training or drunken fighting, you are a master with your fists.
\paragraph{REQUIREMENT} Pugilist 2 and Unarmed Artist 2.
\paragraph{RANK 1} Your unarmed strike uses a d6 + your Strength or Dexterity modifier for damage.
\paragraph{RANK 2} When you get a critical hit with an unarmed strike, you can take the Disarm, Disengage, or Shove action as a free action.
\paragraph{RANK 3} You are never unarmed, for your fists are your weapons.
Your unarmed strikes deal double stamina damage.

% ============================================================================== %
\subsubsection{Whip Adept} \label{tal::whipadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are learned in the use of the whip, using your unique weapon for both combat and support.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You can use your bonus action to make one melee attack with an equipped whip.
\paragraph{RANK 2} You can use a whip to extend the range of the Grapple and Shove actions to the range of the weapon.
\paragraph{RANK 3} You can use your whip as an elongated appendage to perform actions that do not require fine motor skills.
This includes object interactions, such as grabbing a sword or pulling a bag towards you, and ability checks, such as an acrobatics roll to grab a nearby support beam to swing from.

% ============================================================================== %
\subsubsection{Wrestler} \label{tal::wrestler}
\small{\textcolor{gray}{Strength}}

\normalsize
Every part of your body is a weapon and you wield it expertly.
\paragraph{REQUIREMENTS} Grappler 2 and Combat Improviser 2.
\paragraph{RANK 1} Once per round, as part of your action, you many deal your Strength modifier in damage to any creature you are grappling.
\paragraph{RANK 2} You can use a grappled creature of a size equal or lower to yours as an improvised weapon.
\paragraph{RANK 3} You learn the Charge technique.

% ============================================================================== %
