% !TEX root = ../main.tex
\subsection*{Piety \& Boons} \label{ssec::pietyandboons}
Being a god's champion carries no benefits in and of itself.
The gods do reward the devotion of their champions, though.
The strength of your devotion to your god is measured by your piety score.
As you increase that score, you gain blessings from your god.

Piety has nothing to do with faith or belief, except insofar as a person's thoughts and ideals drive them to action in a god's service.
Your piety score reflects the actions you have taken in your god's service --- actions that the god richly rewards.

When you choose a god to worship, your piety score related to that god is 0.
Your piety score increases by 1 when you do something to advance the god's interests or behave in accordance with the god's ideals.
The gods expect great deeds from their champions, so your piety score typically increases only when you accomplish a significant goal, make a significant sacrifice of your own self-interest, or otherwise when the DM sees fit.

The gods bestow favors on those who prove their devotion.
When your piety score crosses certain thresholds --- 3, 10, 25, and 50 --- you gain a benefit detailed in this section of your choice.
If your piety score exceeds and then falls below one of those thresholds, you lose the benefit you gained at the higher tier.

\subsubsection{Piety 3+}
    \subparagraph{Agonizing Strikes}
        You can add your Wisdom modifier to the damage of an attack.
        You can use this feature a number of times equal to your Wisdom modifier.
        You regain all expended uses of this feature when you finish a short rest.
    \subparagraph{Beast Speech}
        You can comprehend and verbally communicate with any creature with an Intelligence score of 5 or less.
    \subparagraph{Godly Influence}
        Your proficiency level in Persuasion and Deception is increased by 1.
    \subparagraph{Hero's Vigor}
        You gain 1d4 + 4 temporary hit points after you finish a short rest.
    \subparagraph{Nyx's Shield}
        While you're not wearing an armor, your AC is 12 + your Dexterity modifier.
        You can use a shield and retain this benefit.
    \subparagraph{Pact Weapon}
        During a long rest, you mark a weapon of your choice as a symbol to your god.
        That weapon is infused with your god's power, gaining a +1 bonus to attack and damage rolls for you until you finish a long rest.
    \subparagraph{Unyielding Sight}
        You can see in darkness to a distance of 24 meters.

\pagebreak

\subsubsection{Piety 10+}
    \subparagraph{A God's Gaze}
        Once per short rest, you can use an action to see through solid objects and darkness up to a range of 6 meters.
        This effect lasts for a minute.
    \subparagraph{Fagalian Cloak}
        Once per short rest, you can activate a godly aura to a radius of 1-meter around yourself as an action.
        You gain advantage on Intimidation checks while the aura is active, and all unfriendly creatures in the aura take necrotic damage equal to your Wisdom modifier (minimum of 1) at the start of their turns.
        This effect lasts for a minute or until you dismiss it as an action.
    \subparagraph{Freedom of Movement}
        You cannot be affected by difficult terrain, and your speed cannot be reduced except when you are restrained.
    \subparagraph{Godly Gift}
        You gain access to one spell with a spell point cost equal to 0.
        The spell is chosen by your DM, and pertains to your god.
    \subparagraph{Heavenly Protection}
        Once per short rest, you can negate all damage from one attack made against you as a reaction.
        You can use this ability after you know how much damage the attack would make.
    \subparagraph{Hero's Smite}
        All your successful melee attacks deal 1 force damage in addition to their normal damage.
    \subparagraph{Nyx's Veil}
        When you are in dim light or darkness, you can use two actions to become invisible.
        This invisibility remains until you take an action or reaction.

\subsubsection{Piety 25+}
    Your two boons are improved in a manner chosen by your DM.
    In addition, you can change one or both of your previously selected boons.

\subsubsection{Piety 50+}
    An ability score of your choice is increased by 2, as is your maximum for that score.
    In addition, you become a champion of your god, and they can grant you an artifact pertaining to them.

\newpage
