\chapter{Spells}
% TODO: Add Charm Person (https://5e.tools/spells.html#charm%20person_phb) spell.
% TODO: Add Detect Thoughts (https://5e.tools/spells.html#detect%20thoughts_phb).
% TODO: Add Mage Hand (https://5e.tools/spells.html#mage%20hand_phb).
% TODO: Add Misty Step (https://5e.tools/spells.html#misty%20step_phb).
% TODO: Add Invisibility (https://5e.tools/spells.html#invisibility_phb).
% TODO: Add Slow and Haste.
% TODO: Add Alter Self (https://5e.tools/spells.html#alter%20self_phb).
% TODO: Add Confusion.
\DndSpellHeader%
    {Beautiful Typesetting}
    {4th-level illusion}
    {1 action}
    {5 feet}
    {S, M (ink and parchment, which the spell consumes)}
    {Until dispelled}
You are able to transform a written message of any length into a beautiful scroll. All creatures within range that can see the scroll must make a wisdom saving throw or be charmed by you until the spell ends.

While the creature is charmed by you, they cannot take their eyes off the scroll and cannot willingly move away from the scroll. Also, the targets can make a wisdom saving throw at the end of each of their turns. On a success, they are no longer charmed.

% ============================================================================== %
\DndSpellHeader % Only available to Moonborn Oths.
    {Light \label{spell::light}}
    {Moonborn cantrip}
    {1 action}
    {Touch}
    {M (a firefly or a gram of silver moss)}
    {1 hour}
You touch one object that is no larger than 3 meters in any dimension.
Until the spell ends, the object sheds bright light in a 9-meter radius and dim light for an additional 9 meters.
The light is of a pale blue color.
Completely covering the object with something opaque blocks the light.
The spell ends if you cast it again or dismiss it as an action.

If you target an object held or worn by a hostile creature, that creature must succeed on a Dexterity saving throw to avoid the spell.

% ============================================================================== %
\DndSpellHeader % Only available to Moonborn Oths.
    {Faerie Fire \label{spell::faeriefire}}
    {Moonborn 1st-level spell}
    {1 action}
    {Self}
    {S (forewings)}
    {1 minute}
You flutter your forewings, spreading a blue dust into the air.
Each object in a 9-meter radius around you is outlined in a pale blue light.
Any creature in the area when the spell is cast is also outlined in the light.
For the duration, objects and affected creatures shed dim light in a 6-meter radius.

Any attack roll against an affected creature or object has advantage if the attacker can see it, and the affected creature or object can't benefit from being invisible.

A creature can try to shake off the dust as an action by succeeding on a Dexterity saving throw.
The dust stops glowing after a minute.

% ============================================================================== %
\DndSpellHeader % Only available to Moonborn Oths.
    {Glitterdust \label{spell::glitterdust}}
    {Moonborn 2nd-level spell}
    {1 action}
    {Self}
    {S (hindwings)}
    {1 minute}
You flutter your hindwings, spreading a white dust into the air.
A cloud of golden particles covers everyone and everything within a 3-meter radius around you.
All creatures and objects within the area are covered by the dust, which cannot be removed and continues to sparkle until it fades.

For the duration, any target covered by the dust has disadvantage on Dexterity (Stealth) checks, and gains no benefit from being invisible.

Each creature targeted must succeed on a Wisdom saving throw or become blinded for the duration.
The creature can repeat its saving throw at the end of each of its turns, ending the blindness on a success.

% ============================================================================== %
\DndSpellHeader % Only available to Chu'ash Oths.
    {Dancing Lights \label{spell::dancinglights}}
    {Chu'ash cantrip}
    {1 action}
    {36 meters}
    {M (a firefly or a gram of silver moss)}
    {1 hour}
You create up to four torch-sized pale blue orbs within range that hover in the air for the duration.
You can also combine the four lights into one glowing object vaguely resembling a creature of Medium size.
Each light sheds dim light in a 6-meter radius.

As a bonus action on your turn, you can move the lights up to 18 meters to a new spot within range.
A light must be within 6 meters of another light created by this spell, and a light winks out if it exceeds the spell's range.

% ============================================================================== %
\DndSpellHeader % Only available to Chu'ash Oths.
    {Color Spray \label{spell::colorspray}}
    {Chu'ash 1st-level spell}
    {1 action}
    {Self (9-meter cone)}
    {S (hindwings)}
    {1 round}
A dazzling array of flashing, pale-colored light springs from your hindwings.
Roll a number of d10s equal to double your total number of hit dice; the total is how many hit points of creatures this spell can effect.
Creatures in a 9-meter cone originating from you are affected in a ascending order of their current hit points (ignoring unconscious creatures and creatures that can't see).

Starting with the creature that has the lowest current hit points, each creature affected by this spell is blinded until the end of your next turn.
Subtract each creature's hit points from the total before moving on to the creature with the next lowest hit points.
A creature's hit points must be equal to or less than the remaining total for that creature to be affected.

% ============================================================================== %
\DndSpellHeader % Only available to Chu'ash Oths.
  {Blur \label{spell::blur}}
  {Chu'ash 2nd-level spell}
  {1 action}
  {Self}
  {S (forewings)}
  {Concentration, up to 1 minute}
You flutter your forewings in a frantic manner, lifting a refracting golden dust around you.
Your body becomes blurred, shifting and wavering to all who can see you.
For the duration, any creature has disadvantage on attack rolls against you.
An attacker is immune to this effect if it doesn't rely on sight, as with blindsight, or can see through illusions, as with truesight.

% NOTE: This thing? I like it.
% https://www.reddit.com/r/DnDHomebrew/comments/p1qvw6/motleys_high_the_drunken_version_of_haste_you/
