% !TEX root = ../main.tex
\section{Food, Drink, and Lodging} \label{sec::fooddrinkandlodging}
\begin{table*}[b]%
    \begin{DndTable}[width=\linewidth, header=Food and Lodging]{Xlccccc}
        \textbf{Food or Service} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
        \multicolumn{7}{l}{\hspace{0.5cm}\textit{Inn Stay (per day)}} \\
        Squalid              & ---       & --- &     7 fobs    & --- & ---  & PHB 158 \\
        Poor                 & ---       & --- &    10 fobs    & --- & ---  & PHB 158 \\
        Modest               & ---       & --- &    50 fobs    & --- & ---  & PHB 158 \\
        Comfortable          & ---       & --- &    80 fobs    & --- & ---  & PHB 158 \\
        Wealthy              & ---       & --- &     2 agnomas & --- & ---  & PHB 158 \\
        Aristocratic         & ---       & --- &     4 agnomas & --- & ---  & PHB 158 \\
        \multicolumn{7}{l}{\hspace{0.5cm}\textit{Services}} \\
        Coach cab between towns (per km) & --- & --- &  2 fobs    & --- & --- & PHB 159 \\
        Coach cab within a city          & --- & --- &  1 fob     & --- & --- & PHB 159 \\
        Skilled hireling (per day)       & --- & --- &  2 agnomas & --- & --- & PHB 159 \\
        Untrained Hireling (per day)     & --- & --- & 20 fobs    & --- & --- & PHB 159 \\
        Messenger (per km)               & --- & --- &  1 fob     & --- & --- & PHB 159 \\
        Road or gate toll                & --- & --- &  1 fob     & --- & --- & PHB 159 \\
        Ship's passage (per km)          & --- & --- &  5 fobs    & --- & --- & PHB 159 \\
        \multicolumn{7}{l}{\hspace{0.5cm}\textit{Food (per day)}} \\
        Animal Feed          & Mundane   & 1 &       5 fobs    & COO & 5 kg & PHB 157 \\
        Squalid              & Mundane   &  1  &     3 fobs    & COO & ---  & PHB 158 \\
        Poor                 & Mundane   &  1  &     6 fobs    & COO & ---  & PHB 158 \\
        Modest               & Mundane   &  1  &    30 fobs    & COO & ---  & PHB 158 \\
        Comfortable          & Mundane   &  1  &    50 fobs    & COO & ---  & PHB 158 \\
        Wealthy              & Mundane   &  1  &    80 fobs    & COO & ---  & PHB 158 \\
        Aristocratic         & Plain     &  1  &     2 agnomas & COO & ---  & PHB 158 \\
        Banquet (per person) & Common    & 1   &    10 agnomas & COO & ---  & PHB 158 \\
    \end{DndTable}
\end{table*}

\subsection*{Lifestyle Expenses}
    At the beginning of a week or month in a town or city, you choose a lifestyle choice and pay the price to sustain that lifestyle.
    The prices are listed per day, so multiply the cost by 6 for the cost of one week or by 24 for the cost of one month.
    % Your lifestyle might change from one period to the next, based on the funds you have at your disposal, or you might maintain the same lifestyle throughout your character's career.

    Your lifestyle choice can have consequences.
    Maintaining a wealthy lifestyle might help you make contacts with the rich and powerful, though you run the risk of attracting thieves.
    Likewise, living frugally might help you avoid criminals, but you are unlikely to make powerful connections.

    \paragraph{Wretched}
        You live in inhumane conditions.
        With no place to call home, you shelter wherever you can, sneaking into barns, huddling in old crates, and relying on the good graces of people better off than you.
        % A wretched lifestyle presents abundant dangers.
        % Violence, disease, and hunger follow you wherever you go.
        % Other wretched people covet your armor, weapons, and adventuring gear, which represent a fortune by their standards.
        % You are beneath the notice of most people.
    \paragraph{Squalid}
        You live in a leaky stable, a mud-floored hut just outside town, or a vermin-infested boarding house in the worst part of town.
        You have shelter from the elements, but you live in a desperate and often violent environment, in places rife with disease, hunger, and misfortune.
        % You are beneath the notice of most people, and you have few legal protections.
        % Most people at this lifestyle level have suffered some terrible setback.
        % They might be disturbed, marked as exiles, or suffer from disease.
    \paragraph{Poor}
        A poor lifestyle means going without the comforts available in a stable community.
        Simple food and lodgings, threadbare clothing, and unpredictable conditions result in a sufficient, though probably unpleasant, experience.
        Your accommodations might be a room in a flophouse or in the common room above a tavern.
        % You benefit from some legal protections, but you still have to contend with violence, crime, and disease.
        % People at this lifestyle level tend to be unskilled laborers, costermongers, peddlers, thieves, mercenaries, and other disreputable types.
    \paragraph{Modest}
        A modest lifestyle keeps you out of the slums and ensures that you can maintain your equipment.
        You live in an older part of town, renting a room in a boarding house, inn, or temple.
        You don't go hungry or thirsty, and your living conditions are clean, if simple.
        % Ordinary people living modest lifestyles include soldiers with families, laborers, students, priests, and the like.
    \paragraph{Comfortable}
        Choosing a comfortable lifestyle means that you can afford nicer clothing and can easily maintain your equipment.
        You live in a small cottage in a middle-class neighborhood or in a private room at a fine inn.
        You associate with merchants, skilled tradespeople, and military officers.
    \paragraph{Wealthy}
        Choosing a wealthy lifestyle means living a life of luxury, though you might not have achieved the social status associated with the old money of nobility or royalty.
        You live a lifestyle comparable to that of a highly successful merchant, a favored servant of the royalty, or the owner of a few small businesses.
        You have respectable lodgings, usually a spacious home in a good part of town or a comfortable suite at a fine inn.
        % You likely have a small staff of servants.
    \paragraph{Aristocratic}
        You live a life of plenty and comfort.
        You move in circles populated by the most powerful people in the community.
        You have excellent lodgings, perhaps a townhouse in the nicest part of town or rooms in the finest inn.
        % You dine at the best restaurants, retain the most skilled and fashionable tailor, and have servants attending to your every need.
        % You receive invitations to the social gatherings of the rich and powerful, and spend evenings in the company of politicians, guild leaders, high priests, and nobility.
        % You must also contend with the highest levels of deceit and treachery.

    % The wealthier you are, the greater the chance you will be drawn into political intrigue as a pawn or participant.
\subsection*{Meals} \label{ssec::meals}
    Unless otherwise specified, the prices listed for brews are for a feast, which feeds up to 8 creatures.
    Divide this by 8 for the price of one meal.

    A meal is consumed during the day, and its benefits (if any) last for the whole day.
    After cooked, the benefits associated to a meal last for one day, after which the food spoils.
    You can only be affected by one meal at the same time.

    \begin{table*}[b]%
        \begin{DndTable}[width=\linewidth, header=Meals]{Xlccccc}
            \textbf{Meal} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            Loaf of Bread    & Mundane & 1 &  8 fobs    & COO & ---  & PHB 158 \\
            Hunk of Cheese   & Plain   & 1 & 80 fobs    & COO & ---  & PHB 158 \\
            Rations (1 meal) & Plain   & 1 & 50 fobs    & COO & 1 kg & PHB 153 \\
            Chunk of Meat    & Common  & 1 & 24 agnomas & COO & ---  & PHB 158
        \end{DndTable}
    \end{table*}

    % Food: Chili that gives Investiture of Flame

    % Ioun's Stone Pig % Random Ioun strong --- randomized when drinking.
    % Heroes Feast % Heroes Feast spell.
\newpage~\newpage
\subsection*{Brews} \label{ssec::brews}
    % TODO. Brews require a TON of balance and to reference the correct sources.
    The prices listed for brews are for a small keg, which fits 8 tankards worth of brew.
    Divide this by 8 for the price of a tankard, or by 16 for the price of a cup.
    Prices consider only the brew itself, not the medium of transportation.

    It takes one minute to drink a brew and gain its benefits, which can be done at the end of a short rest.
    You can only be affected by one brew at the same time.
    % After drinking a brew a creature rolls a DC 8 Constitution saving throw.
    % On a failure, it empties the content of the brew

    \begin{table*}[b]%
        \begin{DndTable}[width=\linewidth, header=Brews]{Xlccccc}
            \textbf{Brew} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            Ale                      & Mundane   & 2 &      20 fobs    & BRE &  4 kg   & PHB 158 \\
            Common Wine              & Plain     & 1 &       3 agnomas & BRE &  4 kg   & PHB 158 \\
            Ale of Heroism           & Common    & 3 &      50 agnomas & BRE &  4 kg   & --- \\
            Dozing Wine              & Common    & 3 &      50 agnomas & BRE &  4 kg   & --- \\
            Exalted Beer             & Common    & 3 &      50 agnomas & BRE &  4 kg   & --- \\
            Expeditious Brew         & Common    & 3 &      50 agnomas & BRE &  4 kg   & --- \\
            Laughing Ale             & Common    & 3 &      50 agnomas & BRE &  4 kg   & --- \\
            Beer of Vitality         & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Brew of Absorption       & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Brew of Giant's Strength & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Calming Wine             & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Dead Man's Ale           & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Fine Wine                & Uncommon  & 2 &     200 agnomas & BRE &  4 kg   & PHB 158 \\
            Madman Wine              & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Speaker's Whiskey        & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Thassa's Mockery         & Uncommon  & 3 &     250 agnomas & BRE &  4 kg   & --- \\
            Breathkiller             & Rare      & 3 &   2,500 agnomas & BRE &  4 kg   & --- \\
            Brew of Clairvoyance     & Rare      & 3 &   2,500 agnomas & BRE &  4 kg   & --- \\
            Brew of Invulnerability  & Rare      & 3 &   2,500 agnomas & BRE &  4 kg   & --- \\
            Brew of Letargy          & Rare      & 3 &   2,500 agnomas & BRE &  4 kg   & --- \\
            Brew of Maximum Power    & Rare      & 3 &   2,500 agnomas & BRE &  4 kg   & EGW 268 \\
            Mindblower               & Rare      & 3 &   2,500 agnomas & BRE &  4 kg   & --- \\
            Soulcatcher (Bottle)     & Rare      & 8 &   5,000 agnomas & BRE &  0.5 kg & --- \\
            Brainbender              & Very Rare & 3 &  25,000 agnomas & BRE &  4 kg   & --- \\
            Brew of Vitality         & Very Rare & 3 &  25,000 agnomas & BRE &  4 kg   & --- \\
            Brew of Speed            & Very Rare & 3 &  25,000 agnomas & BRE &  4 kg   & --- \\
            Erebos' Ooze (Jar)       & Very Rare & 8 &  50,000 agnomas & BRE &  1 kg   & ERLW 278 \\
            Kickstarter (Bottle)     & Very Rare & 8 &  50,000 agnomas & BRE &  0.5 kg & --- \\
            Dancer's Whiskey         & Legendary & 3 & 125,000 agnomas & BRE &  4 kg   & --- \\
            Groundshaker             & Legendary & 3 & 125,000 agnomas & BRE &  4 kg   & --- \\
            Purphoros' Maker         & Legendary & 3 & 125,000 agnomas & BRE &  4 kg   & --- \\
            Seer's Vodka             & Legendary & 3 & 125,000 agnomas & BRE &  4 kg   & ---
        \end{DndTable}
    \end{table*}

    \paragraph{Ale of Heroism} % Heroism
        This ale is honey-flavored, reminding you of those most important to you.
        A creature who drinks this is imbued with bravery.
        For an hour, the creature is immune to being frightened and gains 1 temporary hit point at the start of each of its turns.
        After the hour passes, the creature loses all temporary hit points gained from this brew.
    \paragraph{Beer of Vitality} % Aid
        This beer emboldens creatures with toughness and resolve.
        The drinker's hit point maximum and current hit points increase by 5 for 8 hours.
    \paragraph{Brainbender} % Confusion
        This brew is a nut-flavored greenish liquid.
        The liquid assaults and twists creatures' minds, spawning delusions and provoking uncontrolled action.
        Each creature that drinks the brew must succeed on a DC 16 Wisdom saving throw or be affected by it for an hour.

        An affected target can't take reactions and must roll a d10 at the start of each of its turns to determine its behavior for that turn.

        \begin{DndTable}[width=\linewidth, header=Confusion Behaviour]{lX}
            \textbf{d10} & \textbf{Behaviour} \\
            1            & The creature uses all its movement to move in a random direction. To determine the direction, roll a d8 and assign a direction to each die face.
            The creature doesn't take any other action this turn. \\
            2-6	         & The creature doesn't move or take actions this turn. \\
            7-8	         & The creature uses its action to make a melee attack against a randomly determined creature within its reach.
            If there is no creature within its reach, the creature does nothing this turn. \\
            9-10         & The creature can act and move normally.
        \end{DndTable}

        Every 10 minutes, an affected creature can make a DC 16 Wisdom saving throw.
        If it succeeds, this effect ends for that it.
    \paragraph{Breathkiller} % Stinking Cloud
        This atrocity of a brew is a yellow muddy liquid that leaves a terrible itching sensation upon passing through your throat.
        After drinking it, a creature becomes surrounded by a 6-meter-radius sphere of yellow, nauseating gas centered on itself.
        The cloud spreads around corners, and its area is heavily obscured.
        The cloud lingers in the air for an hour after the brew is drunk.

        Each creature that is completely within the cloud at the start of its turn must make a DC 14 Constitution saving throw against poison.
        On a failed save, the creature spends its action that turn retching and reeling.
        Creatures that don't need to breathe or are immune to poison automatically succeed on this saving throw.
    \paragraph{Brew of Absorption} % Absorb Elements + Dragon's breath of the absorbed element
        This drink seems to remain in your throat after drinking it, ready to return to the world on command.
        When the drinker takes acid, cold, fire, lightning, or poison damage within 8 hours of drinking the brew, it can use its reaction to gain resistance against the attack.
        As part of the same reaction, it can then exhale energy in a 4.5 meter cone.
        Each creature in the area must make a DC 12 Dexterity saving throw, taking 3d6 damage of the absorbed type on a failed save, or half as much damage on a successful one.
        The drinker can only use this ability once during the brew's duration.
    \paragraph{Brew of Clairvoyance} % Clairvoyance
        An eyeball bobs in this yellowish vodka but vanishes as the brew is drunk.
        Upon drinking this brew, you create an invisible sensor within 2 kilometers in a location familiar to you (a place you have visited or seen before) or in an obvious location that is unfamiliar to you (such as behind a door, around a corner, or in a grove of trees).
        The sensor remains in place for the duration, and it can't be attacked or otherwise interacted with.

        You can see and hear through the sensor as if you were in its space.

        A creature that can see the sensor (such as a creature with truesight) sees a luminous, intangible orb about the size of your fist.

        The sensor remains in position for 8 hours, after which it disappears.
    \paragraph{Brew of Giant Strength}
        This brew's transparent liquid has floating in it a sliver of fingernail from a cyclops.
        When you drink it, your Strength score changes to 21 for 1 hour.
        The potion has no effect on you if your Strength is equal to or greater than that score.
    \paragraph{Brew of Invulnerability}
        This syrupy liquid looks like liquefied iron.
        For an hour after drinking it, you have resistance to all physical damage.
    \paragraph{Brew of Letargy} % Slow
        This thick whiskey seems to flow slower than naturally possible.
        After drinking it, a creature must succeed on a DC 14 Wisdom saving throw or be affected by this brew for an hour.

        An affected target's speed is halved, it takes a -2 penalty to AC and Dexterity saving throws, and it can't use reactions.
        On its turn, it has only 2 actions instead of the normal 3.

        If the creature attempts to cast a spell with a casting time of 2 or more actions, roll a d20.
        On an 11 or higher, the spell doesn't take effect until the creature's next turn, and the creature must use its actions on that turn to complete the spell.
        If it can't, the spell is wasted.

        A creature affected by this brew makes another DC 14 Wisdom saving throw every 10 minutes.
        On a successful save, the effect ends for it.
    \paragraph{Brew of Maximum Power}
        This glowing purple liquid smells of sugar and plum, but it has a muddy taste.

        The first time you cast a damage-dealing spell of 4th level or lower within an hour after drinking the brew, instead of rolling dice to determine the damage dealt, you can instead use the highest number possible for each die.
    \paragraph{Brew of Speed} % Haste
        This black liquid flows faster than what seems reasonable.
        For an hour, the drinker's speed is doubled, it gains a +2 bonus to AC, it has advantage on Dexterity saving throws, and it gains an additional action on each of its turns.

        When the effect ends, the target can't move or take actions for a minute, as a wave of lethargy sweeps over it.
    \paragraph{Brew of Vitality} % Potion of Vitality
        The brew's crimson liquid regularly pulses with dull light, calling to mind a heartbeat.
        When you drink this brew, it removes any exhaustion you are suffering and cures any disease or poison affecting you.
        For the next 24 hours, you regain the maximum number of hit points for any Hit Die you spend.
    \paragraph{Calming Wine} % Calm Emotions
        This wine's fruity flavor seems to calm emotions on command.
        Any creature who drinks this rolls a DC 12 Charisma saving throw.
        A creature can choose to fail this saving throw if it wishes.
        If a creature fails, two effects occur with a duration of an hour:
        \begin{itemize}
            \item Any effect causing a target to be charmed or frightened is suppressed.
            When this effect ends, any suppressed effect resumes, provided that its duration has not expired in the meantime.
            \item The target feels indifferent about creatures that it is hostile toward.
            This indifference ends if the target is attacked or harmed by a spell or if it witnesses any of its friends being harmed.
            When the effect ends, the creature becomes hostile again, unless the DM rules otherwise.
        \end{itemize}

        A creature affected by this brew makes another DC 12 Charisma saving throw every 10 minutes.
        On a successful save, the effect ends for it.
    \paragraph{Dancer's Whiskey} % Otto's Irresistible Dance
        This fuzzy pink brew feels like small explosions happening inside your mouth.
        After finishing the brew, the drinker begins a comic dance in place: shuffling, tapping its feet, and capering for an hour.

        A dancing creature must use all its movement to dance without leaving its space and has disadvantage on Dexterity saving throws and attack rolls.
        While the target is affected by this brew, other creatures have advantage on attack rolls against it.
        Every 10 minutes, a dancing creature makes a DC 18 Wisdom saving throw to regain control of itself.
        On a successful save, the effect ends.
    \paragraph{Dead Man's Ale} % Blindness/Deafness
        This brew looks like common ale, hiding a terrible effect within.
        After drinking it, the creature rolls a DC 12 Constitution saving throw.
        If it fails, the target is blinded for an hour.

        A creature affected by this brew can makes another DC 12 Constitution saving throw every 10 minutes.
        On a successful save, the effect ends for it.
    \paragraph{Dozing Wine} % Sleep
        This wine is so comforting that it sends creatures into slumber.
        Any creature who drinks this must succeed on a DC 10 Constitution saving throw.
        On a failure, the creature falls unconscious for an hour, until the sleeper takes damage, or someone uses an action to shake or slap the sleeper awake.

        A creature affected by this brew makes another DC 10 Constitution saving throw every 10 minutes.
        On a successful save, the effect ends for it.
    \paragraph{Erebos' Ooze (Jar) $\odot$} \label{item::erebosooze} % Kyrzin's Ooze
        This opalescent, symbiotic goo comes sealed in a jar and slowly shifts and moves, as if endlessly exploring the jar's interior.
        You can attune to this item by drinking the contents of the jar, unlocking the following properties.

        \paragraph{Resistant} While attuned to Erebos' ooze, you have resistance to poison and acid damage, and you're immune to the poisoned condition.
        \paragraph{Amorphous} Using two actions, you can speak a command word and cause your body to assume the amorphous qualities of an ooze.
        For the next minute, you (along with any equipment you're wearing or carrying) can move through a space as narrow as 1 inch wide without squeezing.
        Once you use this property, it can't be used again until the next dawn.
        \paragraph{Acid Breath} Using two actions, you can exhale acid in a 6-meter line that is 1 meters wide.
        Each creature in that line must make a DC 15 Dexterity saving throw, taking 36 (8d8) acid damage on a failed save, or half as much damage on a successful one.
        Once you use this property, it can't be used again until the next dawn.
        \paragraph{Symbiotic Nature} The ooze can't be removed from you while you're attuned to it, and you can't voluntarily end your attunement to it.
        The only way to remove the ooze is by drinking an Oozekiller potion (see page \pageref{item::oozekiller}).

        If you die while the ooze is inside you, it bursts out and engulfs you, turning your corpse into a black pudding.
    \paragraph{Exalted Beer} % Bless
        The sweet flavor of this beer truly is a blessing.
        After drinking it, the creature can add a d4 to any attack roll or saving throw it makes for one hour.
    \paragraph{Expeditious Brew} % Expeditious Retreat
        This brew feels like caustic acid falling through your throat.
        After drinking it, the creature gains a bonus of 2 meters to its movement speed for one hour.
    \paragraph{Groundshaker} % Investiture of Stone
        Small bits of stone float aimlessly in this amber root beer.
        For an hour after drinking it, bits of rock spread across your body, and you gain the following benefits:
        \begin{itemize}
            \item You have resistance to bludgeoning, piercing, and slashing damage from nonmagical attacks.
            \item You can use your action to create a small earthquake on the ground in a 4.5-meter radius centered on you.
            Other creatures on that ground must succeed on a DC 18 Dexterity saving throw or be knocked prone.
            \item You can move across difficult terrain made of earth or stone without spending extra movement.
            You can move through solid earth or stone as if it was air and without destabilizing it, but you can't end your movement there.
            If you do so, you are ejected to the nearest unoccupied space, this effect ends, and you are stunned until the end of your next turn.
        \end{itemize}
    \paragraph{Kickstarter (Bottle)} % Awaken
        This color-changing thick liquid is said to contain the very essence of the tides.
        Any Huge or smaller beast with an intelligence of 3 or less can receive the effect of this potion.
        The target gains an Intelligence of 10.

        The awakened beast is charmed by you for 30 days or until you or your companions do anything harmful to it.
        When the charmed condition ends, the awakened creature chooses whether to remain friendly to you, based on how you treated it while it was charmed.

        After this period passes, the creature needs a qualar to remain sentient, and it suffers Dementia effects normally (See page \pageref{ssec::dementia}).
    \paragraph{Laughing Brew} % Tasha's Hideous Laughter
        This fuzzy and bubbly drink seems to vibrate with astounding speed.
        After drinking it, the creature perceives everything as hilariously funny and falls into fits of laughter.
        The creature must succeed on a DC 10 Wisdom saving throw or fall prone, becoming incapacitated and unable to stand up for up to an hour.
        A creature with an Intelligence score of 4 or less isn't affected.

        A creature affected by this brew makes another DC 10 Wisdom saving throw every 10 minutes and when it takes damage.
        The target has advantage on the saving throw if it's triggered by damage.
        On a success, the effect ends.
    \paragraph{Madman Wine} % Crown of Madness
        This wine looks normal, but has a somewhat odd flavor.
        A creature who drinks this must succeed on a DC 12 Wisdom saving throw or become charmed for a minute.
        While charmed, madness glows in the creature's eyes.

        The charmed creature must use its action before moving on each of its turns to make a melee attack against a creature other than itself within 1 meter of it chosen randomly.
        If no creatures are within reach, it moves towards the closest creature to attack it.

        The target can make a DC 12 Wisdom saving throw at the end of each of its turns.
        On a success, the effect ends.
    \paragraph{Mindblower} % Speak with Plants + Hallucinatory Terrain
        This brew is a clear liquid indistinguishable from water.
        Upon drinking it, you can communicate with any plant within 6 meters of you and issue it simple commands for 8 hours.
        You can question plants about events in the spell's area within the past day, gaining information about creatures that have passed, weather, and other circumstances.

        You can also turn difficult terrain caused by plant growth (such as thickets and undergrowth) into ordinary terrain that lasts for the duration.
        Or you can turn ordinary terrain where plants are present into difficult terrain that lasts for the duration, causing vines and branches to hinder pursuers, for example.

        Plants might be able to perform other tasks on your behalf, at the DM's discretion. The spell doesn't enable plants to uproot themselves and move about, but they can freely move branches, tendrils, and stalks.

        If a plant creature is in the area, you can communicate with it as if you shared a common language, but you gain no magical ability to influence it.

        This spell can cause the plants created by the entangle spell to release a restrained creature.

        While under the effect of this brew, all terrain looks hard to traverse, and your movement speed is halved.
    \paragraph{Purphoros' Maker} % Flesh to Stone
        Upon drinking this unassuming wine, a creature begins to turn into stone.
        If the drinker's body is made of flesh, the creature must make a DC 18 Constitution saving throw.
        On a failed save, it is restrained as its flesh begins to harden.
        On a successful save, the creature isn't affected.

        A creature restrained by this effect must make another DC 18 Constitution saving throw at the end of each of its turns.
        If it successfully saves against this brew three times, the effect ends.
        If it fails its saves three times, it is turned to stone and subjected to the petrified condition until the effect is removed.
        The successes and failures don't need to be consecutive; keep track of both until the target collects three of a kind.

        If the creature is physically broken while petrified, it suffers from similar deformities if it reverts to its original state.
    \paragraph{Seer's Vodka} % True Seeing
        Reflections in this clear vodka seem out of place, as if the turbulent liquid displaced light in turbulent ways.
        This brew gives the drinker the ability to see things as they actually are.
        For 8 hours, the creature has truesight, and notices secrets hidden by magic out to a range of 24 meters.
    \paragraph{Soulcatcher} % Revivify
        As two actions, you can force a creature that has died within the last minute to drink this liquid.
        That creature returns to life with 1 hit point.
        This spell can't return to life a creature that has died of old age, nor can it restore any missing body parts.
    \paragraph{Speaker's Whiskey} % Zone of Truth on a target
        This strong whiskey seems to pick at your brain, forcing you to feel remorse about your misdeeds.
        Any creature who drinks this must make a DC 12 Charisma saving throw.
        On a failed save, a creature can't speak a deliberate lie for an hour.
        A skilled brewer knows whether each creature succeeds or fails on its saving throw.

        An affected creature is aware of the effect and can thus avoid answering questions to which it would normally respond with a lie.
        Such creatures can be evasive in its answers as long as it remains within the boundaries of the truth.
    \paragraph{Thassa's Mockery} % Water Breathing
        This transparent vodka has fish scales floating in it, which must be drinked with the brew to gain its effect.
        This drinks grants a creature the ability to breathe underwater for 8 hours.
        Affected creatures also retain their normal mode of respiration.
\newpage
