% !TEX root = ../main.tex
\section{Poisons} \label{sec::poisons}
    Poisons are small amounts of dangerous liquids contained in a vial.
    Poisons have varied methods of application, which is the medium needed to administer the poison to a victim.

    Using two actions, you can coat one slashing or piercing weapon or three pieces of ammunition with poison.
    Poison can remain effective in a weapon for 1 minute after coating or until the weapon strucks a target three times.

    \begin{table*}[b]%
        \begin{DndTable}[width=\linewidth, header=Poisons]{Xccccccc}
            \textbf{Poison} & \textbf{Rarity} & \textbf{Method} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            Basic Poison          & Common    & Injury   &  1 &     30 agnomas & POI & --- & PHB  153 \\
            Assassin's Blood      & Uncommon  & Ingested &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Burnt Othur Fumes     & Uncommon  & Inhaled  &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Carrion Crawler Mucus & Uncommon  & Contact  &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Essence of Ether      & Uncommon  & Inhaled  &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Sprouting Poison      & Uncommon  & Injury   &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Malice                & Uncommon  & Inhaled  &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Oil of Taggit         & Uncommon  & Contact  &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Pale Tincture         & Uncommon  & Ingested &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Serpent Venom         & Uncommon  & Injury   &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Torpor                & Uncommon  & Ingested &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Truth Serum           & Uncommon  & Ingested &  1 &    150 agnomas & POI & --- & DMG  258 \\
            Midnight Tears        & Rare      & Ingested &  1 &  1,500 agnomas & POI & --- & DMG  258 \\
            Nidhogg Poison        & Rare      & Injury   &  1 &  1,500 agnomas & POI & --- & DMG  258 \\
            Wyvern Poison         & Rare      & Injury   &  1 &  1,200 agnomas & POI & --- & DMG  258 \\
            Erebos' Whisper       & Very Rare & Inhaled  &  1 & 15,000 agnomas & POI & --- & VRGR  83
        \end{DndTable}
    \end{table*}

    \paragraph{Assassin's Poison}
        A creature subjected to this poison must make a DC 10 Constitution saving throw.
        On a failed save, it takes 6 (1d12) poison damage and is poisoned for 24 hours.
        On a successful save, the creature takes half damage and isn't poisoned.
    \paragraph{Basic Poison} \label{item::basicpoison}
        You can use the poison in this vial to coat one slashing or piercing weapon or up to three pieces of ammunition.
        Applying the poison takes two actions.
        A creature hit by the poisoned weapon or ammunition must make a DC 10 Constitution saving throw or take 1d4 poison damage.
        Once applied, the poison retains potency for 1 minute before drying.
    \paragraph{Burnt Othur Fumes}
        A creature subjected to this poison must succeed on a DC 13 Constitution saving throw or take 10 (3d6) poison damage, and must repeat the saving throw at the start of each of its turns.
        On each successive failed save, the character takes 3 (1d6) poison damage.
        After three successful saves, the poison ends.
    \paragraph{Carrion Crawler Mucus}
        This poison must be harvested from a dead or incapacitated carrion crawler.
        A creature subjected to this poison must succeed on a DC 13 Constitution saving throw or be poisoned for 1 minute.
        The poisoned creature is paralyzed.
        The creature can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success.
    \paragraph{Essence of Ether}
        A creature subjected to this poison must succeed on a DC 15 Constitution saving throw or become poisoned for 8 hours.
        The poisoned creature is unconscious.
        The creature wakes up if it takes damage or if another creature takes two actions to shake it awake.
    \paragraph{Erebos' Whisper}
        A creature subjected to this poison must succeed on a DC 18 Constitution saving throw or experience a terrible nightmare the next time they sleep.
        Echoes of a phantasmal monstrosity spawn a nightmare that lasts the duration of the target's sleep and prevents the target from gaining any benefit from that rest.
        In addition, when the target wakes up, it takes 3d6 psychic damage.
    \paragraph{Sprouting Poison}
        This poison is typically made only in a place far removed from sunlight.
        A creature subjected to this poison must succeed on a DC 13 Constitution saving throw or be poisoned for 1 hour.
        If the saving throw fails by 5 or more, the creature is also unconscious while poisoned in this way.
        The creature wakes up if it takes damage or if another creature takes two actions to shake it awake.
    \paragraph{Malice}
        A creature subjected to this poison must succeed on a DC 15 Constitution saving throw or become poisoned for 1 hour.
        The poisoned creature is blinded.
    \paragraph{Midnight Tears}
        A creature that ingests this poison suffers no effect until the stroke of midnight.
        If the poison has not been neutralized before then, the creature must succeed on a DC 17 Constitution saving throw, taking 31 (9d6) poison damage on a failed save, or half as much damage on a successful one.
    \paragraph{Oil of Taggit}
        A creature subjected to this poison must succeed on a DC 13 Constitution saving throw or become poisoned for 24 hours.
        The poisoned creature is unconscious.
        The creature wakes up if it takes damage.
    \paragraph{Pale Tincture}
        A creature subjected to this poison must succeed on a DC 16 Constitution saving throw or take 3 (1d6) poison damage and become poisoned.
        The poisoned creature must repeat the saving throw every 24 hours, taking 3 (1d6) poison damage on a failed save.
        Until this poison ends, the damage the poison deals can't be healed by any means.
        After seven successful saving throws, the effect ends and the creature can heal normally.
    \paragraph{Serpent Venom}
        This poison must be harvested from a dead or incapacitated poisonous snake.
        A creature subjected to this poison must succeed on a DC 11 Constitution saving throw, taking 10 (3d6) poison damage on a failed save, or half as much damage on a successful one.
    \paragraph{Torpor}
        A creature subjected to this poison must succeed on a DC 15 Constitution saving throw or become poisoned for 4d6 hours.
        The poisoned creature is incapacitated.
    \paragraph{Truth Serum}
        A creature subjected to this poison must succeed on a DC 11 Constitution saving throw or become poisoned for 1 hour.
        The poisoned creature can't knowingly speak a lie.
    \paragraph{Wyvern Poison}
        This poison must be harvested from a dead or incapacitated wyvern.
        A creature subjected to this poison must make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on a failed save, or half as much damage on a successful one.
\newpage~\newpage
