% !TEX root = ../main.tex
\section{Wondrous Items} \label{sec::wondrousitems}
    \begin{table*}[b]%
        \begin{DndTable}[width=\linewidth, header=Wondrous Items]{Xcccccc}
            \textbf{Item} & \textbf{Rarity} & \textbf{Mats.} & \textbf{Total Cost} & \textbf{Tools} & \textbf{Weight} & \textbf{Source} \\
            Component Pouch                  & Common    & 1 &      25 agnomas & LEA & 1 kg   & PHB   151 \\
            Gem of Brightness                & Common    & 8 &     100 agnomas & JEW & 0.5 kg & DMG   171 \\
            Spell Scroll (Cantrip)           & Common    & 1 &      20 agnomas & CAL & ---    & DMG   199 \\
            Spell Scroll (1st-level)         & Common    & 2 &      30 agnomas & CAL & ---    & DMG   200 \\
            Spellbook                        & Common    & 3 &      50 agnomas & CAL & 1.5 kg & PHB   153 \\
            Decanter of Endless Water        & Uncommon  & 8 &     500 agnomas & GLA & 2 kg   & DMG   161 \\
            Fiend Sensor                     & Uncommon  & 4 &     300 agnomas & JEW & ---    & ---       \\
            Eversmoking Bottle               & Uncommon  & 8 &     500 agnomas & GLA & 0.5 kg & DMG   168 \\
            Firetrap                         & Uncommon  & 4 &     250 agnomas & GLA & 1 kg   & ---       \\
            Goggles of Night                 & Uncommon  & 8 &     500 agnomas & GLA & ---    & DMG   172 \\
            Pearl of Power                   & Uncommon  & 8 &     500 agnomas & JEW & ---    & DMG   184 \\
            Pharika's Ointment               & Uncommon  & 8 &     500 agnomas & COO & ---    & DMG   179 \\
            Spell Scroll (2nd-level)         & Uncommon  & 1 &     150 agnomas & CAL & ---    & DMG   201 \\
            Spell Scroll (3rd-level)         & Uncommon  & 2 &     200 agnomas & CAL & ---    & DMG   202 \\
            Stone of Good Luck               & Uncommon  & 8 &     500 agnomas & MAS & ---    & DMG   205 \\
            Stone of Ill Luck                & Uncommon  & 8 &     500 agnomas & MAS & ---    & TftYP 229 \\
            Zuan                             & Uncommon  & 1 &     150 agnomas & ALC & ---    & ---       \\
            Crystal Ball                     & Rare      & 8 &   5,000 agnomas & GLA & 1.5 kg & DMG   159 \\
            Feather Token: Anchor            & Rare      & 8 &   5,000 agnomas & JEW & ---    & DMG   188 \\
            Feather Token: Swan              & Rare      & 8 &   5,000 agnomas & CAR & ---    & DMG   188 \\
            Figurine of Wondrous Power       & Rare      & 8 &   5,000 agnomas & MAS & ---    & DMG   170 \\
            Folding Boat                     & Rare      & 4 &   3,000 agnomas & CAR & 2 kg   & DMG   170 \\
            Frithling Glass Home             & Rare      & 8 &   5,000 agnomas & GLA & 0.5 kg & ---       \\
            Gem of Seeing                    & Rare      & 8 &   5,000 agnomas & JEW & 0.5 kg & DMG   172 \\
            Horseshoes of Speed              & Rare      & 8 &   5,000 agnomas & SMI & ---    & DMG   175 \\
            Jamming Shackles                 & Rare      & 8 &   5,000 agnomas & CAR & ---    & DMG   165 \\
            Kruphix Stone (Rare)             & Rare      & 8 &   5,000 agnomas & MAS & ---    & DMG   176 \\
            Rod of Leadership                & Rare      & 8 &   5,000 agnomas & GLA & 1 kg   & DMG   197 \\
            Spell Scroll (4th-level)         & Rare      & 1 &   1,500 agnomas & CAL & ---    & DMG   203 \\
            Spell Scroll (5th-level)         & Rare      & 2 &   2,000 agnomas & CAL & ---    & DMG   204
        \end{DndTable}
    \end{table*}
    \begin{table*}[b]%
        \begin{DndTable}[width=\linewidth, header=Wondrous Items (Cont.)]{Xcccccc}
            Crystal of Absorption            & Very Rare & 8 &  50,000 agnomas & GLA & 1 kg.  & DMG   195 \\
            % Crystalline Chronicle            & Very Rare & 8 &  50,000 agnomas & GLA & 1.5 kg & TCE   124 \\
            Kruphix Stone (Very Rare)        & Very Rare & 8 &  50,000 agnomas & MAS & ---    & DMG   176 \\
            Manual of Bodily Health          & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   180 \\
            Manual of Gainful Exercise       & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   180 \\
            Manual of Golems                 & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   180 \\
            Manual of Quickness of Action    & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   181 \\
            Rod of Alertness                 & Very Rare & 8 &  50,000 agnomas & GLA & 1 kg   & DMG   196 \\
            Shard of Nuagal                  & Very Rare & 8 &  50,000 agnomas & GLA & 1 kg   & DMG   197 \\
            Spell Scroll (6th-level)         & Very Rare & 1 &  15,000 agnomas & CAL & ---    & DMG   205 \\
            Spell Scroll (7th-level)         & Very Rare & 2 &  20,000 agnomas & CAL & ---    & DMG   206 \\
            Spell Scroll (8th-level)         & Very Rare & 4 &  30,000 agnomas & CAL & ---    & DMG   207 \\
            Tome of Clear Thought            & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   209 \\
            Tome of Leadership and Influence & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   209 \\
            Tome of Understanding            & Very Rare & 8 &  50,000 agnomas & CAL & 2.5 kg & DMG   209 \\
            Crystal Ball of Mind Reading     & Legendary & 6 & 200,000 agnomas & GLA & 1.5 kg & DMG   159 \\
            Crystal Ball of Telepathy        & Legendary & 6 & 200,000 agnomas & GLA & 1.5 kg & DMG   159 \\
            Crystal Ball of True Seeing      & Legendary & 6 & 200,000 agnomas & GLA & 1.5 kg & DMG   159 \\
            Kruphix Stone (Legendary)        & Legendary & 8 & 250,000 agnomas & MAS & ---    & DMG   176 \\
            Pearl of Nightfall               & Legendary & 8 & 250,000 agnomas & JEW & ---    & EGW   268 \\
            Rod of Might                     & Legendary & 8 & 250,000 agnomas & GLA & 1.5 kg & DMG   196 \\
            Sovereign Glue                   & Legendary & 8 & 250,000 agnomas & COO & ---    & DMG   200 \\
            Spell Scroll (9th-level)         & Legendary & 1 &  75,000 agnomas & CAL & ---    & DMG   208 \\
            Tome of the Stilled Tongue       & Legendary & 8 & 250,000 agnomas & CAL & 2.5 kg & DMG   208
        \end{DndTable}
    \end{table*}

    \paragraph{Component Pouch}
        A component pouch is a small, watertight leather belt pouch that has compartments to hold all the material components and other special items you need to cast your spells, except for those components that have a specific cost (as indicated in a spell's description).
    \paragraph{Crystal Ball $\odot$}
        Made by wandering zaloths, this item is infused with their strange magic.

        This crystal ball is about 15 centimeters in diameter.
        While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.
    \paragraph{Crystal of Absorption $\odot$}
        Designed by zaloths, this item is infused with their strange magic.

        While holding this crystal, you can use your reaction to absorb a spell that is targeting only you and not with an area of effect.
        The absorbed spell's effect is canceled, and the spell's energy --- not the spell itself --- is stored in the crystal.
        The energy has the same level as the spell when it was cast.
        The crystal can absorb and store up to 50 spell points worth of spells over the course of its existence.
        Once the crystal absorbs 50 spell points, it can't absorb more.
        If you are targeted by a spell that the crystal can't store, the crystal has no effect on that spell.

        When you become attuned to the crystal, you know how many spell points the crystal has absorbed over the course of its existence, and how many spell points it currently has stored.

        If you are a spellcaster holding the crystal, you can convert energy stored in it into spell points to cast spells you know.
        You can use the spell points stored in the crystal instead of your normal spell points, but otherwise cast the spell as normal.

        A newly found crystal has 1d10 spell points stored in it already.
        A crystal that can no longer absorb spells and has no spell points remaining becomes nonmagical.
    \paragraph{Crystal Ball of Mind Reading $\odot$}
        Made by wandering zaloths, this item is infused with their strange magic.

        This crystal ball is about 15 centimeters in diameter.
        While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.

        You can use an action to cast the detect thoughts spell (see page \pageref{spell::detectthoughts}) with a save DC of 17 while you are scrying with the crystal ball, targeting creatures you can see within 30 feet of the spell's sensor.
        You don't need to concentrate on this detect thoughts to maintain it during its duration, but it ends if scrying ends.
    \paragraph{Crystal Ball of Telepathy $\odot$}
        Made by wandering zaloths, this item is infused with their strange magic.

        This crystal ball is about 15 centimeters in diameter.
        While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.

        While scrying with the crystal ball, you can communicate telepathically with creatures you can see within 6 meters of the spell's sensor.
        You can also use an action to cast the suggestion spell (see page \pageref{spell::suggestion}) with save DC 17 through the sensor on one of those creatures.
        You don't need to concentrate on this suggestion to maintain it during its duration, but it ends if scrying ends.
        Once used, the suggestion power of the crystal ball can't be used again until the next dawn.
    \paragraph{Crystal Ball of True Seeing $\odot$}
        Made by wandering zaloths, this item is infused with their strange magic.

        This crystal ball is about 15 centimeters in diameter.
        While touching it, you can cast the scrying spell (see page \pageref{spell::scrying}) with save DC 17 with it.

        While scrying with the crystal ball, you have truesight with a radius of 24 meters centered on the spell's sensor.
    % \paragraph{Crystalline Chronicle $\odot$}
    %     Made by wandering zaloths, this item is infused with their strange magic.
    %     You can only attune to this item if you have taken the spellcaster feat (page \pageref{feat::spellcaster}).
    %
    %     An etched crystal sphere the size of a grapefruit hums faintly and pulses with irregular flares of inner light.
    %     The crystal contains the following spells: detect thoughts (see page \pageref{spell::detectthoughts}), intellect fortress (see page \pageref{spell::intellectfortress}), Rary's telepathic bond (see page \pageref{spell::rarystelepathicbond}), sending (see page \pageref{spell::sending}), telekinesis (see page \pageref{spell::telekinesis}), Tasha's mind whip (see page \pageref{spell::tashasmindwhip}), and Tenser's floating disk (see page \pageref{spell::tensersfloatingdisc}).
    %     While attuned to this item you know all these spells, and your knowledge of them fades when you end your attunement with it.
    %
    %     While you are holding the crystal, you can use it as a spellcasting focus for these spells, and you know the mage hand (see page \pageref{spell::magehand}), mind sliver (see page \pageref{spell::mindsliver}), and message (see page \pageref{spell::message}) cantrips if you don't already know them.
    %
    %     The crystal has 3 charges, and it regains 1d3 expended charges daily at dawn.
    %     You can use the charges to cast a spell given by this item without verbal, somatic, or material components of up to 100 agnomas.
    \paragraph{Decanter of Endless Water}
        This decanter can contain up to 8 liters of water, which is compressed to extreme lengths when inside.
        Upon being opened, a 6-meter long geyser gushes forth from the decanter.
        As an action while holding the decanter, you can aim the geyser at a creature you can see within 6 meters of you.
        The target must succeed on a DC 12 Strength saving throw or take 1d4 bludgeoning damage and fall prone.
        Instead of a creature, you can target an object that isn't being worn or carried and that weighs no more than 100 kg.
        The object is either knocked over or pushed up to 3 meters away from you.

        To use this ability the decanter must be filled with water, a process that takes half a minute.
    \paragraph{Eversmoking Bottle}
        Smoke leaks from the lead-stoppered mouth of this glass bottle, which weighs 0.5 kg.
        When you use two actions to remove the stopper, a cloud of thick smoke pours out in a 12-meter radius from the bottle.
        The cloud's area is heavily obscured.
        Each minute the bottle remains open and within the cloud, the radius increases by 2 meters until it reaches its maximum radius of 24 meters.

        The cloud persists as long as the bottle is open.
        Closing the bottle requires an action.
        Once the bottle is closed, the cloud disperses after 10 minutes.
        A moderate wind can also disperse the smoke after 1 minute, and a strong wind can do so after 1 round.
    \paragraph{Firetrap}
        A firetrap is an spherical glass container about the size of a bottle.
        A flamespeaker can use a firetrap as a spellcasting focus, and is the required material component to cast the \textbf{Screaming Bead} spell (see page \pageref{spell::screamingbead}).
    \paragraph{Folding Boat}
        This object appears as a wooden box that measures 30 cm long, 15 cm wide, and 15 cm deep.
        It weighs 2 kilograms and floats.
        It can be opened to store items inside.

        Using two actions, the box can be unfolded into a boat 3 meters long, 1 meter wide, and 60 cm deep.
        The boat has one pair of oars, a mast, and a lateen sail.
        The boat can hold up to four Medium creatures comfortably.

        Using two actions, the folding boat can fold back into a box, provided that no creatures are aboard.
    \paragraph{Fiend Sensor}
        This small ruby glows slightly when it is within 24 meters of a fiend.
    \paragraph{Figurine of Wondrous Power}
        This figurine is a statuette of a beast small enough to fit in a pocket.
        If you use an action to throw the figurine to a point on the ground within 12 meters of you, the figurine becomes a living creature.
        If the space where the creature would appear is occupied by other creatures or objects, or if there isn't enough space for the creature, the figurine doesn't become a creature.

        The creature is friendly to you and your companions.
        It understands your languages and obeys your spoken commands.
        If you issue no commands, the creature defends itself but takes no other actions.

        The creature exists for a duration specific to each figurine.
        At the end of the duration, the creature reverts to its figurine form.
        It reverts to a figurine early if it drops to 0 hit points or if you use an action to speak the command word again while touching it.
        When the creature becomes a figurine again, its property can't be used again until a week has passed.

        \begin{itemize}
            \item \textbf{Bronze Griffon}.
            This bronze statuette is of a griffon rampant.
            It can become a griffon for up to 6 hours.
            \item \textbf{Golden Lions}.
            These gold statuettes of lions are always created in pairs.
            You can use one figurine or both simultaneously.
            Each can become a lion for up to 1 hour.
            \item \textbf{Ivory Goats}.
            These ivory statuettes of goats are always created in sets of three.
            Each goat looks unique and functions differently from the others.
            Their properties are as follows:
            \begin{itemize}
                \item The goat of traveling can become a Large goat with the same statistics as a riding horse.
                It lasts for 24 hours.
                \item The goat of travail becomes a giant goat for up to 3 hours.
                Once it has been used, it can't be used again until 30 days have passed.
                \item The goat of terror becomes a giant goat for up to 3 hours.
                The goat can't attack, but you can remove its horns and use them as weapons.
                One horn becomes a +1 lance, and the other becomes a +2 longsword.
                Removing a horn requires an action, and the weapons disappear and the horns return when the goat reverts to figurine form.

                In addition, the goat radiates a 6-meter-radius aura of terror while you are riding it.
                Any creature hostile to you that starts its turn in the aura must succeed on a DC 15 Wisdom saving throw or be frightened of the goat for 1 minute, or until the goat reverts to figurine form.
                The frightened creature can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success. Once it successfully saves against the effect, a creature is immune to the goat's aura for the next 24 hours.
                Once the figurine has been used, it can't be used again until 15 days have passed.
            \end{itemize}
            \item \textbf{Onyx Dog}.
            This onyx statuette of a dog can become a mastiff for up to 6 hours.
            The mastiff has an Intelligence of 8.
            The dog has darkvision out to a range of 12 meters and can see invisible creatures and objects within that range.
            \item \textbf{Silver Raven}.
            This silver statuette of a raven can become a raven for up to 12 hours.
            While in raven form, you can attach a letter to the raven's leg and tell it a location you know within 12 hours of travel, and the raven will go there to relay the message.
        \end{itemize}
    \paragraph{Frithling Glass Home} \label{item::frithlingglasshome}
        This colored glass bottle weights 0.5 kg.
        The bottle can serve as a comfortable home for up to 8 frithlings, as long as the frithlings get along with each other.
        The frithlings are thankful towards you for giving them a home and taking them in your adventures, and can perform tasks asked by you within their ability, and will occasionally give you favors or gifts for your friendship.
        % The frithlings need to eat and drink, each consuming 1/8th of the rations and doses of water that a normal-sized humanoid needs.

        If you fail to provide the frithlings basic needs or constantly put them in danger they will abandon you, usually without warning.
    \paragraph{Gem of Brightness}
        This blue gem sheds bright light in a 6-meter radius and dim light for an additional 6 meters.
    \paragraph{Gem of Seeing}
        This gem is attached to a short wooden pole.
        While peering through the gem, you gain truesight out to a range of 24 meters.
    \paragraph{Goggles of Night}
        While wearing these dark lenses, you have darkvision out to a range of 12 meters.
        If you already have darkvision, wearing the goggles increases its range by 12 meters.
    \paragraph{Horseshoes of Speed}
        These iron horseshoes come in a set of four.
        While all four shoes are affixed to the hooves of a horse or similar creature, they increase the creature's walking speed by 6 meters.
    \paragraph{Jamming Shackles}
        You can use an action to place these shackles on an incapacitated creature.
        The shackles adjust to fit a creature of Small to Large size.
        In addition to serving as mundane manacles, the shackles prevent a creature bound by them from using any method of movement, including teleportation or travel to a different plane of existence.

        You and any creature you designate when you use the shackles can use an action to remove them.
        Once every 30 days, the bound creature can make a DC 30 Strength (Athletics) check.
        On a success, the creature breaks free and destroys the shackles.
    \paragraph{Kruphix Stone $\odot\odot$} \label{item::kruphixstone}
        Many types of Kruphix stones exist, each type a distinct combination of shape and color.

        When you use an action to toss one of these stones into the air, the stone orbits your head at a distance of 30 centimeters and confers a benefit to you.
        Thereafter, another creature must use an action to grasp or net the stone to separate it from you, either by making a successful attack roll against AC 24 or a successful DC 24 Dexterity (Acrobatics) check.
        You can use an action to seize and stow the stone, ending its effect.

        A stone has AC 24, 10 hit points, and resistance to all damage.
        It is considered to be an object that is being worn while it orbits your head.

        Attuning to a Kruphix stone requires two attunement slots.
        You can carry any number of Kruphix stones using the same attunement slots.
        You cannot attune to more than one Kruphix stone of the same type at once.

        Rare Kruphix stones:
        \begin{itemize}
            \item \textbf{Awareness}.
            You can't be surprised while this dark blue rhomboid orbits your head.
            \item \textbf{Protection}.
            You gain a +1 bonus to AC while this dusty rose prism orbits your head.
            \item \textbf{Reserve}.
            While this stone orbits your head, you can cast any spell stored in it.
            The spell uses the slot level, spell save DC, spell attack bonus, and spellcasting ability of the original caster, but is otherwise treated as if you cast the spell.
            The spell cast from the stone is no longer stored in it, freeing up space.
            \item \textbf{Sustenance}.
            As long as this clear spindle spends at least 4 hours under direct, unobstructed sunlight, you don't need to eat or drink while it orbits your head.
        \end{itemize}

        Very rare Kruphix stones:
        \begin{itemize}
            \item \textbf{Absorption}.
            While this pale lavender ellipsoid orbits your head, you can use your reaction to cancel a spell of 4th level or lower cast by a creature you can see and targeting only you.

            Once the stone has canceled 20 levels of spells, it burns out and turns dull gray, losing its magic.
            If you are targeted by a spell whose level is higher than the number of spell levels the stone has left, the stone can't cancel it.
            \item \textbf{Agility}.
            Your Dexterity score increases by 2, to a maximum of 22, while this deep red sphere orbits your head.
            \item \textbf{Fortitude}.
            Your Constitution score increases by 2, to a maximum of 22, while this pink rhomboid orbits your head.
            \item \textbf{Insight}.
            Your Wisdom score increases by 2, to a maximum of 22, while this incandescent blue sphere orbits your head.
            \item \textbf{Intellect}.
            Your Intelligence score increases by 2, to a maximum of 22, while this marbled scarlet and blue sphere orbits your head.
            \item \textbf{Leadership}.
            Your Charisma score increases by 2, to a maximum of 22, while this marbled pink and green sphere orbits your head.
            \item \textbf{Might}.
            Your Strength score increases by 2, to a maximum of 22, while this pale blue rhomboid orbits your head.
        \end{itemize}

        Legendary Kruphix stones:
        \begin{itemize}
            \item \textbf{Greater Absorption}.
            While this marbled lavender and green ellipsoid orbits your head, you can use your reaction to cancel a spell of 8th level or lower cast by a creature you can see and targeting only you.

            Once the stone has canceled 50 levels of spells, it burns out and turns dull gray, losing its magic.
            If you are targeted by a spell whose level is higher than the number of spell levels the stone has left, the stone can't cancel it.
            \item \textbf{Proficiency}.
            Your proficiency bonus increases by 1 while this pale green prism orbits your head.
            \item \textbf{Regeneration}.
            You regain 5 hit points at the end of each hour this pearly white spindle orbits your head, provided that you have at least 1 hit point.
        \end{itemize}
    \paragraph{Manual of Bodily Health}
        This book contains health and diet tips from all around the world.
        If you spend 6 long rests studying the book's contents and practicing its guidelines, your Constitution score increases by 2, as does your maximum for that score.
        A creature can benefit from this manual only once in its life.
    \paragraph{Manual of Gainful Exercise}
        This book describes fitness exercises from the harshest mountains of the north.
        If you spend 6 long rests studying the book's contents and practicing its guidelines, your Strength score increases by 2, as does your maximum for that score.
        A creature can benefit from this manual only once in its life.
    \paragraph{Manual of Golems}
        This tome contains information and incantations necessary to make a golem.
        To decipher and use the manual, you must be a spellcaster with at least 60 spell points.
        A creature that can't use a manual of golems and attempts to read it takes 6d6 psychic damage.

        To create a golem, you must spend 10 long rests working without interruption with the manual at hand and resting no more than 8 hours per day.
        You must also pay 50,000 agnomas to purchase supplies.
        The golem becomes animate when the ashes of the manual are sprinkled on it.
        It is under your control, and it understands and obeys your spoken commands.
    \paragraph{Manual of Quickness of Action}
        This book contains coordination and balance exercises worthy of the most elegant of the circus-folk.
        If you spend 6 long rests studying the book's contents and practicing its guidelines, your Dexterity score increases by 2, as does your maximum for that score.
        A creature can benefit from this manual only once in its life.
    \paragraph{Pearl of Nightfall $\odot$}
        Used to summon night, this 15-centimeter-diameter, jet-black orb is cold to the touch.
        You can spend 10 minutes to activate it, causing the area within 15 kilometer of it at the moment of activation to become night even if it is daytime.
        This night lasts for 24 hours, until you cancel it as an action, or until your attunement to the pearl ends.
        Once used, the pearl can't be used again for 24 hours.
    \paragraph{Pearl of Power $\odot$}
        While this pearl is on your person, you can use an action to regain 5 spell points.
        Once you have used the pearl, it can't be used again until the next dawn.
    \paragraph{Pharika's Ointment}
        This glass jar, 7 centimeters in diameter, contains 5 doses of a thick mixture that smells faintly of aloe.

        Taking up one minute, one dose of the ointment can be swallowed or applied to the skin.
        The creature that receives it regains 2d8 + 2 hit points and ceases to be poisoned.
    \paragraph{Rod of Alertness $\odot$}
        This glass rod has a flanged head.
        It has the following properties.
        \begin{itemize}
            \item \textbf{Alertness}
            While holding the rod, you have advantage on Wisdom (Perception) checks and on rolls for initiative.
            \item \textbf{Protective Aura}
            Using two actions, you can plant the haft end of the rod in the ground, whereupon the rod's head sheds bright light in a 12-meter radius and dim light for an additional 12 meters.
            While in that bright light, you and any creature that is friendly to you gain a +1 bonus to AC and saving throws and can sense the location of any invisible hostile creature that is also in the bright light.
            The rod's head stops glowing and the effect ends after 10 minutes, or when a creature uses an action to pull the rod from the ground.
            This property can't be used again until the next dawn.
        \end{itemize}
    \paragraph{Rod of Leadership $\odot$}
        Said to be designed by king Olag for Khedrat's top military personnel, this rod can command respect from anyone around you.
        You can use two actions to present the rod and command obedience from each creature of your choice that you can see within 24 meters of you.
        Each target must succeed on a DC 15 Wisdom saving throw or be charmed by you for 8 hours.
        While charmed in this way, the creature regards you as its trusted leader.
        If harmed by you or your companions, or commanded to do something contrary to its nature, a target ceases to be charmed in this way.
        The rod can't be used in this way again until the next dawn.
    \paragraph{Rod of Might $\odot$}
        This glass rod has a straight and unassuming shape, and it functions as a mace that grants a +3 bonus to attack and damage rolls made with it.
        An item of intricate design, you can transform this rod into four different forms as an action.
        As another action you can transform the rod back to its original form or to another of its special forms.
        \begin{itemize}
            \item \textbf{Spear}.
            The rod's head folds down, a spear point springs from the rod's tip, and the rod's handle lengthens into a 1.8-meter haft, transforming the rod into a spear that grants a +3 bonus to attack and damage rolls made with it.
            \item \textbf{Ladder}.
            The rod transforms into a climbing pole up to 10 meters long, as you specify.
            In surfaces as hard as granite, a spike at the bottom and three hooks at the top anchor the pole.
            Horizontal bars 8 centimeters long fold out from the sides, 30 centimeters apart, forming a ladder.
            The pole can bear up to 2,000 kg.
            More weight or lack of solid anchoring causes the rod to revert to its normal form.
            \item \textbf{Ram}.
            The rod transforms into a handheld battering ram and grants its user a +10 bonus to Strength checks made to break through doors, barricades, and other barriers.
            \item \textbf{Compass}.
            The rod assumes or remains in its normal form and indicates magnetic north (Nothing happens if this function of the rod is used in a location that has no magnetic north).
        \end{itemize}

        In addition, you can add one of the following effect to this rod's attacks by expending an extra action:
        \begin{itemize}
            \item \textbf{Drain Life}.
            When you hit a creature with a melee attack using the rod, you can force the target to make a DC 17 Constitution saving throw.
            On a failure, the target rakes an extra 4d6 necrotic damage, and you regain a number of hit points equal to half that necrotic damage.
            This property can't be used again until the next dawn.
            \item \textbf{Paralyze}.
            When you hit a creature with a melee attack using the rod, you can force the target to make a DC 17 Strength saving throw.
            On a failure, the target is paralyzed for 1 minute.
            The target can repeat the saving throw at the end of each of its turns, ending the effect on a success.
            This property can't be used again until the next dawn.
            \item \textbf{Terrify}.
            While holding the rod, you can use an action to force each creature you can see within 6 meters of you to make a DC 17 Wisdom saving throw.
            On a failure, a target is frightened of you for 1 minute.
            A frightened target can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success.
            This property can't be used again until the next dawn.
        \end{itemize}
    \paragraph{Shard of Nuagal}
        The origins of these shards are unknown, and only a master glassblower can evoke the following effects from it.

        While holding this shard, you can use an action to activate it.
        The shard then instantly transports you and up to 199 other willing creatures you can see to an island in Nuagal, the blue moon.
        The island is a tranquil garden, and contains enough water and food to sustain its visitors.

        For each hour spent in the island, a visitor regains hit points as if it had spent 1 hit die.
        Visitors remain in the island for up to 6 days.

        When the time runs out or you use an action to end it, all visitors reappear in the location they occupied when you activated the shard, or an unoccupied space nearest that location.
        The shard loses its power when it is used in this way.
    \paragraph{Sovereign Glue} \label{item::sovereignglue}
        This viscous, milky-white substance can form a permanent adhesive bond between any two objects.
        It must be stored in a jar or flask that has been coated inside with oil of slipperiness (see page \pageref{item::oilofslipperiness}).
        A container contains 7 uses.

        One use of the glue can cover a 50 centimeters square surface.
        The glue takes 1 minute to set.
        Once it has done so, the bond it creates can be broken only by the application of universal solvent (see page \pageref{item::universalsolvent}).
    \paragraph{Spell Scroll} \label{item::spellscroll}
        A spell scroll bears the words of a single spell, written as a cipher.
        You can read the scroll and cast its spell without providing any material components.
        Casting the spell by reading the scroll requires the spell's normal casting time.
        Once the spell is cast, the words on the scroll fade, and it crumbles to dust.
        If the casting is interrupted, the scroll is not lost.

        To cast the spell, you must make an ability check using your spellcasting ability to determine whether you cast it successfully.
        The DC depends on the scroll rarity.
        If you already know the spell, you don't need to succeed on this DC.
        On a failed check, the spell disappears from the scroll with no other effect.

        Once the spell is cast, the words on the scroll fade, and the scroll itself crumbles to dust.

        The DC and attack bonus from spell scrolls are specified in the spell scroll table.

        A spell on a spell scroll can be copied just as spells in spellbooks can be copied.
        A creature proficient with calligrapher's supplies can copy a spell from a spell scroll.
        The copier must succeed on an Intelligence (Arcana) check with a DC equal to the Casting DC of the scroll.
        If the check succeeds, the spell is successfully copied.
        Whether the check succeeds or fails, the spell scroll is destroyed.

        When writing a spell scroll, you decide the language in which is written among the languages you know.
        To read a spell scroll, you must speak the language in which it's written.

        \begin{DndTable}[width=\linewidth, header=Spell Scrolls]{Xccc}
            \textbf{SP Cost} & \textbf{Casting DC} & \textbf{Spell Save DC} & \textbf{Attack Bonus} \\
            0          & 10 & 13 &  +5 \\
            1          & 10 & 13 &  +5 \\
            2          & 11 & 13 &  +5 \\
            3          & 12 & 13 &  +5 \\
            4          & 13 & 15 &  +7 \\
            5          & 13 & 15 &  +7 \\
            6          & 14 & 15 &  +7 \\
            7          & 15 & 17 &  +9 \\
            8          & 15 & 17 &  +9 \\
            9          & 16 & 17 &  +9 \\
            10         & 17 & 18 & +10 \\
            11         & 17 & 18 & +10 \\
            12         & 18 & 18 & +10 \\
            13 or more & 19 & 19 & +11
        \end{DndTable}
    \paragraph{Spellbook} \label{item::spellbook}
        A spellbook is a leather-bound tome with 100 blank vellum pages suitable for recording spells.
        A creature capable of spellcasting can store any spell they know in the book.
        As part of a long rest, the creature can change its known spells with any set of spells written on the book, as long as they fulfill all the requirements to cast each spell.

        As part of a short rest, a creature proficient with calligrapher's supplies can attempt to copy one spell from one spellbook to another, or from a spell scroll to a spellbook.
        The Intelligence (Arcana) DC required to do this is the same as the Casting DC specified in the spell scrolls table.
    \paragraph{Stone of Good Luck $\odot$}
        While this polished agate is on your person, you gain a +1 bonus to ability checks and saving throws.
    \paragraph{Stone of Ill Luck $\odot$}
        This polished agate appears to be a stone of good luck to anyone who tries to identify it, and it confers that item's property while on your person.

        While this item is on your person, you take a -2 penalty to ability checks and saving throws.
        The DM secretly applies this penalty, assuming you are adding the item's bonus.
    \paragraph{Tome of Clear Thought}
        This book contains memory and logic exercises worthy of the great oth scholars of yore.
        If you spend 6 long rests studying the book's contents and practicing its guidelines, your Intelligence score increases by 2, as does your maximum for that score.
        A creature can benefit from this manual only once in its life.
    \paragraph{Tome of Leadership and Influence}
        This book contains guidelines for influencing and charming others.
        If you spend 6 long rests studying the book's contents and practicing its guidelines, your Charisma score increases by 2, as does your maximum for that score.
        A creature can benefit from this manual only once in its life.
    \paragraph{Tome of the Stilled Tongue $\odot$}
        When you attune to this item, you can use it as a spellbook.
        In addition, while holding the tome, you can use one action to cast a spell you have written in this tome, without expending spell points or using any verbal or somatic component.
        Once used, this property of the tome can't be used again until the next dawn.

        While attuned to this book, only you can read the spells written on it; all other creatures see random scribbles.
        When you end your attunement with the item, all words written fade from it.
    \paragraph{Tome of Understanding}
        This book contains intuition and insight exercises.
        If you spend 6 long rests studying the book's contents and practicing its guidelines, your Wisdom score increases by 2, as does your maximum for that score.
        A creature can benefit from this manual only once in its life.
    \paragraph{Zuan $\odot$} \label{item::zuan}
        A zuan is a pearl infused by an alchemist to act as the medium for their spells.
        Once you attune to a zuan, you form a sympathetic bond with it, allowing you to move it through the air just by willing it.
        As a free action on your turn, you can move your zuan in any direction up to 6 meters.
        You zuan cannot be more than 24 meters away from you at any time.
