% !TEX root = ../main.tex
\section{Mediums} \label{sec::mediums}
% A
% B
% C
% D
% E
\DndSpellHeader{Electric Link: Charge \label{medium::charge}}
    {Sympathy medium}
    {1 action}
    {12 mt.}
    {S}
    {Up to an hour}
    You add a charge to a creature or object within range.
    A creature or object can have a total number of charges lesser or equal to your spellcasting ability modifier + your spellcasting proficiency bonus, but an arbitrary number of creatures can have charges at the same time.
    A creature can lose its charges only by being affected by certain sympathy spells, as specified in the spells' descriptions.

    Using two actions, you can affect a charged creature or object in one of the following ways:
    \begin{itemize}
        \item \textbf{Attract}.
        You cause the creature or object to be attracted to the closest metal object it is not wearing or carrying.
        The creature must succeed on a Strength saving throw or be moved a number of meters equal to the number of charges it has towards the object.
        Creatures of size Large or larger make this roll with advantage.
        Objects automatically roll a number equal to their weight (in kg) divided by 5.
        \item \textbf{Discharge}.
        You cause the creature to violently discharge, causing it to lose all charges.
        The creature must roll a Constitution saving throw.
        A creature takes 1d6 thunder damage plus 1d6 lightning damage for each charge it loses in this way on a failed save, taking half damage on a successful one.
        This spell's base damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).
        \item \textbf{Repel}.
        You cause two charged creatures or objects to be repelled from each other.
        Creatures must succeed on a Strength saving throw or be moved a number of meters equal to half the sum of the number of charges the two creatures have (rounded down).
        Creatures of size Large or larger make this roll with advantage.
        Objects automatically roll a number equal to their weight (in kg) divided by 5.
    \end{itemize}
\DndSpellHeader{Electric Link: Dry Air \label{medium::dryair}}
    {Skycaller medium}
    {2 action}
    {12 mt.}
    {S, M (an aragonite shard)}
    {Concentration, up to 10 minutes}
    You dry the air in a 4-meter-radius sphere, allowing charges to easily accumulate in the area.
    Creatures that start their turn in the sphere or that move into it during their turn there increase their charges by one.
    Charges applied by this medium last for an hour, and work the same as charges applied through the \textbf{Charge} medium (page \pageref{medium::charge}).
% F
\DndSpellHeader{Fagal Affinity: Rage \label{medium::rage}}
    {Warchanter medium}
    {2 actions}
    {Touch}
    {V}
    {Up to 10 minutes}
    A small crimson tetrahedron emerges from your zuan, penetrating the skin of a willing creature of your choice within range.
    The creature takes 1d4 piercing damage as it is infused with primal ferocity, entering a rage.

    While raging, a creature gains the following benefits:
    \begin{itemize}
        \item It has advantage on Strength checks and Strength saving throws.
        \item When it makes a melee weapon attack using Strength, it gains a bonus to the damage roll equal to your spellcasting ability modifier.
        \item It has resistance to bludgeoning, piercing, and slashing damage.
        \item If it is able to cast spells, it can't cast them or concentrate on them while raging.
    \end{itemize}

    For each round that the creature is raging you burn 1 spell point.
    The rage ends if the creature falls unconscious or dies.
    You can also use an action on your turn to end the rage.

    While the creature is raging, you can use an action and consume two additional spell points to produce one of the following effects:
    \subparagraph{Primal Frenzy}
    During the creature's next turn, it can make a single melee weapon attack as a free action during its turn.
    This attack doesn't cause and isn't affected by the multiple attack penalty.
    \subparagraph{Feral Instinct}
    Until the beginning of your next turn, the creature cannot be charmed or frightened.
    If it is charmed or frightened when you use this ability, the effect ends.
    \subparagraph{Instinctive Pounce}
    When you use this ability, the creature can move up to its moving speed towards a creature within reach and make a melee attack using Strength as a reaction.

    Only one creature can be affected by this medium at the same time.
\DndSpellHeader{Fagal Affinity: Volatilize \label{medium::volatilize}}
    {Alchemy medium}
    {1/2 actions}
    {---}
    {S}
    {Up to an hour}
    You reduce your zuan's blue or indigo alignment by 2 points, or both by 1 point.
    When you do this, you increase your zuan's silver alignment by 3 points.
    The number of silver alignment points of your zuan is represented by the S letter in your character sheet, and its maximum number is equal to your spellcasting ability modifier (minimum of 2).

    When you cast this spell, you can choose to use an additional action to discharge up to S/2 (rounded down) pebbles from your zuan, reducing its silver alignment by 1 point.
    The pebbles dart toward creatures of your choice within 12 meters of your zuan.
    Make spell attack against the targets.
    On a hit, the target takes 1d6 bludgeoning damage.

    This spell's damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).

    You can use this spell once per turn.
% G
% H
\DndSpellHeader{Heat Link: Ember \label{medium::ember}}
    {Sympathy medium}
    {2 actions}
    {12 mt.}
    {S}
    {Up to an hour}
    You produce a lingering ember that tethers to a point of your choice within range.
    The ember can lie on a point occupied by another creature, stays in position for the spell's duration, and is visible.
    Other creatures can snuff out the flame by covering it in water or by enclosing it on a closed volume of medium or lesser size.
    You can have a number of embers active at the same time equal to your spellcasting ability modifier.

    Using an action, you can affect an ember in one of the following ways:
    \begin{itemize}
        \item \textbf{Move}.
        You move the ember up to 6 meters to a point within range.
        \item \textbf{Snuff Out}.
        You harmlessly snuff out the ember.
        \item \textbf{Explode}.
        The ember explodes, harming any creature(s) within a meter of the ember.
        The creature(s) must succeed on a Dexterity saving throw, taking 1d10 fire damage on a failed save.
        This damage increases by 1d10 when you reach 5th level (2d10), 11th level (3d10), and 17th level (4d10).
    \end{itemize}
\DndSpellHeader{Heat Link: Firetrap \label{medium::firetrap}}
    {Flamespeaker medium}
    {2 actions}
    {Self}
    {S, M (Firetrap)}
    {Until dispelled}
    You produce a lingering ember inside a firetrap you are carrying.
    This flame can be used to cast any sympathy spell as if it were a normal ember, but it doesn't count towards your total number of embers.
    You can move the ember outside the firetrap as if it were a normal ember, but it explodes at the end of your turn without requiring an action from you.
% I
% J
% K
\DndSpellHeader{Kegal Affinity: Bond \label{medium::bond}}
    {Alchemy medium}
    {1 hour}
    {---}
    {S, M (turtle shell and rations of food)}
    {24 hours}
    You prepare a poached soup using a number of rations lesser or equal than your spellcasting ability modifier.
    An empowering bond is formed amongst all who eat a fill of this soup.
    This bond lasts for 24 hours.

    While any bonded creature is within 6 meters of another, it can roll a d4 and add the number rolled to an attack roll, an ability check, or a saving throw it makes.
    Each creature can add the d4 no more than once per turn.

    In addition, when a creature affected by this bond is about to take damage, a second bound creature within 6 meters of it can use its reaction to take all the damage instead.

    The benefits of both these bonds extend to 12 meters when you reach level 11.
\DndSpellHeader{Kegal Affinity: Condense \label{medium::condense}}
    {Alchemy medium}
    {1/2 actions}
    {---}
    {S}
    {Up to 1 hour}
    You increase the indigo alignment of your zuan by 2 points.
    The number of indigo alignment points of your zuan is represented by the I letter in your character sheet, and its maximum number is equal to your spellcasting ability modifier (minimum of 2).
    Every time you cast a spell related to this affinity, you reduce the indigo alignment of your zuan by 1 point, but increase its blue and silver alignments by 1 point.

    When you cast this spell, you can choose to use an additional action to discharge a small amount of mercury from your zuan, reducing its indigo alignment by 1 point.
    The mercury darts towards a creature of your choice within 12 meters of it.
    Make a spell attack against the target.
    On a hit, the target takes 1d8 cold damage, and its speed is reduced by I meters until the start of your next turn as the mercury seeps into its skin.
    You cannot reduce a creature's movement speed to less than 2 meters with this spell.

    This spell's damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).

    You can use this spell once per turn.
% L
% M
% N
\DndSpellHeader{Nuagal Affinity: Dissolve \label{medium::dissolve}}
    {Alchemy medium}
    {1/2 actions}
    {---}
    {S}
    {Up to an hour}
    You increase the blue alignment of your zuan by 2 points.
    The number of blue alignment points of your zuan is represented by the B letter in your character sheet, and its maximum number is equal to your spellcasting ability modifier (minimum of 2).
    Every time you cast a spell related to this affinity, you reduce the blue alignment of your zuan by 1 point, but increase its indigo and silver alignments by 1 point.

    When you cast this spell, you can choose to use an additional action to emit a noxious gas from your zuan, reducing its blue alignment by 1 point.
    One creature within B meters of your zuan must succeed on a Constitution saving throw or take 1d12 poison damage.

    This spell's damage increases by 1d12 when you reach 5th level (2d12), 11th level (3d12), and 17th level (4d12).

    You can use this spell once per turn.
\DndSpellHeader{Nuagal Affinity: Toxic Cuts \label{medium::toxiccuts}}
    {Deathtoucher medium}
    {2 actions}
    {Self}
    {S, M (a tiny dose of arsenic)}
    {Up to 1 hour}
    Using your zuan, you infuse a piercing or slashing melee weapon or an ammunition container with arsenic, making the melee weapon or pieces of ammunition toxic.
    When you do so, you choose one of the following effects:
    \subparagraph{Toxify}
    Each successful attack made with the weapon increases the level of toxicity in the target.
    The maximum toxicity level a creature can have is equal to your spellcasting ability modifier.
    \subparagraph{Bane}
    Each successful attack made with the weapon deals bonus poison damage equal to the level of toxicity in the target creature.

    As a free action during your turn, you can switch from one effect to the other while this spell is active.

    You burn one spell point for every turn you maintain this spell active.
% O
% P
% Q
% R
% S
\DndSpellHeader{Similarity Link: Frithbind \label{medium::frithbind}}
    {Sympathy medium}
    {2 action}
    {12 mt.}
    {V, M (a frithling)}
    {Up to an hour}
    You create a sympathetic link to a willing frithling of your choice within range.
    This link is different in nature to others, as the frithling isn't affected by negative or positive effects commonly associated to your tethered links.
    This binding doesn't count towards your normal limit to bound creatures and objects, but you can only have one frithling bound in this way at once.
    If a frithling dies, its link is automatically broken.

    As part of the actions used to form this link, you can ask the frithling to approach a creature of your choice and take shelter inside any object in its possession.
    The frithling can use a reaction to move up to 4 meters and use it's \textbf{Shelter} trait on the selected object.
    The creature in possession of the object is bound by the link until you use a free action to tell the frithling to abandon it.
\DndSpellHeader{Similarity Link: Tether \label{medium::tether}}
    {Sympathy medium}
    {1 action}
    {12 mt.}
    {S}
    {Up to an hour}
    You create a sympathetic link to a creature or object within range, linking it to all other creatures and objects already affected by this spell.
    You can maintain a link between a number of creatures and objects equal to your spellcasting ability modifier (minimum of 2).
    When a creature dies, its link is automatically broken.

    Using two actions, you can affect all linked creatures and objects in one of the following ways:
    \begin{itemize}
        \item \textbf{Disconnect}.
        You break the link, freeing all affected creatures.
        \item \textbf{Harm}.
        Any time one of the linked creatures takes damage until the end of your next turn, all other creatures take 1d4 force damage (roll once for all creatures).
        \item \textbf{Ward}.
        All linked creatures can roll a d4 and add the number rolled to one saving throw of their choice before the end of your next turn.
    \end{itemize}
% T
% U
% V
% W
% X
% Y
% Z

\newpage
