% !TEX root = ../main.tex
\section{Minor Spells} \label{sec::minorspells}
% A
\DndSpellHeader{Acid Arrow \label{spell::acidarrow}}
    {Alchemy spell - 3 spell points}
    {2/3 actions}
    {18 meters}
    {S, M (powdered rhubarb leaf and an adder's stomach)}
    {Instantaneous}
    A shimmering green arrow streaks forth from your zuan into a target within range, bursting in a spray of acid.
    Make a ranged spell attack against the target.
    On a hit, the target takes 4d4 acid damage immediately and 2d4 acid damage at the end of its next turn.
    On a miss, the arrow splashes the target with acid for half as much of the initial damage and no damage at the end of its next turn.

    When you cast this spell, you can use up to 7 additional spell points, increasing the damage (both initial and later) by 1d4 for each point.

    In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
    When you do so, you infuse your zuan with acid.
    The next time your zuan touches a creature, it must succeed on a Constitution saving throw or take 2d4 acid damage for each alignment point consumed in this way.
\DndSpellHeader{Acid Splash \label{spell::acidsplash}}
    {Alchemy spell - 0 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Instantaneous}
    You turn your zuan into a bubble of acid, which is then hurled towards a creature within range.
    Choose one creature you can see within range, or choose two creatures you can see within range that are within a meter of each other.
    A target must succeed on a Dexterity saving throw or take 1d6 acid damage.

    This spell's damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).

    Any ground splahes by the bubble becomes difficult terrain for I rounds.
\DndSpellHeader{Aqueous Form \label{spell::aqueousform}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {24 meters}
    {S, M (a pint of water)}
    {Concentration, up to 1 hour}
    You transform a willing linked creature into a pool of water.
    It returns to its true form after 1 hour, if it becomes incapacitated or dies, or if you lose concentration.

    The creature is under the following effects while in this form:
    \subparagraph{Liquid Movement}
    It has a swimming speed of 6 meters.
    It can move over or through other liquids.
    It can enter and occupy the space of another creature.
    It can rise up to its normal height, and it can pass through even Tiny openings.
    It extinguish flames in any space it enters.

    \subparagraph{Watery Resilience}
    It has resistance to bludgeoning, piercing, and slashing damage.
    It also has advantage on Strength, Dexterity, and Constitution saving throws.

    \subparagraph{Limitations}
    It can't talk, attack, cast spells, or activate items.
    Any objects it was carrying or wearing melds into its new form and are inaccessible, though it continues to be affected by anything it's wearing, such as armor.

    By spending up to 15 additional spell points, you can affect up to 6 linked creatures with this spell, using 3 spell points for each creature beyond the first.
% B
\DndSpellHeader{Booming Blade \label{spell::boomingblade}}
    {Sympathy spell - 0 spell points}
    {1 action}
    {12 meters}
    {V}
    {1 round}
    You apply one charge on a metallic weapon or piece of ammunition.
    The weapon discharges on a successful attack against a target, adding a charge to it.

    In addition to the attack's normal effects, the attack deals an extra 1d8 thunder damage on a hit.
    This damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).

    If the attacked creature moves before the start of your next turn, you can use your reaction to cause it to violently discharge.
    The creature takes 1d8 lightning damage plus an extra 1d8 lightning damage for each charge lost in this way.
    This effect's base damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).
\DndSpellHeader{Burn Wounds \label{spell::burnwounds}}
    {Sympathy spell - 2 spell points}
    {2 actions}
    {24 meters}
    {S, M (a piece of cloth)}
    {Instantaneous}
    You heal a creature within 3 meters of an ember.
    The creature regains a number of hit points equal to 1d8 + your spellcasting ability modifier.

    You can consume up to 8 additional spell points when you cast this spell, healing the target 1d8 hit points for each spell point consumed.
    In addition, you can use another action and consume 1 spell point to end the frightened condition on the target.
\DndSpellHeader{Burning Cone \label{spell::burningcone}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {B-meter cone}
    {V, S}
    {Instantaneous}
    A thin sheet of flames shoots forth from your zuan.
    Each creature in a B-meter cone must make a Dexterity saving throw.
    A creature takes 3d6 fire damage on a failed save, or half as much damage on a successful one.
    The fire ignites any flammable objects in the area that aren't being worn or carried.

    You can consume up to 8 additional spell points when you cast this spell, the damage increases by 1d6 for each point beyond the first 2.
    In addition, you can consume 4 spell points and an action to cause the zuan to spin while casting this spell, changing its range to a B-meter circle instead of a cone.
% C
\DndSpellHeader{Call Lightning \label{spell::calllightning}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {24 meters}
    {V, S}
    {Concentration, up to 10 minutes}
    You charge a circular area of ground with a 12-meter radius.
    The spell fails if there is no direct access to the sky above the area.

    On each of your turns until the spell ends, you can use an action to call down lightning towards a creature or object with at least one charge.
    Each creature within 1 meter of the targetted point must make a Dexterity saving throw.
    A creature takes 3d10 lightning damage on a failed save, or half as much damage on a successful one.
    You can call down lightning in this way only once per turn.

    If you are outdoors in stormy conditions when you cast this spell, the spell's damage increases by 1d10.

    Upon being hit by lightning, a creature loses one charge.

    You can consume up to 12 additional spell points when casting this spell, increasing the damage done by each lightning strike by 1d10 for each 2 extra spell points used in this way.
    In addition, by consuming 2 spell points, you can use another action to call down one subsequent lightning strike during your turn.
\DndSpellHeader{Calm Emotions \label{spell::calmemotions}}
    {Alchemy spell - 3 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {V, S}
    {Concentration, up to 1 minute}
    You create a B-meter-radius sphere of calmness around your zuan.
    Each creature in the sphere's radius must make a Charisma saving throw; a creature can choose to fail this saving throw if it wishes.
    If a creature fails its saving throw, choose one of the following two effects.

    You can suppress any effect causing a target to be charmed or frightened.
    When this spell ends, any suppressed effect resumes, provided that its duration has not expired in the meantime.

    Alternatively, you can make a target indifferent about creatures of your choice that it is hostile toward.
    This indifference ends if the target is attacked or harmed by a spell or if it witnesses any of its friends being harmed.
    When the spell ends, the creature becomes hostile again, unless the DM rules otherwise.

    While concentrating on this spell, you can choose to use 2 actions and spend 4 additional spell points to extend the effect of this spell to one hour.
\DndSpellHeader{Catapult \label{spell::catapult}}
    {Sympathy spell - 2 spell points}
    {2 actions}
    {24 meters}
    {S}
    {Instantaneous}
    Choose one object with which you are linked that weighs 3 kg or less within range.
    The object flies in a straight line up to 18 meters in a direction you choose before falling to the ground, stopping early if it impacts against a solid surface.
    If the object would strike a creature, that creature must make a Dexterity saving throw.
    On a failed save, the object strikes the target and stops moving.
    When the object strikes something, the object and what it strikes each take 3d6 bludgeoning damage.

    You can consume up to 8 additional spell points when casting this spell.
    The maximum weight of the objects that you can target with this spell increases by 3 kg, and the damage increases by 1d6, for each spell point above the first two.
\DndSpellHeader{Caustic Brew \label{spell::causticbrew}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {30-meter line}
    {V, S, M (a bit of rotten food)}
    {Concentration, up to 1 minute}
    A stream of acid emanates from your zuan in a line 6 meters long and 1 meter wide in a direction you choose.
    Each creature in the line must succeed on a Dexterity saving throw or be covered in acid for the spell's duration or until a creature uses two action to scrape or wash the acid off itself or another creature.
    A creature covered in the acid takes 2d4 acid damage at start of each of its turns.

    The ground under the line is covered in acid, becoming difficult terrain for I rounds.
    In addition, any creature that starts its turn on it or moves through it takes 1d4 acid damage as the acid burns its soles.

    When you cast this spell, you can use up to 8 additional spell points to increase its damage by 2d4 and 1d4 for each point respectively.
\DndSpellHeader{Continual Flame \label{spell::continualflame}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {Touch}
    {V, S, M (a bit of moss, which the spell consumes)}
    {Until dispelled}
    You infuse a bit of moss with volatility, causing it to give off a faint green glow.
    The glowing moss provides bright light in a 4-meter radius and dim light for an additioanl 4 meters.
    This light can be covered or hidden, but not smothered.
\DndSpellHeader{Cure \label{spell::cure}}
    {Alchemy spell - 2 spell points}
    {1 action}
    {Touch}
    {V, M (a pint of honey)}
    {Instantaneous}
    You cause your zuan to excrete one pint of healing ointment.
    If this ointment touches a creature, the creature regains hit points equal to 1d4 + your spellcasting ability modifier.
    This spell has no effect on undead or constructs.

    This liquid can be stored in a flask, where it remains effective for I hours.

    You can consume up to 8 additional spell points when you cast this spell, increasing the healing by 1d4 for each point.
% D
\DndSpellHeader{Deflect \label{spell::deflect}}
    {Sympathy spell - 2 spell points}
    {1 reaction, which you take in response to being attacked}
    {Self}
    {V}
    {Instantaneous}
    You impose disadvantage on an attack made against you using a weapon made of metal, like an arrow or a sword.

    You can consume 1 additional spell point to use this spell against an attack made with a non-metallic weapon.
\DndSpellHeader{Dispel Magic \label{spell::dispelmagic}}
    {Alchemy spell - 5 spell points}
    {2 actions}
    {24 meters}
    {V, S}
    {Instantaneous}
    Choose one creature, object, or magical effect within range.
    Any spell that costs 5 spell points or less on the target ends.
    For each spell that costs more than that, make an ability check using your spellcasting ability.
    The DC equals 6 + its spell point cost.
    On a successful check, the spell ends.

    You can consume up to 8 additional spell points when you cast this spell.
    When you do so, you automatically end the effects of a spell on the target if the spell's cost is equal to or less than the cost you consumed.
% E
\DndSpellHeader{Elemental Protection \label{spell::elementalprotection}}
    {Alchemy spell - 5 spell points}
    {2 actions}
    {Touch or 1-meter-radius sphere}
    {V, S}
    {Concentration, up to 1 hour}
    For the duration, a willing creature within a meter of your zuan has resistance to one damage type of your choice: acid, cold, fire, lightning, or thunder.

    You can spend an additional action and 4 more spell points to cause this effect on all willing creatures within a meter of your zuan --- including you.
\DndSpellHeader{Ensnaring Strike \label{spell::ensnaringstrike}}
    {Alchemy spell - 2 spell points}
    {1/2 action}
    {Self}
    {V}
    {Concentration, up to 1 minute}
    The next time you hit a creature with a weapon attack before this spell ends, a writhing mass of thorny vines appears at the point of impact, and the target must succeed on a Strength saving throw or be restrained by the vines until the spell ends.
    A Large or larger creature has advantage on this saving throw.
    If the target succeeds on the save, the vines shrivel away.

    While restrained by this spell, the target takes 1d6 piercing damage at the start of each of its turns.
    A creature restrained by the vines or one that can touch the creature can use two actions to make a Strength check against your spell save DC.
    On a success, the target is freed.

    When you cast this spell, you can choose to spend up to 8 additional spell points, increasing the damage by 1d6 for each point.

    In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
    Upon sprouting, the vines are smoldering hot, dealing 1d6 fire damage for each silver alignment point consumed to a restrained creature at the start of each of its turns.
\DndSpellHeader{Entangle \label{spell::entangle}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {4-meter square}
    {V, S, M (a thorn)}
    {Concentration, up to 1 minute}
    Your zuan falls to the ground, causing grasping weeds and vines sprout in a 4-meter square starting from where it fell.
    For the duration, these plants turn the ground in the area into difficult terrain.

    A creature in the area when you cast the spell must succeed on a Strength saving throw or be restrained by the entangling plants until the spell ends.
    A creature restrained by the plants can use its action to make a Strength check against your spell save DC.
    On a success, it frees itself.

    When the spell ends, the conjured plants wilt away, and the difficult terrain remains for I rounds.
% F
\DndSpellHeader{Faerie Fire \label{spell::faeriefire}}
    {Sympathy spell - 2 spell points}
    {2 actions}
    {24 meters}
    {S}
    {Concentration, up to 1 minute}
    You choose one linked creature or object within range.
    Until the spell ends, the creature or object sheds bright light in a 4-meter radius and dim light for an additional 4 meters.
    The light can be colored as you like.
    Completely covering the target with something opaque blocks the light.
    The spell ends if you cast it again or dismiss it as an action.

    If you target a creature or an object held or worn by a hostile creature, that creature must succeed on a Dexterity saving throw to avoid the spell.
    Any attack made against an affected creature has advantage if the attacker can see it, and the affected creature or object can't benefit from being invisible.

    You can consume up to 8 additional spell points to affect up to 8 additional linked creatures or object with this spell, 1 point per creature or object.
\DndSpellHeader{Feather Fall \label{spell::featherfall}}
    {Sympathy spell - 2 spell points}
    {1 reaction, which you take when you or a creature within 24 meters of you falls}
    {24 meters}
    {S, M (a small feather or a rock)}
    {1 minute}
    Choose any number of linked creatures within range.
    A falling creature's rate of descent slows to 12 meters per round until the spell ends.
    If the creature lands before the spell ends, it takes no falling damage and can land on its feet, and the spell ends for that creature.

    You can consume up to 6 additional spell points when you cast this spell, allowing you to target one non-linked creature for each spell point used.
\DndSpellHeader{Fireball \label{spell::fireball}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {24 meters}
    {V, S}
    {Instantaneous}
    You cause a bright streak to flash from an ember you choose within range, which then blossoms with a low roar into an explosion of flame.
    Each creature in a 4-meter-radius sphere centered on that point must make a Dexterity saving throw.
    A target takes 8d6 fire damage on a failed save, or half as much damage on a successful one.

    The fire spreads around corners.
    It ignites flammable objects in the area that aren't being worn or carried.

    You can consume up to 6 additional spell points to increase the damage by 1d6 for each spell point used.
    In addition, you can consume another action and 3 additional spell points to cause all creatures that failed the saving throw to be pulled 2 meters towards the center of the fireball.
\DndSpellHeader{Fog Cloud \label{spell::fogcloud}}
    {Sympathy spell - 2 spell points}
    {1 action}
    {24 meters}
    {S, M (a drop of water)}
    {up to 1 hour}
    You create a 2-meter-radius sphere of fog centered on an ember within range.
    The sphere spreads around corners, and its area is heavily obscured.
    It lasts for the duration, until a wind of moderate or greater speed disperses it, or until you choose to end the effect as a free action.

    You can consume up to 8 additional spell points to increase the range of this spell by 1 meter for each spell point beyond 2.
    In addition, you can use another action and consume 2 additional spell points to heat the fog.
    When a creature enters the spell's area for the first time on a turn or starts its turn there, that creature takes 1d8 fire damage.
\DndSpellHeader{Frostbite \label{spell::frostbite}}
    {Sympathy spell - 2 spell points}
    {2 actions}
    {24 meters}
    {S, M (a snowflake)}
    {Instantaneous}
    You drain heat out of one creature within 3 meters of one ember.
    The target must make a Constitution saving throw.
    On a failed save, the target takes 2d8 cold damage, and it has disadvantage on the next weapon attack roll it makes before the end of its next turn.

    You can consume up to 8 additional spell points to increase the damage by 1d8 for each point used.
    In addition, you can use another action and consume 2 additional spell points to prevent the creature from healing until the start of your next turn.
% G
\DndSpellHeader{Grease \label{spell::grease}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {2-meter square}
    {V, S, M (a bit of butter)}
    {1 minute}
    Slick grease covers the ground in a 2-meter square centered on your zuan and turns it into difficult terrain for the duration.

    When the grease appears, each creature standing in its area must succeed on a Dexterity saving throw or fall prone.
    A creature that enters the area or ends its turn there must also succeed on a Dexterity saving throw or fall prone.

    If fire touches the grease, it burns for I rounds.
    In addition to its other effects, any creature that enters the area or ends its turn there take 1d8 fire damage.

    When you cast this spell, you can choose to use up to 8 additional spell points, increasing the length of the square's sides by a meter for each additional spell point used.
% H
\DndSpellHeader{Heat Metal \label{spell::heatmetal}}
    {Sympathy spell - 3 spell points}
    {2 actions}
    {24 meters}
    {S, M (a piece of metal)}
    {Concentration, up to 1 minute}
    You cause a metal object within range to glow red-hot.
    You cause the object to glow red-hot.
    You or the targetted object must be within 3 meters of an ember.
    Any creature in physical contact with the object takes 2d8 fire damage when you cast the spell.
    Until the spell ends, you can use another action on each of your subsequent turns to cause this damage again.

    If a creature is holding or wearing the object and takes the damage from it, the creature must succeed on a Constitution saving throw or drop the object if it can.
    If it doesn't drop the object, it has disadvantage on attack rolls and ability checks until the start of your next turn.

    You can consume up to 7 spell points to increase the damage by 1d8 for each additional spell point consume.
    Additionally, you can use another action and consume 3 additional spell points to target a non-metallic object with this spell.
% I
\DndSpellHeader{Ice Storm \label{spell::icestorm}}
    {Alchemy spell - 6 spell points}
    {2 actions}
    {4-meter-radius, 8-meter-high cylinder}
    {V, S, M (a pinch of dust and drops of water)}
    {Instantaneous}
    A hail of rock-hard ice pounds to the ground in a 4-meter-radius, 8-meter-high cylinder centered on your zuan.
    Each creature in the cylinder must make a Dexterity saving throw.
    A creature takes 2d8 bludgeoning damage and 4d6 cold damage on a failed save, or half as much damage on a successful one.

    Hailstones turn the storm's area of effect into difficult terrain for I rounds.

    When you cast the spell, you can choose to use up to 5 additional spell points, increasing the bludgeoning damage by 1d8 for each additional point used.
\DndSpellHeader{Inflict Wounds \label{spell::inflictwounds}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {Touch}
    {V, S}
    {Instantaneous}
    Make a melee spell attack against a creature a meter from your zuan.
    On a hit, the target takes 3d10 necrotic damage.

    When you cast this spell, you can choose to use up to 8 additional spell points, increasing the damage by 1d10 for each point.

    In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
    If you do so, the area hit by your zuan turns into a sickly color as poison seeps into the skin of the affected creature.
    In addition to the radiant damage, the creature takes 1d10 poison damage at the start of each of its turns for a number of rounds equal to the alignment points consumed in this way.
    Constructs are immune to this effect.
\DndSpellHeader{Investiture of Wind \label{spell::investitureofwind}}
    {Alchemy spell - 7 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {V, S}
    {Concentration, up to 10 minutes}
    Until the spell ends, wind whirls in a B-meter-radius sphere centered on your zuan, causing the following effects:

    \begin{itemize}
        \item Ranged weapon attacks that pass through the sphere have disadvantage on the attack roll.
        \item Creatures inside the sphere gain a flying speed of 12 meters.
        These creatures also move together with your zuan when you move it.
        Any creature still flying when the spell ends falls, unless they can somehow prevent it.
        \item Once per turn while concentrating on the spell, you can use an actions to create a 3-meter cube of swirling wind centered on a point within 12 meters of your zuan.
        Each creature in that area must make a Constitution saving throw.
        A creature takes 2d10 bludgeoning damage on a failed save, or half as much damage on a successful one.
        If a Large or smaller creature fails the save, that creature is also pushed up to 2 meters away from the center of the cube.
    \end{itemize}
% J
% K
\DndSpellHeader{Kruphix's Mockery \label{spell::kruphixsmockery}}
    {Alchemy spell - 6 spell points}
    {1 minute}
    {6 meters}
    {V, S, M (a small stone)}
    {8 hours}
    You divide your zuan into 2, allowing the new stone to orbit a willing creature of your choice within range (including yourself) while the old still acts as your zuan.
    The new zuan emulates a \textbf{Kruphix Stone} (see page \pageref{item::kruphixstone}), boosting the abilities of the creature.
    You choose the stone to take one of the following shapes when you cast this spell:
    \begin{itemize}
        \item \textbf{Agility}.
        The creature's Dexterity score increases by 2, to a maximum of 22, while this deep red sphere orbits its head.
        \item \textbf{Awareness}.
        The creature can't be surprised while this dark blue rhomboid orbits its head.
        \item \textbf{Fortitude}.
        The creature's Constitution score increases by 2, to a maximum of 22, while this pink rhomboid orbits its head.
        \item \textbf{Insight}.
        The creature's Wisdom score increases by 2, to a maximum of 22, while this incandescent blue sphere orbits its head.
        \item \textbf{Intellect}.
        The creature's Intelligence score increases by 2, to a maximum of 22, while this marbled scarlet and blue sphere orbits its head.
        \item \textbf{Leadership}.
        The creature's Charisma score increases by 2, to a maximum of 22, while this marbled pink and green sphere orbits its head.
        \item \textbf{Might}.
        The creature's Strength score increases by 2, to a maximum of 22, while this pale blue rhomboid orbits its head.
        \item \textbf{Protection}.
        The creature gains a +1 bonus to AC while this dusty rose prism orbits its head.
    \end{itemize}

    A stone has AC 20, 10 hit points, and resistance to all damage.
    It is considered to be an object that is being worn while it orbits a head.
    A destroyed stone fades into dust as it falls to the ground.

    A creature can only benefit from one stone generated in this way at once.

    If you cast this spell again before its duration is up, all the stones generated by this spell are lost.

    When you cast this spell, you can choose to use up to 10 additional spell points.
    One new stone is created for each 2 points added.
    These stones can be the same or different from each other and can orbit any number of willing creatures.
% L
\DndSpellHeader{Light \label{spell::light}}
    {Sympathy spell - 0 spell points}
    {1 action}
    {24 meters}
    {V, S}
    {1 hour}
    Using an action, you cause an ember within range to shed a warm, bright light in a 4-meter radius and dim light for an additional 4 meters.
    Completely covering the ember with something opaque blocks the light.
    The spell ends if you cast it again or dismiss it as an action.
\DndSpellHeader{Lightning Bolt \label{spell::lightningbolt}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {20-meter line}
    {V, S}
    {Instantaneous}
    A stroke of lightning forming a line 20 meters long and 1 meter wide blasts out from you, aiming a charged creature of your choice.
    Each creature in the line must make a Dexterity saving throw.
    A creature takes 8d6 lightning damage on a failed save, or half as much damage on a successful one.

    The lightning ignites flammable objects in the area that aren't being worn or carried.

    You can consume up to 6 additional spell points when you cast this spell, increasing the damage by 1d6 for each additional point.
    In addition, you can use another action and spend 2 additional spell points to discharge all affected creatures, dealing an additional 1d6 lightning damage for each lost charge.
\DndSpellHeader{Locate \label{spell::locate}}
    {Sympathy spell - 3 spell points}
    {2 actions}
    {---}
    {M (a part of a creature, such as hair or a nail)}
    {Up to 24 hours}
    You can track the creature from which the material component of this spell came from.
    You sense the direction to the creature's location, as long as it is in any location besides Nyx.
% M
\DndSpellHeader{Magic Missile \label{spell::magicmissile}}
    {Alchemy spell - 2 spell points}
    {2 actions}
    {24 meters}
    {V, S}
    {Instantaneous}
    You create S glowing darts of force from your zuan.
    Each dart hits a creature of your choice that you can see within range.
    A dart deals 1d4 + 1 force damage to its target.
    The darts all strike simultaneously, and you can direct them to hit one creature or several.

    You can use up to 8 additional spell points when you cast this spell, creating one more dart for each point.
\DndSpellHeader{Mass Healing \label{spell::masshealing}}
    {Alchemy spell - 5 spell points}
    {1 action}
    {B-meter-radius sphere}
    {V}
    {Instantaneous}
    All friendly creatures within B meters of your zuan regain hit points equal to 1d4 + your spellcasting modifier.
    This spell has no effect on undead or constructs.

    You can consume up to 6 additional spell points when casting this spell, increasing the healing by 1d4 for each point.
\DndSpellHeader{Minute Meteors \label{spell::minutemeteors}}
    {Alchemy spell - 5 spell points}
    {2 actions}
    {Touch}
    {V, S, M (niter, sulfur, and pine tar formed into a bead)}
    {Concentration, up to 10 minutes}
    You cause S tiny meteors to spawn from your zuan, which float and orbit your zuan for the spell's duration.
    When you cast the spell --- and as an action on each of your turns thereafter --- you can expend one or two of the meteors, sending them streaking toward a point or points you choose within 24 meters of your zuan.
    Once a meteor reaches its destination or impacts against a solid surface, the meteor explodes.
    Each creature within a meter of the point where the meteor explodes must make a Dexterity saving throw.
    A creature takes 2d6 fire damage on a failed save, or half as much damage on a successful one.

    When you cast this spell, you can choose to spend up to 6 additional spell points.
    The number of meteors you create increases by two for each point.
\DndSpellHeader{Misty Step \label{spell::mistystep}}
    {Sympathy spell - 3 spell points}
    {1 actions}
    {Self meters}
    {V}
    {Instantaneous}
    You teleport up to 6 meters to an unoccupied space that you can see.
    You must have at least one charge to use this spell.
% N
% O
% P
\DndSpellHeader{Poison Breath \label{spell::poisonbreath}}
    {Alchemy spell - 2 spell points}
    {2/3 actions}
    {B-meter cone}
    {V, M (hot pepper dust)}
    {Instantaneous}
    You cause your zuan to spew a poisonous cloud in a B-meters cone.
    Each creature in the area must make a Constitution saving throw, taking 3d6 poison damage on a failed save, or half as much damage on a successful one.

    You can consume up to 8 additional spell points to increase the damage of this spell by 1d6 for each spell point beyond 2.
    In addition, you can use another action and consume an additional spell points to induce a creature within 24 meters to exhale the cloud as a reaction.
    The creature must succeed on a Constitution saving throw or it exhales the cloud in a direction of your choice.
    A creature can choose to fail this saving throw.
\DndSpellHeader{Pulse Wave \label{spell::pulsewave}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {Self (6-meter cone)}
    {S}
    {Instantaneous}
    You create intense pressure, unleash it in a 6-meter cone, and decide whether the pressure pulls or pushes linked creatures and objects.
    Each creature in that cone must make a Constitution saving throw.
    A creature takes 6d6 force damage on a failed save, or half as much damage on a successful one.
    Every creature that fails the save is either pulled 3 meters toward you or pushed 3 meters away from you, depending on the choice you made for the spell.

    In addition, unsecured linked objects that are completely within the cone are likewise pulled or pushed 3 meters.

    You can consume up to 6 spell points when you cast this spell, increasing the damage by 1d6 and the distance pulled or pushes by 1 meter for each additional point.
% Q
% R
% S
\DndSpellHeader{Scold \label{spell::scold}}
    {Sympathy spell - 2 spell points}
    {1 reaction, which you take in response to being damaged by a creature within 24 meters of you that you can see}
    {24 meters}
    {V, S}
    {Instantaneous}
    You cause an ember to dart towards the creature that damaged you, surrounding it by hellish flames.
    The creature must make a Dexterity saving throw.
    It takes 2d10 fire damage on a failed save, or half as much damage on a successful one.

    You can consume up to 8 spell points to increase the damage dealt by 1d10 for each additional spell point consumed.
\DndSpellHeader{Searing Smite \label{spell::searingsmite}}
    {Sympathy spell - 2 spell points}
    {1 action}
    {24 meters}
    {V}
    {Concentration, up to 1 minute}
    You cause an ember within 3 meters of a creature to infuse its weapon.
    The next time it hits a creature with a weapon attack during the spell's duration, the weapon flares with white-hot intensity.
    The attack deals an extra 1d6 fire damage to the target and causes it to ignite in flames.
    At the start of each of its turns until the spell ends, the target must make a Constitution saving throw.
    On a failed save, it takes 1d6 fire damage.
    On a successful save, the spell ends.
    If the target or a creature within a meter of it uses two actions to put out the flames, or if some other effect douses the flames (such as the target being submerged in water), the spell ends.

    You can consume up to 8 spell points with when you cast this spell, increasing the initial extra damage by 1d6 for each additional spell point consumed.
    In addition, you can consume a spell point each time the target rolls the Constitution saving throw to force it to roll with disadvantage.
\DndSpellHeader{Shadow Weapon \label{spell::shadowweapon}}
    {Alchemy spell - 3 spell points}
    {1 action}
    {Touch}
    {V, S}
    {Concentration, up to 1 minute}
    You allow your zuan to transform into a staff of solidified gloom, which can be grabbed by yourself as a free action or by a creature within a meter of it as a reaction.
    This staff lasts until the spell ends.
    It counts as a simple melee weapon that deals 2d6 necrotic damage on a hit or 2d8 if used with two hands, and has the finesse, light, and versatile properties.
    In addition, when the staff is used to attack a target that is in dim light or darkness, the attack roll is made with advantage.

    If the weapon is dropped, it dissipates at the end of the round.

    You can use up to 6 additional spell points when you cast this spell, increasing the number of damage dice by 1 for each 2 spell points used.

    When you attack with this weapon, you can choose to use another action to allow your zuan to feed off the target of your attack.
    If you do so, the attack gains a damage bonus equal to your spellcasting ability modifier, and you increase the silver alignment of your zuan by 1.
    If this attack increases its alignment beyond the maximum value, it reverts to that at the end of your next turn.
\DndSpellHeader{Shared Essence \label{spell::sharedessence}}
    {Sympathy spell - 6 spell points}
    {2 actions}
    {24 meters}
    {V, S}
    {Concentration, up to 1 hour}
    All linked creatures must make a Constitution saving throw, with disadvantage if they are within 6 meters of any other linked creature.
    Any creature can willingly fail the save.
    If a creature succeeds on the save, it is unaffected by the spell, but remains linked for all other purposes.

    When damage or healing is dealt to one of the creatures tethered by this spell, it is instead divided between all of them.
    If one of the creatures dies, the other creatures remain affected.
\DndSpellHeader{Sinkhole \label{spell::sinkhole}}
    {Sympathy spell - 6 spell points}
    {2 actions}
    {24 meters}
    {S, M (a piece of rock)}
    {Instantaneous}
    All linked creatures are pushed by a tremendous force towards the middle point between all of them.
    Each creature must make a Strength saving throw.
    On a failed save, the creature takes 5d10 force damage and is pulled up to 4 meters in a straight line toward this point (even if that point is in the air).
    On a successful save, the creature takes half as much damage and isn't pulled.

    You can consume up to 5 additional spell points when you cast this spell, increasing the damage dealt by 1d10 per spell point.
    In addition, you can use another action and consume 2 spell points to move the middle point to the location of one of the linked creatures.
\DndSpellHeader{Spray \label{spell::spray}}
    {Sympathy spell - 2 spell points}
    {2 actions}
    {Self (3-meter cone)}
    {V, S}
    {1 round}
    You overcharge all charged creatures in a 3-meter cone in front of you.
    All creatures affected by this spell are blinded until the end of your next turn.
    Creatures with 3 or more charges must succeed on a Constitution saving throw.
    On a failed save, they are also paralyzed for the duration.

    Upon being affected by this spell, a creature loses one charge.
\DndSpellHeader{Stinking Cloud \label{spell::stinkingcloud}}
    {Alchemy spell - 5 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {V, S, M (a rotten egg)}
    {Concentration, up to 1 minute}
    You create a B-meter-radius sphere of yellow, nauseating gas centered on your zuan.
    The cloud spreads around corners, and its area is heavily obscured.
    The cloud lingers in the air for the duration.

    Each creature that is completely within the cloud at the start of its turn must make a Constitution saving throw against poison.
    On a failed save, the creature spends its action that turn retching and reeling.
    Creatures that don't need to breathe or are immune to poison automatically succeed on this saving throw.

    A moderate wind disperses the cloud after 4 rounds.
    A strong wind disperses it after 1 round.

    Once per turn while concentrating on the spell, you can use an action on your turn to move the cloud up to 4 meters in a direction of your choice.
\DndSpellHeader{Stride \label{spell::stride}}
    {Sympathy spell - 2 spell points}
    {1 action}
    {24 meters}
    {V, S}
    {1 hour}
    Choose a charged creature within range.
    The creature's movement speed is increased by one meter for each charge it has for the duration of the spell.
    In addition, the creature's jump distance is tripled for the duration.

    If the creature loses all charges or is lifted off the ground via any method, it loses this benefit.

    You can use up to 8 additional spell points, increasing the number of creatures affected by the spell by 1 for each spell points consumed.
% T
\DndSpellHeader{Thunderwave \label{spell::thunderwave}}
    {Sympathy spell - 2 spell points}
    {2 actions}
    {24 meters (3-meter cube)}
    {V, S}
    {Instantaneous}
    A wave of thunderous force sweeps out from you or a charged creature of your choice within range.
    Each creature in a 3-meter cube originating from the target (excluding the target) must make a Constitution saving throw.
    On a failed save, a creature takes 2d8 thunder damage and is pushed 2 meters away from the target.
    On a successful save, a creature takes half as much damage and isn't pushed.

    The targetted creature loses all charges when it is affected by this spell.

    In addition, unsecured objects that are completely within the area of effect are automatically pushed 2 meters away from you by the spell's effect, and the spell emits a thunderous boom audible out to 60 meters.

    You can consume up to 8 additional spell points, increasing the damage by 1d8 for each spell point used.
    In addition, you can use another action and consume 3 additional spell points to cause all creatures that fail the saving throw to lose their movement speed until the start of your next turn.
% U
% V
% W
\DndSpellHeader{Wall of Water \label{spell::wallofwater}}
    {Alchemy spell - 5 spell points}
    {2/3 actions}
    {Variable}
    {V, S, M (a pint of water)}
    {Concentration, up to 10 minutes}
    Water seeps from your zuan, creating a wall of water on the ground.
    You can make the wall up to 6 meters long, 2 meters high, and 30 cm thick, or you can make a ringed wall up to 4 meters in diameter, 4 meters high, and 30 cm thick.
    The wall vanishes when the spell ends.
    The wall's space is difficult terrain.

    Any ranged weapon attack that enters the wall's space has disadvantage on the attack roll, and fire damage is halved if the fire effect passes through the wall to reach its target.
    Spells that deal cold damage that pass through the wall cause the area of the wall they pass through to freeze solid (at least a 1-meter-square section is frozen).
    Each 1-meter-square frozen section has AC 5 and 15 hit points.
    Reducing a frozen section to 0 hit points destroys it.
    When a section is destroyed, the wall's water doesn't fill it.

    After the spell ends, the water falls to the ground, causing it to be affected by the \textbf{Grease} spell (page \pageref{spell::grease}) for I rounds.
    This grease cannot burn.

    When you cast this spell, you can choose to spend another action and 2 additional spell points to cause the water to be boiling hot.
    Any creature that passes through the wall or starts its turn in it must roll a Constitution saving throw, taking 2d8 fire damage on a successful save or half as much on a failed save.
\DndSpellHeader{Watery Sphere \label{spell::waterysphere}}
    {Alchemy spell - 6 spell points}
    {2 actions}
    {1-meter-radius sphere}
    {V, S, M (a droplet of water)}
    {Concentration, up to 1 minute}
    You dissolve your zuan into a sphere of water with a 1-meter radius.
    The sphere remains for the spell's duration.

    Any creature in the sphere's space must make a Strength saving throw.
    On a successful save, a creature is ejected from that space to the nearest unoccupied space of the creature's choice outside the sphere.
    A Huge or larger creature succeeds on the saving throw automatically, and a Large or smaller creature can choose to fail it.
    On a failed save, a creature is restrained by the sphere and is engulfed by the water.
    At the end of each of its turns, a restrained target can repeat the saving throw, ending the effect on itself on a success.

    The sphere can restrain as many as four Medium or smaller creatures or one Large creature.
    If the sphere restrains a creature that causes it to exceed this capacity, a random creature that was already restrained by the sphere falls out of it and lands prone in a space within a meter of it.

    Any creature restrained by the sphere moves with it.
    You can ram the sphere into creatures, forcing them to make the saving throw.

    When the spell ends, the sphere falls to the ground and extinguishes all normal flames within 6 meters of it.
    Any creature restrained by the sphere is knocked prone in the space where it falls.
    Your zuan reforms while the water remains in a 6-meter-radius circle, causing the ground to be affected by the Grease (page \pageref{spell::grease}) spell for I rounds.
    This grease cannot burn.

    When you cast this spell, you can choose to spend another action and 3 additional spell points to cause the water to be boiling hot.
    Any creature that starts its turn in the ball takes 2d8 fire damage.
% X
% Y
% Z

\newpage
