% !TEX root = ../main.tex
\section{Major Spells} \label{sec::majorspells}
% A
\DndSpellHeader{Acid Breath \label{spell::acidbreath}}
    {Alchemy spell - 3 spell points}
    {1 action}
    {Touch}
    {V, S, M (a hot pepper)}
    {Concentration, up to 1 minute}
    You touch one willing creature with your zuan and imbue it with the power to spew acid from its mouth, provided it has one.
    Until the spell ends, the creature can use two actions to exhale acid in a 3-meter cone.
    Each creature in that area must make a Dexterity saving throw, taking 3d6 acid damage on a failed save, or half as much damage on a successful one.

    When you lose concentration on this spell, the effect remains for an additional I/2 rounds.

    When you cast this spell, you can choose to use up to 7 additional spell points, increasing the damage by 1d6 for each additional point.
    In addition, you can use 2 actions and 2 spell points on your turn to induce the creature to spew the acid in a direction of its choice as a reaction.
\DndSpellHeader{Adjust Density \label{spell::adjustdensity}}
    {Sympathy spell - 0 spell points}
    {2 actions}
    {30 meters}
    {S}
    {Concentration, up to 1 minute}
    You can alter the weight of all linked objects and creatures.

    For up to one minute, you produce one of the following effects on the targets:
    \subparagraph{Lighten}
    The weight of the target is halved.
    Its speed is increased by 2 meters, it can jump twice as far as normal, and it has disadvantage on Strength checks and Strength saving throws.
    \subparagraph{Burden}
    The weight of the target is doubled.
    Its speed is reduced by 2 meters, and it has advantage on Strength checks and Strength saving throws.
    \subparagraph{Crush}
    The weight of the target is quadrupled.
    The creature's speed is halved, and it must roll a Constitution saving throw at the start of each of its turns.
    On a failed save, it takes 1d8 force damage.
\DndSpellHeader{Antimagic Field \label{spell::antimagicfield}}
    {Alchemy spell - 11 spell points}
    {2 actions}
    {B/2-meter-radius sphere}
    {V, S, M (a pinch of powdered iron or iron filings)}
    {Concentration, up to 1 hour}
    A B/2-meter-radius invisible sphere of antimagic surrounds a zuan of your choice.
    Within the sphere, spells can't be cast, summoned creatures disappear, and all enchantments are lost.
    Until the spell ends, the sphere moves with the zuan, centered on it.

    Spells and other magical effects are suppressed in the sphere and can't protrude into it.
    Spell points expended to cast a suppressed spell are consumed.
    While an effect is suppressed, it doesn't function, but the time it spends suppressed counts against its duration.

    \paragraph{Targeted Effects}
    Spells and other magical effects that target a creature or an object in the sphere have no effect on that target.

    \paragraph{Areas of Magic}
    The area of another spell or magical effect, such as fireball, can't extend into the sphere.
    If the sphere overlaps an area of magic, the part of the area that is covered by the sphere is suppressed.
    For example, the flames created by a wall of fire are suppressed within the sphere, creating a gap in the wall if the overlap is large enough.

    \paragraph{Spells}
    Any active spell or other magical effect on a creature or an object in the sphere is suppressed while the creature or object is in it.

    \paragraph{Enchanted Items}
    The properties and powers of enchanted items are suppressed in the sphere.
    An enchanted weapon's properties and powers are suppressed if it is used against a target in the sphere or wielded by an attacker in the sphere.
    If the weapon or a piece of magic ammunition fully leaves the sphere (for example, if you fire a magic arrow or throw a magic spear at a target outside the sphere), the magic of the item ceases to be suppressed as soon as it exits.

    \paragraph{Magical Travel}
    Teleportation fails to work in the sphere, whether the sphere is the destination or the departure point for such magical travel.
    A portal to another location or plane  temporarily closes while in the sphere.

    \paragraph{Creatures and Objects}
    A creature or object summoned or created by magic temporarily winks out of existence in the sphere.
    Such a creature instantly reappears once the space the creature occupied is no longer within the sphere.

    \paragraph{Dispel Magic}
    Spells and magical effects such as dispel magic have no effect on the sphere.
    Likewise, the spheres created by different antimagic field spells don't nullify each other.
\DndSpellHeader{Aura of Purity \label{spell::auraofpurity}}
    {Alchemy spell - 6 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {V}
    {Concentration, up to 10 minutes}
    Purifying energy radiates from your zuan in an aura with a B-meter radius.
    Until the spell ends, the aura moves with it, centered on the zuan.
    Each nonhostile creature in the aura (including you) can't become diseased, has resistance to poison damage, and has advantage on saving throws against effects that cause any of the following conditions: blinded, charmed, deafened, frightened, paralyzed, poisoned, and stunned.

    Once per turn while concentrating on this spell, you can consume one action and 2 spell points to heal all creatures within the aura hit points equal to 1d4 + your spellcasting ability modifier.
\DndSpellHeader{Aura of Vitality \label{spell::auraofvitality}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Concentration, up to 1 minute}
    You cause healing energy to radiate from an ember within range with a 3-meter radius.
    Until the spell ends, you can use an action to cause one creature in the aura (including you) to regain 2d6 hit points.
    You can heal a creature using this effect only once during your turn.

    When you heal a creature with this spell, you can choose to consume 1 spell point to give the creature resistance against fire or cold damage (your choice) until the start of your next turn.
% B
\DndSpellHeader{Brilliance \label{spell::brilliance}}
    {Sympathy spell - 5 spell points}
    {1 actions}
    {30 meters}
    {V, S}
    {1 hour}
    You cause an ember affected by the Light spell to quickly increase in brightness.
    It emits a bright light in a 12-meter radius and sheds dim light for an additional 12 meters.

    Completely covering the ember with an opaque object, such as a bowl or a helm, blocks the light.

    When you cast this spell, you can use another action and consume 2 additional spell points to cause the light to spark fiercely upon being cast.
    Any creature (excluding you) in a 12-meter radius of the ember must roll a Constitution saving throw.
    On a failed save, a creature becomes blinded until the end of your next turn.
% C
\DndSpellHeader{Chain Lightning \label{spell::chainlightning}}
    {Sympathy spell - 9 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Instantaneous}
    You create a bolt of lightning that arcs toward a target of your choice that you can see within range.
    Bolts then leap from that target to all creatures with at least one charge within 6 meters of the first target.
    A target can be a creature or an object and can be targeted by only one of the bolts.

    A target must make a Dexterity saving throw.
    The target takes 10d8 lightning damage on a failed save, or half as much damage on a successful one.

    You can consume up to 3 spell points to increase the range of the leaping bolts by 3 meters for each additional spell point consumed.
    In addition, you can use another action and spend 3 spell points to discharge all affected creatures, dealing an additional 1d8 lightning damage for each lost charge.
\DndSpellHeader{Cloudkill \label{spell::cloudkill}}
    {Alchemy spell - 7 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {S, M (rotten food)}
    {Concentration, up to 10 minutes}
    You cause your zuan to discharge a B-meter-radius sphere of poisonous, yellow-green fog.
    The fog spreads around corners.
    It lasts for the duration or until strong wind disperses the fog, ending the spell.
    Its area is heavily obscured.

    When a creature enters the spell's area for the first time on a turn or starts its turn there, that creature must make a Constitution saving throw.
    The creature takes 5d8 poison damage on a failed save, or half as much damage on a successful one.
    Creatures are affected even if they hold their breath or don't need to breathe.

    The fog moves 2 meters away from you at the start of each of your turns, rolling along the surface of the ground.
    The vapors, being heavier than air, sink to the lowest level of the land, even pouring down openings.

    You can consume up to 4 additional spell points when you cast this spell, increasing the damage by 1d8 for each point consumed.
    Once per turn while concentrating on the spell, you can use an action on your turn to move the cloud up to 4 meters in a direction of your choice.
\DndSpellHeader{Cone of Cold \label{spell::coneofcold}}
    {Alchemy spell - 7 spell points}
    {2 actions}
    {12-meter-cone}
    {V, S, M (a small glass cone)}
    {Instantaneous}
    A blast of cold air erupts from your zuan.
    Each creature in a 12-meter cone must make a Constitution saving throw.
    A creature takes 8d8 cold damage on a failed save, or half as much damage on a successful one.

    A creature killed by this spell becomes a frozen statue until it thaws.

    The ground under the cone becomes difficult terrain for I rounds.

    When you cast this spell, you can choose to use up to 4 additional spell points, increasing the cold damage dealt by 1d8 for each point consumed.
\DndSpellHeader{Contagion \label{spell::contagion}}
    {Alchemy spell - 7 spell points}
    {2 actions}
    {Touch}
    {V, S}
    {7 days}
    You move your zuan to touch a creature within a meter of it.
    Make a melee spell attack against the creature.
    On a hit, the target is poisoned.

    At the end of each of the poisoned target's turns, the target must make a Constitution saving throw.
    If the target succeeds on three of these saves, it is no longer poisoned, and the spell ends.
    If the target fails three of these saves, the target is no longer poisoned, but choose one of the diseases below.
    The target is subjected to the chosen disease for the spell's duration.

    Since this spell induces a natural disease in its target, any effect that removes a disease or otherwise ameliorates a disease's effects apply to it.

    \paragraph{Blinding Sickness}
    Pain grips the creature's mind, and its eyes turn milky white.
    The creature has disadvantage on Wisdom checks and Wisdom saving throws and is blinded.
    \paragraph{Filth Fever}
    A raging fever sweeps through the creature's body.
    The creature has disadvantage on Strength checks, Strength saving throws, and attack rolls that use Strength.
    \paragraph{Flesh Rot}
    The creature's flesh decays.
    The creature has disadvantage on Charisma checks and vulnerability to all damage.
    \paragraph{Mindfire}
    The creature's mind becomes feverish.
    The creature has disadvantage on Intelligence checks and Intelligence saving throws, and the creature must roll on the Confusion Behaviour table every turn during combat.
    \paragraph{Seizure}
    The creature is overcome with shaking.
    The creature has disadvantage on Dexterity checks, Dexterity saving throws, and attack rolls that use Dexterity.
    \paragraph{Slimy Doom}
    The creature begins to bleed uncontrollably.
    The creature has disadvantage on Constitution checks and Constitution saving throws.
    In addition, whenever the creature takes damage, it is stunned until the end of its next turn.

    \begin{DndTable}[width=\linewidth, header=Confusion Behaviour]{lX}
        \textbf{d10} & \textbf{Behaviour} \\
        1 &
        The creature uses all its movement to move in a random direction.
        To determine the direction, roll a d8 and assign a direction to each die face.
        The creature doesn't take any other action this turn. \\
        2-6 &
        The creature doesn't take actions this turn. \\
        7-8 &
        The creature uses its action to make a melee attack against a randomly determined creature within its reach.
        If there is no creature within its reach, the creature does nothing this turn. \\
        9-10 &
        The creature can act and move normally.
    \end{DndTable}
\DndSpellHeader{Counterspell \label{spell::counterspell}}
    {Alchemy spell - 5 spell points}
    {1 reaction, which you take when you see a creature within 12 meters of your zuan casting a spell}
    {12 meters}
    {S}
    {Instantaneous}
    You attempt to interrupt a creature in the process of casting a spell.
    Make an ability check using your spellcasting ability.
    The DC equals 6 + the number of spell points used to cast the spell.
    On a success, the creature's spell fails and has no effect.

    When you cast this spell, you can choose to spend 3 additional spell points to charge your zuan with the lost energy.
    The next time you damage a creature using your zuan before the end of your next turn, the creature takes an additional Sd6 force damage from the accumulated volatility.
\DndSpellHeader{Crown of Stars \label{spell::crownofstars}}
    {Alchemy spell - 10 spell points}
    {2 actions}
    {Touch}
    {V, S}
    {1 hour}
    S star-like motes of light appear and orbit your zuan until the spell ends.
    You can use an action to send one of the motes streaking toward one creature or object within 24 meters of your zuan.
    When you do so, make a ranged spell attack.
    On a hit, the target takes 4d12 radiant damage.
    Whether you hit or miss, the mote is expended.
    The spell ends early if you expend the last mote.

    If you have four or more motes remaining, they shed bright light in a 6-meter radius and dim light for an additional 30 meters.
    If you have one to three motes remaining, they shed dim light in a 6-meter radius.

    When you cast this spell, you can choose to spend up to 4 additional spell points, increasing the number of motes by one for each point.
% D
\DndSpellHeader{Death Ward \label{spell::deathward}}
    {Alchemy spell - 6 spell points}
    {2/3 actions}
    {Touch}
    {V, S}
    {8 hours}
    A creature within a meter of your zuan is infused with a shard off it.

    The first time the target would drop to 0 hit points as a result of taking damage, the target instead drops to 1 hit point, and the spell ends.

    If the spell is still in effect when the target is subjected to an effect that would kill it instantaneously without dealing damage, that effect is instead negated against the target, and the spell ends.

    When you cast this spell, you can choose to use an additional action and 3 more spell points to infuse the zuan shard with volatility.
    If the spell ends as the result of an attack, the shard leaves the creature and darts toward the source of the damage.
    If it's a creature, it must roll a Dexterity saving throw as the shard attempts to crystallize on its skin.
    On a failed save, the creature takes Sd8 piercing damage, taking half damage on a successful save.
% E
\DndSpellHeader{Effigy \label{spell::effigy}}
    {Sympathy spell - 5 spell points}
    {1 action}
    {12 meters}
    {S, M (a part of a creature, such as hair or a nail)}
    {Up to 1 hour}
    You create a similarity link to the creature from which the material component of this spell came from.
    All saving throws the creature makes against your sympathy spells are made with disadvantage.
    For all other purposes, this link behaves the same as the one produced by the Tether spell.
\DndSpellHeader{Eject \label{spell::eject}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {Self (15-meter sphere)}
    {V}
    {Concentration, up to 1 minute}
    You cause a strong magnetic push or pull (your choice) to emanate from you.
    Each creature with at least one charge that starts its turn inside a 15-meter sphere centered on you must succeed on a Strength saving throw or be pushed or pulled 3 meters from you in a straight line pointed towards you.
    Creatures with 3 or more charges make this roll with disadvantage.

    In addition, moving through the charged sphere is hard, and any charged creature inside it has its movement speed halved.

    As an action on each of your turns before the spell ends, you can change the direction of the force.

    Using another action and consuming 3 additional spell points when casting this spell, you can target any creature within 30 meters of you instead of yourself.
\DndSpellHeader{Electric Arc \label{spell::electricarc}}
    {Sympathy spell - 0 spell points}
    {2 actions}
    {3 meters}
    {V, S}
    {Instantaneous}
    You create an arc of lightning that strikes one creature of your choice that you can see within 3 meters of you.
    The target must succeed on a Dexterity saving throw, taking 1d10 lightning damage on a failed save.
    This damage increases by 1d10 when you reach 5th level (2d10), 11th level (3d10), and 17th level (4d10).
    In addition, this attack applies a charge on the target.

    If the creature moves before the start of your next turn, you can use your reaction to cause the creature to violently discharge.
    The creature takes 1d8 lightning damage plus an extra 1d8 lightning damage for each charge lost in this way.
    This effect's base damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).
\DndSpellHeader{Elemental Bane \label{spell::elementalbane}}
    {Alchemy spell - 6 spell points}
    {2 actions}
    {Touch or 1-meter-radius sphere}
    {V, S}
    {Concentration, up to 1 minute}
    Choose one creature within a meter of your zuan, and choose one of the following damage types: acid, cold, fire, lightning, or thunder.
    The target must succeed on a Constitution saving throw or be affected by the spell for its duration.
    The first time each turn the affected target takes damage of the chosen type, the target takes an extra 2d6 damage of that type.
    Moreover, the target loses any resistance to that damage type until the spell ends.

    You can spend an additional action and 4 more spell points to cause this effect on all creatures within a meter of your zuan.
% F
\DndSpellHeader{Fire Shield \label{spell::fireshield}}
    {Sympathy spell - 6 spell points}
    {2 actions}
    {Self}
    {V, S}
    {10 minutes}
    You cause an ember to dart towards you, wreathing your body in thin and wispy flames.
    The flames shed a bright light in a 2-meter radius and dim light for an additional 2 meters.
    You can end the spell early by using an action to return the ember to its normal form.

    The flames provide you with a warm shield or a chill shield, as you choose.
    The warm shield grants you resistance to cold damage, and the chill shield grants you resistance to fire damage.

    You cannot use the ember to cast other spells while it acts as a shield.

    In addition, whenever a creature within a meter of you hits you with a melee attack, the shield erupts with flame.
    The attacker takes 2d8 fire damage from a warm shield, or 2d8 cold damage from a cold shield.

    By using another action and consuming 3 additional spell points, you can cause an ember to target another creature within 24 meters of you, causing this same effect on it instead of you.
\DndSpellHeader{Fire Storm \label{spell::firestorm}}
    {Sympathy spell - 10 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Instantaneous}
    You manifest a storm made up of sheets of roaring flame to appear in all embers within range.
    The area of each storm consists of 3-meter cubes.
    A creature in an area overlaping two cubes is subjected to the effect only once.

    Each creature in the area must make a Dexterity saving throw.
    It takes 7d10 fire damage on a failed save, or half as much damage on a successful one.

    The fire damages objects in the area and ignites flammable objects that aren't being worn or carried.

    You can use another action and consume 3 additional spell points to cause the storms to linger until the start of your next turn.
    When a creature enters the spell's area for the first time on a turn or starts its turn there, that creature takes 2d10 fire damage.
\DndSpellHeader{Flame Arrows \label{spell::flamearrows}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {24 meters}
    {S, M (An arrow or bolt)}
    {Concentration, up to 1 hour}
    You infuse a container holding ammunition with an ember within 3 meters of you.
    When a target is hit by a ranged weapon attack using a piece of ammunition drawn from the container, the target takes an extra 1d6 fire damage.
    The spell ends on a piece of ammunition when it hits or misses, and the spell ends when twelve pieces of ammunition have been drawn from the container.

    You can consume up to 6 additional spell points to increase the number of pieces of ammunition infused by two for each point.
    When an infused munition is shot, you can use your reaction and one spell point to move an ember to the location where it hits, dealing 2d6 additional fire damage to the target.
\DndSpellHeader{Freezing Sphere \label{spell::freezingsphere}}
    {Sympathy spell - 9 spell points}
    {2 actions}
    {30 meters}
    {S, M (a fistful of snow)}
    {Instantaneous}
    You turn an ember into an icy kernel about the size of a sling stone, which is cool to the touch.
    The kernel shatters when it impacts a surface, exploding into a 6-meter-radius sphere.
    Each creature in the area must make a Constitution saving throw.
    On a failed save, a creature takes 10d6 cold damage.
    On a successful save, it takes half as much damage.

    If the globe strikes a body of water or a liquid that is principally water (not including water-based creatures), it freezes the liquid to a depth of 15 cm over an area 6 meters square.
    This ice lasts for 1 minute.
    Creatures that were swimming on the surface of frozen water are trapped in the ice.
    A trapped creature can use an action to make a Strength check against your spell save DC to break free.

    You can consume up to 3 additional spell points to increase the damage by 1d6 for each spell point.
    In addition, you can consume another action and 3 additional spell points to cause any creature that fails the saving throw to be slowed.
    Slowed creatures can only take 2 actions during their next turn.
% G
% H
\DndSpellHeader{Harm \label{spell::harm}}
    {Alchemy spell - 9 spell points}
    {2 actions}
    {24 meters}
    {V, S}
    {Instantaneous}
    You unleash a virulent disease on a creature within 24 meters of your zuan.
    The target must make a Constitution saving throw.
    On a failed save, it takes 14d6 necrotic damage, or half as much damage on a successful save.
    The damage can't reduce the target's hit points below 1.
    If the target fails the saving throw, its hit point maximum is reduced for 1 hour by an amount equal to the necrotic damage it took.
    Any effect that removes a disease allows a creature's hit point maximum to return to normal before that time passes.
\DndSpellHeader{Haste \label{spell::haste}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Up to 1 minute}
    Choose a charged creature within range.
    That creature gains a +2 bonus to AC, advantage on Dexterity saving throws, gains an additional action on each of its turns, and its multiple attack penalty is reduced by 1.

    Every turn the target is affected by this spell it loses one charge.
    The spell ends when the creature drops to zero charges, drops to 0 hit points, or a minute passes since this spell was casted.

    When the spell ends, the target can't move or take actions until after its next turn, as a wave of lethargy sweeps over it.
\DndSpellHeader{Hold \label{spell::hold}}
    {Sympathy spell - 7 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Concentration, up to 1 minute}
    Choose a charged creature that you can see within range.
    The target must succeed on a Constitution saving throw or be paralyzed for the duration.
    At the end of each of its turns, the target can make another Constitution saving throw.
    On a success, the spell ends on the target.

    At the start of each of its turn while affected by this spell, the creature loses one charge.

    You can use up to 12 additional spell points when you cast this spell, affecting another charged creature within range for each 3 additional spell points.
\DndSpellHeader{Horrid Wilting \label{spell::horridwilting}}
    {Alchemy spell - 11 spell points}
    {2 actions}
    {6-meter cube}
    {V, S, M (a bit of sponge)}
    {Instantaneous}
    You draw the moisture from every creature in a 6-meter cube centered on your zuan.
    Each creature in that area must make a Constitution saving throw.
    Constructs and undead aren't affected, and plants and oozes make this saving throw with disadvantage.
    A creature takes 12d8 necrotic damage on a failed save, or half as much damage on a successful one.

    Nonmagical plants in the area that aren't creatures, such as trees and shrubs, wither and die instantly.

    When you cast this spell, you can choose to use another action and 2 additional spell points to allow your zuan to feed off the absorbed moisture.
    Each creature that takes damage from this spell increases your zuan's silver alignment by 1.
    If this spell increases its alignment beyond the maximum value, it reverts to that at the end of your next turn.
% I
\DndSpellHeader{Immolation \label{spell::immolation}}
    {Sympathy spell - 7 spell points}
    {2 actions}
    {30 meters}
    {S, M (an piece taken from the target creature)}
    {Concentration, up to 1 minute}
    You cause flames to wreathe one creature you can see within range.
    You or the creature must be standing within 3 meters of an ember.

    The target must make a Constitution saving throw.
    It takes 8d6 fire damage on a failed save, or half as much damage on a successful one.
    The target also burns for the spell's duration.
    The burning target sheds bright light in a 6-meter radius and dim light for an additional 6 meters.
    At the end of each of its turns, the target repeats the saving throw.
    It takes 4d6 fire damage on a failed save.

    You can consume up to 4 spell points to increase the initial damage by 1d6 for each additional spell point consumed.
\DndSpellHeader{Incendiary Cloud \label{spell::incendiarycloud}}
    {Alchemy spell - 11 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {V, S}
    {Concentration, up to 1 minute}
    A swirling cloud of smoke shot through with white-hot embers appears in a B-meter-radius sphere centered on your zuan.
    The cloud spreads around corners and is heavily obscured.
    It lasts for the duration or until a wind of moderate or greater speed disperses it.

    When the cloud appears, each creature in it must make a Dexterity saving throw.
    A creature takes 10d8 fire damage on a failed save, or half as much damage on a successful one.
    A creature must also make this saving throw when it enters the spell's area for the first time on a turn or ends its turn there.

    The cloud moves along with your zuan.

    Each turn while the spell is active, you can use an action and consume 2 spell points to cause the ground under the smoke to heat up, turning it into difficult terrain for one minute.
    Any creature that starts its turn standing in this terrain or moves through it takes 1d6 fire damage.
\DndSpellHeader{Investiture \label{spell::investiture}}
    {Sympathy spell - 9 spell points}
    {2 actions}
    {30 meters}
    {S, M (a stone or a shard of ice)}
    {Concentration, up to 10 minutes}
    You choose a linked creature within range, riming its body in stone or ice, depending on the material component used.

    While under investiture of stone, the creature gains the following benefits:
    \begin{itemize}
        \item It gains resistance to bludgeoning, piercing, and slashing damage.
        \item It can use two actions to create a small earthquake on the ground in a 3-meter radius centered on it.
        Other creatures on that ground must succeed on a Dexterity saving throw or be knocked prone.
        \item It can move across difficult terrain made of earth or stone without spending extra movement.
        It can move through solid earth or stone as if it was air and without destabilizing it, but it can't end your movement there.
        If it does so, it is ejected to the nearest unoccupied space, the spell ends, and it is stunned until the end of its next turn.
    \end{itemize}

    While under investiture of ice, the creature gains the following benefits:
    \begin{itemize}
        \item It is immune to cold damage and has resistance to fire damage.
        \item It can move across difficult terrain created by ice or snow without spending extra movement.
        \item The ground in a 2-meter radius around it is icy and is difficult terrain for creatures other than it.
        The radius moves with it.
        \item It can use two actions to create a 3-meter cone of freezing wind extending from its outstretched hand in a direction it chooses.
        Each creature in the cone must make a Constitution saving throw.
        A creature takes 4d6 cold damage on a failed save, or half as much damage on a successful one.
        A creature that fails its save against this effect has its speed halved until the start of the creature's next turn.
    \end{itemize}

    By spending up to 25 additional spell points, you can affect up to 6 linked creatures with this spell, using 5 spell points for each creature beyond the first.
% J
% K
% L
\DndSpellHeader{Life Ceding \label{spell::lifeceding}}
    {Sympathy spell - 7 spell points}
    {2 actions}
    {30 meters}
    {S, M (a drop of blood)}
    {Instantaneous}
    You transfer life from one tethered creature to mend another's injuries.
    A linked creature of your choice takes 4d8 necrotic damage, and another linked creature of your choice regains a number of hit points equal to the damage taken.

    You can consume up to 4 additional spell points, increasing the damage and healing dealt by 1d8 for each spell point used.
    In addition, you can consume another action and 2 spell points to transfer the hit points between all other linked creatures.
    You choose how many hit points are transfered to each.
\DndSpellHeader{Lightning Arrow \label{spell::lightningarrow}}
    {Sympathy spell - 5 spell points}
    {1 action}
    {12 meters}
    {V, S}
    {Concentration, up to 1 minute}
    You apply a charge on a piece of ammunition or thrown weapon.
    The next time this object is used to make a ranged weapon attack during the spell's duration, it transforms into a bolt of lightning.
    The attack roll is made as normal.
    The target takes 4d8 lightning damage on a hit, or half as much damage on a miss, instead of the weapon's normal damage.

    Whether the attack hits or misses, each creature within 2 meters of the target must make a Dexterity saving throw.
    Each of these creatures takes 2d8 thunder damage on a failed save, or half as much damage on a successful one.

    The piece of ammunition or weapon then returns to its normal form.

    You can consume up to 6 additional spell points, increasing the damage for both effects by 1d8 for each spell point consumed.
    In addition, you can use another action and consume 4 additional spell points to cause all creatures that fail the save to be paralyzed until the start of the attacker's next turn.
% M
% N
% O
% P
\DndSpellHeader{Platinum Shield \label{spell::platinumshield}}
    {Alchemy spell - 10 spell points}
    {1 action}
    {2-meter-radius sphere}
    {V, S, M (a platinum piece)}
    {Concentration, up to 1 minute}
    You create a field of silvery light that surrounds your zuan.
    The field sheds dim light out to a meter.
    While surrounded by the field, a creature gains the following benefits:

    \paragraph{Cover}
    The creature has half cover.
    \paragraph{Damage Resistance}
    The creature has resistance to acid, cold, fire, lightning, and poison damage.
    \paragraph{Evasion}
    If the creature is subjected to an effect that allows it to make a Dexterity saving throw to take only half damage, the creature instead takes no damage if it succeeds on the saving throw, and only half damage if it fails.

    When the spell ends, the field dissolves into water, restoring Id4 hit points to any creature that was immersed in it.
% Q
% R
\DndSpellHeader{Radiating Pressure \label{spell::radiatingpressure}}
    {Sympathy spell - 7 spell points}
    {2 actions}
    {Self (6-meter radius)}
    {S}
    {Instantaeous}
    You strike the ground, creating a burst of pressure that ripples outward from you.
    Each linked creature within 6 meters of you must succeed on a Constitution saving throw or take 5d6 thunder damage, as well as 5d6 force, and be knocked prone.
    A creature that succeeds on its saving throw takes half as much damage and isn't knocked prone.

    You can consume up to 4 spell points to increase the damages done by 1d6 each for each additional point consumed.
\DndSpellHeader{Ravenous Void \label{spell::ravenousvoid}}
    {Sympathy spell - 13 spell points}
    {3 actions}
    {50 meters}
    {S, M (a chunk of iron)}
    {Concentration, up to 1 minute}
    You create a 4-meter-radius sphere of destructive force at the middle point between all linked creatures.
    For the spell's duration, the sphere and any space within 20 meters of it is difficult terrain to all linked creatures.

    A linked creature that starts its turn within 20 meters of the sphere must succeed on a Strength saving throw or be pulled straight toward the sphere's center, ending in an unoccupied space as close to the center as possible.
    A creature that enters the sphere for the first time on a turn or starts its turn there takes 5d10 force damage and is restrained until it is no longer in the sphere.
    If the sphere is in the air, the restrained creature hovers inside the sphere.
    A creature can use two actions to make a Strength check against your spell save DC, ending this restrained condition on itself or another creature in the sphere that it can reach.
\DndSpellHeader{Remote Movement \label{spell::remotemovement}}
    {Sympathy spell - 7 spell points}
    {2 actions}
    {30 meters}
    {S}
    {Concentration, up to 10 minutes}
    You gain the ability to move or manipulate linked creatures or objects by thought.
    When you cast the spell, and using two actions each round for the duration, you can exert your will on one linked creature or object that you can see within range, causing the appropriate effect below.
    You can affect the same target round after round, or choose a new one at any time.
    If you switch targets, the prior target is no longer affected by the spell.

    \subparagraph{Creature}
    You can try to move a Huge or smaller creature.
    Make an ability check with your spellcasting ability contested by the creature's Strength check.
    If you win the contest, you move the creature up to 6 meters in any direction, including upward but not beyond the range of this spell.
    Until the end of your next turn, the creature is restrained in your grip.
    A creature lifted upward is suspended in mid-air.
    On subsequent rounds, you can use your actions to attempt to maintain your grip on the creature by repeating the contest.

    \subparagraph{Object}
    You can try to move an object that weighs up to 500 kg.
    If the object isn't being worn or carried, you automatically move it up to 6 meters in any direction, but not beyond the range of this spell.
    If the object is worn or carried by a creature, you must make an ability check with your spellcasting ability contested by that creature's Strength check.
    If you succeed, you pull the object away from that creature and can move it up to 6 meters in any direction but not beyond the range of this spell.

    You can exert fine control on objects with your grip, such as manipulating a simple tool, opening a door or a container, stowing or retrieving an item from an open container, or pouring the contents from a vial.
\DndSpellHeader{Restoration \label{spell::restoration}}
    {Alchemy spell - 3 spell points}
    {2 actions}
    {Touch}
    {V, S}
    {Instantaneous}
    A healing gas flows from your zuan towards a creature within a meter of it.
    This ends one disease or one condition of your choice afflicting it.
    The condition can be blinded, deafened, paralyzed, or poisoned.

    As an alternative, you can consume 4 additional spell points to undo more debilitating effects.
    You can reduce the target's exhaustion level by one, or end of the following effects on it:
    \begin{itemize}
        \item One effect that charmed or petrified the target,
        \item any reduction to one of the target's ability scores, or
        \item one effect reducing the target's hit point maximum.
    \end{itemize}

    In addition, you can choose to imbue this effect onto a pearl within a meter of your zuan.
    The pearl stores this effect for I hours, healing a creature from one of the described effects just as it is applied.
% S
\DndSpellHeader{Sickening Radiance \label{spell::sickeningradiance}}
    {Alchemy spell - 6 spell points}
    {2/3 actions}
    {6-meter-radius sphere}
    {V, S, M (a bit of moss)}
    {Concentration, up to 10 minutes}
    Dim, greenish light spreads within a 6-meter-radius sphere centered on your zuan.
    The light spreads around corners, and it lasts until the spell ends.

    When a creature moves into the spell's area for the first time on a turn or starts its turn there, that creature must succeed on a Constitution saving throw or take 4d10 radiant damage, and it suffers one level of exhaustion and emits a dim, greenish light in a 1-meter radius.
    This light makes it impossible for the creature to benefit from being invisible.
    The light and any levels of exhaustion caused by this spell go away when the spell ends.

    When you cast this spell, you can choose to use another action and consume all your

    In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
    If you do so, the radiance burns the skin of all creatures that fail on the Constitution saving throw.
    In addition to the radiant damage, they take 1d8 fire damage at the start of each of their turns for a number of rounds equal to the alignment points consumed in this way.
    Constructs are immune to this effect.
\DndSpellHeader{Steam Burst \label{spell::steamburst}}
    {Sympathy spell - 3 spell points}
    {2 actions}
    {30 meters}
    {S, M (a pint of water)}
    {Instantaneous}
    You burst an ember into an eruption of steam.
    Every creature within 2 meters of the ember must make a Strength saving throw.
    A target takes 4d6 fire damage and is pushed 2 meters away from the ember on a failed save.
    On a successful save, the creature takes half damage and isn't pushed.

    You can consume up to 7 additional spell points to increase the damage by 1d6 for each point used.
    In addition, you can consume another action and 2 additional spell points to increase the number of meters a creature is pushed by 2.
\DndSpellHeader{Storm Sphere \label{spell::stormsphere}}
    {Sympathy spell - 6 spell points}
    {2 actions}
    {30 meters}
    {V, S}
    {Concentration, up to 1 minute}
    A 4-meter-radius sphere of whirling air springs into existence, centered on a point you choose within range.
    The sphere remains for the spell's duration.
    Each creature in the sphere when it appears or that ends its turn there must succeed on a Strength saving throw or take 2d6 bludgeoning damage.
    The sphere's space is difficult terrain.

    Until the spell ends, you can use an action on each of your turns to cause a bolt of lightning to leap from the center of the sphere toward one charged creature you choose within 12 meters of the center.
    Make a ranged spell attack.
    You have advantage on the attack roll if the target is in the sphere.
    On a hit, the target takes 4d6 lightning damage.
    You can use this effect only once per turn.
    When using this attack, you can consume 3 spell points to cause the attack to target all charged creatures within range.

    Upon being hit by this lightning, a creature loses one charge.

    Creatures within 6 meters of the sphere have disadvantage on Wisdom (Perception) checks made to listen.

    You can consume up to 5 additional spell points when casting the spell, increasing the damage for each of its effects by 1d6 for each spell point consumed.
% T
\DndSpellHeader{Thunder Step \label{spell::thunderstep}}
    {Sympathy spell - 5 spell points}
    {2 actions}
    {18 meters}
    {V}
    {Instantaneous}
    You teleport yourself to an unoccupied space you can see within range.
    Immediately after you disappear, a thunderous boom sounds, and each creature within 2 meters of the space you left must make a Constitution saving throw, taking 3d10 thunder damage on a failed save, or half as much damage on a successful one.
    The thunder can be heard from up to 60 meters away.

    You can bring along objects as long as their weight doesn't exceed what you can carry.
    You can also teleport one willing creature of your size or smaller who is carrying gear up to its carrying capacity.
    The creature must be within 1 meter of you when you cast this spell, and there must be an unoccupied space within 1 meter of your destination space for the creature to appear in; otherwise, the creature is left behind.

    You must have at least 3 charges to use this spell.

    You can consume up to 6 additional spell points when you cast this spell, increasing the damage dealt by 1d10 for each point.
\DndSpellHeader{Tidal Wave \label{spell::tidalwave}}
    {Alchemy spell - 5 spell points}
    {2/3 actions}
    {Variable}
    {V, S, M (a pint of water)}
    {Instantaneous}
    Your zuan dissolves into a wave of water that crashes down on an area within range.
    The area can be up to 6 meters long, up to 2 meters wide, and up to 2 meters tall.
    Each creature in that area must make a Dexterity saving throw.
    On a failed save, a creature takes 4d8 bludgeoning damage and is knocked prone.
    On a successful save, a creature takes half as much damage and isn't knocked prone.
    The water then spreads out across the ground in all directions, extinguishing unprotected flames in its area and within 6 meters of it, and then it vanishes.

    After casting the spell, the water falls to the ground, causing the affected area to be affected by the \textbf{Grease} spell (page \pageref{spell::grease}) for I rounds.
    This grease cannot burn.

    When you cast this spell, you can choose to spend another action and 2 additional spell points to cause the water to be boiling hot.
    Creatures that fail the Dexterity saving throw also take 2d8 fire damage on a successful save or half as much on a failed one.
% U
\DndSpellHeader{Ukarilth's Staff \label{spell::ukarilthsstaff}}
    {Alchemy spell - 10 spell points}
    {2 actions}
    {Touch}
    {V, S, M (a piece of iron)}
    {Concentration, up to 1 minute}
    You transform your zuan into a long, thin cylinder resembling a quarterstaff.
    The staff is a mass of scintillating colors and it lasts for the duration.

    When the staff appears, you make a melee spell attack against a target of your choice within a meter of the staff.
    On a hit, the target takes 3d10 force damage.
    Once per turn until the spell ends, you can use an action on each of your turns to move the staff up to 4 meters to a spot you can see and repeat this attack against the same target or a different one.

    When you attack with this weapon, you can choose to use another action to allow your zuan to feed off the target of your attack.
    If you do so, the attack gains a damage bonus equal to your spellcasting ability modifier, and you increase the silver alignment of your zuan by 1.
    If this attack increases its alignment beyond the maximum value, it reverts to that at the end of your next turn.
% V
\DndSpellHeader{Vampiric Touch \label{spell::vampirictouch}}
    {Alchemy spell - 5 spell points}
    {2/3 actions}
    {Touch}
    {V, S}
    {Concentration, up to 1 minute}
    You let the natural volatility of your zuan to take control, allowing it to syphon life.
    Make a melee spell attack against a creature within a meter of your zuan.
    On a hit, the target takes 3d6 necrotic damage, and you regain hit points equal to half the amount of necrotic damage dealt.
    Until the spell ends, you can make the attack again on each of your turns using two actions.

    You can use up to 6 additional spell points when you cast this spell, increasing the damage by 1d6 for each point.

    Each time you attack a creature with this spell, you can choose to use another action and reduce your zuan's silver alignment by 1.
    If you do so, the creature cannot regain hit points until the start of your next turn.
\DndSpellHeader{Vitriolic Sphere \label{spell::vitriolicsphere}}
    {Alchemy spell - 6 spell points}
    {2 actions}
    {4-meter-radius sphere}
    {V, S, M (slug bile)}
    {Instantaneous}
    You cause your zuan to become a 30-centimeter-diameter ball of emerald acid.
    Upon touching any surface, it explodes into a 4-meter-radius sphere.
    Each creature in the area must make a Dexterity saving throw.
    On a failed save, a creature takes 10d4 acid damage and is covered in acid for I rounds.

    A creature covered in acid takes 5d4 acid damage at the end of its turns unless it or other creature uses two actions to shake the acid off its body.

    You can consume up to 5 additional spell points, increasing the initial damage by 2d4 for each additional spell point.
% W
\DndSpellHeader{Wall of Light \label{spell::walloflight}}
    {Sympathy spell - 7 spell points}
    {2 actions}
    {30 meters}
    {S}
    {Concentration, up to 10 minutes}
    A shimmering wall of bright light appears between two linked creatures or objects you choose within range.
    The wall is 2 meters high, and 1 meter thick.
    The wall blocks line of sight, but creatures and objects can pass through it.
    It emits bright light out to 24 meters and dim light for an additional 24 meters.

    When the wall appears, each creature in its area (excluding the sources of the wall) must make a Constitution saving throw.
    On a failed save, a creature takes 4d8 radiant damage, and it is blinded for 1 minute.
    On a successful save, it takes half as much damage and isn't blinded.
    A blinded creature can make a Constitution saving throw at the end of each of its turns, ending the effect on itself on a success.

    A creature that ends its turn in the wall's area takes 4d8 radiant damage.

    You can use up to 4 spell points when you cast this spell, increasing the damage by 1d8 for each additional point.
    In addition, you can use another action and 3 spell points to cause the spell to also affect both source points.
\DndSpellHeader{Wall of Thorns \label{spell::wallofthorns}}
    {Alchemy spell - 9 spell points}
    {2 actions}
    {Variable}
    {V, S, M (a handful of thorns)}
    {Concentration, up to 10 minutes}
    Your zuan falls to the ground, causing a wall of tough, pliable, tangled brush bristling with needle-sharp thorns to grow from it.
    The wall appears on a solid surface and lasts for the duration.
    You choose to make the wall up to 12 meters long, 2 meters high, and 1 meter thick or a circle that has a 4-meter diameter and is up to 4 meters high and 1 meter thick.
    The wall blocks line of sight.

    When the wall appears, each creature within its area must make a Dexterity saving throw.
    On a failed save, a creature takes 7d8 piercing damage, or half as much damage on a successful save.

    A creature can move through the wall, albeit slowly and painfully.
    For every meter a creature moves through the wall, it must spend 4 meters of movement.
    Furthermore, the first time a creature enters the wall on a turn or ends its turn there, the creature must make a Dexterity saving throw.
    It takes 7d8 slashing damage on a failed save, or half as much damage on a successful one.

    After the spell ends, the ground under it remains affected by the \textbf{Entangle} (page \pageref{spell::entangle}) for I rounds.

    When you cast this spell, you can choose to spend up to 6 additional spell points, increasing both types of damage by 1d8 for each additional 2 points.
\DndSpellHeader{Web \label{spell::web}}
    {Alchemy spell - 3 spell points}
    {2 actions}
    {4-meter cube}
    {V, S, M (a bit of spiderweb)}
    {Concentration, up to 1 hour}
    You conjure a mass of thick, sticky webbing from your zuan.
    The webs fill a 4-meter cube from that point for the duration.
    The webs are difficult terrain and lightly obscure their area.

    If the webs aren't anchored between two solid masses (such as walls or trees) or layered across a floor, wall, or ceiling, the conjured web collapses on itself, and the spell ends at the start of your next turn.
    Webs layered over a flat surface have a depth of a meter.

    Each creature that starts its turn in the webs or that enters them during its turn must make a Dexterity saving throw.
    On a failed save, the creature is restrained as long as it remains in the webs or until it breaks free.

    A creature restrained by the webs can use its action to make a Strength check against your spell save DC.
    If it succeeds, it is no longer restrained.

    The webs are flammable.
    Any 1-meter cube of webs exposed to fire burns away in I rounds, dealing 2d4 fire damage to any creature that starts its turn in the fire.

    When you cast this spell, you can choose to use up to 14 additional spell points, increasing the length of the cube's sides by a meter for each 2 additional spell points consumed.
\DndSpellHeader{Whirlwind \label{spell::whirlwind}}
    {Alchemy spell - 10 spell points}
    {2 actions}
    {B/2-meter-radius, B-meter-high cylinder}
    {V, M (a piece of straw)}
    {Concentration, up to 1 minute}
    A whirlwind howls down from your zuan.
    The whirlwind is a B/2-meter-radius, B-meter-high cylinder centered on the zuan.
    The whirlwind moves along with your zuan.
    The whirlwind sucks up any Medium or smaller objects that aren't secured to anything and that aren't worn or carried by anyone.

    A creature must make a Dexterity saving throw the first time on a turn that it enters the whirlwind or that the whirlwind enters its space, including when the whirlwind first appears.
    A creature takes 10d6 bludgeoning damage on a failed save, or half as much damage on a successful one.
    In addition, a Large or smaller creature that fails the save must succeed on a Strength saving throw or become restrained in the whirlwind until the spell ends.
    When a creature starts its turn restrained by the whirlwind, the creature is pulled 1 meter higher inside it, unless the creature is at the top.
    A restrained creature moves with the whirlwind and falls when the spell ends, unless the creature has some means to stay aloft.

    A restrained creature can use an action to make a Strength or Dexterity check against your spell save DC.
    If successful, the creature is no longer restrained by the whirlwind and is hurled 3d12 meters away from it in a random direction.
% X
% Y
% Z
\DndSpellHeader{Zone of Truth \label{spell::zoneoftruth}}
    {Alchemy spell - 3 spell points}
    {2 actions}
    {B-meter-radius sphere}
    {V, S}
    {10 minutes}
    You create a zone that guards against deception in a B-meter-radius sphere centered on your zuan.
    Until the spell ends, a creature that enters the spell's area for the first time on a turn or starts its turn there must make a Charisma saving throw.
    On a failed save, a creature can't speak a deliberate lie while in the radius.
    You know whether each creature succeeds or fails on its saving throw.

    An affected creature is aware of the spell and can thus avoid answering questions to which it would normally respond with a lie.
    Such creatures can be evasive in its answers as long as it remains within the boundaries of the truth.

\newpage~\newpage
