% !TEX root = ../main.tex
\section{Alchemy}
\subsection*{Nuagal Affinity}
    \DndSpellHeader{Nuagal Affinity: Dissolve \label{medium::dissolve}}
        {Alchemy medium}
        {X actions}
        {RANGE mt.}
        {COMPONENTS}
        {DURATION}
        DESCRIPTION
    \DndSpellHeader{I: Poison Breath \label{spell::poisonbreath}}
        {Alchemy spell - 2 spell points}
        {2/3 actions}
        {B-meter cone}
        {V, M (hot pepper dust)}
        {Instantaneous}
        You cause your zuan to spew a poisonous cloud in a B-meters cone.
        Each creature in the area must make a Constitution saving throw, taking 3d6 poison damage on a failed save, or half as much damage on a successful one.

        You can consume up to 8 additional spell points to increase the damage of this spell by 1d6 for each spell point beyond 2.
        In addition, you can use another action and consume an additional spell points to induce a creature within 24 meters to exhale the cloud as a reaction.
        The creature must succeed on a Constitution saving throw or it exhales the cloud in a direction of your choice.
        A creature can choose to fail this saving throw.
    \DndSpellHeader{II: Cloudkill \label{spell::cloudkill}}
        {Alchemy spell - 7 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {S, M (rotten food)}
        {Concentration, up to 10 minutes}
        You cause your zuan to discharge a B-meter-radius sphere of poisonous, yellow-green fog.
        The fog spreads around corners.
        It lasts for the duration or until strong wind disperses the fog, ending the spell.
        Its area is heavily obscured.

        When a creature enters the spell's area for the first time on a turn or starts its turn there, that creature must make a Constitution saving throw.
        The creature takes 5d8 poison damage on a failed save, or half as much damage on a successful one.
        Creatures are affected even if they hold their breath or don't need to breathe.

        The fog moves 2 meters away from you at the start of each of your turns, rolling along the surface of the ground.
        The vapors, being heavier than air, sink to the lowest level of the land, even pouring down openings.

        You can consume up to 4 additional spell points when you cast this spell, increasing the damage by 1d8 for each point consumed.
        Once per turn while concentrating on the spell, you can use an action on your turn to move the cloud up to 4 meters in a direction of your choice.
    \DndSpellHeader{I: Burning Cone \label{spell::burningcone}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {B-meter cone}
        {V, S}
        {Instantaneous}
        A thin sheet of flames shoots forth from your zuan.
        Each creature in a B-meter cone must make a Dexterity saving throw.
        A creature takes 3d6 fire damage on a failed save, or half as much damage on a successful one.
        The fire ignites any flammable objects in the area that aren't being worn or carried.

        You can consume up to 8 additional spell points when you cast this spell, the damage increases by 1d6 for each point beyond the first 2.
        In addition, you can consume 4 spell points and an action to cause the zuan to spin while casting this spell, changing its range to a B-meter circle instead of a cone.
    \DndSpellHeader{II: Incendiary Cloud \label{spell::incendiarycloud}}
        {Alchemy spell - 11 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {V, S}
        {Concentration, up to 1 minute}
        A swirling cloud of smoke shot through with white-hot embers appears in a B-meter-radius sphere centered on your zuan.
        The cloud spreads around corners and is heavily obscured.
        It lasts for the duration or until a wind of moderate or greater speed disperses it.

        When the cloud appears, each creature in it must make a Dexterity saving throw.
        A creature takes 10d8 fire damage on a failed save, or half as much damage on a successful one.
        A creature must also make this saving throw when it enters the spell's area for the first time on a turn or ends its turn there.

        The cloud moves along with your zuan.

        Each turn while the spell is active, you can use an action and consume 2 spell points to cause the ground under the smoke to heat up, turning it into difficult terrain for one minute.
        Any creature that starts its turn standing in this terrain or moves through it takes 1d6 fire damage.
    \DndSpellHeader{I: Dispel Magic \label{spell::dispelmagic}}
        {Alchemy spell - 5 spell points}
        {2 actions}
        {24 meters}
        {V, S}
        {Instantaneous}
        Choose one creature, object, or magical effect within range.
        Any spell that costs 5 spell points or less on the target ends.
        For each spell that costs more than that, make an ability check using your spellcasting ability.
        The DC equals 6 + its spell point cost.
        On a successful check, the spell ends.

        You can consume up to 8 additional spell points when you cast this spell.
        When you do so, you automatically end the effects of a spell on the target if the spell's cost is equal to or less than the cost you consumed.
    \DndSpellHeader{II: Antimagic Field \label{spell::antimagicfield}}
        {Alchemy spell - 11 spell points}
        {2 actions}
        {B/2-meter-radius sphere}
        {V, S, M (a pinch of powdered iron or iron filings)}
        {Concentration, up to 1 hour}
        A B/2-meter-radius invisible sphere of antimagic surrounds a zuan of your choice.
        Within the sphere, spells can't be cast, summoned creatures disappear, and all enchantments are lost.
        Until the spell ends, the sphere moves with the zuan, centered on it.

        Spells and other magical effects are suppressed in the sphere and can't protrude into it.
        Spell points expended to cast a suppressed spell are consumed.
        While an effect is suppressed, it doesn't function, but the time it spends suppressed counts against its duration.

        \paragraph{Targeted Effects}
        Spells and other magical effects that target a creature or an object in the sphere have no effect on that target.

        \paragraph{Areas of Magic}
        The area of another spell or magical effect, such as fireball, can't extend into the sphere.
        If the sphere overlaps an area of magic, the part of the area that is covered by the sphere is suppressed.
        For example, the flames created by a wall of fire are suppressed within the sphere, creating a gap in the wall if the overlap is large enough.

        \paragraph{Spells}
        Any active spell or other magical effect on a creature or an object in the sphere is suppressed while the creature or object is in it.

        \paragraph{Enchanted Items}
        The properties and powers of enchanted items are suppressed in the sphere.
        An enchanted weapon's properties and powers are suppressed if it is used against a target in the sphere or wielded by an attacker in the sphere.
        If the weapon or a piece of magic ammunition fully leaves the sphere (for example, if you fire a magic arrow or throw a magic spear at a target outside the sphere), the magic of the item ceases to be suppressed as soon as it exits.

        \paragraph{Magical Travel}
        Teleportation fails to work in the sphere, whether the sphere is the destination or the departure point for such magical travel.
        A portal to another location or plane  temporarily closes while in the sphere.

        \paragraph{Creatures and Objects}
        A creature or object summoned or created by magic temporarily winks out of existence in the sphere.
        Such a creature instantly reappears once the space the creature occupied is no longer within the sphere.

        \paragraph{Dispel Magic}
        Spells and magical effects such as dispel magic have no effect on the sphere.
        Likewise, the spheres created by different antimagic field spells don't nullify each other.
    \DndSpellHeader{I: Stinking Cloud \label{spell::stinkingcloud}}
        {Alchemy spell - 5 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {V, S, M (a rotten egg)}
        {Concentration, up to 1 minute}
        You create a B-meter-radius sphere of yellow, nauseating gas centered on your zuan.
        The cloud spreads around corners, and its area is heavily obscured.
        The cloud lingers in the air for the duration.

        Each creature that is completely within the cloud at the start of its turn must make a Constitution saving throw against poison.
        On a failed save, the creature spends its action that turn retching and reeling.
        Creatures that don't need to breathe or are immune to poison automatically succeed on this saving throw.

        A moderate wind disperses the cloud after 4 rounds.
        A strong wind disperses it after 1 round.

        Once per turn while concentrating on the spell, you can use an action on your turn to move the cloud up to 4 meters in a direction of your choice.
    \DndSpellHeader{II: Contagion \label{spell::contagion}}
        {Alchemy spell - 7 spell points}
        {2 actions}
        {Touch}
        {V, S}
        {7 days}
        You move your zuan to touch a creature within a meter of it.
        Make a melee spell attack against the creature.
        On a hit, the target is poisoned.

        At the end of each of the poisoned target's turns, the target must make a Constitution saving throw.
        If the target succeeds on three of these saves, it is no longer poisoned, and the spell ends.
        If the target fails three of these saves, the target is no longer poisoned, but choose one of the diseases below.
        The target is subjected to the chosen disease for the spell's duration.

        Since this spell induces a natural disease in its target, any effect that removes a disease or otherwise ameliorates a disease's effects apply to it.

        \paragraph{Blinding Sickness}
        Pain grips the creature's mind, and its eyes turn milky white.
        The creature has disadvantage on Wisdom checks and Wisdom saving throws and is blinded.
        \paragraph{Filth Fever}
        A raging fever sweeps through the creature's body.
        The creature has disadvantage on Strength checks, Strength saving throws, and attack rolls that use Strength.
        \paragraph{Flesh Rot}
        The creature's flesh decays.
        The creature has disadvantage on Charisma checks and vulnerability to all damage.
        \paragraph{Mindfire}
        The creature's mind becomes feverish.
        The creature has disadvantage on Intelligence checks and Intelligence saving throws, and the creature must roll on the Confusion Behaviour table every turn during combat.
        \paragraph{Seizure}
        The creature is overcome with shaking.
        The creature has disadvantage on Dexterity checks, Dexterity saving throws, and attack rolls that use Dexterity.
        \paragraph{Slimy Doom}
        The creature begins to bleed uncontrollably.
        The creature has disadvantage on Constitution checks and Constitution saving throws.
        In addition, whenever the creature takes damage, it is stunned until the end of its next turn.

        \begin{DndTable}[width=\linewidth, header=Confusion Behaviour]{lX}
            \textbf{d10} & \textbf{Behaviour} \\
            1 &
            The creature uses all its movement to move in a random direction.
            To determine the direction, roll a d8 and assign a direction to each die face.
            The creature doesn't take any other action this turn. \\
            2-6 &
            The creature doesn't take actions this turn. \\
            7-8 &
            The creature uses its action to make a melee attack against a randomly determined creature within its reach.
            If there is no creature within its reach, the creature does nothing this turn. \\
            9-10 &
            The creature can act and move normally.
        \end{DndTable}
    \DndSpellHeader{I: Mass Healing \label{spell::masshealing}}
        {Alchemy spell - 5 spell points}
        {1 action}
        {B-meter-radius sphere}
        {V}
        {Instantaneous}
        All friendly creatures within B meters of your zuan regain hit points equal to 1d4 + your spellcasting modifier.
        This spell has no effect on undead or constructs.

        You can consume up to 6 additional spell points when casting this spell, increasing the healing by 1d4 for each point.
    \DndSpellHeader{II: Aura of Purity \label{spell::auraofpurity}}
        {Alchemy spell - 6 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {V}
        {Concentration, up to 10 minutes}
        Purifying energy radiates from your zuan in an aura with a B-meter radius.
        Until the spell ends, the aura moves with it, centered on the zuan.
        Each nonhostile creature in the aura (including you) can't become diseased, has resistance to poison damage, and has advantage on saving throws against effects that cause any of the following conditions: blinded, charmed, deafened, frightened, paralyzed, poisoned, and stunned.

        Once per turn while concentrating on this spell, you can consume one action and 2 spell points to heal all creatures within the aura hit points equal to 1d4 + your spellcasting ability modifier.
    \DndSpellHeader{I: Calm Emotions \label{spell::calmemotions}}
        {Alchemy spell - 3 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {V, S}
        {Concentration, up to 1 minute}
        You create a B-meter-radius sphere of calmness around your zuan.
        Each creature in the sphere's radius must make a Charisma saving throw; a creature can choose to fail this saving throw if it wishes.
        If a creature fails its saving throw, choose one of the following two effects.

        You can suppress any effect causing a target to be charmed or frightened.
        When this spell ends, any suppressed effect resumes, provided that its duration has not expired in the meantime.

        Alternatively, you can make a target indifferent about creatures of your choice that it is hostile toward.
        This indifference ends if the target is attacked or harmed by a spell or if it witnesses any of its friends being harmed.
        When the spell ends, the creature becomes hostile again, unless the DM rules otherwise.

        While concentrating on this spell, you can choose to use 2 actions and spend 4 additional spell points to extend the effect of this spell to one hour.
    \DndSpellHeader{II: Zone of Truth \label{spell::zoneoftruth}}
        {Alchemy spell - 3 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {V, S}
        {10 minutes}
        You create a zone that guards against deception in a B-meter-radius sphere centered on your zuan.
        Until the spell ends, a creature that enters the spell's area for the first time on a turn or starts its turn there must make a Charisma saving throw.
        On a failed save, a creature can't speak a deliberate lie while in the radius.
        You know whether each creature succeeds or fails on its saving throw.

        An affected creature is aware of the spell and can thus avoid answering questions to which it would normally respond with a lie.
        Such creatures can be evasive in its answers as long as it remains within the boundaries of the truth.
    \DndSpellHeader{I: Elemental Protection \label{spell::elementalprotection}}
        {Alchemy spell - 5 spell points}
        {2 actions}
        {Touch or 1-meter-radius sphere}
        {V, S}
        {Concentration, up to 1 hour}
        For the duration, a willing creature within a meter of your zuan has resistance to one damage type of your choice: acid, cold, fire, lightning, or thunder.

        You can spend an additional action and 4 more spell points to cause this effect on all willing creatures within a meter of your zuan --- including you.
    \DndSpellHeader{II: Elemental Bane \label{spell::elementalbane}}
        {Alchemy spell - 6 spell points}
        {2 actions}
        {Touch or 1-meter-radius sphere}
        {V, S}
        {Concentration, up to 1 minute}
        Choose one creature within a meter of your zuan, and choose one of the following damage types: acid, cold, fire, lightning, or thunder.
        The target must succeed on a Constitution saving throw or be affected by the spell for its duration.
        The first time each turn the affected target takes damage of the chosen type, the target takes an extra 2d6 damage of that type.
        Moreover, the target loses any resistance to that damage type until the spell ends.

        You can spend an additional action and 4 more spell points to cause this effect on all creatures within a meter of your zuan.
    \DndSpellHeader{I: Investiture of Wind \label{spell::investitureofwind}}
        {Alchemy spell - 7 spell points}
        {2 actions}
        {B-meter-radius sphere}
        {V, S}
        {Concentration, up to 10 minutes}
        Until the spell ends, wind whirls in a B-meter-radius sphere centered on your zuan, causing the following effects:

        \begin{itemize}
            \item Ranged weapon attacks that pass through the sphere have disadvantage on the attack roll.
            \item Creatures inside the sphere gain a flying speed of 12 meters.
            These creatures also move together with your zuan when you move it.
            Any creature still flying when the spell ends falls, unless they can somehow prevent it.
            \item Once per turn while concentrating on the spell, you can use an actions to create a 3-meter cube of swirling wind centered on a point within 12 meters of your zuan.
            Each creature in that area must make a Constitution saving throw.
            A creature takes 2d10 bludgeoning damage on a failed save, or half as much damage on a successful one.
            If a Large or smaller creature fails the save, that creature is also pushed up to 2 meters away from the center of the cube.
        \end{itemize}
    \DndSpellHeader{II: Whirlwind \label{spell::whirlwind}}
        {Alchemy spell - 10 spell points}
        {2 actions}
        {B/2-meter-radius, B-meter-high cylinder}
        {V, M (a piece of straw)}
        {Concentration, up to 1 minute}
        A whirlwind howls down from your zuan.
        The whirlwind is a B/2-meter-radius, B-meter-high cylinder centered on the zuan.
        The whirlwind moves along with your zuan.
        The whirlwind sucks up any Medium or smaller objects that aren't secured to anything and that aren't worn or carried by anyone.

        A creature must make a Dexterity saving throw the first time on a turn that it enters the whirlwind or that the whirlwind enters its space, including when the whirlwind first appears.
        A creature takes 10d6 bludgeoning damage on a failed save, or half as much damage on a successful one.
        In addition, a Large or smaller creature that fails the save must succeed on a Strength saving throw or become restrained in the whirlwind until the spell ends.
        When a creature starts its turn restrained by the whirlwind, the creature is pulled 1 meter higher inside it, unless the creature is at the top.
        A restrained creature moves with the whirlwind and falls when the spell ends, unless the creature has some means to stay aloft.

        A restrained creature can use an action to make a Strength or Dexterity check against your spell save DC.
        If successful, the creature is no longer restrained by the whirlwind and is hurled 3d12 meters away from it in a random direction.
\subsection*{Kegal Affinity}
    \DndSpellHeader{Kegal Affinity: Condense \label{medium::condense}}
        {Alchemy medium}
        {X actions}
        {RANGE mt.}
        {COMPONENTS}
        {DURATION}
        DESCRIPTION
    \DndSpellHeader{I: Acid Splash \label{spell::acidsplash}}
        {Alchemy spell - 0 spell points}
        {2 actions}
        {30 meters}
        {V, S}
        {Instantaneous}
        You turn your zuan into a bubble of acid, which is then hurled towards a creature within range.
        Choose one creature you can see within range, or choose two creatures you can see within range that are within a meter of each other.
        A target must succeed on a Dexterity saving throw or take 1d6 acid damage.

        This spell's damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).

        Any ground splahes by the bubble becomes difficult terrain for I rounds.
    \DndSpellHeader{II: Vitriolic Sphere \label{spell::vitriolicsphere}}
        {Alchemy spell - 6 spell points}
        {2 actions}
        {4-meter-radius sphere}
        {V, S, M (slug bile)}
        {Instantaneous}
        You cause your zuan to become a 30-centimeter-diameter ball of emerald acid.
        Upon touching any surface, it explodes into a 4-meter-radius sphere.
        Each creature in the area must make a Dexterity saving throw.
        On a failed save, a creature takes 10d4 acid damage and is covered in acid for I rounds.

        A creature covered in acid takes 5d4 acid damage at the end of its turns unless it or other creature uses two actions to shake the acid off its body.

        You can consume up to 5 additional spell points, increasing the initial damage by 2d4 for each additional spell point.
    \DndSpellHeader{I: Cure \label{spell::cure}}
        {Alchemy spell - 2 spell points}
        {1 action}
        {Touch}
        {V, M (a pint of honey)}
        {Instantaneous}
        You cause your zuan to excrete one pint of healing ointment.
        If this ointment touches a creature, the creature regains hit points equal to 1d4 + your spellcasting ability modifier.
        This spell has no effect on undead or constructs.

        This liquid can be stored in a flask, where it remains effective for I hours.

        You can consume up to 8 additional spell points when you cast this spell, increasing the healing by 1d4 for each point.
    \DndSpellHeader{II: Restoration \label{spell::restoration}}
        {Alchemy spell - 3 spell points}
        {2 actions}
        {Touch}
        {V, S}
        {Instantaneous}
        A healing gas flows from your zuan towards a creature within a meter of it.
        This ends one disease or one condition of your choice afflicting it.
        The condition can be blinded, deafened, paralyzed, or poisoned.

        As an alternative, you can consume 4 additional spell points to undo more debilitating effects.
        You can reduce the target's exhaustion level by one, or end of the following effects on it:
        \begin{itemize}
            \item One effect that charmed or petrified the target,
            \item any reduction to one of the target's ability scores, or
            \item one effect reducing the target's hit point maximum.
        \end{itemize}

        In addition, you can choose to imbue this effect onto a pearl within a meter of your zuan.
        The pearl stores this effect for I hours, healing a creature from one of the described effects just as it is applied.
    \DndSpellHeader{I: Entangle \label{spell::entangle}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {4-meter square}
        {V, S, M (a thorn)}
        {Concentration, up to 1 minute}
        Your zuan falls to the ground, causing grasping weeds and vines sprout in a 4-meter square starting from where it fell.
        For the duration, these plants turn the ground in the area into difficult terrain.

        A creature in the area when you cast the spell must succeed on a Strength saving throw or be restrained by the entangling plants until the spell ends.
        A creature restrained by the plants can use its action to make a Strength check against your spell save DC.
        On a success, it frees itself.

        When the spell ends, the conjured plants wilt away, and the difficult terrain remains for I rounds.
    \DndSpellHeader{II: Wall of Thorns \label{spell::wallofthorns}}
        {Alchemy spell - 9 spell points}
        {2 actions}
        {Variable}
        {V, S, M (a handful of thorns)}
        {Concentration, up to 10 minutes}
        Your zuan falls to the ground, causing a wall of tough, pliable, tangled brush bristling with needle-sharp thorns to grow from it.
        The wall appears on a solid surface and lasts for the duration.
        You choose to make the wall up to 12 meters long, 2 meters high, and 1 meter thick or a circle that has a 4-meter diameter and is up to 4 meters high and 1 meter thick.
        The wall blocks line of sight.

        When the wall appears, each creature within its area must make a Dexterity saving throw.
        On a failed save, a creature takes 7d8 piercing damage, or half as much damage on a successful save.

        A creature can move through the wall, albeit slowly and painfully.
        For every meter a creature moves through the wall, it must spend 4 meters of movement.
        Furthermore, the first time a creature enters the wall on a turn or ends its turn there, the creature must make a Dexterity saving throw.
        It takes 7d8 slashing damage on a failed save, or half as much damage on a successful one.

        After the spell ends, the ground under it remains affected by the \textbf{Entangle} (page \pageref{spell::entangle}) for I rounds.

        When you cast this spell, you can choose to spend up to 6 additional spell points, increasing both types of damage by 1d8 for each additional 2 points.
    \DndSpellHeader{I: Wall of Water \label{spell::wallofwater}}
        {Alchemy spell - 5 spell points}
        {2/3 actions}
        {Variable}
        {V, S, M (a pint of water)}
        {Concentration, up to 10 minutes}
        Water seeps from your zuan, creating a wall of water on the ground.
        You can make the wall up to 6 meters long, 2 meters high, and 30 cm thick, or you can make a ringed wall up to 4 meters in diameter, 4 meters high, and 30 cm thick.
        The wall vanishes when the spell ends.
        The wall's space is difficult terrain.

        Any ranged weapon attack that enters the wall's space has disadvantage on the attack roll, and fire damage is halved if the fire effect passes through the wall to reach its target.
        Spells that deal cold damage that pass through the wall cause the area of the wall they pass through to freeze solid (at least a 1-meter-square section is frozen).
        Each 1-meter-square frozen section has AC 5 and 15 hit points.
        Reducing a frozen section to 0 hit points destroys it.
        When a section is destroyed, the wall's water doesn't fill it.

        After the spell ends, the water falls to the ground, causing it to be affected by the \textbf{Grease} spell (page \pageref{spell::grease}) for I rounds.
        This grease cannot burn.

        When you cast this spell, you can choose to spend another action and 2 additional spell points to cause the water to be boiling hot.
        Any creature that passes through the wall or starts its turn in it must roll a Constitution saving throw, taking 2d8 fire damage on a successful save or half as much on a failed save.
    \DndSpellHeader{II: Tidal Wave \label{spell::tidalwave}}
        {Alchemy spell - 5 spell points}
        {2/3 actions}
        {Variable}
        {V, S, M (a pint of water)}
        {Instantaneous}
        Your zuan dissolves into a wave of water that crashes down on an area within range.
        The area can be up to 6 meters long, up to 2 meters wide, and up to 2 meters tall.
        Each creature in that area must make a Dexterity saving throw.
        On a failed save, a creature takes 4d8 bludgeoning damage and is knocked prone.
        On a successful save, a creature takes half as much damage and isn't knocked prone.
        The water then spreads out across the ground in all directions, extinguishing unprotected flames in its area and within 6 meters of it, and then it vanishes.

        After casting the spell, the water falls to the ground, causing the affected area to be affected by the \textbf{Grease} spell (page \pageref{spell::grease}) for I rounds.
        This grease cannot burn.

        When you cast this spell, you can choose to spend another action and 2 additional spell points to cause the water to be boiling hot.
        Creatures that fail the Dexterity saving throw also take 2d8 fire damage on a successful save or half as much on a failed one.
    \DndSpellHeader{I: Caustic Brew \label{spell::causticbrew}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {30-meter line}
        {V, S, M (a bit of rotten food)}
        {Concentration, up to 1 minute}
        A stream of acid emanates from your zuan in a line 6 meters long and 1 meter wide in a direction you choose.
        Each creature in the line must succeed on a Dexterity saving throw or be covered in acid for the spell's duration or until a creature uses two action to scrape or wash the acid off itself or another creature.
        A creature covered in the acid takes 2d4 acid damage at start of each of its turns.

        The ground under the line is covered in acid, becoming difficult terrain for I rounds.
        In addition, any creature that starts its turn on it or moves through it takes 1d4 acid damage as the acid burns its soles.

        When you cast this spell, you can use up to 8 additional spell points to increase its damage by 2d4 and 1d4 for each point respectively.
    \DndSpellHeader{II: Acid Breath \label{spell::acidbreath}}
        {Alchemy spell - 3 spell points}
        {1 action}
        {Touch}
        {V, S, M (a hot pepper)}
        {Concentration, up to 1 minute}
        You touch one willing creature with your zuan and imbue it with the power to spew acid from its mouth, provided it has one.
        Until the spell ends, the creature can use two actions to exhale acid in a 3-meter cone.
        Each creature in that area must make a Dexterity saving throw, taking 3d6 acid damage on a failed save, or half as much damage on a successful one.

        When you lose concentration on this spell, the effect remains for an additional I/2 rounds.

        When you cast this spell, you can choose to use up to 7 additional spell points, increasing the damage by 1d6 for each additional point.
        In addition, you can use 2 actions and 2 spell points on your turn to induce the creature to spew the acid in a direction of its choice as a reaction.
    \DndSpellHeader{I: Grease \label{spell::grease}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {2-meter square}
        {V, S, M (a bit of butter)}
        {1 minute}
        Slick grease covers the ground in a 2-meter square centered on your zuan and turns it into difficult terrain for the duration.

        When the grease appears, each creature standing in its area must succeed on a Dexterity saving throw or fall prone.
        A creature that enters the area or ends its turn there must also succeed on a Dexterity saving throw or fall prone.

        If fire touches the grease, it burns for I rounds.
        In addition to its other effects, any creature that enters the area or ends its turn there take 1d8 fire damage.

        When you cast this spell, you can choose to use up to 8 additional spell points, increasing the length of the square's sides by a meter for each additional spell point used.
    \DndSpellHeader{II: Web \label{spell::web}}
        {Alchemy spell - 3 spell points}
        {2 actions}
        {4-meter cube}
        {V, S, M (a bit of spiderweb)}
        {Concentration, up to 1 hour}
        You conjure a mass of thick, sticky webbing from your zuan.
        The webs fill a 4-meter cube from that point for the duration.
        The webs are difficult terrain and lightly obscure their area.

        If the webs aren't anchored between two solid masses (such as walls or trees) or layered across a floor, wall, or ceiling, the conjured web collapses on itself, and the spell ends at the start of your next turn.
        Webs layered over a flat surface have a depth of a meter.

        Each creature that starts its turn in the webs or that enters them during its turn must make a Dexterity saving throw.
        On a failed save, the creature is restrained as long as it remains in the webs or until it breaks free.

        A creature restrained by the webs can use its action to make a Strength check against your spell save DC.
        If it succeeds, it is no longer restrained.

        The webs are flammable.
        Any 1-meter cube of webs exposed to fire burns away in I rounds, dealing 2d4 fire damage to any creature that starts its turn in the fire.

        When you cast this spell, you can choose to use up to 14 additional spell points, increasing the length of the cube's sides by a meter for each 2 additional spell points consumed.
    \DndSpellHeader{I: Ice Storm \label{spell::icestorm}}
        {Alchemy spell - 6 spell points}
        {2 actions}
        {4-meter-radius, 8-meter-high cylinder}
        {V, S, M (a pinch of dust and drops of water)}
        {Instantaneous}
        A hail of rock-hard ice pounds to the ground in a 4-meter-radius, 8-meter-high cylinder centered on your zuan.
        Each creature in the cylinder must make a Dexterity saving throw.
        A creature takes 2d8 bludgeoning damage and 4d6 cold damage on a failed save, or half as much damage on a successful one.

        Hailstones turn the storm's area of effect into difficult terrain for I rounds.

        When you cast the spell, you can choose to use up to 5 additional spell points, increasing the bludgeoning damage by 1d8 for each additional point used.
    \DndSpellHeader{II: Cone of Cold \label{spell::coneofcold}}
        {Alchemy spell - 7 spell points}
        {2 actions}
        {12-meter-cone}
        {V, S, M (a small glass cone)}
        {Instantaneous}
        A blast of cold air erupts from your zuan.
        Each creature in a 12-meter cone must make a Constitution saving throw.
        A creature takes 8d8 cold damage on a failed save, or half as much damage on a successful one.

        A creature killed by this spell becomes a frozen statue until it thaws.

        The ground under the cone becomes difficult terrain for I rounds.

        When you cast this spell, you can choose to use up to 4 additional spell points, increasing the cold damage dealt by 1d8 for each point consumed.
    \DndSpellHeader{I: Watery Sphere \label{spell::waterysphere}}
        {Alchemy spell - 6 spell points}
        {2 actions}
        {1-meter-radius sphere}
        {V, S, M (a droplet of water)}
        {Concentration, up to 1 minute}
        You dissolve your zuan into a sphere of water with a 1-meter radius.
        The sphere remains for the spell's duration.

        Any creature in the sphere's space must make a Strength saving throw.
        On a successful save, a creature is ejected from that space to the nearest unoccupied space of the creature's choice outside the sphere.
        A Huge or larger creature succeeds on the saving throw automatically, and a Large or smaller creature can choose to fail it.
        On a failed save, a creature is restrained by the sphere and is engulfed by the water.
        At the end of each of its turns, a restrained target can repeat the saving throw, ending the effect on itself on a success.

        The sphere can restrain as many as four Medium or smaller creatures or one Large creature.
        If the sphere restrains a creature that causes it to exceed this capacity, a random creature that was already restrained by the sphere falls out of it and lands prone in a space within a meter of it.

        Any creature restrained by the sphere moves with it.
        You can ram the sphere into creatures, forcing them to make the saving throw.

        When the spell ends, the sphere falls to the ground and extinguishes all normal flames within 6 meters of it.
        Any creature restrained by the sphere is knocked prone in the space where it falls.
        Your zuan reforms while the water remains in a 6-meter-radius circle, causing the ground to be affected by the Grease (page \pageref{spell::grease}) spell for I rounds.
        This grease cannot burn.

        When you cast this spell, you can choose to spend another action and 3 additional spell points to cause the water to be boiling hot.
        Any creature that starts its turn in the ball takes 2d8 fire damage.
    \DndSpellHeader{II: Platinum Shield \label{spell::platinumshield}}
        {Alchemy spell - 10 spell points}
        {1 action}
        {2-meter-radius sphere}
        {V, S, M (a platinum piece)}
        {Concentration, up to 1 minute}
        You create a field of silvery light that surrounds your zuan.
        The field sheds dim light out to a meter.
        While surrounded by the field, a creature gains the following benefits:

        \paragraph{Cover}
        The creature has half cover.
        \paragraph{Damage Resistance}
        The creature has resistance to acid, cold, fire, lightning, and poison damage.
        \paragraph{Evasion}
        If the creature is subjected to an effect that allows it to make a Dexterity saving throw to take only half damage, the creature instead takes no damage if it succeeds on the saving throw, and only half damage if it fails.

        When the spell ends, the field dissolves into water, restoring Id4 hit points to any creature that was immersed in it.
\subsection*{Fagal Affinity}
    \DndSpellHeader{Fagal Affinity: Volatilize \label{medium::volatilize}}
        {Alchemy medium}
        {X actions}
        {RANGE mt.}
        {COMPONENTS}
        {DURATION}
        DESCRIPTION
    \DndSpellHeader{Fagal Affinity: Rage \label{medium::rage}}
        {Warchanter medium}
        {2 actions}
        {Touch}
        {V}
        {Up to 10 minutes}
        A small crimson tetrahedron emerges from your zuan, penetrating the skin of a willing creature of your choice within range.
        The creature takes 1d4 piercing damage as it is infused with primal ferocity, entering a rage.

        While raging, a creature gains the following benefits:
        \begin{itemize}
            \item It has advantage on Strength checks and Strength saving throws.
            \item When it makes a melee weapon attack using Strength, it gains a bonus to the damage roll equal to your spellcasting ability modifier.
            \item It has resistance to bludgeoning, piercing, and slashing damage.
            \item If it is able to cast spells, it can't cast them or concentrate on them while raging.
        \end{itemize}

        For each round that the creature is raging you burn 1 spell point.
        The rage ends if the creature falls unconscious or dies.
        You can also use an action on your turn to end the rage.

        While the creature is raging, you can use an action and consume two additional spell points to produce one of the following effects:

        \subparagraph{Primal Frenzy}
        During the creature's next turn, it can make a single melee weapon attack as a free action during its turn.
        This attack doesn't cause and isn't affected by the multiple attack penalty.
        \subparagraph{Feral Instinct}
        Until the beginning of your next turn, the creature cannot be charmed or frightened.
        If it is charmed or frightened when you use this ability, the effect ends.
        \subparagraph{Instinctive Pounce}
        When you use this ability, the creature can move up to its moving speed towards a creature within reach and make a melee attack using Strength as a reaction.

        Only one creature can be affected by this medium at the same time.
    \DndSpellHeader{Rhelath's Dance \label{spell::rhelathsdance}}
        {Warchanter signature spell - Variable spell points}
        {2 actions}
        {Touch}
        {V, M (a few hairs from a bull)}
        {Concentration, up to 10 minutes}
        You endow a creature affected by the Rage medium with endurance fueled by your alchemy.
        Until the spell ends, the creature gains the following benefits:

        \begin{itemize}
            \item The creature gains a number of temporary hit points equal to your level times 5.
            If any of these remain when the spell ends, they are lost.
            \item The creature's multiple attack penalty is reduced to 0.
            \item When the creature hits a target with a melee weapon attack using Strength, that target takes an extra 1d6 force damage.
            This damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).
            \item The creature has advantage on Constitution saving throws.
            \item The creature's fingernails sharpen, ready to deliver a corrosive attack.
            On an unarmed strike, the creature can choose to deal 1d8 acid damage + their Strength modifier instead of the normal damage for such an attack.
        \end{itemize}

        When this effect ends, the creature must succeed on a DC 15 Constitution saving throw or suffer one level of exhaustion.

        The cost for casting this spell is equal to your level divided by 2 (rounded down).

        Every turn the creature is affected by this spell, your zuan loses 1 fagal alignment point.
        If it drops to zero, the spell ends early.
    \DndSpellHeader{I: Ensnaring Strike \label{spell::ensnaringstrike}}
        {Alchemy spell - 2 spell points}
        {1/2 action}
        {Self}
        {V}
        {Concentration, up to 1 minute}
        The next time you hit a creature with a weapon attack before this spell ends, a writhing mass of thorny vines appears at the point of impact, and the target must succeed on a Strength saving throw or be restrained by the vines until the spell ends.
        A Large or larger creature has advantage on this saving throw.
        If the target succeeds on the save, the vines shrivel away.

        While restrained by this spell, the target takes 1d6 piercing damage at the start of each of its turns.
        A creature restrained by the vines or one that can touch the creature can use two actions to make a Strength check against your spell save DC.
        On a success, the target is freed.

        When you cast this spell, you can choose to spend up to 8 additional spell points, increasing the damage by 1d6 for each point.

        In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
        Upon sprouting, the vines are smoldering hot, dealing 1d6 fire damage for each silver alignment point consumed to a restrained creature at the start of each of its turns.
    \DndSpellHeader{I: Acid Arrow \label{spell::acidarrow}}
        {Alchemy spell - 3 spell points}
        {2/3 actions}
        {18 meters}
        {S, M (powdered rhubarb leaf and an adder's stomach)}
        {Instantaneous}
        A shimmering green arrow streaks forth from your zuan into a target within range, bursting in a spray of acid.
        Make a ranged spell attack against the target.
        On a hit, the target takes 4d4 acid damage immediately and 2d4 acid damage at the end of its next turn.
        On a miss, the arrow splashes the target with acid for half as much of the initial damage and no damage at the end of its next turn.

        When you cast this spell, you can use up to 7 additional spell points, increasing the damage (both initial and later) by 1d4 for each point.

        In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
        When you do so, you infuse your zuan with acid.
        The next time your zuan touches a creature, it must succeed on a Constitution saving throw or take 2d4 acid damage for each alignment point consumed in this way.
    \DndSpellHeader{I: Minute Meteors \label{spell::minutemeteors}}
        {Alchemy spell - 5 spell points}
        {2 actions}
        {Touch}
        {V, S, M (niter, sulfur, and pine tar formed into a bead)}
        {Concentration, up to 10 minutes}
        You cause S tiny meteors to spawn from your zuan, which float and orbit your zuan for the spell's duration.
        When you cast the spell --- and as an action on each of your turns thereafter --- you can expend one or two of the meteors, sending them streaking toward a point or points you choose within 24 meters of your zuan.
        Once a meteor reaches its destination or impacts against a solid surface, the meteor explodes.
        Each creature within a meter of the point where the meteor explodes must make a Dexterity saving throw.
        A creature takes 2d6 fire damage on a failed save, or half as much damage on a successful one.

        When you cast this spell, you can choose to spend up to 6 additional spell points.
        The number of meteors you create increases by two for each point.
    \DndSpellHeader{II: Crown of Stars \label{spell::crownofstars}}
        {Alchemy spell - 10 spell points}
        {2 actions}
        {Touch}
        {V, S}
        {1 hour}
        S star-like motes of light appear and orbit your zuan until the spell ends.
        You can use an action to send one of the motes streaking toward one creature or object within 24 meters of your zuan.
        When you do so, make a ranged spell attack.
        On a hit, the target takes 4d12 radiant damage.
        Whether you hit or miss, the mote is expended.
        The spell ends early if you expend the last mote.

        If you have four or more motes remaining, they shed bright light in a 6-meter radius and dim light for an additional 30 meters.
        If you have one to three motes remaining, they shed dim light in a 6-meter radius.

        When you cast this spell, you can choose to spend up to 4 additional spell points, increasing the number of motes by one for each point.
    \DndSpellHeader{I: Magic Missile \label{spell::magicmissile}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {24 meters}
        {V, S}
        {Instantaneous}
        You create S glowing darts of force from your zuan.
        Each dart hits a creature of your choice that you can see within range.
        A dart deals 1d4 + 1 force damage to its target.
        The darts all strike simultaneously, and you can direct them to hit one creature or several.

        You can use up to 8 additional spell points when you cast this spell, creating one more dart for each point.
    \DndSpellHeader{II: Counterspell \label{spell::counterspell}}
        {Alchemy spell - 5 spell points}
        {1 reaction, which you take when you see a creature within 12 meters of your zuan casting a spell}
        {12 meters}
        {S}
        {Instantaneous}
        You attempt to interrupt a creature in the process of casting a spell.
        Make an ability check using your spellcasting ability.
        The DC equals 6 + the number of spell points used to cast the spell.
        On a success, the creature's spell fails and has no effect.

        When you cast this spell, you can choose to spend 3 additional spell points to charge your zuan with the lost energy.
        The next time you damage a creature using your zuan before the end of your next turn, the creature takes an additional Sd6 force damage from the accumulated volatility.
    \DndSpellHeader{I: Kruphix's Mockery \label{spell::kruphixsmockery}}
        {Alchemy spell - 6 spell points}
        {1 minute}
        {6 meters}
        {V, S, M (a small stone)}
        {8 hours}
        You divide your zuan into 2, allowing the new stone to orbit a willing creature of your choice within range (including yourself) while the old still acts as your zuan.
        The new zuan emulates a \textbf{Kruphix Stone} (see page \pageref{item::kruphixstone}), boosting the abilities of the creature.
        You choose the stone to take one of the following shapes when you cast this spell:
        \begin{itemize}
            \item \textbf{Agility}.
            The creature's Dexterity score increases by 2, to a maximum of 22, while this deep red sphere orbits its head.
            \item \textbf{Awareness}.
            The creature can't be surprised while this dark blue rhomboid orbits its head.
            \item \textbf{Fortitude}.
            The creature's Constitution score increases by 2, to a maximum of 22, while this pink rhomboid orbits its head.
            \item \textbf{Insight}.
            The creature's Wisdom score increases by 2, to a maximum of 22, while this incandescent blue sphere orbits its head.
            \item \textbf{Intellect}.
            The creature's Intelligence score increases by 2, to a maximum of 22, while this marbled scarlet and blue sphere orbits its head.
            \item \textbf{Leadership}.
            The creature's Charisma score increases by 2, to a maximum of 22, while this marbled pink and green sphere orbits its head.
            \item \textbf{Might}.
            The creature's Strength score increases by 2, to a maximum of 22, while this pale blue rhomboid orbits its head.
            \item \textbf{Protection}.
            The creature gains a +1 bonus to AC while this dusty rose prism orbits its head.
        \end{itemize}

        A stone has AC 20, 10 hit points, and resistance to all damage.
        It is considered to be an object that is being worn while it orbits a head.
        A destroyed stone fades into dust as it falls to the ground.

        A creature can only benefit from one stone generated in this way at once.

        If you cast this spell again before its duration is up, all the stones generated by this spell are lost.

        When you cast this spell, you can choose to use up to 10 additional spell points.
        One new stone is created for each 2 points added.
        These stones can be the same or different from each other and can orbit any number of willing creatures.
    \DndSpellHeader{II: Death Ward \label{spell::deathward}}
        {Alchemy spell - 6 spell points}
        {2/3 actions}
        {Touch}
        {V, S}
        {8 hours}
        A creature within a meter of your zuan is infused with a shard off it.

        The first time the target would drop to 0 hit points as a result of taking damage, the target instead drops to 1 hit point, and the spell ends.

        If the spell is still in effect when the target is subjected to an effect that would kill it instantaneously without dealing damage, that effect is instead negated against the target, and the spell ends.

        When you cast this spell, you can choose to use an additional action and 3 more spell points to infuse the zuan shard with volatility.
        If the spell ends as the result of an attack, the shard leaves the creature and darts toward the source of the damage.
        If it's a creature, it must roll a Dexterity saving throw as the shard attempts to crystallize on its skin.
        On a failed save, the creature takes Sd8 piercing damage, taking half damage on a successful save.
    \DndSpellHeader{I: Continual Flame \label{spell::continualflame}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {Touch}
        {V, S, M (a bit of moss, which the spell consumes)}
        {Until dispelled}
        You infuse a bit of moss with volatility, causing it to give off a faint green glow.
        The glowing moss provides bright light in a 4-meter radius and dim light for an additioanl 4 meters.
        This light can be covered or hidden, but not smothered.
    \DndSpellHeader{II: Sickening Radiance \label{spell::sickeningradiance}}
        {Alchemy spell - 6 spell points}
        {2/3 actions}
        {6-meter-radius sphere}
        {V, S, M (a bit of moss)}
        {Concentration, up to 10 minutes}
        Dim, greenish light spreads within a 6-meter-radius sphere centered on your zuan.
        The light spreads around corners, and it lasts until the spell ends.

        When a creature moves into the spell's area for the first time on a turn or starts its turn there, that creature must succeed on a Constitution saving throw or take 4d10 radiant damage, and it suffers one level of exhaustion and emits a dim, greenish light in a 1-meter radius.
        This light makes it impossible for the creature to benefit from being invisible.
        The light and any levels of exhaustion caused by this spell go away when the spell ends.

        When you cast this spell, you can choose to use another action and consume all your

        In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
        If you do so, the radiance burns the skin of all creatures that fail on the Constitution saving throw.
        In addition to the radiant damage, they take 1d8 fire damage at the start of each of their turns for a number of rounds equal to the alignment points consumed in this way.
        Constructs are immune to this effect.
    \DndSpellHeader{I: Inflict Wounds \label{spell::inflictwounds}}
        {Alchemy spell - 2 spell points}
        {2 actions}
        {Touch}
        {V, S}
        {Instantaneous}
        Make a melee spell attack against a creature a meter from your zuan.
        On a hit, the target takes 3d10 necrotic damage.

        When you cast this spell, you can choose to use up to 8 additional spell points, increasing the damage by 1d10 for each point.

        In addition, you can choose to use another action to consume some your zuan's silver alignment when casting this spell.
        If you do so, the area hit by your zuan turns into a sickly color as poison seeps into the skin of the affected creature.
        In addition to the radiant damage, the creature takes 1d10 poison damage at the start of each of its turns for a number of rounds equal to the alignment points consumed in this way.
        Constructs are immune to this effect.
    \DndSpellHeader{II: Vampiric Touch \label{spell::vampirictouch}}
        {Alchemy spell - 5 spell points}
        {2/3 actions}
        {Touch}
        {V, S}
        {Concentration, up to 1 minute}
        You let the natural volatility of your zuan to take control, allowing it to syphon life.
        Make a melee spell attack against a creature within a meter of your zuan.
        On a hit, the target takes 3d6 necrotic damage, and you regain hit points equal to half the amount of necrotic damage dealt.
        Until the spell ends, you can make the attack again on each of your turns using two actions.

        You can use up to 6 additional spell points when you cast this spell, increasing the damage by 1d6 for each point.

        Each time you attack a creature with this spell, you can choose to use another action and reduce your zuan's silver alignment by 1.
        If you do so, the creature cannot regain hit points until the start of your next turn.
    \DndSpellHeader{II: Harm \label{spell::harm}}
        {Alchemy spell - 9 spell points}
        {2 actions}
        {24 meters}
        {V, S}
        {Instantaneous}
        You unleash a virulent disease on a creature within 24 meters of your zuan.
        The target must make a Constitution saving throw.
        On a failed save, it takes 14d6 necrotic damage, or half as much damage on a successful save.
        The damage can't reduce the target's hit points below 1.
        If the target fails the saving throw, its hit point maximum is reduced for 1 hour by an amount equal to the necrotic damage it took.
        Any effect that removes a disease allows a creature's hit point maximum to return to normal before that time passes.
    \DndSpellHeader{II: Horrid Wilting \label{spell::horridwilting}}
        {Alchemy spell - 11 spell points}
        {2 actions}
        {6-meter cube}
        {V, S, M (a bit of sponge)}
        {Instantaneous}
        You draw the moisture from every creature in a 6-meter cube centered on your zuan.
        Each creature in that area must make a Constitution saving throw.
        Constructs and undead aren't affected, and plants and oozes make this saving throw with disadvantage.
        A creature takes 12d8 necrotic damage on a failed save, or half as much damage on a successful one.

        Nonmagical plants in the area that aren't creatures, such as trees and shrubs, wither and die instantly.

        When you cast this spell, you can choose to use another action and 2 additional spell points to allow your zuan to feed off the absorbed moisture.
        Each creature that takes damage from this spell increases your zuan's silver alignment by 1.
        If this spell increases its alignment beyond the maximum value, it reverts to that at the end of your next turn.
    \DndSpellHeader{I: Shadow Weapon \label{spell::shadoweapon}}
        {Alchemy spell - 3 spell points}
        {1 action}
        {Touch}
        {V, S}
        {Concentration, up to 1 minute}
        You allow your zuan to transform into a staff of solidified gloom, which can be grabbed by yourself as a free action or by a creature within a meter of it as a reaction.
        This staff lasts until the spell ends.
        It counts as a simple melee weapon that deals 2d6 necrotic damage on a hit or 2d8 if used with two hands, and has the finesse, light, and versatile properties.
        In addition, when the staff is used to attack a target that is in dim light or darkness, the attack roll is made with advantage.

        If the weapon is dropped, it dissipates at the end of the round.

        You can use up to 6 additional spell points when you cast this spell, increasing the number of damage dice by 1 for each 2 spell points used.

        When you attack with this weapon, you can choose to use another action to allow your zuan to feed off the target of your attack.
        If you do so, the attack gains a damage bonus equal to your spellcasting ability modifier, and you increase the silver alignment of your zuan by 1.
        If this attack increases its alignment beyond the maximum value, it reverts to that at the end of your next turn.
    \DndSpellHeader{II: Ukarilth's Staff \label{spell::ukarilthsstaff}}
        {Alchemy spell - 10 spell points}
        {2 actions}
        {Touch}
        {V, S, M (a piece of iron)}
        {Concentration, up to 1 minute}
        You transform your zuan into a long, thin cylinder resembling a quarterstaff.
        The staff is a mass of scintillating colors and it lasts for the duration.

        When the staff appears, you make a melee spell attack against a target of your choice within a meter of the staff.
        On a hit, the target takes 3d10 force damage.
        Once per turn until the spell ends, you can use an action on each of your turns to move the staff up to 4 meters to a spot you can see and repeat this attack against the same target or a different one.

        When you attack with this weapon, you can choose to use another action to allow your zuan to feed off the target of your attack.
        If you do so, the attack gains a damage bonus equal to your spellcasting ability modifier, and you increase the silver alignment of your zuan by 1.
        If this attack increases its alignment beyond the maximum value, it reverts to that at the end of your next turn.
