% !TEX root = ../main.tex
\section{Signature Spells} \label{sec::signaturespells}
% A
% B
\DndSpellHeader{Chain Healing \label{spell::chainhealing}}
    {Shellpoacher signature spell - Variable spell points}
    {2 actions}
    {---}
    {V, S}
    {Instantaneous}
    All bound creatures within 6 meters of another bound creature regain a number of d8s equal to half your level (rounded down) + your spellcasting ability modifier in hit points.
    In addition, a creature that receives healing through this spell gains a +1 bonus to AC and saving throws until the end of your next turn.

    This spell consumes a number of spell points equal to half your level (rounded down).
    When you reach 11th level, the maximum range around a bound creature is extended to 12 meters.
% C
% D
% E
% F
% G
\DndSpellHeader{Guided Strike \label{spell::guidedstrike}}
    {Frithbinder signature spell - 0 spell points}
    {1 action}
    {12 meters}
    {S}
    {Instantaneous}
    You ask frithling linked to you within range to shelter inside an object within 4 meters of the frithling as a reaction.
    If the object is used to strike a creature, you can spend an action or a reaction and 2 spell points to give advantage to the related attack or disadvantage on the related saving throw, and cause the strike to deal an additional 2d6 radiant damage.

    You can consume up to 8 additional spell points when casting this spell, increasing the damage by 1d6 for each spell points beyond the first two used.
    In addition, you can consume 2 additional spell points to cause the frithling to switch shelter to an object worn by the creature stuck by the object as if it was affected by the \textbf{Frithbind} medium (page \pageref{medium::frithbind}).
% H
% I
% J
% K
% L
% M
% N
% O
% P
\DndSpellHeader{Pharika's Execution \label{spell::pharikasexecution}}
    {Deathtoucher signature spell - Variable spell points}
    {2 actions}
    {Touch}
    {S}
    {Instantaneous}
    You make a melee weapon attack with a piercing or slashing weapon or a ranged attack against a creature afflicted with at least one level of toxicity.
    On a hit, in addition to the normal damage of the attack, you burn through all the arsenic accumulated in the target, dealing 1d4 poison and 1d4 necrotic damage for each toxicity level.
    When you do this, you also gain a number of temporary hit points equal to half the toxicity levels burned plus the number of spell points used to cast this spell, and the toxicity level of the target is reduced to 0.

    Both damage dice of this spell increase to a d6 when you reach 5th level, to a d8 when you reach 11th level, and to a d10 at 17th level.

    Using this spell requires a number of spell points equal to half your level.
% Q
% R
\DndSpellHeader{Rhelath's Dance \label{spell::rhelathsdance}}
    {Warchanter signature spell - Variable spell points}
    {2 actions}
    {Touch}
    {V, M (a few hairs from a bull)}
    {Concentration, up to 10 minutes}
    You endow a creature affected by the Rage medium with endurance fueled by your alchemy.
    Until the spell ends, the creature gains the following benefits:

    \begin{itemize}
        \item The creature gains a number of temporary hit points equal to your level times 5.
        If any of these remain when the spell ends, they are lost.
        \item The creature's multiple attack penalty is reduced to 0.
        \item When the creature hits a target with a melee weapon attack using Strength, that target takes an extra 1d8 force damage.
        This damage increases by 1d6 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).
        \item The creature has advantage on Constitution saving throws.
        \item The creature's fingernails sharpen, ready to deliver a corrosive attack.
        On an unarmed strike, the creature can choose to deal 1d8 acid damage + their Strength modifier instead of the normal damage for such an attack.
    \end{itemize}

    When this effect ends, the creature must succeed on a DC 15 Constitution saving throw or suffer one level of exhaustion.

    The cost for casting this spell is equal to your level divided by 2 (rounded down).

    Every turn the creature is affected by this spell, your zuan loses 1 silver alignment point.
    If it drops to zero, the spell ends early.
% S
\DndSpellHeader{Screaming Bead \label{spell::screamingbead}}
    {Flamespeaker signature spell - 2 spell points}
    {2 actions}
    {30 meters}
    {S, M (a firetrap)}
    {Up to 24 hours}
    You cause an ember within range to turn into a glowing yellow bead.
    When you end the spell, the bead blossoms with a low roar into an explosion of flame that spreads around corners.
    Each creature in a 4-meter-radius sphere centered on that point must make a Dexterity saving throw.
    A creature takes fire damage equal to the total accumulated damage on a failed save, or half as much damage on a successful one.

    The spell's base damage is 2d6.
    If at the end of your turn the bead has not yet detonated, the bead grows slightly and the damage increases by 2d6.
    The maximum number of damage dice of this spell is equal to your level.
    When the spell reaches this damage, the bead stops growing.

    The bead sheds a bright light up to a radius equal to 1/4ths its number of damage dice in meters and dim light up to double that distance.

    The fire damages objects in the area and ignites flammable objects that aren't being worn or carried.

    This spell consumes two spell points when you cast it, and one additional spell point for each two damage dice added to it (one additional point at 4d6, another at 6d6, etc).
\DndSpellHeader{Skycall \label{spell::skycall}}
    {Skycaller signature spell - Variable spell points}
    {2 actions}
    {30 meters}
    {S, M (an aragonite shard)}
    {Instantaneous}
    You call lightning down from the sky, landing in the middle of the sphere affected by the \textbf{Dry Air} medium (page \pageref{medium::dryair}).
    All creatures in the sphere must make a Dexterity saving throw.
    A creature takes a number of d10s equal to half your level (rounded down) in lightning damage on a failed save, plus 1d10 thunder damage for each charge they have.
    Charged creatures within a 4-meter radius of the sphere must also make the saving throw, taking 1d10 thunder damage for each charge they have.
    A creature that takes thunder damage from this spell loses all its charges.

    This spell consumes a number of spell points equal to half your level (rounded down).
% T
% U
% V
% W
% X
% Y
% Z
