% !TEX root = ../main.tex
\section{Miscellaneous Spells}
This section contains spells not directly related to any school, like the innate magic from oths and zaloths.

% A
\DndSpellHeader{Alter Self \label{spell::alterself}}
    {Miscellaneous Spell}
    {2 actions}
    {Self}
    {S}
    {1 hour}
    You assume a different form.
    When you cast the spell, choose one of the following options, the effects of which last for the duration of the spell.
    While the spell lasts, you can end one option as an action to gain the benefits of a different one.

    \paragraph{Aquatic Adaptation}
        You adapt your body to an aquatic environment, sprouting gills and growing webbing between your fingers.
        You can breathe underwater and gain a swimming speed equal to your walking speed.

    \paragraph{Change Appearance}
        You transform your appearance.
        You decide what you look like, including your height, weight, facial features, sound of your voice, hair length, coloration, and distinguishing characteristics, if any.
        You can make yourself appear as a member of another kin, though none of your statistics change.
        You also can't appear as a creature of a different size than you, and your basic shape stays the same; if you're bipedal, you can't use this spell to become quadrupedal, for instance.
        At any time for the duration of the spell, you can use two actions to change your appearance in this way again.

    \paragraph{Natural Weapons}
        You grow claws, fangs, spines, horns, or a different natural weapon of your choice.
        Your unarmed strikes deal 1d6 bludgeoning, piercing, or slashing damage, as appropriate to the natural weapon you chose.
        You use your proficiency with simple weapons for your unarmed strikes.
        Finally, the natural weapon has a +1 bonus to the attack and damage rolls you make using it.
% B
\DndSpellHeader{Burning Hands \label{spell::burninghands}}
    {Miscellaneous spell}
    {2 actions}
    {3-meter cone}
    {S}
    {Instantaneous}
    As you hold your hands with thumbs touching and fingers spread, a thin sheet of flames shoots forth from your outstretched fingertips.
    Each creature in a 3-meter cone must make a Dexterity saving throw.
    A creature takes 3d6 fire damage on a failed save, or half as much damage on a successful one.

    The fire ignites any flammable objects in the area that aren't being worn or carried.
% C
\DndSpellHeader{Charm Person \label{spell::charmperson}}
    {Miscellaneous Spell}
    {2 actions}
    {6 meters}
    {V, S}
    {1 hour}
    You attempt to charm a humanoid you can see within range.
    It must make a Wisdom saving throw, and does so with advantage if you or your companions are fighting it.
    If it fails the saving throw, it is charmed by you until the spell ends or until you or your companions do anything harmful to it.
    The charmed creature regards you as a friendly acquaintance.
    When the spell ends, the creature knows it was charmed by you.
% D
\DndSpellHeader{Detect Thoughts \label{spell::detectthoughts}}
    {Miscellaneous Spell}
    {2 actions}
    {Self}
    {S}
    {Concentration, up to 1 minute}
    For the duration, you can perceive the thoughts of certain creatures.
    When you cast the spell and as your action on each turn until the spell ends, you can focus your mind on any one creature that you can see within 6 meters of you.
    If the creature you choose has an Intelligence of 3 or lower or doesn't speak any language, the creature is unaffected.

    You initially learn the surface thoughts of the creature-what is most on its mind in that moment.
    As an action, you can either shift your attention to another creature's thoughts or attempt to probe deeper into the same creature's mind.
    If you probe deeper, the target must make a Wisdom saving throw.
    If it fails, you gain insight into its reasoning (if any), its emotional state, and something that looms large in its mind (such as something it worries over, loves, or hates).
    If it succeeds, the spell ends.
    Either way, the target knows that you are probing into its mind, and unless you shift your attention to another creature's thoughts, the creature can use its action on its turn to make an Intelligence check contested by your Intelligence check; if it succeeds, the spell ends.

    Questions verbally directed at the target creature naturally shape the course of its thoughts, so this spell is particularly effective as part of an interrogation.

    You can also use this spell to detect the presence of thinking creatures you can't see.
    When you cast the spell or as your action during the duration, you can search for thoughts within 6 meters of you.
    You can't detect a creature with an Intelligence of 3 or lower or one that doesn't speak any language.

    Once you detect the presence of a creature in this way, you can read its thoughts for the rest of the duration as described above, even if you can't see it, but it must still be within range.
\DndSpellHeader{Dust Devil \label{spell::dustdevil}}
    {Miscellaneous spell}
    {2 actions}
    {12 meters}
    {S}
    {Concentration, up to 1 minute}
    Choose an unoccupied 1-meter cube of air that you can see within range.
    An elemental force that resembles a dust devil appears in the cube and lasts for the spell's duration.

    Any creature that ends its turn within a meter of the dust devil must make a Strength saving throw.
    On a failed save, the creature takes 1d8 bludgeoning damage and is pushed 2 meters away from the dust devil.
    On a successful save, the creature takes half as much damage and isn't pushed.

    As an action, you can move the dust devil up to 6 meters in any direction.
    If the dust devil moves over sand, dust, loose dirt, or light gravel, it sucks up the material and forms a 2-meter-radius cloud of debris around itself that lasts until the start of your next turn.
    The cloud heavily obscures its area.
% E
% F
% G
\DndSpellHeader{Gust \label{spell::gust}}
    {Miscellaneous spell}
    {2 actions}
    {6 meters}
    {S}
    {Instantaneous}
    You seize the air and compel it to create one of the following effects at a point you can see within range:
    \begin{itemize}
        \item One Medium or smaller creature that you choose must succeed on a Strength saving throw or be pushed up to 1 meter away from you.
        \item You create a small blast of air capable of moving one object that is neither held nor carried and that weighs no more than 2.5 kg.
        The object is pushed up to 2 meters away from you.
        It isn't pushed with enough force to cause damage.
        \item You create a harmless sensory effect using air, such as causing leaves to rustle, wind to slam shutters closed, or your clothing to ripple in a breeze.
    \end{itemize}
% H
% I
\DndSpellHeader{Ice Knife \label{spell::iceknife}}
    {Miscellaneous spell}
    {2 actions}
    {12 meters}
    {S}
    {Instantaneous}
    You create a shard of ice and fling it at one creature within range.
    Make a ranged spell attack against the target.
    On a hit, the target takes 1d10 piercing damage.
    Hit or miss, the shard then explodes.
    The target and each creature within a meter of it must succeed on a Dexterity saving throw or take 2d6 cold damage.
\DndSpellHeader{Icy Surface \label{spell::icysurface}}
    {Miscellaneous spell}
    {2 actions}
    {12 meters}
    {S}
    {1 minute}
    A thin sheet of ice covers the ground in a 4-meter square centered on a point within range.
    Upon entering the surface, a creature must succeed on a Dexterity saving throw.
    On a failed save, the creature slides across the surface until it hits a creature or object, or until its outside of the square.
    Upon hitting something, a creature takes 1d6 bludgeoning damage.

    When the sheet appears, each creature standing in its area must succeed on a Dexterity saving throw or fall prone, taking 1d6 bludgeoning damage.
    A creature that ends its turn there must also succeed on a Dexterity saving throw or fall prone and take the same damage.
\DndSpellHeader{Invisibility \label{spell::invisibility}}
    {Miscellaneous spell}
    {2 actions}
    {Touch}
    {S}
    {Concentration, up to 1 hour}
    A creature you touch becomes invisible until the spell ends.
    Anything the target is wearing or carrying is invisible as long as it is on the target's person.
    The spell ends for a target that attacks or casts a spell.
% J
% K
% L
% M
\DndSpellHeader{Minor Illusion \label{spell::minorillusion}}
    {Miscellaneous spell}
    {2 actions}
    {6 meters}
    {S}
    {1 minute}
    You create a sound or an image of an object within range that lasts for the duration.
    The illusion also ends if you dismiss it as an action or cast this spell again.

    If you create a sound, its volume can range from a whisper to a scream.
    It can be your voice, someone else's voice, a lion's roar, a beating of drums, or any other sound you choose.
    The sound continues unabated throughout the duration, or you can make discrete sounds at different times before the spell ends.

    If you create an image of an object---such as a chair, muddy footprints, or a small chest---it must be no larger than a 1-meter cube.
    The image can't create sound, light, smell, or any other sensory effect.
    Physical interaction with the image reveals it to be an illusion, because things can pass through it.

    If a creature uses its action to examine the sound or image, the creature can determine that it is an illusion with a successful Intelligence (Investigation) check against your spell save DC.
    If a creature discerns the illusion for what it is, the illusion becomes faint to the creature.
% N
% O
% P
\DndSpellHeader{Produce Flame \label{spell::produceflame}}
    {Miscellaneous spell}
    {1 action}
    {Self}
    {S}
    {10 minutes}
    A flickering flame appears in your hand.
    The flame remains there for the duration and harms neither you nor your equipment.
    The flame sheds bright light in a 2-meter radius and dim light for an additional 2 meters.
    The spell ends if you dismiss it as an action or if you cast it again.

    You can also attack with the flame, although doing so ends the spell.
    When you cast this spell, or as an action on a later turn, you can hurl the flame at a creature within 6 meters of you.
    Make a ranged spell attack.
    On a hit, the target takes 1d8 fire damage.

    This spell's damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).
% Q
% R
% S
\DndSpellHeader{Scorcher \label{spell::scorcher}}
    {Miscellaneous spell}
    {2 actions}
    {6 meters}
    {S}
    {Instantaneous}
    A line of roaring flame 6 meter long and 1 meter wide emanates from you in a direction you choose.
    Each creature in the line must make a Dexterity saving throw.
    A creature takes 3d8 fire damage on a failed save, or half as much damage on a successful one.
\DndSpellHeader{Scrying \label{spell::scrying}}
    {Miscellaneous Spell}
    {Until Dispelled}
    {Self}
    {V, S, M (a crystal ball worth at least 2,000 agnomas)}
    {Concentration, up to 10 minutes}
    You can see and hear a particular creature you choose that is on the same plane as you.
    The target must make a Wisdom saving throw, which is modified by how well you know the target and the sort of physical connection you have to it.
    If a target knows you're casting this spell, it can fail the saving throw voluntarily if it wants to be observed.

    \begin{DndTable}[width=\linewidth, header=Knowledge of Target]{lc}
        \textbf{Knowledge} & \textbf{Save Modifier} \\
        Secondhand (you have heard of the target) & +5 \\
        Firsthand (you have met the target)       & +0 \\
        Familiar (you know the target well)       & -5
    \end{DndTable}

    \begin{DndTable}[width=\linewidth, header=Connection to Target]{lc}
        \textbf{Connection} & \textbf{Save Modifier} \\
        Likeness or picture                               & -2 \\
        Possession or garment                             & -4 \\
        Body part, lock of hair, bit of nail, or the like & -10
    \end{DndTable}

    On a successful save, the target isn't affected, and you can't use this spell against it again for 24 hours.

    On a failed save, the spell creates an invisible sensor within 2 meters of the target.
    You can see and hear through the sensor as if you were there.
    The sensor moves with the target, remaining within 2 meters of it for the duration.
    A creature that can see invisible objects sees the sensor as a luminous orb about the size of your fist.

    Instead of targeting a creature, you can choose a location you have seen before as the target of this spell.
    When you do, the sensor appears at that location and doesn't move.
\DndSpellHeader{Shatter \label{spell::shatter}}
    {Miscellaneous spell}
    {2 actions}
    {12 meters}
    {S}
    {Instantaneous}
    A sudden loud ringing noise, painfully intense, erupts from a point of your choice within range.
    Each creature in a 2-meter-radius sphere centered on that point must make a Constitution saving throw.
    A creature takes 3d8 thunder damage on a failed save, or half as much damage on a successful one.
    A creature made of inorganic material such as stone, crystal, or metal has disadvantage on this saving throw.

    An object that isn't being worn or carried also takes the damage if it's in the spell's area.
\DndSpellHeader{Shivers \label{spell::shivers}}
    {Miscellaneous spell}
    {2 actions}
    {12 meters}
    {S}
    {Instantaneous}
    You cause numbing frost to form on one creature that you can see within range.
    The target must make a Constitution saving throw.
    On a failed save, the target takes 1d6 cold damage, and it has disadvantage on the next weapon attack roll it makes before the end of its next turn.

    The spell's damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).
\DndSpellHeader{Shocking Grasp \label{spell::shockinggrasp}}
    {Miscellaneous spell}
    {2 actions}
    {Touch}
    {S}
    {Instantaneous}
    Lightning springs from your hand to deliver a shock to a creature you try to touch.
    Make a melee spell attack against the target.
    You have advantage on the attack roll if the target is wearing armor made of metal.
    On a hit, the target takes 1d8 lightning damage, and it can't take reactions until the start of its next turn.

    The spell's damage increases by 1d8 when you reach 5th level (2d8), 11th level (3d8), and 17th level (4d8).
\DndSpellHeader{Slowfall \label{spell::slowfall}}
    {Miscellaneous spell}
    {1 reaction, which you take when you or a creature within 60 feet of you falls}
    {12 meters}
    {S}
    {1 minute}
    Choose up to five falling creatures within range.
    A falling creature's rate of descent slows to 12 meters per round until the spell ends.
    If the creature lands before the spell ends, it takes no falling damage and can land on its feet, and the spell ends for that creature.
\DndSpellHeader{Suggestion \label{spell::suggestion}}
    {Miscellaneous Spell}
    {2 actions}
    {6 meters}
    {V}
    {Concentration, up to 8 hours}
    You suggest a course of activity (limited to a sentence or two) and influence a creature you can see within range that can hear and understand you.
    Creatures that can't be charmed are immune to this effect.
    The suggestion must be worded in such a manner as to make the course of action sound reasonable.
    Asking the creature to stab itself, throw itself onto a spear, immolate itself, or do some other obviously harmful act ends the spell.

    The target must make a Wisdom saving throw.
    On a failed save, it pursues the course of action you described to the best of its ability.
    The suggested course of action can continue for the entire duration.
    If the suggested activity can be completed in a shorter time, the spell ends when the subject finishes what it was asked to do.

    You can also specify conditions that will trigger a special activity during the duration.
    For example, you might suggest that a knight give her warhorse to the first beggar she meets.
    If the condition isn't met before the spell expires, the activity isn't performed.

    If you or any of your companions damage the target, the spell ends.
\DndSpellHeader{Sunbeam \label{spell::sunbeam}}
    {Miscellaneous Spell}
    {2 actions}
    {Self (12-meter line)}
    {S}
    {Concentration, up to 1 minute}
    A beam of brilliant light flashes out from your hand in a 1-meter-wide, 12-meter-long line.
    Each creature in the line must make a Constitution saving throw.
    On a failed save, a creature takes 6d8 radiant damage and is blinded until your next turn.
    On a successful save, it takes half as much damage and isn't blinded by this spell.
    Fiends have disadvantage on this saving throw.

    You can create a new line of radiance as your action on any turn until the spell ends.

    For the duration, a mote of brilliant radiance shines in your hand.
    It sheds bright light in a 6-meter radius and dim light for an additional 6 meters.
    This light is sunlight.
% T
\DndSpellHeader{Telekinesis \label{spell::telekinesis}}
    {Miscellaneous Spell}
    {2 actions}
    {6 meters}
    {S}
    {1 minute}
    On your turn, you can use your action to manipulate an object, open an unlocked door or container, stow or retrieve an item from an open container, or pour the contents out of a vial within range.

    You cannot attack with this spell, or carry and object that weighs more than 5 kg.
\DndSpellHeader{Sonic Boom \label{spell::sonicboom}}
    {Miscellaneous spell}
    {2 actions}
    {3-meter cube}
    {S}
    {Instantaneous}
    A wave of thunderous force sweeps out from you.
    Each creature in a 3-meter cube originating from you must make a Constitution saving throw.
    On a failed save, a creature takes 2d8 thunder damage and is pushed 2 meters away from you.
    On a successful save, the creature takes half as much damage and isn't pushed.

    In addition, unsecured objects that are completely within the area of effect are automatically pushed 2 meters away from you by the spell's effect, and the spell emits a thunderous boom audible out to 60 meters.
% U
% V
% W
% X
% Y
% Z
