% !TEX root = ../main.tex
\section{Miscellaneous Spells}
This section contains spells not directly related to any school, like the innate magic from oths and zaloths and spells so commonplace that any spellcaster can learn them.

spell::alterself
spell::charmperson
spell::detectthoughts
spell::intellectfortress
spell::invisibility
spell::magehand
spell::message
spell::mindsliver
spell::rarystelepathicbond
spell::scrying
spell::sending
spell::suggestion
spell::sunbeam
spell::tashasmindwhip
spell::telekinesis
spell::tensersfloatingdisc

creature::frithling

\subsection*{Cantrips}
    \DndSpellHeader{Bewitchery \label{spell::bewitchery}}
        {Miscellaneous cantrip}
        {2 actions}
        {6 meters}
        {V}
        {Up to 1 minute}
        You manifest a minor wonder, a sign of strange power, within range.
        You create one of the following magical effects within range:
        \begin{itemize}
            \item Your voice booms up to three times as loud as normal for 1 minute.
            \item You cause flames to flicker, brighten, dim, or change color for 1 minute.
            \item You cause harmless tremors in the ground for 1 minute.
            \item You create an instantaneous sound that originates from a point of your choice within range, such as a rumble of thunder, the cry of a raven, or ominous whispers.
            \item You instantaneously cause an unlocked door or window to fly open or slam shut.
            \item You alter the appearance of your eyes for 1 minute.
        \end{itemize}
        If you cast this spell multiple times, you can have up to three of its 1-minute effects active at a time, and you can dismiss such an effect as an action.
    \DndSpellHeader{Mage Hand \label{spell::magehand}}
        {Miscellaneous cantrip}
        {2 actions}
        {6 meters}
        {V, S}
        {1 minute}
        An invisible force only you can perceive appears at a point you choose within range.
        You can manipulate this force as if it was a floating hand.
        The hand lasts for the duration or until you dismiss it as an action.
        The hand vanishes if it is ever more than 6 meters away from you or if you cast this spell again.

        You can use an action to control the hand.
        You can use the hand to manipulate an object, open an unlocked door or container, stow or retrieve an item from an open container, or pour the contents out of a vial.
        You can move the hand up to 6 meters each time you use it.

        The hand can't attack, activate magic items, or carry more than 5 kilograms.
    \DndSpellHeader{Prestidigitation \label{spell::prestidigitation}}
        {Miscellaneous cantrip}
        {2 actions}
        {2 meters}
        {V, S}
        {Up to 1 hour}
        This spell is a minor magical trick that novice spellcasters use for practice.
        You create one of the following magical effects within range:
        \begin{itemize}
            \item You create an instantaneous, harmless sensory effect, such as a shower of sparks, a puff of wind, faint musical notes, or an odd odor.
            \item You instantaneously light or snuff out a candle, a torch, or a small campfire.
            \item You instantaneously clean or soil an object no larger than 30 liters.
            \item You chill, warm, or flavor up to 30 liters of nonliving material for 1 hour.
            \item You make a color, a small mark, or a symbol appear on an object or a surface for 1 hour.
            \item You create a nonmagical trinket or an illusory image that can fit in your hand and that lasts until the end of your next turn.
        \end{itemize}
        If you cast this spell multiple times, you can have up to three of its non-instantaneous effects active at a time, and you can dismiss such an effect using two actions.
\subsection*{1st-level Spells}
    \DndSpellHeader{Charm Person \label{spell::charmperson}}
        {1st-level miscellaneous}
        {2/3 actions}
        {6 meters}
        {V, S}
        {1 hour}
        You attempt to charm a humanoid you can see within range.
        It must make a Wisdom saving throw, and does so with advantage if you or your companions are fighting it.
        If it fails the saving throw, it is charmed by you until the spell ends or until you or your companions do anything harmful to it.
        The charmed creature regards you as a friendly acquaintance.
        When the spell ends, the creature knows it was charmed by you.

        If you cast this spell using 3 actions, the target can't make the Wisdom saving throw with advantage, even if you or your companions are fighting it.

        \paragraph{At Higher Levels}
        When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
        The creatures must be within 6 meters of each other when you target them.
    \DndSpellHeader{Mage Armor \label{spell::magearmor}}
        {1st-level miscellaneous}
        {1 action}
        {Touch}
        {V, S, M (a piece of cured leather)}
        {8 hours}
        You touch a willing creature who isn't wearing armor, and a protective magical force surrounds it until the spell ends.
        The target's base AC becomes 13 + its Dexterity modifier.
        The spell ends if the target dons armor or if you dismiss the spell as an action.
    \DndSpellHeader{Shield \label{spell::shield}}
        {1st-level miscellaneous}
        {1 reaction, which you take when you are hit by an attack}
        {Self}
        {V, S}
        {1 round}
        An invisible barrier of magical force appears and protects you.
        Until the start of your next turn, you have a +5 bonus to AC, including against the triggering attack.
