% !TEX root = ../main.tex
\section{Bestiary}

\begin{DndMonster}[float*=b,width=\textwidth + 8pt]{Frithling}
\begin{multicols}{2}
    \DndMonsterType{Tiny elemental, unaligned}

    \DndMonsterBasics[
        armor-class = {15},
        hit-points  = {\DndDice{2d4}},
        speed       = {4 mt., climb 4 mt., swim 4 mt.},
    ]

    \DndMonsterAbilityScores[
        str = 1,
        dex = 20,
        con = 10,
        int = 14,
        wis = 16,
        cha = 16,
    ]

    \DndMonsterDetails[
        skills = {Acrobatics +7, Perception +7, Stealth +7},
        senses = {blindsight 12 mt., passive Perception 17},
        languages = {---},
        challenge = 0,
    ]

    % Traits
    \DndMonsterAction{Evasion}
        When the frithling is subjected to an effect that allows it to make a Dexterity saving throw to take only half damage, it instead takes no damage if it succeeds on the saving throw, and only half damage if it fails.

    \DndMonsterAction{Unusual Nature}
        The frithling doesn't require air, food, or drink.
        When it dies, it turns into a handful of flower petals, a cloud of pollen, a stone statuette resembling its former self, a tiny sphere of smooth stone, or a puddle of fresh water.

    \DndMonsterSection{Actions}
        \DndMonsterAction{Gift (1/Day)}
        The frithling targets a humanoid it can see within 1 meter of it.
        The target gains a trinket or charm of the DM's choice.
        See chapter 7 of the Dungeon Masters Guide for more information on trinkets and supernatural charms.

        \DndMonsterAction{Shelter}
        The frithling takes shelter inside an object in its space.
        The frithling can't be targeted by any attack, spell, or other effect while inside this shelter, and the shelter doesn't impair the frithling's blindsight.
        The frithling can use it's action to emerge from a shelter.
        If its shelter is destroyed, the frithling is forced out and appears in the shelter's space, but is otherwise unharmed.
\end{multicols}
\end{DndMonster}
