% !TEX root = ../main.tex
\chapter{Mechanic Changes} \label{ch::mechanicchanges}

\DndDropCapLine{S}{trands may break alone, but twisted}
\textit{make a braid.
Together on their own, the journey shall be made.}

\hspace*{\fill} --- Anonymous song.

This book includes major mechanical changes.
These mostly focus on allowing players to embrace the worldbuilding aspects of Yuadrem by freeing up their character building options.
These changes are of course optional, but most of the rules in the book were designed with them in mind.

Then, optional rules are included.
Yuadrem is a harsh continent, and these rules help set the atmosphere to reflect this.
They are completely optional, and a healthy gaming table should discuss which should be included or excluded in their game.

\begin{DndComment}[float=h]{Help Wanted!}
    This entire book was designed with the major mechanical changes considered, yet the author realizes that this can alienate a large part of the community.
    You may want to play in Yuadrem without these changes.
    If this is the case, many other mechanics need to be changed accordingly to acommodate this.

    If for some insane reason you want to take on this challenge, you are encouraged to contact the book's author.
    We could work together on this, discussing appropiate retribution and co-authorship terms.
\end{DndComment}

\input{03mechanics/10threeactionsystem}
\input{03mechanics/20classlessdnd}
% \input{03mechanics/30feats}
\input{03mechanics/40optionalrules}
