% !TEX root = ../main.tex
\section{Classless D\&D} \label{sec::classlessdnd}
\DndDropCapLine{A}{n inch away from death, a band of}
fellows barely manages to escape from a bloodthirsty nidhogg.
Worn and weary, they settle against an outcrop of rocks, taking a moment to catch their breath.

Nightfall comes all too fast, and they improvise a campfire to keep them warm during the night.
Just as they begin their well-deserved rest, they feel an unsettling rumbling beneath their feet.
What they originally thought was a strange-looking rock starts moving, revealing itself to be a troll.
Tired they scramble for arms, a gat grabbing their mace, and an ird her trusty quarterstaff.

\subsection*{Call to Adventure}
    Adventurers leave home as any person would, picking up an assortment of skills and feats on the road.
    Unskilled and untrained, they take their time to become experts in what they do.
    Lest they become prey to a savage beast or an opportunist bandit.

\subsection*{Creating a character}
    Your first step in playing is creating a character of your own.
    You choose a kin, which will determine their physical characteristics and provide them with a set of traits.
    Then, you choose a background, which describes what they did before joining the adventuring life and provides them with one feature.
    Additionally, your character's kin and background will give them access to a specific set of feats.
    You also choose your character's tidal alignment, invent the personality, appearance, and backstory of your character.

    \subsubsection{Ability Scores}
        After choosing your character's kin and background, it's time to generate their ability scores randomly.
        Roll four d6s and record the total of the highest three dice on a piece of scratch paper.
        Do this five more times, so that you have six numbers.

        Now take your six numbers and write each beside one of your character's six abilities to assign scores to Strength, Dexterity, Constitution, Intelligence, Wisdom, and Charisma.
        Afterward, make any changes to your ability scores as a result of your kin choice.

        After assigning your ability scores, determine your ability modifiers.
        This is done by subtracting 10 from the ability score and then dividing the result by 2 (round down).
        Write the modifier next to each of your scores.

    \subsubsection{Hit Points and Hit Dice}
        On creation, your character has a number of hit points equal to 8 + their Constitution modifier.
        Upon leveling up, roll a d8 and add the number rolled + your character's Constitution modifier to their hit point pool.
        Alternatively, you can forgo this roll and simply add 5 + your character's Constitution modifier.

        Your character has a number of hit dice equal to their level.
        By default all these hit dice are d8s, but they can be improved (or worsened) by taking relevant major character advancement, which are described in their own section at page \pageref{ssec::majorcharacteradvancement}.

    \subsubsection{Proficiency Levels}
        Instead of having one particular proficiency bonus, your character has specific proficiency levels in different skills, proficiencies, and saving throws.
        Proficiency levels in skills and proficiencies are gained via feats, while in saving throws they are gained at specific levels, as is listed in the Character Progression Table.

        There are five proficiency levels:
        \subparagraph{Untrained} Completely unskilled in the practice, you have no proficiency bonus.
        \subparagraph{Competent} Some basic experience gives you a +2 proficiency bonus.
        \subparagraph{Skilled} Practice makes perfect, you have a +4 proficiency bonus.
        \subparagraph{Expert} A fully realized professional, you have a +6 proficiency bonus.
        \subparagraph{Legendary} Your skill is lauded, and your crafts acclaimed.
        You have a +12 proficiency bonus.

    % NOTE. It might be cool to find a way to make this look more like the official class summary tables.
    \begin{DndTable}[width=\linewidth, header=Character Progression Table]{ccX}
        \textbf{Level} & \textbf{Required FP} & \textbf{Feature} \\
        1              & 0                    & 2 Saving Throw Improvements \\
        2              & 1                    & Ability Score Improvement \\
        3              & 2                    & Major Character Advancement \\
        4              & 3                    & Ability Score Improvement \\
        5              & 5                    & Saving Throw Improvement \\
        6              & 7                    & Ability Score Improvement \\
        7              & 9                    & - \\
        8              & 11                   & Ability Score Improvement \\
        9              & 13                   & Saving Throw Improvement \\
        10             & 15                   & Ability Score Improvement \\
        11             & 18                   & Major Character Advancement \\
        12             & 21                   & Ability Score Improvement \\
        13             & 24                   & Saving Throw Improvement \\
        14             & 27                   & Ability Score Improvement \\
        15             & 30                   & - \\
        16             & 34                   & Ability Score Improvement \\
        17             & 39                   & Saving Throw Improvement \\
        18             & 44                   & Ability Score Improvement \\
        19             & 51                   & Major Character Advancement \\
        20             & 60                   & Ability Score Improvement
    \end{DndTable}

\input{03mechanics/21beyondfirstlevel}
\input{03mechanics/22majorcharacteradvancement}
\input{03mechanics/23fightingstyles}
% \input{03mechanics/20feats}
