% !TEX root = ../main.tex
\subsection*{Major Character Advancement} \label{ssec::majorcharacteradvancement}
Upon reaching levels 3, 11, and 19, your character gains major character advancements.
These are similar to feats, but have stronger effects and are more limited.

\subsubsection{Ability Modifier Improvement} \label{mca::abilitymodifierimprovement}
    Increase an ability modifier of your choice by 2.
    In addition, your maximum for that score is now 24.

\subsubsection{Legendary Proficiency} \label{mca::legendaryproficiency}
    Increase your level of proficiency in two skills or proficiencies to legendary, increasing your proficiency bonus on those skills to +12.
    You must have an expert level of proficiency in both.

\subsubsection{Fighting Style} \label{mca::fightingstyle}
    You learn a fighting style of your choice, or upgrade one that you already know.
    The list of fighting styles is available in page \pageref{ssec::fightingstyles}.

\subsubsection{Hit Die Improvement} \label{mca::hitdieimprovement}
    You increase your hit die from a d6 to a d8, a d8 to a d10, or a d10 to a d12.
    Additionally, you gain a number of hit points equal to your level when you take this major character advancement.

\subsubsection{Spellcasting School} \label{mca::spellcastingschool}
    You join a new spellcasting school from a doctrine different to the one you already follow.
    When you do this, you learn one medium from the new doctrine, and the signature medium and spell from the spellcasting school.

    In addition, you can learn any spell from the new doctrine as you normally would learn a new spell.

\subsubsection{Upgraded Spellcasting} \label{mca::upgradedspellcasting}
    You expand your spellcasting ability beyond its normal limit.
    You reduce your hit die from a d8 to a d6, a d10 to a d8, or a d12 to a d10.
    In addition, you lose a number of hit points equal to your level when you take this major character advancement.

    In exchange for this sacrifice, you gain the ability to cast higher level spells and add more spell points to your pool.
    Your total number of spell points and maximum spell level is available in the table below.

    \begin{DndTable}[width=\linewidth, header=Spellcasting Ability]{XX}
        \textbf{Level} & \textbf{Spell Points} \\
         1st           &   4 \\
         2nd           &   6 \\
         3rd           &  14 \\
         4th           &  17 \\
         5th           &  27 \\
         6th           &  32 \\
         7th           &  38 \\
         8th           &  44 \\
         9th           &  57 \\
        10th           &  64 \\
        11th           &  73 \\
        12th           &  73 \\
        13th           &  83 \\
        14th           &  83 \\
        15th           &  94 \\
        16th           &  94 \\
        17th           & 107 \\
        18th           & 114 \\
        19th           & 123 \\
        20th           & 133
    \end{DndTable}

    \paragraph{Requirements} Spellcaster feat (page \pageref{feat::spellcaster}).
