% !TEX root = ../main.tex
\addcontentsline{toc}{section}{Spellcasting Feats}
\subsection*{Spellcasting Feats}
All feats in this section require the \textbf{Spellcaster} feat (see page \pageref{feat::spellcaster}), except naturally for the feat itself.

\begin{DndTable}[width=\linewidth, header=General Spellcasting Feat List]{ll}
    \textbf{Spellcasting Ability} & \textbf{Feat}                                                                \\
    \textbf{---}                  & \textbf{Spellcaster}            (page \pageref{feat::spellcaster})           \\
    \textbf{---}                  & \textbf{Avid Caster}            (page \pageref{feat::avidcaster})            \\
    Intelligence                  & \textbf{Careful Spell}          (page \pageref{feat::carefulspell})          \\
    Intelligence                  & \textbf{Heedful Aim}            (page \pageref{feat::heedfulaim})            \\
    Intelligence                  & \textbf{Seeking Spell}          (page \pageref{feat::seekingspell})          \\
    Intelligence                  & \textbf{Spell Sniper}           (page \pageref{feat::spellsniper})           \\
    Intelligence                  & \textbf{Tactical Wit}           (page \pageref{feat::tacticalwit})           \\
    Wisdom                        & \textbf{Durable Magic}          (page \pageref{feat::durablemagic})          \\
    Wisdom                        & \textbf{Extended Spell}         (page \pageref{feat::extendedspell})         \\
    Wisdom                        & \textbf{Focused Casting}        (page \pageref{feat::focusedcasting})        \\
    Wisdom                        & \textbf{Numerous Mediums}       (page \pageref{feat::numerousmediums})       \\
    Wisdom                        & \textbf{Twinned Spell}          (page \pageref{feat::twinnedspell})          \\
    Charisma                      & \textbf{Empowered Spell}        (page \pageref{feat::empoweredspell})        \\
    Charisma                      & \textbf{Heightened Spell}       (page \pageref{feat::heightenedspell})       \\
    Charisma                      & \textbf{Quick Casting}          (page \pageref{feat::quickcasting})          \\
    Charisma                      & \textbf{Spontaneous Deflection} (page \pageref{feat::spontaneousdeflection}) \\
    Charisma                      & \textbf{Subtle Spell}           (page \pageref{feat::subtlespell})
\end{DndTable}

\begin{DndTable}[width=\linewidth, header=School Spellcasting Feat List]{ll}
    \textbf{Doctrine or School} & \textbf{Feat}                                                                \\
    Alchemy 1                   & \textbf{Acidic Discharge}       (page \pageref{feat::acidicdischarge})       \\
    Alchemy 1                   & \textbf{Fogs of Nuagal}         (page \pageref{feat::fogsofnuagal})          \\
    Alchemy 1                   & \textbf{Quenching Smoke}        (page \pageref{feat::quenchingsmoke})        \\
    Alchemy 1                   & \textbf{Magic Surge}            (page \pageref{feat::magicsurge})            \\
    Alchemy 1                   & \textbf{Slippery Surface}       (page \pageref{feat::slipperysurface})       \\
    Alchemy 1                   & \textbf{Unstable Air}           (page \pageref{feat::unstableair})           \\
    Alchemy 2                   & \textbf{Alchemical Crafting}    (page \pageref{feat::alchemicalcrafting})    \\
    Alchemy 2                   & \textbf{Altered Air}            (page \pageref{feat::alteredair})            \\
    Alchemy 2                   & \textbf{Infused Vials}          (page \pageref{feat::infusedvials})          \\
    Alchemy 2                   & \textbf{Mutable Spells}         (page \pageref{feat::mutablespells})         \\
    Sympathy 1                  & \textbf{Comforting Flame}       (page \pageref{feat::comfortingflame})       \\
    Sympathy 1                  & \textbf{Emboldening Connection} (page \pageref{feat::emboldeningconnection}) \\
    Sympathy 1                  & \textbf{Forced Disattachment}   (page \pageref{feat::forceddisattachment})   \\
    Sympathy 1                  & \textbf{Scalding Ember}         (page \pageref{feat::scaldingember})         \\
    Sympathy 1                  & \textbf{Tamed Lightning}        (page \pageref{feat::tamedlightning})        \\
    Sympathy 1                  & \textbf{Violent Discharge}      (page \pageref{feat::violentdischarge})      \\
    Sympathy 2                  & \textbf{Overexertion}           (page \pageref{feat::overexertion})          \\
    Sympathy 2                  & \textbf{Stored Energy}          (page \pageref{feat::storedenergy})          \\
    Sympathy 2                  & \textbf{Storm Arteries}         (page \pageref{feat::stormarteries})         \\
    Sympathy 2                  & \textbf{Sympathist's Fuel}      (page \pageref{feat::sympathistsfuel})       \\
    Deathtouching               & \textbf{Arsenic Infusion}       (page \pageref{feat::arsenicinfusion})       \\
    Deathtouching               & \textbf{Baneful Poison}         (page \pageref{feat::banefulpoison})         \\
    Deathtouching               & \textbf{Deep Toxicity}          (page \pageref{feat::deeptoxicity})          \\
    Deathtouching               & \textbf{Inherited Curse}        (page \pageref{feat::inheritedcurse})        \\
    Deathtouching               & \textbf{Stinging Toxin}         (page \pageref{feat::stingingtoxin})         \\
    Deathtouching               & \textbf{Weakened Body}          (page \pageref{feat::weakenedbody})          \\
    Frithbinding                & \textbf{Frithling Posse}        (page \pageref{feat::frithlingposse})        \\
    Frithbinding                & \textbf{Frithling Spellcasting} (page \pageref{feat::frithlingspellcasting}) \\
    Frithbinding                & \textbf{Frith's Light}          (page \pageref{feat::frithslight})           \\
    Frithbinding                & \textbf{Frith's Protection}     (page \pageref{feat::frithsprotection})      \\
    Frithbinding                & \textbf{Gift of the Wilds}      (page \pageref{feat::giftofthewilds})        \\
    Frithbinding                & \textbf{Shared Shelter}         (page \pageref{feat::sharedshelter})         \\
    Flamespeaking               & \textbf{Guiding Spark}          (page \pageref{feat::guidingspark})          \\
    Flamespeaking               & \textbf{Message in the Ash}     (page \pageref{feat::messageintheash})       \\
    Flamespeaking               & \textbf{Prophetic Smoke}        (page \pageref{feat::propheticsmoke})        \\
    Flamespeaking               & \textbf{Stored Fuel}            (page \pageref{feat::storedfuel})            \\
    Flamespeaking               & \textbf{Twist the Lines}        (page \pageref{feat::twistthelines})         \\
    Flamespeaking               & \textbf{Vigorous Scream}        (page \pageref{feat::vigorousscream})        \\
    Shellpoacher                & \textbf{Blessed Healer}         (page \pageref{feat::blessedhealer})         \\
    Shellpoacher                & \textbf{Bountiful Soup}         (page \pageref{feat::bountifulsoup})         \\
    Shellpoacher                & \textbf{Preserve Life}          (page \pageref{feat::preservelife})          \\
    Shellpoacher                & \textbf{Protector's Resilience} (page \pageref{feat::protectorsresilience})  \\
    Shellpoacher                & \textbf{Restoring Meals}        (page \pageref{feat::restoringmeals})        \\
    Shellpoacher                & \textbf{Warding Bond}           (page \pageref{feat::wardingbond})           \\
    Skycalling                  & \textbf{Biting Lightning}       (page \pageref{feat::bitinglightning})       \\
    Skycalling                  & \textbf{Exploding Aragonite}    (page \pageref{feat::explodingaragonite})    \\
    Skycalling                  & \textbf{Javelin of Keranos}     (page \pageref{feat::javelinofkeranos})      \\
    Skycalling                  & \textbf{Protective Field}       (page \pageref{feat::protectivefield})       \\
    Skycalling                  & \textbf{Thunder Gems}           (page \pageref{feat::thundergems})           \\
    Skycalling                  & \textbf{Unbound Storm}          (page \pageref{feat::unboundstorm})          \\
    Warchanting                 & \textbf{Bloodshot}              (page \pageref{feat::bloodshot})             \\
    Warchanting                 & \textbf{Brutal Critical}        (page \pageref{feat::brutalcritical})        \\
    Warchanting                 & \textbf{Cosmic Savaregy}        (page \pageref{feat::cosmicsavaregy})        \\
    Warchanting                 & \textbf{Rage Beyond Death}      (page \pageref{feat::ragebeyonddeath})       \\
    Warchanting                 & \textbf{Strong Liquor}          (page \pageref{feat::strongliquor})          \\
    Warchanting                 & \textbf{Unending Fury}          (page \pageref{feat::unendingfury})
\end{DndTable}

% A
\subsubsection{Acidic Discharge} \label{feat::acidicdischarge}
    Whenever you consume an indigo alignment point, you can cause your zuan to discharge a small amount of acid.
    The acid extends out to a range of a meter, and is difficult terrain.
    In addition, any creature that steps on the acid takes 1d6 acid damage.
    \paragraph{Requirements} Doctrine: Alchemy.
\subsubsection{Alchemical Crafting (2 FP)} \label{feat::alchemicalcrafting}
    As part of a long rest, you can aid a creature in the creation of an item, halving its material cost.
    You can only use this feat to aid an item created through Alchemist's Supplies, Brewer's Supplies, Cook's Utensils, or a Poisoner's Kit.
    \paragraph{Requirements} Doctrine: Alchemy, MCA: Upgraded Spellcasting.
\subsubsection{Altered Air (2 FP)} \label{feat::alteredair}
    Using two actions, you can cause your zuan to emit an aura of your choice:
    \begin{itemize}
        \item \textbf{Noxious Gas}.
        The air around your zuan becomes heavy.
        All creatures within 3 meters of it have a -1 penalty to their AC and have disadvantage on Dexterity saving throws.
        Constructs are unaffected by this effect.
        \item \textbf{Scalding Steam}.
        Your zuan emits steam out to a range of a meter.
        The area becomes heavily obscured, and any creature that starts its turn in or enters the area takes 2d6 fire damage.
        \item \textbf{Emboldening Aura}.
        A stimulating aura radiates from your zuan out to a range of 3 meters.
        All creatures in this range receive a +1 bonus to their AC and have advantage on Strength saving throws.
        Constructs are unaffected by this effect.
    \end{itemize}

    The aura remains in effect until you dismiss it as an action on your turn.
    \paragraph{Requirements} Doctrine: Alchemy, MCA: Upgraded Spellcasting.
\subsubsection{Arsenic Infusion} \label{feat::arsenicinfusion}
    While you have the \textbf{Toxify} effect from the \textbf{Toxic Cuts} medium (page \pageref{medium::toxiccuts}) active, your own body becomes a medium for arsenic.
    At the start of each of your turns, you emit a gas in a 1-meter radius, increasing the toxicity level of all creatures within a meter of you by 1.
    \paragraph{Requirements} School: Deathtouching, Competent proficiency with Poisoner's Supplies.
\subsubsection{Avid Caster (3 FP)} \label{feat::avidcaster}
    You increase your spellcasting ability bonus by 2.
    You can take this feat two times.
% B
\subsubsection{Baneful Poison} \label{feat::banefulpoison}
    While you have the \textbf{Bane} effect from the \textbf{Toxic Cuts} medium (page \pageref{medium::toxiccuts}) active, you can choose to deal extra damage on an attack, but to force the target to roll a Constitution saving throw against your spell save DC.
    On a failed save, the creature is poisoned.
    A creature repeats this saving throw at the end of each of its turns.
    \paragraph{Requirements} School: Deathtouching, Competent proficiency with Poisoner's Supplies.
\subsubsection{Biting Lightning} \label{feat::bitinglightning}
    The area created by the \textbf{Dry Air} medium (page \pageref{medium::dryair}) is considered difficult terrain.
    In addition, any creature inside the area takes 1d4 thunder damage for each charge it receives while inside it.
    \paragraph{Requirements} School: Skycalling, Competent proficiency with Jeweler's Tools.
\subsubsection{Blessed Healer (2 FP)} \label{feat::blessedhealer}
    You can add your spellcasting ability modifier to any healing you do via any mean.
    \paragraph{Requirements} School: Shellpoaching, Skilled proficiency with Cook's Utensils.
\subsubsection{Bloodshot} \label{feat::bloodshot}
    As part of a short rest, you can brew one vial worth of Bloodshot.
    A creature can drink the liquid using two actions.
    Alternatively, you can force a willing creature to drink it using two actions.

    Until the end of its next turn, the creature's multiple attack penalty is reduced to 0, and it gains a bonus to damage rolls equal to your spellcasting ability modifier.
    \paragraph{Requirements} School: Warchanting, Competent proficiency with Brewer's Supplies.
\subsubsection{Bountiful Soup} \label{feat::bountifulsoup}
    The number of rations you can use to make poached soup is increased by 1.
    In addition, you can use cooked rations instead of rations to make poached soup.

    You can take this feat two additional times, increasing the number of rations used by 1 each time.
    \paragraph{Requirements} School: Shellpoaching, Skilled proficiency with Cook's Utensils.
\subsubsection{Brutal Critical} \label{feat::brutalcritical}
    While raging, a creature can roll one additional weapon damage die when determining the extra damage for a critical hit with a melee attack.

    You can take this feat two additional times, increasing the damage dice rolled by one each time.
    \paragraph{Requirements} School: Warchanting, Skilled proficiency with Brewer's Supplies.
% C
\subsubsection{Careful Spell} \label{feat::carefulspell}
    When you cast a spell that forces other creatures to make a saving throw, you can protect one of those creatures from the spell's full force.

    You can take this feat two additional times.
    The first, you increase the number of creatures you can protect to 3.
    The second, the number of creatures you can protect is equal to your Intelligence modifier (minimum of 3).
    \paragraph{Requirements} Ability Modifier: Intelligence.
\subsubsection{Comforting Flame} \label{feat::comfortingflame}
    All allied creatures within 3 meters of at least one ember gain a +1 bonus to their AC.
    \paragraph{Requirements} Doctrine: Sympathy.
\subsubsection{Cosmic Savagery} \label{feat::cosmicsavaregy}
    While under the effect of the \textbf{Rhelath's Dance} spell, the raging creature gains an additional benefit when you use the extra effects of the \textbf{Rage} spell:

    \subparagraph{Primal Frenzy}
    The creature makes attack rolls with advantage during its next turn.
    \subparagraph{Feral Instinct}
    The creature gains advantage on Constitution and Dexterity saving throws until the start of your next turn.
    \subparagraph{Instinctive Pounce}
    The creature's speed is increase by 2 meters until the start of your next turn.
    \paragraph{Requirements} School: Warchanting, Expert proficiency with Brewer's Supplies.
% D
\subsubsection{Deep Toxicity} \label{feat::deeptoxicity}
    The maximum level of toxicity you can give a creature is increased by one.

    You can take this feat two additional times, increasing this number by 1 each time.
    \paragraph{Requirements} School: Deathtouching, Skilled proficiency with Poisoner's Supplies.
\subsubsection{Durable Magic} \label{feat::durablemagic}
    When you cast a spell that requires concentration, you can spend an additional action to still yourself while casting.
    While you maintain concentration on the spell, you have a +2 bonus to AC and all saving throws.
    \paragraph{Requirements} Ability Modifier: Wisdom.
% E
\subsubsection{Emboldening Connection} \label{feat::emboldeningconnection}
    All creatures connected via a similarity link gain a +1 bonus to all saving throws for each other creature attached through the link.
    \paragraph{Requirements} Doctrine: Sympathy.
\subsubsection{Empowered Spell (2FP)} \label{feat::empoweredspell}
    When you roll damage for a spell, you can spend a spell point to reroll a number of the damage dice up to your Charisma modifier (minimum of one).
    You must use the new rolls.
    \paragraph{Requirements} Ability Modifier: Charisma.
\subsubsection{Exploding Aragonite} \label{feat::explodingaragonite}
    As part of a short rest, you can imbue lightning onto a piece of aragonite.
    You consume a number of spell points lesser or equal to your spellcasting ability modifier when you do this.
    The next time the aragonite hits a hard surface, it shatters, releasing lightning bolts towards all creatures in a 4-meter-radius from it.
    All creatures affected must make a Dexterity saving throw.
    A creature takes a number of d6s equal to the number of spell points consumed by this ability in thunder damage on a failed save and is pushed 2 meters away from the aragonite.

    You can take this feat two additional times, increasing the maximum number of spell points that can be stored by the aragonite by an amount equal to your spellcasting ability modifier each time.
    \paragraph{Requirements} School: Skycalling, Skilled proficiency with Jeweler's Tools.
\subsubsection{Extended Spell} \label{feat::extendedspell}
    When you cast a spell that has a duration of 1 minute or longer, you can spend a spell point to double its duration, to a maximum of 24 hours.
    \paragraph{Requirements} Ability Modifier: Wisdom.
% F
\subsubsection{Focused Casting (2FP)} \label{feat::focusedcasting}
    You gain a bonus to any Constitution saving throws you make to maintain concentration on a spell.
    The bonus equals your Wisdom modifier (minimum of +1).
    \paragraph{Requirements} Ability Modifier: Wisdom.
\subsubsection{Fogs of Nuagal} \label{feat::fogsofnuagal}
    Whenever you consume a blue alignment point, you can cause zuan to emit harmless steam out to a range of a meter.
    All creatures in range must succeed on a Dexterity saving throw or they use their reactions to cover from the steam.
    \paragraph{Requirements} Doctrine: Alchemy.
\subsubsection{Forced Disattachment} \label{feat::forceddisattachment}
    Whenever a sympathetic link is broken, all linked creatures are affected by a wave of lethargy.
    Until the end of your next turn, they can only take 2 actions per turn, their movement speed is reduced by 2 meters, and their AC is reduced by 2.
    \paragraph{Requirements} Doctrine: Sympathy.
\subsubsection{Frith's Light} \label{feat::frithslight}
    When a creature is affected by the \textbf{Guided Bolt} spell (page \pageref{spell::guidedbolt}), it is surrounding by a glittering dim light.
    All attacks made against it are made with advantage until the end of your next turn.

    Only one creature may be affected by this light at once.
    \paragraph{Requirements} School: Frithbinding, Expert proficiency with Cobbler's Tools.
\subsubsection{Frith's Protection} \label{feat::frithsprotection}
    You can add a d4 to any saving throw you roll.

    You can use this feat a number of times equal to the number of frithlings that travel along with you, regaining all uses after a short rest.
    \paragraph{Requirements} School: Frithbinding, Competent proficiency with Cobbler's Tools.
\subsubsection{Frithling Posse} \label{feat::frithlingposse}
    You can affect maintain a link with one additional frithling using the \textbf{Frithbind} medium (see page \pageref{medium::frithbind}).

    You can take this feat two additional times, increasing the number of frithlings you can bind at once by one.
    Note that you have only two shoes and thus can only have two frithling companions at once.
    You can use a \textbf{Frithling Glass Home} (see page \pageref{item::frithlingglasshome}) to increase this number by 8.
    \paragraph{Requirements} School: Frithbinding, Skilled proficiency with Cobbler's Tools.
\subsubsection{Frithling Spellcasting} \label{feat::frithlingspellcasting}
    As a free action, you ask a friendly frithling to cast one of the following spells:
    \begin{itemize}
        \item \textbf{Forecast}.
        The frithling creates a tiny, harmless sensory effect that predicts what the weather will be at your location for the next 24 hours.
        The effect might manifest as a golden orb for clear skies, a cloud for rain, falling snowflakes for snow, and so on.
        This effect persists for 1 round.
        \item \textbf{Guidance}.
        The frithling touches one willing creature.
        For up to an hour, the target can roll a d4 and add the number rolled to one ability check of its choice.
        It can roll the die before or after making the ability check.
        The spell then ends.
        \item \textbf{Pass without Trace}.
        For up to an hour, a veil of shadows and silence radiates from the frithling, masking it and its companions from detection.
        For up to an hour and requiring concentration from the frithling, each creature you choose within 6 meters of the frithling (including it) has a +10 bonus to Dexterity (Stealth) checks and can't be tracked except by magical means.
        A creature that receives this bonus leaves behind no tracks or other traces of its passage.
        \item \textbf{Resistance}.
        The frithling touches one willing creature.
        Once before an hour passes, the target can roll a d4 and add the number rolled to one saving throw of its choice.
        It can roll the die before or after making the saving throw.
        The spell then ends.
    \end{itemize}

    A frithling can only cast one such spell per short rest.
    \paragraph{Requirements} School: Frithbinding, Competent proficiency with Cobbler's Tools.
% G
\subsubsection{Gift of the Wilds (2 FP)} \label{feat::giftofthewilds}
    As part of a long rest, you can ask your frithling companions for a gift.
    Only one such gift can be active at a time, and if you ask for a new one the old one loses its properties.
    You can this gift to another creature, but frithlings may grow angry at you if you do so unwarranted.
    The gifts you may choose from are:
    \begin{itemize}
        \item \textbf{Charm of Biting}.
        Once per day, you can wreathe your weapon with biting cold for 1 minute as an action.
        Until this effect ends, you deal an extra 1d4 necrotic damage when you hit with a melee or ranged weapon attack.
        \item \textbf{Charm of Many Lives}.
        When you drop to 0 hit points as a result of taking damage, you can choose to drop to 1 hit point instead.
        You can use this effect once per day.
        \item \textbf{Charm of the Crystal Heart}.
        As an action, you can gain resistance to piercing and slashing damage, but you gain vulnerability to bludgeoning damage for a minute.
        You can use this effect once per day.
        \item \textbf{Charm of the Maimed}.
        This charm allows you to regrow a lost appendage or organ, such as an arm, a foot, or an eye.
        The process takes one week and requires you to have the charm in your possession for the duration.
        \item \textbf{Charm of the Troll}.
        When you take necrotic damage, you can use your reaction to reduce the damage to 0.
        You regain a number of hit points equal to half the necrotic damage you would have taken.
        You can use this ability once per day.
        \item \textbf{Charm of Vitality}.
        Once per day, this charm allows you to remove one level of exhaustion and cure one poison affecting you.
    \end{itemize}

    If you have 4 or more frithling companions, carrying your charm also increases your Charisma score by 2 (to a maximum of 22), as an affable aura surrounds you.
    This effect does not carry over to other creatures you pass on a charm to.
    \paragraph{Requirements} School: Frithbinding, Expert proficiency with Cobbler's Tools.
\subsubsection{Guiding Spark} \label{feat::guidingspark}
    When you cast a spell that deals fire damage, you can expend one spell point to look into the trail of sparks and predict the creature's movements.
    Any ally that attacks the creature before the start of your next turn can roll a d4 and add the number rolled to the attack roll.
    \paragraph{Requirements} School: Flamespeaking, Competent proficiency with Glassblower's Tools.
% H
\subsubsection{Heedful Aim (2FP)} \label{feat::heedfulaim}
    Your ranged spell attacks ignore half cover and three-quarters cover.
    \paragraph{Requirements} Ability Modifier: Intelligence.
\subsubsection{Heightened Spell} \label{feat::heightenedspell}
    When you cast a spell that forces a creature to make a saving throw to resist its effects, you can spend 3 spell points to give one target of the spell disadvantage
    \paragraph{Requirements} Ability Modifier: Charisma.
% I
\subsubsection{Infused Vials} \label{feat::infusedvials}
    As a ritual, you can infuse a vial of water with a spell.
    The ritual takes a minute to be finished and consumes the number of spell points that casting the spell normally would have.
    The water is transformed by the spell, changing in appearance to something to resembles to stored spell.
    Whenever the vial is opened by any means, the spell is cast on it as if you had casted it.

    You can keep only one vial infused in this way at a time.

    You can take this feat two more times, increasing the number of vials that can be infused at the same time by one each time.
    \paragraph{Requirements} Doctrine: Alchemy, MCA: Upgraded Spellcasting.
\subsubsection{Inherited Curse} \label{feat::inheritedcurse}
    If a creature falls unconscious or dies as a result of you using the \textbf{Pharika's Execution} spell (page \pageref{spell::pharikasexecution}), a creature of your choice within 3 meters of it gains a toxicity level equal to the one of the former.
    \paragraph{Requirements} School: Deathtouching, Expert proficiency with Poisoner's Supplies.
% J
\subsubsection{Javelin of Keranos (2 FP)} \label{feat::javelinofkeranos}
    While under a storm, you can call on Keranos to imbue your attacks with electricity.
    Any time you deal damage through any means to another creature, that attack bonus thunder damage equal to twice your spellcasting ability modifier.
    \paragraph{Requirements} School: Skycalling, Expert proficiency with Jeweler's Tools.
% K
% L
% M
\subsubsection{Magic Surge} \label{feat::magicsurge}
    Your spellcasting can unleash surges of untamed magic.
    Immediately after your zuan loses any amount of silver alignment points, roll a d100.
    If the roll is equal or less than the amount of points lost, roll on the Magic Surge table to create a random effect.

    If a Wild Magic effect is a spell, you cannot control it in any way.
    If it normally requires concentration, it doesn't require concentration in this case; the spell lasts for its full duration.

    \begin{DndTable}[width=\linewidth, header=Magic Surge]{lX}
        \textbf{d20}     & \textbf{Effect} \\
        01 & You gain vulnerability to all damage for the next minute. \\
        02 & All creatures within 6 meters of your zuan gain vulnerability to piercing damage for the next minute. \\
        03 & The creature closest to your zuan levitates for a minute.
        While levitating, it can move up to 4 meters in any direction when it uses the move action.
        When the minute ends, the creature falls to the ground. \\
        04 & Each creature within 6 meters of your zuan takes 1d10 necrotic damage.
        You regain hit points equal to the sum of the necrotic damage dealt. \\
        05 & You teleport up to 12 meters to an unoccupied space of your choice that you can see. \\
        06 & You regain a number of spell points equal to half your level (rounded down). \\
        07 & You regain 2d10 hit points. \\
        08 & A protective barrier appears around you for the next minute, granting you a +2 bonus to AC. \\
        09 & Creatures have disadvantage on saving throws against the next spell you cast in the next minute that involves a saving throw. \\
        10 & Maximize the damage of the next damaging spell you cast within the next minute. \\
        11 & You can take one additional action immediately. \\
        12 & If you die within the next minute, you immediately come back to life with 1 hit point. \\
        13 & A random creature within 12 meters of your zuan becomes poisoned for 1d4 hours. \\
        14 & You cast \textbf{Fireball} (see page \pageref{spell::fireball}) centered on your zuan. \\
        15 & You cast \textbf{Grease} (see page \pageref{spell::grease}) centered on your zuan. \\
        16 & You cast \textbf{Fog Cloud} (see page \pageref{spell::fogcloud}) centered on your zuan. \\
        17 & Your zuan glows with bright light in a 6-meter radius for the next minute.
        Any creature that ends its turn within a meter of it is blinded until the end of its next turn. \\
        18 & Up to three creatures you choose within 6 meters of your zuan take 4d10 lightning damage. \\
        19 & You cast \textbf{Freezing Sphere} (see page \pageref{spell::spell::freezingsphere}) centered on your zuan. \\
        20 & A confused frithling is teleported a meter from your zuan.
    \end{DndTable}
    \paragraph{Requirements} Doctrine: Alchemy.
\subsubsection{Message in the Ash (2 FP)} \label{feat::messageintheash}
    You can call on Purphoros to intervene on your behalf when your need is great.

    Describe the assistance you seek, and roll percentile dice.
    If you roll a number equal to or lower than your level, Purphoros intervenes.
    The DM chooses the nature of the intervention.
    If the deity intervenes, you can't use this feat again for a week.
    Otherwise, you can use it again after you finish a short rest.

    At 20th level, your call for intervention succeeds automatically, no roll required.
    \paragraph{Requirements} School: Flamespeaking, Expert proficiency with Glassblower's Tools.
\subsubsection{Mutable Spells} \label{feat::mutablespells}
    Whenever you deal acid of fire damage to a creature, you can use one spell point to change to damage type to fire or acid respectively.
    \paragraph{Requirements} Doctrine: Alchemy, MCA: Upgraded Spellcasting.
% N
\subsubsection{Numerous Mediums} \label{feat::numerousmediums}
    The maximum number of mediums of the same type you can maintain is increased by one.

    You can take this feat two additional times, increasing the maximum number of mediums by one each time.
    \paragraph{Requirements} Ability Modifier: Wisdom.
% O
\subsubsection{Overexertion (2FP)} \label{feat::overexertion}
    As a free action, you can choose to gain a number of spell points equal to a third of your total spell points.
    When you do this, you gain one level of exhaustion, and gain vulnerability to cold damage until you take a short rest.
    \paragraph{Requirements} Doctrine: Sympathy, MCA: Upgraded Spellcasting.
% P
\subsubsection{Preserve Life (2 FP)} \label{feat::preservelife}
    Using two actions, you evoke healing energy to restore life to some or all bound creatures.
    You can restore a number of hit points equal to five times your level, dividing them between bound creatures as you see fit.
    This feat can restore a creature to no more than half of its hit point maximum.
    You can't use this feature on an undead or a construct.
    \paragraph{Requirements} School: Shellpoaching, Expert proficiency with Cook's Utensils.
\subsubsection{Prophetic Smoke} \label{feat::propheticsmoke}
    When you deal fire damage to a creature, you can expend one spell point to look into the pattern of smoke and foresee the creature's movements.
    The next attack the creature does against you is made with disadvantage.
    \paragraph{Requirements} School: Flamespeaking, Competent proficiency with Glassblower's Tools.
\subsubsection{Protective Field} \label{feat::protectivefield}
    Any creature standing inside the area created by the \textbf{Dry Air} medium (page \pageref{medium::dryair}) gains resistance against lightning damage.
    If they leave this area, they retain this resistance until the start of their next turn.
    \paragraph{Requirements} School: Skycalling, Competent proficiency with Jeweler's Tools.
\subsubsection{Protector's Resilience} \label{feat::protectorsresilience}
    When a bound creature takes damage in another's place, it can choose to half the damage done.
    A creature can use this ability only once per day.
    \paragraph{Requirements} School: Shellpoaching, Competent proficiency with Cook's Utensils.
% Q
\subsubsection{Quenching Smoke} \label{feat::quenchingsmoke}
    As an action, you can choose to consume a number of blue alignment points of your choice to emit thick smoke from your zuan.
    The smoke spreads out to a range equal to 2 times the number of points consumed, spreading around corners.
    It remains in position until the start of your next turn or until a strong wind disperses it.
    The smoke's area is heavily obscured for the duration, and all fires and flames inside it subside, even those created by spells.
    \paragraph{Requirements} Doctrine: Alchemy.
\subsubsection{Quick Casting (2FP)} \label{feat::quickcasting}
    When you cast a spell that has a casting time of 2 or more actions, you can spend 3 spell points to reduce the casting time by 1 action for this casting.
    \paragraph{Requirements} Ability Modifier: Charisma.
% R
\subsubsection{Rage Beyond Death (2 FP)} \label{feat::ragebeyonddeath}
    The power that fuels a creature's rage allows it to shrug off fatal blows.

    While a creature is raging, having 0 hit points doesn't knock it unconscious.
    It still must make death saving throws, and it suffers the normal effects of taking damage while at 0 hit points.
    However, if it would die due to failing death saving throws, it doesn't die until the rage ends, and it dies then only if it still has 0 hit points.
    \paragraph{Requirements} School: Warchanting, Expert proficiency with Brewer's Supplies.
\subsubsection{Restoring Meals} \label{feat::restoringmeals}
    When a creature eats any meal cooked by you, it is healed by 1d8 hit points.
    \paragraph{Requirements} School: Shellpoaching, Competent proficiency with Cook's Utensils.
% S
\subsubsection{Scalding Ember} \label{feat::scaldingember}
    Upon starting its turn within a meter of at least one ember, a creature takes 1d6 fire damage.
    \paragraph{Requirements} Doctrine: Sympathy.
\subsubsection{Seeking Spell} \label{feat::seekingspell}
    If you make an attack roll for a spell and miss, you can spend 2 spell points to reroll the d20, and you must use the new roll.
    \paragraph{Requirements} Ability Modifier: Intelligence.
\subsubsection{Shared Shelter (2 FP)} \label{feat::sharedshelter}
    Home can be wherever you are.
    During a short or long rest, you can invoke a frithling's inherent hiding ability to guard your respite.
    At the start of the rest, you touch a point in space, and an invisible, 6-meter-radius sphere appears, centered on that point.
    Total cover blocks the sphere.

    While within the sphere, you and your allies gain a +5 bonus to Dexterity (Stealth) and Wisdom (Perception) checks, and any light in the sphere isn't visible outside it.

    The sphere vanishes at the end of the rest or when you leave the sphere.
    \paragraph{Requirements} School: Frithbinding, Skilled proficiency with Cobbler's Tools.
\subsubsection{Slippery Surface} \label{feat::slipperysurface}
    As an action, you can choose to consume a number of indigo alignment points of your choice to exhude a slippery liquid from your zuan.
    The liquid extends out to a circle with a radius equal to twice the number of points consumed, and evaporates at the start of your next turn.

    Any creature that is standing in the liquid when you cast the spell, starts their turn there, or enters the area must succeed on a Dexterity saving throw or fall prone.
    If a creature tries to stand up, it must succeed on another Dexterity saving throw or fall prone again.
    \paragraph{Requirements} Doctrine: Alchemy.
\subsubsection{Spell Sniper (2FP)} \label{feat::spellsniper}
    When you cast a spell hat has a range of 1 meter or greater, you can spend one spell point to double the range of the spell.

    When you cast a spell that has a range of touch, you can spend 1 spell point to make the range of the spell 6 meters.
    \paragraph{Requirements} Ability Modifier: Intelligence.
\subsubsection{Spellcaster (2 FP)} \label{feat::spellcaster}
    By joining one spellcasting school of your choice, you learn how to cast spells.
    Pick a spellcasting school from the Spellcasting chapter (page \pageref{ch::spellcasting}).
    The benefits associated to each school are denoted on their respective sections.
    For the rules of spellcasting, see page \pageref{sec::spellcastingrules}.
\subsubsection{Spontaneous Deflection} \label{feat::spontaneousdeflection}
    You can weave your magic to fortify yourself against harm.
    When you are hit by an attack or you fail a saving throw, you can consume one spell point and use your reaction to gain a +2 bonus to your AC against that attack or a +4 bonus to that saving throw.
    \paragraph{Requirements} Ability Modifier: Charisma.
\subsubsection{Stinging Toxin (2 FP)} \label{feat::stingingtoxin}
    Creatures with a level of toxicity greater or equal than 3 roll saving throws against being poisoned with disadvantage.

    In addition, if a creature is immune to poison damage, it loses this immunity and gains resistance to poison damage when their level of toxicity is greater or equal than 3.
    \paragraph{Requirements} School: Deathtouching, Skilled proficiency with Poisoner's Supplies.
\subsubsection{Stored Energy (2FP)} \label{feat::storedenergy}
    Whenever one of your embers fades, a creature is completely discharged, or a similarity link is broken, you feel a surge in energy.
    Once when you deal damage to a creature through any mean before the end of your next turn, it takes an additional 1d6 force damage.
    This damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).
    \paragraph{Requirements} Doctrine: Sympathy, MCA: Upgraded Spellcasting.
\subsubsection{Stored Fuel} \label{feat::storedfuel}
    As part of a short rest, you can store a number of unspent spell points equal to your spellcasting ability modifier in a firetrap you are carrying.
    You can recover any number of these spell points at any point as a free action as long as you carry the firetrap.

    The maximum number of spell points that a firetrap can carry is equal to your spellcasting ability modifier.

    You can take this feat two additional times, multiplying the maximum number of points stored per short rest and the maximum number of spell points a firetrap can carry by two each time.
    \paragraph{Requirements} School: Flamespeaking, Skilled proficiency with Glassblower's Tools.
\subsubsection{Storm Arteries} \label{feat::stormarteries}
    Whenever you take fire or lightning damage, you gain one spell point.

    You can take this feat two additional times, increasing the number of spell points gained in this way by one for each time.
    \paragraph{Requirements} Doctrine: Sympathy, MCA: Upgraded Spellcasting.
\subsubsection{Strong Liquor (2 FP)} \label{feat::strongliquor}
    Whenever a creature drinks a brew prepared by you, it gains advantage on all Constitution and Strength saving throws for an hour.
    \paragraph{Requirements} School: Warchanting, Skilled proficiency with Brewer's Supplies.
\subsubsection{Subtle Spell} \label{feat::subtlespell}
    When you cast a spell, you can spend 1 additional spell point to cast it without any somatic or verbal components.
    \paragraph{Requirements} Ability Modifier: Charisma.
\subsubsection{Sympathist's Fuel} \label{feat::sympathistsfuel}
    When you make a Constitution saving throw to stave off the effects of extreme cold, you can choose to spend one spell point and automatically succeed.

    In addition, when you take cold damage, you can spend a number of spell points equal to half the number of damage dice of the attack (rounded down) to reduce the damage dealt by half.
    \paragraph{Requirements} Doctrine: Sympathy, MCA: Upgraded Spellcasting.
% T
\subsubsection{Tactical Wit} \label{feat::tacticalwit}
    You gain a bonus to your initiative rolls equal to your Intelligence modifier.
    In addition, you can spend two spell points at the beginning of combat to roll initiative with advantage.
    \paragraph{Requirements} Ability Modifier: Intelligence.
\subsubsection{Tamed Lightning} \label{feat::tamedlightning}
    All creatures charged by you deal thunder damage equal to half the number of charges they have (rounded down) on all melee attacks.
    \paragraph{Requirements} Doctrine: Sympathy.
\subsubsection{Thunder Gems (2 FP)} \label{feat::thundergems}
    Any time you craft an object using your set of Jeweler's Tools, you can imbue lightning into any gemstone that is part of the produced item.
    The DC to craft the item is increased by 5, but its total selling value is multiplied by $1.5$, as the gemstone gains an otherworldly shine.

    In addition, if the item can be equipped, you can work with your DM to add a lightning-related property to the item.
    \paragraph{Requirements} School: Skycalling, Skilled proficiency with Jeweler's Tools.
\subsubsection{Twinned Spell (2FP)} \label{feat::twinnedspell}
    When you cast a spell that targets only one creature and doesn't have a range of self, you can spend a number of spell points equal to half the total cost of the spell (rounded up) to target a second creature in range with the same spell (1 spell point if the spell has a cost of 0).

    To be eligible, a spell must be incapable of targeting more than one creature.
    \paragraph{Requirements} Ability Modifier: Wisdom.
\subsubsection{Twist the Lines (2FP)} \label{feat::twistthelines}
    As a reaction, you can expend two spell points to force a creature to reroll an attack roll.
    \paragraph{Requirements} School: Flamespeaking, Skilled proficiency with Glassblower's Tools.
% U
\subsubsection{Unbound Storm} \label{feat::unboundstorm}
    When you cast the \textbf{Skycall} spell (page \pageref{spell::skycall}), you can target any point within range, instead of only the middle of the area affected by the \textbf{Dry Air} medium.
    \paragraph{Requirements} School: Skycalling, Expert proficiency with Jeweler's Tools.
\subsubsection{Unending Fury} \label{feat::unendingfury}
    After you end the spell, the effects of \textbf{Rage} remain for an additional round.
    \paragraph{Requirements} School: Warchanting, Competent proficiency with Brewer's Supplies.
\subsubsection{Unstable Air} \label{feat::unstableair}
    As an action, you can choose to consume a number of silver alignment points of your choice, infusing the air around your zuan in volatility.
    This aura extends out to a range with a radius equal to the number of points consumed in meters.

    Select a damage type between acid, cold, fire, lightning, or thunder.
    Until the start of your next turn, all creatures in the aura gain vulnerability to the chosen damage type.
    If they are resistant, they lose that resistance but don't gain vulnerability.
    If they are immune, they lose the immunity but become resistant.
    \paragraph{Requirements} Doctrine: Alchemy.
% V
\subsubsection{Vigorous Scream} \label{feat::vigorousscream}
    The radius of the \textbf{Screaming Bead} spell (see page \pageref{spell::screamingbead}) is extended to 6 meters.

    In addition, its range is extended to 12/18 mt.
    \paragraph{Requirements} School: Flamespeaking, Expert proficiency with Glassblower's Tools.
\subsubsection{Violent Discharge} \label{feat::violentdischarge}
    When a creature loses a charge via any means, it takes 1d6 thunder damage.
    \paragraph{Requirements} Doctrine: Sympathy.
% W
\subsubsection{Warding Bond} \label{feat::wardingbond}
    Whenever you use the \textbf{Chain Healing} spell (page \pageref{spell::chainhealing}), you can choose to give all affected creatures resistance to all damage until the end of your next turn.
    Each time a creature takes damage while under this effect, another willing creature takes the same damage.
    If no bound creature is willing, you take the damage.
    \paragraph{Requirements} School: Shellpoaching, Expert proficiency with Cook's Utensils.
\subsubsection{Weakened Body (2 FP)} \label{feat::weakenedbody}
    Whenever a creature takes poison damage as a result of failing a saving throw against poison, it also takes necrotic damage equal to the number of toxicity levels it has plus your spellcasting ability modifier.
    A creature can only take this extra damage once per round.
    \paragraph{Requirements} School: Deathtouching, Expert proficiency with Poisoner's Supplies.
% X
% Y
% Z

\newpage~\newpage
