% !TEX root = ../main.tex
\chapter{Classless D\&D} \label{ch::classlessdnd}
\DndDropCapLine{A}{n inch away from death, a band of}
fellows barely manages to escape from a bloodthirsty nidhogg.
Worn and weary, they settle against an outcrop of rocks, taking a moment to catch their breath.

Nightfall comes all too fast, and they improvise a campfire to keep them warm during the night.
Just as they begin their well-deserved rest, they feel an unsettling rumbling beneath their feet.
What they originally thought was a strange-looking rock starts moving, revealing itself to be a troll.
Tired they scramble for arms, a gat grabbing their mace, and an ird her trusty quarterstaff.

\subsection*{Call to Adventure}
    Adventurers leave home as any person would, picking up an assortment of skills and feats on the road.
    Unskilled and untrained, they take their time to become experts in what they do.
    Lest they become prey to a savage beast or an opportunist bandit.

\subsection*{Creating a character}
    Instead of gaining experience, your character gains \textbf{Feat Points} (FP) as they adventure.
    Feat points are spent in proficiencies and feats.
    As your character gains feat points, they will improve their ability scores and increase their level.

    % TODO: ADD STUFF AND MAKE THIS BETTER.
    \begin{DndTable}[width=\linewidth, header=Character Progression Table]{ccc}
        \textbf{Level} & \textbf{Required FP} & \textbf{Feature} \\
        1             & 0                    & - \\
        2             & 1                    & Ability Score Improvement \\
        3             & 2                    & - \\
        4             & 4                    & Ability Score Improvement \\
        5             & 6                    & - \\
        6             & 8                    & Ability Score Improvement \\
        7             & 10                   & - \\
        8             & 12                   & Ability Score Improvement \\
        9             & 15                   & - \\
        10            & 18                   & Ability Score Improvement \\
        11            & 21                   & - \\
        12            & 24                   & Ability Score Improvement \\
        13            & 28                   & - \\
        14            & 32                   & Ability Score Improvement \\
        15            & 36                   & - \\
        16            & 40                   & Ability Score Improvement \\
        17            & 46                   & - \\
        18            & 52                   & Ability Score Improvement \\
        19            & 60                   & - \\
        20            & 70                   & Ability Score Improvement
    \end{DndTable}

    % As they level up, your character will gain \textbf{ability score improvements} (ASI), \textbf{proficiency points} (PP), and \textbf{feat points} (FP).
    % As their name suggests, the first are increments to your character's ability scores, the second to buy proficiencies, and the third to buy feats.
    % % If you wish for a simpler system, you can always emulate a certain class by taking feats in an order that follows that class' natural progression.

    % NOTE: It might be a good idea to find a way to make this look more like the official class summary tables

\input{06classless/01experience}
% \input{06classless/020feats}
% \input{06classless/03techniques}
% \newpage
