% !TEX root = ../main.tex
\subsection*{Kin Feats}

% GAT
\subsubsection{Force of Will} \label{feat::forceofwill}
    You can plant yourself in place with all your weight, making you very difficult to move.
    As long as your feet are on the ground, you have advantage on any ability checks or saving throws made to move you or force you to fall prone.
    \paragraph{Requirements} Gat or Quies kin.
\subsubsection{Powerful Build} \label{feat::powerfulbuild}
    You count as one size larger when determining your carrying capacity and the weight you can push, drag, or lift.
    \paragraph{Requirements} Gat or Tortle kin.
\subsubsection{Goat's Strength} \label{feat::goatsstrength}
    You complement your natural strengths with hard training.
    The DC related to the Push action gains a +2 bonus for you.
    Additionally, any attack made with your horns gains a +2 to its attack rolls.

    You can take this feat three times.
    \paragraph{Requirements} Gat kin.
\subsubsection{Efficient Craftsgat} \label{feat::efficientcraftsgat}
    They say that a gat is born with tools in their hands.
    Crafting times with the artisan's tools related to your craftgatship trait are halved for you.
    \paragraph{Requirements} Gat kin.
\subsubsection{Relentless Endurance} \label{feat::relentlessendurance}
    When you are reduced to 0 hit points but not killed outright, you can drop to 1 hit point instead.
    You can't use this feature again until you finish a long rest.
    \paragraph{Requirements} Gat kin.
\subsubsection{Stonecutting} \label{feat::stonecutting}
    Originally designed as miners, all gats have a history in stonecutting.
    Whenever you make an Intelligence (History) check related to the origin of stonework, you are considered of Legendary proficiency in the History skill, adding a proficiency bonus of +12 to the check instead of your normal proficiency bonus in the skill.
\subsubsection{Legendary Craftsgat (2 FP)} \label{feat::legendarycraftsgat}
    Above the average gat, you are legendary at the use of your tools.
    Your proficiency with the artisan's tools related to your craftgatship trait is increased to Legendary, incresing your proficiency bonus to +12 with them.
    \paragraph{Requirements} Gat kin. Expert proficiency with a set of artisan's tools.
% NOVES GAT
\subsubsection{Mountain Born} \label{feat::mountainborn}
    You are acclimated to high altitude.
    You don't suffer the effects associated to the cold or lack of oxygen of any elevation up to 10,000 meters.
    You also have a climbing speed of 6 meters.
    \paragraph{Requirements} Noves Gat or Thulkraka Ird subrace.
\subsubsection{Stone's Endurance} \label{feat::stonesendurance}
    You can focus yourself to occasionally shrug off injury.
    When you take damage, you can use your reaction to roll a d12.
    Add your Constitution modifier to the number rolled, and reduce the damage by that total.
    After you use this trait, you can't use it again until you finish a short rest.
    \paragraph{Requirements} Noves Gat or Juggernaut Quies subrace.
\subsubsection{Gat Resilience (2 FP)} \label{feat::gatresilience}
    The horned kin possesses an almost otherwordly hardiness.
    You have advantage on saving throws against poison and are resistant against poison damage.
    \paragraph{Requirements} Noves Gat subrace.
% BUGHNA GAT
\subsubsection{Hardy} \label{feat::hardy}
    Resilience comes as natural to you as breathing.
    As long as you are not already an expert, you increase your proficiency in the Survival skill.
    Additionally, you can choose to add your Constitution modifier to Survival ability checks instead of your Wisdom modifier.
    \paragraph{Requirements} Bughna Gat or Gannagian Warrior subrace.
\subsubsection{Mirthful Leaps} \label{feat::mirthfulleaps}
    Whenever you make a long or high jump, you can roll a d4 and add the number rolled to the number of meters you cover, even when making a standing jump.
    This extra distance costs movement as normal.
    \paragraph{Requirements} Bughna Gat or Grung kin.
\subsubsection{Exercised Mind (2 FP)} \label{feat::exercisedmind}
    Generational learning has taught you that a qualar is only as strong as your will is.
    You are naturally good staving off dementia.
    You can choose to change the Demetia saving throw (see page \pageref{ssec::dementia}) from Intelligence to Wisdom, and its DC is 12 for you.
    Additionally, if you succeed on the saving throw, you reduce your dementia level by 1.
    \paragraph{Requirements} Bughna Gat subrace.
% TREB GAT
\subsubsection{Relentless Striker} \label{feat::relentlessstriker}
    Your hammering horns are your most valuable weapons, and you are trained to use them as a normal part of your arsenal.
    Melee attack rolls made with your horns don't add to your multiple attack penalty.
    \paragraph{Requirements} Treb Gat subrace.
\subsubsection{Goring Rush} \label{feat::goringrush}
    If you move at least 6 meters towards a creature, you can make one melee attack or use the Push action with your horns against the creature as a free action.
    \paragraph{Requirements} Treb Gat subrace.
\subsubsection{Imposing Presence (2 FP)} \label{feat::imposingpresence}
    You increase your proficiency level in Intimidation or Persuasion to Legendary, increasing your proficiency bonus to +12.
    \paragraph{Requirements} Treb Gat or Cursed Uman subrace. Expert proficiency in the chosen skill.

% IRD
\subsubsection{Perfect Landing} \label{feat::perfectlanding}
    Furthering your natural falling skills, you are trained to handle any fall with ease.
    As long as you are conscious and can freely use your wings, you are immune to fall damage.
    \paragraph{Requirements} Ird kin.
\subsubsection{Songbird} \label{feat::songbird}
    Every so often, you can demonstrate the innate and mystical power of your Charisma.
    You may cast the ​charm person​ spell a number of times equal to your Charisma modifier (Minimum of one) per short rest.
    This spell does not require any somatic components to cast.

    The DC of this spell is equal to 10 + your Charisma modifier, but you can increase this by 2 twice by taking this feat again a second and third time.

    Additionally, you have advantage in any Charisma (Performance) check that involves whistling.
    \paragraph{Requirements} Ird kin.
\subsubsection{Deadly Grip} \label{feat::deadlygrip}
    While flying, you have advantage on Grapple checks made with your talons.
    \paragraph{Requirements} Ird kin.
\subsubsection{Aerial Defense (2 FP)} \label{feat::aerialdefense}
    Creatures who attack you while you're falling, flying, gliding, or jumping have disadvantage on their attack roll.
    \paragraph{Requirements} Ird kin.
\subsubsection{Wing-Assisted Running} \label{feat::wingassistedrunning}
    You increase your base walking speed by 1.5 meters.
    Additionally, you gain a climbing speed equal to half your flying speed.
    \paragraph{Requirements} Ird kin.
\subsubsection{Nimble Step} \label{feat::nimblestep}
    Opportunity attacks made against you are rolled with disadvantage.
    \paragraph{Requirements} Ird or Zaloth kin.
\subsubsection{Graceful Pass} \label{feat::gracefulpass}
    Using your wings to aid your movement, difficult terrain doesn't cost you extra movement.
    \paragraph{Requirements} Ird or Oth kin.
% QULBABA IRD
\subsubsection{Forest Defender} \label{feat::forestdefender}
    You have received martial training to fight among the branches, and are extremely dangerous to climbing opponents.
    You know the Push action (See page \pageref{act::push}), and the target rolls the saving throw with disadvantage if you climbed, glided, or flew at least 3 meters this turn.
    \paragraph{Requirements} Qulbaba Ird or Marset kin.
\subsubsection{Woodland Hunter} \label{feat::woodlandhunter}
    ​Your accuracy allows you to treat three-quarters cover as half cover and half cover as no cover.
    \paragraph{Requirements} Qulbaba Ird or Gannagian Hunter subrace.
\subsubsection{Keenest Senses (2 FP)} \label{feat::keenestsenses}
    You increase your proficiency level with Insight, Investigation, or Perception from Expert to Legendary, increasing your proficiency bonus with the skill to +12.
    \paragraph{Requirements} Qulbaba Ird or Boggart subrace.
% THULKRAKA IRD
\subsubsection{Thulkraka Steel} \label{feat::thulkrakasteel}
    You are specially skilled with a set of smith's tools.
    You can craft any metal item for half the normal cost.

    Additionally, if you have access to a forge at an altitude of at least 3,000 meters, you can use the quench-hardening technique unique to your people and craft the item for a quarter its normal cost.
    \paragraph{Requirements} Thulkraka Ird subrace.
\subsubsection{Giant Slayer (2 FP)} \label{feat::giantslayer}
    An apprentice of the giant slayers from the north, your skill with heavy weapons is unparalleled.
    You gain a +2 bonus to attack rolls made with heavy weapons, and learn the Reckless Attack action (see page \pageref{act::recklessattack}).
    \paragraph{Requirements} Thulkraka ird subrace.
% DRATL IRD
\subsubsection{Patient} \label{feat::patient}
    When you react with a readied action, you have advantage on the first die roll you make as part of that action.
    \paragraph{Requirements} Dratl Ird subrace.
\subsubsection{Deadly Precision (2 FP)} \label{feat::deadlyprecision}
    Whenever you have advantage on an attack roll using Dexterity, Intelligence, Wisdom, or Charisma, you can reroll one of the dice once.
    Additionally, you learn the Aim action.
    \paragraph{Requirements} Dratl Ird or Sunstruck Oth subrace.

% MARSET
\subsubsection{Born Climber} \label{feat::bornclimber}
    You can use your tail to grab onto branches, and don't require to pass any ability checks to climb.
    Additionally, you are able to freely use your hands while climbing, and you increase your climbing speed by three meters.
    \paragraph{Requirements} Marset kin.
\subsubsection{Impaling Carapace} \label{feat::impalingcarapace}
    Through careful training, you know how to position your natural armor for deadly effect in combat.
    When you grapple a creature, the target takes 3 piercing damage if your grapple check succeeds.
    If another creature grapples you, it takes 3 piercing damage.
    If you start your turn grappling or being grappled by a creature, it takes 3 piercing damage.
    \paragraph{Requirements} Marset or Tortle kin.
\subsubsection{Lip Reading} \label{feat::lipreading}
    If you can see a creature's mouth while it is speaking a language you understand, you can understand what it's saying by reading its lips.
    \paragraph{Requirements} Marset kin.
\subsubsection{Curl Up (2 FP)} \label{feat::curlup}
    You can use one action to curl up, exposing attackers to a wall of your toughened quills.
    While curled up in this way you cannot move, attack, or cast spells with somatic components, and your base armor class becomes 19.
    You cannot benefit from any Dexterity bonus to armor class while curled up, but you can still use shields.

    Any creature that misses you with a melee attack while you are curled up takes 2d8 + your Dexterity modifier piercing damage from your sharp spines.
    You may uncurl as a free action at any point during your turn.
    \paragraph{Requirements} Marset kin.
\subsubsection{Communal} \label{feat::communal}
    Whenever you make an Intelligence (History) check related to the history of your kin, culture, or community, you are considered of Legendary proficiency in the History skill, adding a proficiency bonus of +12 to the check instead of your normal proficiency bonus in the skill.
    \paragraph{Requirements} Marset kin.
\subsubsection{Seedspeech} \label{feat::seedspeech}
    Through sounds and touch, you can communicate simple ideas to living plants, and are able to interpret their responses as simple language.
    Plants do not perceive the world in terms of sight, but most can feel differences in temperature, describe things that have touched them, as well as hear vibrations that happened around them (including speech).
    \paragraph{Requirements} Marset kin.
\subsubsection{Acid Spit} \label{feat::acidspit}
    By repeatedly feeding on toxic tree leaves, your saliva has become as vile as its poison.
    You can use two actions to spit a 1.5 by 9 meters line of acid.
    Every target in the area must make a Dexterity saving throw, with a DC of 8 + your Constitution modifier.
    A creature takes 2d6 acid damage on a failed save, or half as much damage on a successful one.
    The acid damage increases to 3d6 with your 6th hit die, 4d6 with your 11th, and 5d6 with your 16th.
    You can use this trait a number of times equal to your Constitution modifier (Minimum of 1) per short rest.

    You can take this feat 3 additional times, increasing the DC by 2 each time.
    \paragraph{Requirements} Marset kin.
\subsubsection{Natural Forager} \label{feat::naturalforager}
    Due to your nature as a gatherer, all foraging DCs are reduced by 5 for you.
    You can also feed on tree gum, but cannot cook meals for other species with this material.
    \paragraph{Requirements} Marset or Gannagian Gatherer kin.
\subsubsection{Nimble and Deadly (2 FP)} \label{feat::nimbleanddeadly}
    You can move through the space of any creaturee that is of a size larger than you.
    When you do so, the creature takes 3 piercing damage.
    \paragraph{Requirements} Marset kin.

% OTH
\subsubsection{Silent Speech} \label{feat::silentspeech}
    You can communicate with other oths, thri-kreen, and other insectoids using Silent Speech.
    This language can only communicate simple ideas, and it does so via a combination of pheromones and thrumming sounds made with antennae.
    \paragraph{Requirements} Oth kin.
\subsubsection{Silk Spinning} \label{feat::silkspinning}
    Dust kin's silk is known for its beauty and strength, and oth's know how to craft clothes and various items with it.
    Your silk counts as a cloth material, and armor made with it has a +1 bonus to its AC.
    You can produce up to one kg of silk per long rest, which you can store for future use.
    \paragraph{Requirements} Oth kin. At least Untrained proficiency with weaver's tools.
\subsubsection{Keen Mind} \label{feat::keenmind}
    You always know which way is north, and you can always know the number of hours left before the next sunrise or sunset.
    \paragraph{Requirements} Oth kin.
\subsubsection{Predestined} \label{feat::predenstined}
    Once per day you can choose to reroll an attack, skill check, or saving throw.
    You can decide to do this after the roll, but before the outcome of the roll has been determined.
    If you are a Chu'ash oth, consider your Fated trait as one additional use of this feat.

    You can learn this trait 3 times, increasing the number of times you can use this feat per day by one each time.
    On the third time, you gain the ability to use this trait to force an enemy to reroll an attack roll made against you.
    \paragraph{Requirements} Oth kin.
\subsubsection{Third Weapon (2 FP)} \label{feat::thirdweapon}
    You can use your two extra arms to hold a weapon with the light property.
    You can attack with this weapon as a free action after you make a melee weapon attack, reducing the attack roll by the apropiate multiple attack penalty.
    \paragraph{Requirements} Oth kin.
\subsubsection{Born Grappler} \label{feat::borngrappler}
    You don't need to have a hand free to grapple, using both your extra arms to do so.
    If you do have a free arm, you roll for the grapple check with advantage.
    You cannot use this feat if you are holding something in one or both of your extra arms.
    \paragraph{Requirements} Oth kin.
% MOONBORN
\subsubsection{Observant} \label{feat::observant}
    You gain a +5 bonus to your passive Wisdom (Perception) and passive Intelligence (Investigation) scores.
    \paragraph{Requirements} Moonborn Oth or Na'anian Tsanek subrace.
\subsubsection{Linguist} \label{feat::linguist}
    You have studied languages and codes, gaining the following benefits:
    \begin{itemize}
        \item You learn a language of your choice.
        \item You can ably create written ciphers.
        Others can't decipher a code you create unless you teach them, they succeed on an Intelligence check (DC equal to 6 + your Intelligence score), or they use magic to decipher it. % TODO: Figure out what spell (probably from Dremshamad) would be able to do this.
    \end{itemize}
    \paragraph{Requirements} Moonborn Oth subrace.
\subsubsection{Magic Initiate (2 FP)} \label{feat::magicinitiate}
    Your learn two cantrips of your choice from one spellcasting doctrine of your choice.
    In addition, choose one 1st-level spell from the same doctrine.
    You learn that spell and can cast it at its lowest level.
    Once you cast it, you must finish a long rest before you can cast it again using this feat.
    Your spellcasting ability for these spells is Intelligence.
    \paragraph{Requirements} Moonborn Oth subrace.
% CHU'ASH
\subsubsection{Fey Touched} \label{feat::feytouched}
    You learn the misty step (see page \pageref{spell:mistystep}) and one 1st-level spell of your choice.
    The spell must be from the Sympathy doctrine.
    You can cast each of these spells without expending a spell slot.
    Once you cast either of these spells in this way, you can't cast that spell in this way again until you finish a short rest.
    You can also cast these spells using spell slots you have of the appropriate level.
    The spells' spellcasting ability is Intelligence.
    \paragraph{Requirements} Chu'ash Oth subrace.
\subsubsection{Bountiful Luck (2 FP)} \label{feat::bountifulluck}
    Your people have extraordinary luck, which you have learned to lend to your companions when you see them falter.
    You're not sure how you do it; you just wish it, and it happens.
    Surely a sign of fortune's favor!

    When an ally you can see within 9 meters of you rolls a 1 on the d20 for an attack roll, an ability check, or a saving throw, you can use your reaction to let the ally reroll the die.
    The ally must use the new roll.

    When you use this ability, you can't use your Fated trait before the end of your next turn.
    \paragraph{Requirements} Chu'ash Oth subrace.
\subsubsection{Lucky} \label{feat::lucky}
    When you roll a 1 on an attack roll, ability check, or saving throw, you can reroll the die and must use the new roll.
    This doesn't count as a use of your Fated trait.
    \paragraph{Requirements} Chu'ash Oth subrace.
% SUNSTRUCK
\subsubsection{Sun-powered} \label{feat::sunpowered}
    By reabsorbing your sweat and taking in dew, you do not need to drink water to survive.
    You gain full sustenance when you use your Photosynthesis trait, including both food and water.
    Additionally, you only need to keep your hindwings for one hour exposed to sunlight or two hours exposed to moonlight to be properly well fed.
    \paragraph{Requirements} Sunstruck Oth subrace.
\subsubsection{Bone Breaker} \label{feat::bonebreaker}
    While gliding, you can attempt to attack a creature with an eviscerating attack.
    Using two actions, you can swoop down up to your movement speed towards a creature you can see, and make a melee weapon attack roll against it.
    If the attack hits, it's a critical hit.
    The attack is tiring, and you can use this feat only once per combat encounter.
    \paragraph{Requirements} Sunstruck Oth subrace.

% NAENK
\subsubsection{Moss Armor} \label{feat::mossarmor}
    Your plant-based framework provides you with unique resilience.
    You have resistance against lightning damage.
    % You have advantage on saving throws against paralysis and are resistant to lightning damage.
    \paragraph{Requirements} Naenk kin.
\subsubsection{Cellular Regeneration (2 FP)} \label{feat::cellularregeneration}
    As an action, you can stimulate your plant cells to rapidly multiply to quickly regenerate wounds.
    You regain 1 hit point, and regain 1 hit point at the start of each of your turns after, until you've restored an amount equal to twice your level.
    After using this trait, you must take a short rest before using it again.
    If you suffer cold, fire, or necrotic damage, this regeneration is cancelled.
    You are also able to regenerate lost limbs, albeit at a very slow pace: it takes you 1d4+2 months to fully recover a lost arm or leg.
    \paragraph{Requirements} Naenk kin.
\subsubsection{Improved Nuen (2 FP)} \label{feat::improvednuen}
    Your nuens are stronger than average, and you do not half the creature's hit points or hit dice when you raise one.
    Additionally, your nuen grows a thick layer of thorns, gaining the \textbf{Impaling Carapace} feat (see page \pageref{feat::impalingcarapace}).
    \paragraph{Requirements} Gannagian Warrior subrace.
\subsubsection{Smell the Danger} \label{feat::smellthedanger}
    % As long as you are not already a master, you increase your proficiency with the herbalism kit.
    You do not need to roll anything to tell if a plant is poisonous, even if you've never encountered it before.
    \paragraph{Requirements} Gannagian Gatherer subrace.
\subsubsection{Master Gatherer} \label{feat::mastergatherer}
    You increase your proficiency with a herbalism kit to Legendary, increasing your proficiency bonus with it to +12.
    \paragraph{Requirements} Gannagian Gatherer subrace. Expert proficiency with a herbalism kit.

% TSANEK
\subsubsection{Enhanced Spores} \label{feat::enhancedspores}
    You can add a +2 bonus to all of your spore effects' spell save DC.
    % Alternatively, you can add your spellcasting modifier if you have one.

    You can take this feat three times.
    \paragraph{Requirements} Tsanek kin.
\subsubsection{Mycelium Connection} \label{feat::myceliumconnection}
    As an action, you can establish a connection with a creature within 9 meters of you.
    Roll a Wisdom (Insight) check contested by the creature's Wisdom (Insight).
    The creature can choose to fail on this save on purpose.
    If you succeed, you know the location of the creature and can telepathically communicate with it for 24 hours.
    The creature knows that it is connected to you, as it feels your presence pulsating in its head, but it cannot end this connection.

    This ability only works while the creature is touching the ground.
    \paragraph{Requirements} Tsanek kin.
\subsubsection{Telepathic} \label{feat::telepathic}
    You can speak telepathically to any creature you can see within 18 meters of you.
    Your telepathic utterances are in a language you know, and the creature understands you only if it knows that language.
    Your communication doesn't give the creature the ability to respond to you telepathically.

    Additionally, you can cast the detect thoughts (see page \pageref{spell::detectthoughts}) spell, requiring no spell slot or components, and you must finish a short rest before you can cast it this way again.
    Your spellcasting ability for the spell is your choice between Intelligence and Wisdom.
    \paragraph{Requirements} Tsanek or Zaloth kin.

% TORTLE
\subsubsection{Reptile Claws} \label{feat::reptileclaws}
    Your claws are natural weapons, which you can use to make unarmed strikes.
    If you hit with them, you deal slashing damage equal to 1d4 + your Strength modifier, instead of the bludgeoning damage normal for an unarmed strike.
    \paragraph{Requirements} Tortle kin.
\subsubsection{Steam Breath} \label{feat::steambreath}
    Some tortles are born with special abilities, which some say hail from the great dragon turtles of old.
    You can use two actions to exhale a 6 meter cone of scalding steam.
    Every target in the area must make a Dexterity saving throw, with a DC of 8 + your Constitution modifier.
    A creature takes 2d6 fire damage on a failed save, or half as much damage on a successful one.
    The fire damage increases to 3d6 with your 6th hit die, 4d6 with your 11th, and 5d6 with your 16th.
    You can use this trait a number of times equal to your Constitution modifier (Minimum of 1) per short rest.
    Being underwater doesn't grant resistance to this damage.

    You can take this feat 3 additional times, increasing the DC by 2 each time.
    \paragraph{Requirements} Tortle kin.
\subsubsection{Reveler (2 FP)} \label{feat::reveler}
    You increase your proficiency level in Performance or Persuasion to Legendary, increasing your proficiency bonus to +12.
    \paragraph{Requirements} Tortle kin. Expert proficiency in the chosen skill.
% Cast spells while hidden in shell (2 FP)

% GRUNG
\subsubsection{Poison Immunity} \label{feat::poisonimmunity}
    You've developed your poison resistance from constant exposure to poisons in your environment and from your own skin.
    You are immune to poison damage and the poisoned condition.
    \paragraph{Requirements} Grung kin.

% UMAN
\subsubsection{NAME} \label{feat::name}
    DESCRIPTION
    \paragraph{Requirements} Uman kin.
\subsubsection{Savage Attacks} \label{feat::savageattacks}
    When you score a critical hit with a melee weapon attack or unarmed strike, you can roll one of the weapon's damage dice one additional time and add it to the extra damage of the critical hit.
    \paragraph{Requirements} Cursed Uman or Dratl Ird subrace.
\subsubsection{Horned Fury} \label{feat::hornedfury}
    Your fury burns tirelessly.
    You gain the following benefits:
    \begin{itemize}
        \item When you hit with an attack using a melee weapon or unarmed strike, you can roll one of the weapon's damage dice an additional time and add it as extra damage of the weapon's damage type.
        Once you use this ability, you can't use it again until you finish a short rest.
        \item Immediately after you use your Relentless Endurance trait, you can use your reaction to make one weapon attack.
    \end{itemize}
    \paragraph{Requirements} Cursed Uman subrace.

% ZALOTH
\subsubsection{Telekinetic} \label{feat::telekinetic}
    You learn the mage hand (see page \pageref{spell:magehand}) cantrip.
    You can cast it without verbal or somatic components, and you can make the spectral hand invisible.
    If you already know this spell, its range increases by 9 meters when you cast it.
    Its spellcasting ability is the ability increased by this feat.

    You can use the Disarm, Grapple, Help, Search, Shove, and Use Object actions using the hand.
    For the Disarm and Shove actions, you roll Intelligence (Arcana) instead of Strength (Athletics) for the contest.

    You can learn this feat two additional times.
    The second time allows you to use the Grapple action with the hand, rolling Intelligence (Arcana) instead of Strength (Athletics).
    The third time allows you to use the Attack action with the hand, using your Arcana skill as your attack bonus.
    On a hit, the hand's damage is 1d4 + your Intelligence modifier force damage, and this attack is affected from all the normal effects of a melee attack.
    \paragraph{Requirements} Zaloth kin.
\subsubsection{Zaloth Cunning (2 FP)} \label{feat::zalothcunning}
    You have advantage on Intelligence, Wisdom, and Charisma saving throws against magic.
    \paragraph{Requirements} Zaloth kin.

% QUIES
\subsubsection{Integrated Weapon} \label{feat::integratedweapon}
    Your understanding of your own body allows you to modify it with ease.
    As part of a short rest, you can integrate a weapon into your form.
    You can only have one weapon integrated at a time, and you can separate from it as part of a short rest.

    You can equip and unequip your integrated weapon as a free action, and don't provoke opportunity attacks when equipping it.
    When inactive, the weapon is effectively invisible, requiring no check of any kind to conceal.

    You can take this feat two additional times.
    The second time gives you a +1 bonus to damage rolls made with the weapon.
    The third time allows you to make a melee attack as part of the free action used to equip your weapon.
    This attack doesn't cause a multiple attack penalty.
    \paragraph{Requirements} Quies kin.
\subsubsection{Immutable Form} \label{feat::immutableform}
    Embracing your origin, you become protected by the strange designs of the tall kin.
    You are immune to any effect that would alter your form.
    \paragraph{Requirements} Quies kin.
\subsubsection{Long-Limbed (2 FP)} \label{feat::longlimbed}
    You harness your inherited adaptability, learning how to alter your proportions at will.
    When you make a melee attack on your turn, your reach for it is 1.5 meters greater than normal.
    \paragraph{Requirements} Quies kin.
\subsubsection{Designed with a Purpose (2 FP)} \label{feat::designedwithapurpose}
    Following your creator's design, your competence at a particular skill is unparalleled.
    Your proficiency with a skill is increased to Legendary, increasing your proficiency bonus to +12 with it.
    \paragraph{Requirements} Quies Operative subrace. Expert proficiency with a skill.
\subsubsection{Thermal Manipulation} \label{feat::thermalmanipulation}
    The years of hard work have taught you how to manipulate your obsidian extensions, modifying their hardness and properties at will.
    The damage die of your unarmed strikes is increased to a d6.
    Additionally, you can change their damage type to bludgeoning, slashing, fire, or cold as a free action.
    \paragraph{Requirements} Quies Juggernaut subrace.
\subsubsection{Rugged Aspect} \label{feat::ruggedaspect}
    By manipulating the composition of your natural armor, you are able to better shift into specific environments.
    You have advantage on Stealth checks made to hide in rocky and similar terrain.
    \paragraph{Requirements} Quies Slag Worker kin.
