% !TEX root = ../main.tex
\subsubsection{Dagger Savant} \label{feat::daggersavant}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You wield the lightest of blades with the deadliest of skills.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} You can perform one melee attack with a dagger as part of a Grapple, Escape a Grapple, Overrun, or Tumble action.
\paragraph{RANK 2} You gain or improve the Sneak Attack technique.
\paragraph{RANK 3} You learn the Riposte technique.

% ============================================================================== %
\subsubsection{Defensive Duelist} \label{feat::defensiveduelist}
\small{\textcolor{gray}{Dexterity}}

\normalsize
A master of the buckler, you have learned to use it as an addition to your main weapon.
\paragraph{REQUIREMENTS} Buckler Training 2.
\paragraph{RANK 1} When you use the Parry technique, you can roll a d8 instead of a d6 when increasing your AC.
\paragraph{RANK 2} When fighting with a one-handed melee weapon and a light shield, you can add half your shield's AC (rounded up) to the weapon's attack damage.
\paragraph{RANK 3} When you use your Parry technique and the attacking creature misses, you can use the Disarm action against it as part of your reaction.

% ============================================================================== %
\subsubsection{Deft Explorer} \label{feat::deftexplorer}
\small{\textcolor{gray}{Nature}}

\normalsize
You are an unsurpassed explorer, using your uncanny knowledge of nature to understand and survive in any environment.
\paragraph{REQUIREMENTS} Naturalist 3.
\paragraph{RANK 1} You double your proficiency modifier in the Nature skill.
\paragraph{RANK 2} By almost supernatural perception, you can sense the presence of poisons and poisonous creatures within 9 meters of you.
\paragraph{RANK 3} Increase your Intelligence score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Detective} \label{feat::detective}
\small{\textcolor{gray}{Investigation}}

\normalsize
You excel at rooting out secrets and unraveling mysteries.
\paragraph{REQUIREMENTS} Inquisitive 3.
\paragraph{RANK 1} You double your proficiency modifier in the Investigation skill.
\paragraph{RANK 2} You have a +5 bonus to your passive intelligence (Investigation) score.
\paragraph{RANK 3} Increase your Intelligence score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Dual Wielder} \label{feat::dualwielder}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You master fighting with two weapons.
\paragraph{REQUIREMENTS} Dexterity 13. Armed Fighter 2.
\paragraph{RANK 1} When you engage in two-weapon fighting, you can add your ability modifier to the damage of the second attack.
\paragraph{RANK 2} You can draw or stow two one-handed weapons when you would normally be able to draw or stow only one.
\paragraph{RANK 3} You learn the Lock technique.

% ============================================================================== %
\subsubsection{Educated} \label{feat::educated}
\small{\textcolor{gray}{Science}}

\normalsize
From background or perchance you've been given a privileged access to books and teaching thorough your life.
You have an advanced understanding of the natural laws of the world.
\paragraph{RANK 1} You are proficient with the Science skill.
\paragraph{RANK 2} You have advantage on the Identify a Spell action.
\paragraph{RANK 3} You have an intuitive understanding of how to use all sorts of machinery, and can operate siege weapons and heavy machines without performing any ability checks.

% ============================================================================== %
\subsubsection{Empathetic} \label{feat::empathetic}
\small{\textcolor{gray}{Insight}}

\normalsize
You possess keen insight into how other people think and feel.
\paragraph{REQUIREMENTS} Insightful 3.
\paragraph{RANK 1} You double your proficiency modifier in the Insight skill.
\paragraph{RANK 2} You learn the Uncanny Insight technique.
\paragraph{RANK 3} Increase your Wisdom score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Estoc Master} \label{feat::estocmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
A master of thrust, you prefer to focus only on piercing and abandon the slashing capabilities of the rapier.
\paragraph{REQUIREMENTS} Light Sword Adept 2.
\paragraph{RANK 1} Whenever you miss with a melee weapon attack, you can use your reaction to reroll that attack if you're wielding an estoc.
\paragraph{RANK 2} You can attack twice instead of once when you use your reaction to attack with the Riposte technique.
\paragraph{RANK 3} While wielding an estoc, you can attack one additional time when you use the attack action.

% ============================================================================== %
\subsubsection{Far Thruster} \label{feat::farthruster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You take advantage of your long weapon to keep your distance from foes.
\paragraph{REQUIREMENTS} Halberd Adept 2 and Spear Adept 2.
\paragraph{RANK 1} After successfully attacking a creature, you can use the Shove action as a bonus action.
\paragraph{RANK 2} You gain a +2 to your attack rolls made with a polearm against a creature larger than you.
\paragraph{RANK 3} You learn the Extend Reach technique.

% ============================================================================== %
\subsubsection{Fearsome} \label{feat::fearsome}
\small{\textcolor{gray}{Intimidation}}

\normalsize
You become fearsome to others, and people are scared to even talk about you.
\paragraph{REQUIREMENTS} Menacing 3.
\paragraph{RANK 1} You double your proficiency modifier in the Intimidation skill.
\paragraph{RANK 2} You learn the Demoralize technique.
\paragraph{RANK 3} Increase your Charisma score by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Fell Hand} \label{feat::fellhand}
\small{\textcolor{gray}{Strength}}

\normalsize
You are an expert with the greatclub, and can use its raw power to pancake even the hardiest foes.
\paragraph{REQUIREMENTS} Hammer Adept 2.
\paragraph{RANK 1} When you use a greatclub, its damage die changes from a d8 to a d10.
\paragraph{RANK 2} Whenever you miss with a melee attack using a greatclub, the target takes bludgeoning damage equal to your Strength modifier (minimum of 2).
\paragraph{RANK 3} When your target fails its saving throw against your Bonk technique, it also falls prone.

% ============================================================================== %
\subsubsection{Fencer} \label{feat::fencer}
\small{\textcolor{gray}{Dexterity}}

\normalsize
More than a mere combatant, you are able to dance in the battlefield when using your light blades.
\paragraph{REQUIREMENTS} Light Sword Adept 2 and Performer 2.
\paragraph{RANK 1} You gain a +1 to melee attack rolls and AC when only one creature is within 5 feet of you.
\paragraph{RANK 2} When you use your Parry technique and the attacking creature misses, you can use the Riposte technique without using your reaction.
\paragraph{RANK 3} You learn the Focus Strikes technique.

% ============================================================================== %
\subsubsection{Firearm Specialist} \label{feat::firearmspecialist}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are particularly well at combat with pistols, and are a shining example of this new weapon's viability in combat.
\paragraph{REQUIREMENTS} Pistol Adept 2.
\paragraph{RANK 1} You can reload any weapon as a bonus action.
\paragraph{RANK 2} If you are using a pistol in one hand and nothing on the other, you get a +2 bonus to your ranged weapon attacks with it.
\paragraph{RANK 3} You learn the Rapid Repair technique.

% ============================================================================== %
\subsubsection{Flail Adept} \label{feat::flailadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
The flail is a tricky weapon to use, but you have spent countless hours mastering it.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with flails.
\paragraph{RANK 2} When wielding flails, enemies provoke opportunity attacks from you when they enter your reach.
\paragraph{RANK 3} You learn the Sweep technique.

% ============================================================================== %
