% !TEX root = ../main.tex
\subsubsection{Yumi User} \label{feat::yumiuser}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You use the versatility of the yumi to your advantage, improving your aim while kneeling or on horseback.
\paragraph{REQUIREMENTS} Bow Adept 2 and Great Weapon User 1.
\paragraph{RANK 1} You only get disadvantage on ranged attack rolls with a yumi when your target is within 3 meters instead of 6.
\paragraph{RANK 2} At the beginning of your turn, you can reduce your movement to 0 and get advantage on one ranged weapon attack you make during the same turn.
\paragraph{RANK 3} You get a +2 to damage rolls with a yumi if you don't move during your turn or are riding on a mount.

% ============================================================================== %
\subsubsection{Zoophilist} \label{feat::zoophilist}
\small{\textcolor{gray}{Animal Handling}}

\normalsize
You master the techniques needed to train and handle animals.
\paragraph{REQUIREMENTS} Animal Handler 3.
\paragraph{RANK 1} You double your proficiency modifier in the Animal Handling skill.
\paragraph{RANK 2} When you use the Beast Command technique, you can make a Wisdom (Animal Handling) check of DC 20.
If you succeed, you can spend the next 8 hours bonding with the beast, after which it becomes your permanent companion.
You can have only one animal companion at a time.
You can issue commands to your companion using the Beast Command technique without needing to make a Wisdom (Animal Handling) check.
Additionally, your animal companion considers you its kin, and will protect you with its life.
If you fail, the effect of Beast Command works normally, but you cannot try to bond with the same beast again.
\paragraph{RANK 3} Increase your Wisdom score by 1, to a maximum of 20.

% ============================================================================== %
