% % === ARMOR ==================================================================== %
% \subsubsection{Stealthy} \label{feat::stealthy}
% \small{\textcolor{gray}{Stealth}}
%
% \normalsize
% You know how best to hide, and use your dyed light armor to benefit your stealth.
% \paragraph{REQUIREMENTS} Lightly Armored 2 and Sly 2.
% \paragraph{RANK 1} You can take the Hide action as a bonus action on each of your turns.
% \paragraph{RANK 2} If you are hidden, you can move up to 3 meters in the open without revealing yourself if you end the move in a position where you're not clearly visible.
% \paragraph{RANK 3}
%
% \subsubsection{Imposing Figure} \label{feat::imposingfigure}
% \small{\textcolor{gray}{Intimidation}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Menacing 2 and Heavily Armored 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3}
%
% % ============================================================================== %
% \subsubsection{Flexible Fighter} \label{feat::flexiblefighter} %
% \small{\textcolor{gray}{Intelligence}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Intelligence 13. Armed Fighter 2.
% \paragraph{RANK 1} You are able to use weapons with the Trick property.
% \paragraph{RANK 2}
% \paragraph{RANK 3} TECHNIQUE
%
% % ============================================================================== %
% \subsubsection{Adaptable} \label{feat::adaptable} %
% \small{\textcolor{gray}{Intelligence}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Intelligence 16. Flexible Fighter 2.
% \paragraph{RANK 1} % advantage when investigating creatures before combat
% \paragraph{RANK 2}
% \paragraph{RANK 3}
%
% % ============================================================================== %
% % \subsubsection{Nunchaku Master} \label{feat::nunchakumaster}
% % \small{\textcolor{gray}{Dexterity}}
%
% % \normalsize
% % Description.
% % \paragraph{REQUIREMENTS} Flail Adept 2 and Acrobat 2.
% % \paragraph{RANK 1}
% % \paragraph{RANK 2} extra damage
% % \paragraph{RANK 3} ADVANCED TECHNIQUE

% \subsubsection{Numbed Senses} \label{feat::numbedsenses}
% \small{\textcolor{gray}{Constitution}}
%
% \normalsize
% Your heavy experience in manual labor or melee combat has granted you an increased resilience against strikes of all kind.
% \paragraph{REQUIREMENTS} Constitution 13.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3}

% \subsubsection{Desensitized Combatant} \label{feat::desensitizedcombatant}
% \small{\textcolor{gray}{Constitution}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Constitution 16. Numbed Senses 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3}

% \subsubsection{Flexible Fighter} \label{feat::flexiblefighter} %
% \small{\textcolor{gray}{Intelligence}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Intelligence 13. Armed Fighter 2.
% \paragraph{RANK 1} You are able to use weapons with the Trick property.
% \paragraph{RANK 2}
% \paragraph{RANK 3} TECHNIQUE

% \subsubsection{Adaptable} \label{feat::adaptable} %
% \small{\textcolor{gray}{Intelligence}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Intelligence 16. Flexible Fighter 2.
% \paragraph{RANK 1} % advantage when investigating creatures before combat
% \paragraph{RANK 2}
% \paragraph{RANK 3}

% \subsubsection{Experienced Combatant} \label{feat::experiencedcombatant} %
% \small{\textcolor{gray}{Wisdom}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Wisdom 13. Armed Fighter 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3} TECHNIQUE

% \subsubsection{Ready-for-Anything} \label{feat::readyforanything} %
% \small{\textcolor{gray}{Wisdom}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Wisdom 16. Experienced Combatant 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3}

% \subsubsection{Captain} \label{feat::captain}
% \small{\textcolor{gray}{Charisma}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Charisma 13. Armed Fighter 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3} TECHNIQUE

% \subsubsection{Commander} \label{feat::commander}
% \small{\textcolor{gray}{Charisma}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Charisma 16. Mesmerizing Warrior 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3} % Advantage on persuasion, deception, performance, and intimidation checks while fighting

% \subsubsection{Mounted Combatant} \label{feat::mountedcombatant} %
% \small{\textcolor{gray}{Animal Handling}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Animal Handler 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3}

% \subsubsection{Exotic Rider} \label{feat::exoticrider} %
% \small{\textcolor{gray}{Animal Handling}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Mounted Combatant 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3} You don't attack with disadvantage on ranged attacks while riding flying creatures.

% \subsubsection{Hidden Striker} \label{feat::hiddenstriker} %
% \small{\textcolor{gray}{Stealth}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Sly 2 and Armed Fighter 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3} You gain or improve the Sneak Attack technique.

% \subsubsection{Assassin} \label{feat::assassin} %
% \small{\textcolor{gray}{Stealth}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Hidden Striker 2.
% \paragraph{RANK 1}
% \paragraph{RANK 2}
% \paragraph{RANK 3} You gain or improve the Sneak Attack technique.

% \subsubsection{Fire-breather} \label{feat::firebreather}
% \small{\textcolor{gray}{Science}}
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS} Educated 2.
% \paragraph{RANK 1} You are proficient with Drer's fire-breathers.
% \paragraph{RANK 2}
% \paragraph{RANK 3}

% \subsubsection{Drunken Brawler} \label{feat::drunkenbrawler} %
% \small{\textcolor{gray}{}}
% % Skills emulating drunken fighting AND actual bonus when drunk.
%
% \normalsize
% Description.
% \paragraph{REQUIREMENTS}
% \paragraph{RANK 1}
% \paragraph{RANK 2} When you suffer from the effects of drunkenness, you have advantage on Constitution and Strength saving throws.
% \paragraph{RANK 3} You learn the Careless Deflect technique.
\subsubsection{Armed Fighter} \label{feat::armedfighter}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
No one learned how to use a sword without first swinging a stick.
\paragraph{RANK 1} You are proficient with simple weapons.
\paragraph{RANK 2} You can attack twice, instead of once, whenever you take the Attack action on your turn.
\paragraph{RANK 3} You learn one technique of your choice between Bonk, Block, Buttstroke, Feint, Lunge, Parry, Pushing Attack, Protect, Quick Draw, Riposte, Rush, Sweep, and Trip.

% ============================================================================== %
\subsubsection{Armor Breaker} \label{feat::armorbreaker}
\small{\textcolor{gray}{Strength}}

\normalsize
You use your extensive knowledge of heavy armor to improve your effectiveness against it, turning your bludgeoning attacks into devastating metal bending strikes.
\paragraph{REQUIREMENTS} Hammer Adept 2 and Heavily Armored 1.
\paragraph{RANK 1} You can use the Bonk technique as an opportunity attack.
\paragraph{RANK 2} When fighting a target with plate armor or natural armor, you get a +2 bonus to your melee attacks with hammers.
\paragraph{RANK 3} You learn the Fell Strike technique.

% ============================================================================== %
\subsubsection{Axe Adept} \label{feat::axeadept}
\small{\textcolor{gray}{Strength}}

\normalsize
More than a simple tool, you master the use of axes in combat.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with axes.
\paragraph{RANK 2} While wielding an axe, you get advantage on your attack rolls with the Disarm action when forcing your target to drop a shield.
\paragraph{RANK 3} You learn the Rush technique.

% ============================================================================== %
\subsubsection{Ball-and-Chain Master} \label{feat::ballandchainmaster}
\small{\textcolor{gray}{Strength}}

\normalsize
Your increased awareness works in tandem to your flail mastery, allowing you to hit enemies behind obstacles and shields.
\paragraph{REQUIREMENTS} Flail Adept 2 and Insightful 2.
\paragraph{RANK 1} When you use a ball-and-chain, its damage die changes from a d6 to a d8.
\paragraph{RANK 2} When you hit with an opportunity attack using a ball-and-chain, the target must succeed on a Strength saving throw (DC 8 + your proficiency bonus + your Strength modifier) or be knocked prone.
\paragraph{RANK 3} You learn the Shield Sweep technique.

% ============================================================================== %
\subsubsection{Bent Blade Master} \label{feat::bentblademaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your extreme skill with curved swords allows you to cut through flesh with effectiveness and ease.
\paragraph{REQUIREMENTS} Curved Sword Adept 2 and Quick Fingers 2.
\paragraph{RANK 1} While you're wielding at least one curved sword and a creature gets an attack of opportunity on you, they attack with disadvantage.
\paragraph{RANK 2} You get a +2 bonus to your melee weapon attack damage with curved blades.
This extra damage is nullified against targets with chainmail, plate armor, or natural armor.
\paragraph{RANK 3} You learn the Shield Sweep technique.

% ============================================================================== %
\subsubsection{Blade \& Board} \label{feat::bladeandboard}
\small{\textcolor{gray}{Strength}}

\normalsize
You know the perfect balance between defense and attack, making you a formidable foe in melee combat.
\paragraph{REQUIREMENTS} Straight Blade Adept 2 and Shield Training 2, or Axe Adept 2 and Shield Training 2.
\paragraph{RANK 1} When you're wielding a slashing weapon and a shield, you gain a +1 to AC and to your attack damage.
\paragraph{RANK 2} While you're wielding a shield and a creature misses you with a melee attack, you can use your reaction to attack it with a melee attack.
\paragraph{RANK 3} You learn the Bash technique.

% ============================================================================== %
\subsubsection{Blade Breaker} \label{feat::bladebreaker}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You know that the perfect counter against any sword is simply a long pole.
\paragraph{REQUIREMENTS} Staff Fighter 2.
\paragraph{RANK 1} Staves have the Reach property when wielded by you.
\paragraph{RANK 2} You have advantage on the Disarm action and the Parry technique against creatures using any type of sword.
\paragraph{RANK 3} While using a polearm, you can use the Disarm action as your opportunity attack.

% ============================================================================== %
\subsubsection{Blowgun Adept} \label{feat::blowgunadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
While unconventional, you understand the effectiveness of the blowgun when remaining hidden is of the essence.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} You are proficient with blowguns.
\paragraph{RANK 2} You gain a +1 bonus to attack rolls with a blowgun.
Additionally, attacking with a blowgun at long range doesn't impose disadvantage on your ranged weapon attack rolls.
\paragraph{RANK 3} When you hit with a blowgun while hidden, your location is not revealed.

% ============================================================================== %
\subsubsection{Blunt Thrower} \label{feat::bluntthrower}
\small{\textcolor{gray}{Strength}}

\normalsize
You take advantage of the raw practicality of a good hammer, and not even faraway foes can escape the wrath of its face.
\paragraph{REQUIREMENTS} Hammer Adept 2 and Thrown Weapon Master 2.
\paragraph{RANK 1} You don't provoke opportunity attacks when picking weapons up from the floor.
\paragraph{RANK 2} When you hit a creature with an thrown bludgeoning weapon, you divide its moving speed by half (rounded up) during its next turn.
This effect does not stack.
\paragraph{RANK 3} You learn the Hammer Fling technique.

% ============================================================================== %
\subsubsection{Blunt Master} \label{feat::bluntmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your staff is an extension of your body, and it has become an essential part of your movement and defense.
\paragraph{REQUIREMENTS} Staff Fighter 2 and Unarmed Artist 2.
\paragraph{RANK 1} As a bonus action, you can use your staff to propel yourself into the air, making a high jump up to your Dexterity modifier times 1.5 meters.
Additionally, if you have moved at least 3 meters during this round, you can jump in a straight line up to a distance equal to your Dexterity modifier times 3 meters.
\paragraph{RANK 2} You gain a +1 bonus to your AC while using a staff.
Additionally, if you use the weapon with two hands you gain another +1 bonus to your AC.
\paragraph{RANK 3} You learn the Defensive Stance technique.

% ============================================================================== %
\subsubsection{Bow Adept} \label{feat::bowadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
While a long list of new ranged weapons have recently appeared, you know that nothing beats the long range of the traditional bow.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with bows.
\paragraph{RANK 2} After you successfully hit a target with a melee attack using your bow, that creature can't make opportunity attacks against you until the start of your next turn.
\paragraph{RANK 3} You learn the Quick Draw technique.

% ============================================================================== %
\subsubsection{Buckler Training} \label{feat::bucklertraining}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Small shields are much more than a weaker version of the standard shields.
They allow you to remain mobile while still providing a solid defense against even the fastest assailants.
\paragraph{RANK 1} You gain proficiency with light shields.
\paragraph{RANK 2} In combat, you can don or doff a light shield as the free object interaction of your turn.
\paragraph{RANK 3} You learn the Parry technique.

% ============================================================================== %
\subsubsection{Bullet Tinkerer} \label{feat::bullettinkerer}
\small{\textcolor{gray}{Science}}

\normalsize
Firearm ammunition is near impossible to find or purchase in most parts of Yuadrem.
Due to this, learning how to craft it yourself is an essential aspect for using firearms.
\paragraph{REQUIREMENTS} Musket Adept 2 and Educated 2, or Pistol Adept 2 and Educated 2.
\paragraph{RANK 1} You can craft ammunition using a set of Tinker's Tools at half the cost.
\paragraph{RANK 2} If you roll a misfire, you can use your reaction to roll a d20 with disadvantage.
If the number rolled is higher than the weapon's misfire score, the weapon does not misfire.
\paragraph{RANK 3} You learn the Violent Shot technique.
\subsubsection{Combat Improviser} \label{feat::combatimproviser}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Anything can be your weapon.
If you can grab it, you can swing it.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} You are proficient with improvised weapons.
An improvised weapon is anything that is somewhat similar to a simple weapon.
\paragraph{RANK 2} After rolling for initiative, you make your first attack with an improvised weapon at advantage.
\paragraph{RANK 3} You learn one technique of your choice between Bonk, Block, Buttstroke, Feint, Lunge, Parry, Pushing Attack, Protect, Quick Draw, Riposte, Rush, Sweep, and Trip.

% ============================================================================== %
\subsubsection{Covered Shooter} \label{feat::coveredshooter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You know that stealth and range go hand in hand.
\paragraph{REQUIREMENTS} Bow Adept 2 and Sly 2.
\paragraph{RANK 1} If you miss with a ranged attack with a bow or thrown weapon while hidden, the attack doesn't reveal your location, and you remain hidden.
\paragraph{RANK 2} You can treat ranged attack damage die rolls of 1 as 2.
\paragraph{RANK 3} You learn or improve the Sneak Attack technique.

% ============================================================================== %
\subsubsection{Crossbow Adept} \label{feat::crossbowadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are learned with the use of crossbow, and can use it proficiently both for hunting and combat.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with crossbows.
\paragraph{RANK 2} You can change the loading quality of crossbows to reloading.
% You can ignore the loading quality of crossbows.
\paragraph{RANK 3} You learn the Buttstroke technique.

% ============================================================================== %
\subsubsection{Crossbow Expert} \label{feat::crossbowexpert}
\small{\textcolor{gray}{Dexterity}}

\normalsize
While muskets and pistols have largely replaced the old weapons of warfare, you prefer a weapon that won't blow up on your hand every so often.
\paragraph{REQUIREMENTS} Crossbow Adept 2 and Quick Fingers 2.
\paragraph{RANK 1} Being within 1.5 meters of a hostile creature doesn't impose disadvantage on your ranged attack rolls.
Additionally, you don't provoke attacks of opportunity when using the Attack action with a ranged weapon when within the reach of a creature.
\paragraph{RANK 2} You get a +2 bonus to damage rolls when attacking a creature within 1.5 meters of you with a crossbow.
\paragraph{RANK 3} You learn the Prepared Shot technique.

% ============================================================================== %
\subsubsection{Crusher} \label{feat::crusher}
\small{\textcolor{gray}{Strength}}

\normalsize
You are practiced in the art of crushing your enemies.
\paragraph{REQUIREMENTS} Proficiency with at least two martial bludgeoning weapon types.
\paragraph{RANK 1} Once per turn, when you hit a creature with an attack that deals bludgeoning damage, you can move it 1.5 meters to an unoccupied space, provided that the target is no more than one size larger than you.
\paragraph{RANK 2} Increase your Strength by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Whack technique.

% ============================================================================== %
\subsubsection{Curved Sword Adept} \label{feat::curvedswordadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You forfeited the piercing capacity of the straight blades to maximize your deadliness against the unarmored.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with curved swords.
\paragraph{RANK 2} While wielding a curved sword, you get advantage on your attack rolls with the Disarm action when forcing your target to drop a weapon.
\paragraph{RANK 3} You learn the Parry technique.

% ============================================================================== %
\subsubsection{Cutthroat} \label{feat::cutthroat}
\small{\textcolor{gray}{Dexterity}}

\normalsize
A master at concealing your dagger, you act quick and strike hard in combat.
\paragraph{REQUIREMENTS} Dagger Savant 2.
\paragraph{RANK 1} You have advantage on any check to conceal a small weapon on your person.
\paragraph{RANK 2} You gain a +2 bonus to initiative. % when wielding a light weapon.
\paragraph{RANK 3} You gain or improve the Sneak Attack technique.

% ============================================================================== %
\subsubsection{Dagger Savant} \label{feat::daggersavant}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You wield the lightest of blades with the deadliest of skills.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} You can perform one melee attack with a dagger as part of a Grapple, Escape a Grapple, Overrun, or Tumble action.
\paragraph{RANK 2} You gain or improve the Sneak Attack technique.
\paragraph{RANK 3} You learn the Riposte technique.

% ============================================================================== %
\subsubsection{Defensive Duelist} \label{feat::defensiveduelist}
\small{\textcolor{gray}{Dexterity}}

\normalsize
A master of the buckler, you have learned to use it as an addition to your main weapon.
\paragraph{REQUIREMENTS} Buckler Training 2.
\paragraph{RANK 1} When you use the Parry technique, you can roll a d8 instead of a d6 when increasing your AC.
\paragraph{RANK 2} When fighting with a one-handed melee weapon and a light shield, you can add half your shield's AC (rounded up) to the weapon's attack damage.
\paragraph{RANK 3} When you use your Parry technique and the attacking creature misses, you can use the Disarm action against it as part of your reaction.

% ============================================================================== %
\subsubsection{Dual Wielder} \label{feat::dualwielder}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You master fighting with two weapons.
\paragraph{REQUIREMENTS} Dexterity 13. Armed Fighter 2.
\paragraph{RANK 1} When you engage in two-weapon fighting, you can add your ability modifier to the damage of the second attack.
\paragraph{RANK 2} You can draw or stow two one-handed weapons when you would normally be able to draw or stow only one.
\paragraph{RANK 3} You learn the Lock technique.

% ============================================================================== %
\subsubsection{Estoc Master} \label{feat::estocmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
A master of thrust, you prefer to focus only on piercing and abandon the slashing capabilities of the rapier.
\paragraph{REQUIREMENTS} Light Sword Adept 2.
\paragraph{RANK 1} Whenever you miss with a melee weapon attack, you can use your reaction to reroll that attack if you're wielding an estoc.
\paragraph{RANK 2} You can attack twice instead of once when you use your reaction to attack with the Riposte technique.
\paragraph{RANK 3} While wielding an estoc, you can attack one additional time when you use the attack action.

% ============================================================================== %
\subsubsection{Far Thruster} \label{feat::farthruster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You take advantage of your long weapon to keep your distance from foes.
\paragraph{REQUIREMENTS} Halberd Adept 2 and Spear Adept 2.
\paragraph{RANK 1} After successfully attacking a creature, you can use the Shove action as a bonus action.
\paragraph{RANK 2} You gain a +2 to your attack rolls made with a polearm against a creature larger than you.
\paragraph{RANK 3} You learn the Extend Reach technique.

% ============================================================================== %
\subsubsection{Fell Hand} \label{feat::fellhand}
\small{\textcolor{gray}{Strength}}

\normalsize
You are an expert with the greatclub, and can use its raw power to pancake even the hardiest foes.
\paragraph{REQUIREMENTS} Hammer Adept 2.
\paragraph{RANK 1} When you use a greatclub, its damage die changes from a d8 to a d10.
\paragraph{RANK 2} Whenever you miss with a melee attack using a greatclub, the target takes bludgeoning damage equal to your Strength modifier (minimum of 2).
\paragraph{RANK 3} When your target fails its saving throw against your Bonk technique, it also falls prone.

% ============================================================================== %
\subsubsection{Fencer} \label{feat::fencer}
\small{\textcolor{gray}{Dexterity}}

\normalsize
More than a mere combatant, you are able to dance in the battlefield when using your light blades.
\paragraph{REQUIREMENTS} Light Sword Adept 2 and Performer 2.
\paragraph{RANK 1} You gain a +1 to melee attack rolls and AC when only one creature is within 5 feet of you.
\paragraph{RANK 2} When you use your Parry technique and the attacking creature misses, you can use the Riposte technique without using your reaction.
\paragraph{RANK 3} You learn the Focus Strikes technique.

% ============================================================================== %
\subsubsection{Firearm Specialist} \label{feat::firearmspecialist}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are particularly well at combat with pistols, and are a shining example of this new weapon's viability in combat.
\paragraph{REQUIREMENTS} Pistol Adept 2.
\paragraph{RANK 1} You can reload any weapon as a bonus action.
\paragraph{RANK 2} If you are using a pistol in one hand and nothing on the other, you get a +2 bonus to your ranged weapon attacks with it.
\paragraph{RANK 3} You learn the Rapid Repair technique.

% ============================================================================== %
\subsubsection{Flail Adept} \label{feat::flailadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
The flail is a tricky weapon to use, but you have spent countless hours mastering it.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with flails.
\paragraph{RANK 2} When wielding flails, enemies provoke opportunity attacks from you when they enter your reach.
\paragraph{RANK 3} You learn the Sweep technique.

% ============================================================================== %
\subsubsection{Giant Slayer} \label{feat::giantslayer}
\small{\textcolor{gray}{Strength}}

\normalsize
Partaking or not in Krudzal's Eternal War, you use your incredible strength to wield their massive weapons.
\paragraph{REQUIREMENTS} Strength 16. Great Weapon User 2.
\paragraph{RANK 1} You are able to use Krudzal's giant-slayers.
\paragraph{RANK 2} You gain a +1 bonus to damage rolls with weapons with the Great property.
\paragraph{RANK 3} When fighting with a melee giant-slayer, you can attack up to three creatures in range with one attack.
Additionally, you can reload the hand ballista as a bonus action instead of an action.

% ============================================================================== %
\subsubsection{Glaive Master} \label{feat::glaivemaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Different than the common polearm, you know how deadly a glaive can be in capable hands.
\paragraph{REQUIREMENTS} Halberd Adept 2.
\paragraph{RANK 1} When you use a glaive, its damage die changes from a d10 to a d12.
\paragraph{RANK 2} The glaive has the finesse property for you.
\paragraph{RANK 3} When you miss an attack, you can attempt to strike your enemy with the rondel of your glaive as a free action.
On a hit, the target takes 1d4 + your Strength modifier bludgeoning damage.
You can do this once per turn.

% ============================================================================== %
\subsubsection{Grappler} \label{feat::grappler}
\small{\textcolor{gray}{Strength}}

\normalsize
You've developed the skills necessary to hold your own in close-quarters grappling.
\paragraph{REQUIREMENTS} Pugilist 2.
\paragraph{RANK 1} You have advantage on attack rolls against creatures you are grappling.
\paragraph{RANK 2} You benefit from three-quarters cover while you grapple a creature of a size equal or greater than yours.
\paragraph{RANK 3} You learn the Pin technique.

% ============================================================================== %
\subsubsection{Great Weapon User} \label{feat::greatweaponuser}
\small{\textcolor{gray}{Strength}}

\normalsize
You've learned to put the weight of a weapon to your advantage, letting its momentum empower your strikes.
\paragraph{REQUIREMENTS} Strength 13. Armed Fighter 2.
\paragraph{RANK 1} You can use weapons with the great property.
Some of these, like the zweihander and the greataxe, also require you to have proficiency with the corresponding weapon type.
\paragraph{RANK 2} On your turn, when you score a critical hit with a melee weapon or reduce a creature to 0 hit points with one, you can make one melee weapon attack as a bonus action.
\paragraph{RANK 3} You learn the Reckless Strike technique.

% ============================================================================== %
\subsubsection{Greatshield Training} \label{feat::greatshieldtraining}
\small{\textcolor{gray}{Strength}}

\normalsize
When it comes to protecting your life or that of others, you know that size matters.
\paragraph{REQUIREMENTS} Shield Training 1.
\paragraph{RANK 1} You gain proficiency with heavy shields
\paragraph{RANK 2} Creatures standing behind you get three-fourths cover against ranged attacks.
\paragraph{RANK 3} You learn the Protect technique.

% ============================================================================== %
\subsubsection{Gunner} \label{feat::gunner}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Being a new breed of weapon, firearms are constantly subject to change and refinement.
New weapons appear by the minute, and you are an expert at experimenting with them.
\paragraph{REQUIREMENTS} Pistol Adept 2 and Musket Adept 2.
\paragraph{RANK 1} As long as you can examine the weapon for 30 seconds, you are proficient with any kind of firearm, even if it is new or experimental.
\paragraph{RANK 2} Your firearm attacks score a critical hit on a roll of 19-20.
\paragraph{RANK 3} You learn the Reckless Shot technique.

% ============================================================================== %
\subsubsection{Halberd Adept} \label{feat::halberdadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You know that both farmers and nobles use halberds as their weapon of choice for a reason.
\paragraph{REQUIREMENTS} Armed Fighter 2 and Staff Fighter 2.
\paragraph{RANK 1} You are proficient with the many varieties of halberds.
\paragraph{RANK 2} When a creature within 1.5 meters of you makes an attack against a target other than you, you can use your reaction to make a melee weapon attack against the attacking creature.
\paragraph{RANK 3} You learn the Trip technique.

% ============================================================================== %
\subsubsection{Hammer Adept} \label{feat::hammeradept}
\small{\textcolor{gray}{Strength}}

\normalsize
If a hammer will do, why complicate things?
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You gain proficiency with hammer weapons.
\paragraph{RANK 2} If you use the Help action to aid an ally's melee attack while you're wielding a hammer weapon, you knock the target's shield aside momentarily.
In addition to the ally gaining advantage on the attack roll, the ally gains a bonus to the roll equal to the shield's AC bonus.
\paragraph{RANK 3} You learn the Bonk technique.

% ============================================================================== %
\subsubsection{Hand Crossbow Master} \label{feat::handcrossbowmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You can equip, load, and shoot a hand crossbow in an instant, and with deadly effect.
\paragraph{REQUIREMENTS} Crossbow Adept 2.
\paragraph{RANK 1} You can reload a hand crossbow or one-handed firearm without having a free hand.
\paragraph{RANK 2} You can ignore the loading (or reloading) quality of hand crossbows.
\paragraph{RANK 3} You can don and you can doff a one-handed ranged weapon as your free object interaction during your turn.
The two actions don't need to be done in tandem - for example, you can don a hand crossbow, shoot an arrow, and doff it during one turn.

% ============================================================================== %
\subsubsection{Heavily Armored} \label{feat::heavilyarmored}
\small{\textcolor{gray}{Strength}}

\normalsize
You are trained to use heavy armor.
\paragraph{REQUIREMENTS} Moderately Armored 1.
\paragraph{RANK 1} You gain proficiency with heavy armor.
\paragraph{RANK 2} Equipped heavy armor and metal accessories only add half their weight to your encumbrance.
\paragraph{RANK 3} Increase your Strength by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Heavy Armor Master} \label{feat::heavyarmormaster}
\small{\textcolor{gray}{Strength}}

\normalsize
You can use your armor to deflect strikes that would easily kill others.
\paragraph{REQUIREMENTS} Heavily Armored 2 and Athletics 2.
\paragraph{RANK 1} Your hit point maximum increases by an amount equal to your number of hit dice.
Whenever you earn a hit die thereafter, your hit point maximum increases by an additional 1 hit point.
\paragraph{RANK 2} While you are wearing heavy armor, piercing and slashing damage that you take is reduced by 3.
\paragraph{RANK 3} You learn the Defend technique.

% ============================================================================== %
\subsubsection{Heavy Lifter} \label{feat::heavylifter}
\small{\textcolor{gray}{Strength}}

\normalsize
You can easily lift and hurl objects that others can barely move.
\paragraph{REQUIREMENTS} Combat Improviser 2 and Thrown Weapon Master 2.
\paragraph{RANK 1} You can hurl any object or creature you can carry or grapple as you would an improvised weapon.
If you hurl a creature, both it and the target of your attack take 1d6 + your Strength modifier bludgeoning damage.
\paragraph{RANK 2} You count as if you were one size larger for the purpose of determining your carrying capacity.
\paragraph{RANK 3} You learn the Suplex technique.

% ============================================================================== %
\subsubsection{Heavy-Weight Combatant} \label{feat::heavyweightcombatant}
\small{\textcolor{gray}{Athletics}}

\normalsize
You can use the weight of your body and your armor to greatly aid you in combat.
\paragraph{REQUIREMENTS} Heavily Armored 2 and Pugilist 2.
\paragraph{RANK 1} If you are wearing metal gauntlets, your unarmed strike uses a d6 + your Strength modifier for damage.
\paragraph{RANK 2} While you are wearing heavy armor, you roll with advantage when taking the Shove action.
You also roll Strength (Athletics) with advantage when you are targeted by a Shove action.
\paragraph{RANK 3} You have learned to strategically position the crevices in your armor to hurt creatures too close to you.
When you grapple a creature, the target takes 1d6 piercing damage if your grapple check succeeds.
If another creature grapples you, they take 1d6 piercing damage.
If you start your turn grappling or being grappled by a creature, it takes 1d6 piercing damage.

% ============================================================================== %
\subsubsection{Horse Killer} \label{feat::horsekiller}
\small{\textcolor{gray}{Animal Handling}}

\normalsize
Mounts are one of the most common advantages in war, so you've learned to deal with them appropriately.
\paragraph{REQUIREMENTS} Spear Adept 2 and Animal Handler 2.
\paragraph{RANK 1} You can always target a rider's mount with an attack made with a spear, even if the rider can normally deflect this attack to it.
\paragraph{RANK 2} You have a +2 to your attack rolls made against mounts.
\paragraph{RANK 3} You learn the Charge Stopper technique.

% ============================================================================== %
\subsubsection{Immovable Object} \label{feat::immovableobject}
\small{\textcolor{gray}{Strength}}

\normalsize
You are an obstacle.
\paragraph{REQUIREMENTS} Greatshield Training 2.
\paragraph{RANK 1} Creatures can't use a Tumble action to move through your space.
Additionally, you have advantage on Strength (Athletics) checks against being shoved or pushed.
\paragraph{RANK 2} While using a heavy shield, you get three-fourths cover against ranged attacks.
Additionally, you can duck behind your shield as a reaction, granting you full cover against ranged attacks until the start of your next turn.
\paragraph{RANK 3} The movement speed debuff from using a tower shield is halved for you.

% ============================================================================== %
\subsubsection{Insistent Fighter} \label{feat::insistentfighter}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You always maintain your foes at a cozy distance by masterfully manipulating your halberd.
\paragraph{REQUIREMENTS} Halberd Adept 2 and Observant 2.
\paragraph{RANK 1} Creature's provoke opportunity attacks from you even if they take the Disengage action before leaving your reach.
\paragraph{RANK 2} When you hit a creature with an opportunity attack, the creature's speed becomes 0 for the rest of the turn.
\paragraph{RANK 3} Your reach for opportunity attacks with polearms is of at least 3 meters.
Additionally, if you do hit a creature with an opportunity attack, you can choose to pull it towards you by 1.5 meters.

% ============================================================================== %
\subsubsection{Kama Master} \label{feat::kamamaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
From among the common people weapon, you specialize in the use of the kama.
\paragraph{REQUIREMENTS} Pick Adept 2.
\paragraph{RANK 1} When you use a kama, its damage die changes from a d6 to a d8
\paragraph{RANK 2} When you successfully attack a foe with a piercing attack using your kama, you also deal 1d4 slashing damage, unmodified by your dexterity.
\paragraph{RANK 3} You can use the Trip technique as part of an opportunity attack.

% ============================================================================== %
\subsubsection{Light Armor Master} \label{feat::lightarmormaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You make effective use of the increased mobility that comes from the use of light armor.
\paragraph{REQUIREMENTS} Lightly Armored 2.
\paragraph{RANK 1} You can use the Dodge action even if you speed is 0.
\paragraph{RANK 2} If you aren't incapacitated, you can add a +2 bonus to any Dexterity saving throw you make against a spell or other harmful effect that targets only you.
\paragraph{RANK 3} Your learn the Lunge technique.

% ============================================================================== %
\subsubsection{Light Sword Adept} \label{feat::lightswordadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Focused on piercing throw your opponent's armor, you've learned the art of fighting with light swords.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with light swords.
\paragraph{RANK 2} When you are wielding a light sword in one hand and no other weapons, you gain a +2 bonus to damage rolls with that weapon.
\paragraph{RANK 3} You learn the Riposte technique.

% ============================================================================== %
\subsubsection{Lightly Armored} \label{feat::lightlyarmored}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You are trained in the use of light armor.
\paragraph{RANK 1} You gain proficiency with light armor.
\paragraph{RANK 2} Equipped light armor and cloth accessories don't add to your encumbrance.
\paragraph{RANK 3} Increase your Dexterity by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Longsword Master} \label{feat::longswordmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Your proficiency with the longsword is unparalleled, and you regularly prove to your foes that the old sword is as valid today as it was on its golden age.
\paragraph{REQUIREMENTS} Straight Sword Adept 2.
\paragraph{RANK 1} When you use a longsword, its damage die changes from a d10 to a d12.
\paragraph{RANK 2} When a creature misses you with a melee weapon attack, you can roll to use the Disarm action on it as your reaction.
\paragraph{RANK 3} When you use the Block technique and an attack misses you, you can use the Riposte technique without using your reaction.

% ============================================================================== %
\subsubsection{Maiming Strikes} \label{feat::maimingstrikes}
\small{\textcolor{gray}{Strength}}

\normalsize
Your increased proficiency cleaving through wood and stone translates to devastating attacks against flesh and bone.
\paragraph{REQUIREMENTS} Axe Adept 2 and Pick Adept 2.
\paragraph{RANK 1} The last attack you make with the Attack action is rolled with advantage if you hit the target at least once in your turn.
\paragraph{RANK 2} When a creature rolls on the minor \& major injury charts from one of your attacks, they roll with advantage.
\paragraph{RANK 3} You learn the Cleave technique.

% ============================================================================== %
\subsubsection{Medium Armor Master} \label{feat::mediumarmormaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You have extensively practiced moving in medium armor, and make skilled use of its adaptive capabilities.
\paragraph{REQUIREMENTS} Moderately Armored 2.
\paragraph{RANK 1} Wearing medium armor doesn't impose disadvantage on your Dexterity (Stealth) checks.
\paragraph{RANK 2} When you wear medium armor, you can add 3, rather than 2, to your AC if you have a Dexterity of 16 or higher.
\paragraph{RANK 3} While wearing medium armor, you may add half your proficiency bonus, rounded down, to Strength, Dexterity, and Constitution saving throws that don't already include your proficiency bonus.

% ============================================================================== %
\subsubsection{Medium Haft Master} \label{feat::mediumhaftmaster}
\small{\textcolor{gray}{Strength}}

\normalsize
Why learn how to fight with a sword when your tools will do the job?
\paragraph{REQUIREMENTS} Axe Adept 2, Hammer Adept 2, and Pick Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with axes, hammers, and picks.
\paragraph{RANK 2} You can treat any weapon as if it had the Heavy property.
\paragraph{RANK 3} You learn the Shield Break technique.

% ============================================================================== %
\subsubsection{Moderately Armored} \label{feat::moderatelyarmored}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You are trained in the use of medium armor, be it leather, chain, or plate.
\paragraph{REQUIREMENTS} Lightly Armored 1.
\paragraph{RANK 1} You gain proficiency with medium armor.
\paragraph{RANK 2} Equipped medium armor and leather or chain accessories don't add to your encumbrance.
\paragraph{RANK 3} Increase your Strength or Dexterity by 1, to a maximum of 20.

% ============================================================================== %
\subsubsection{Modern Soldier} \label{feat::modernsoldier}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Always up-to-date, you are ready to fight your foes with both a melee and a ranged weapon.
\paragraph{REQUIREMENTS} Straight Sword Adept 2 and Crossbow Adept 2.
\paragraph{RANK 1} When you use the Attack action and attack with a one-handed weapon, you can use your bonus action to attack with a hand crossbow or loaded firearm you are holding.
\paragraph{RANK 2} When using a backsword or a sabre on one hand and your other hand is free, you can hold the back of the blade with your free hand to increase its cutting power.
You add a +2 to your melee weapon attack damage while wielding your weapon in this way.
\paragraph{RANK 3} You learn the Visceral Attack technique.

% ============================================================================== %
\subsubsection{Musket Adept} \label{feat::musketadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Quickly picking up on new trends, you gambled on muskets and their stopping power early on.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with muskets.
\paragraph{RANK 2} While you have a two-handed firearm equipped, you have advantage on rolls against effects that would move you.
\paragraph{RANK 3} You learn the Buttstroke technique.

% ============================================================================== %
\subsubsection{Pick Adept} \label{feat::pickadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
For you, there is no difference between mining ore and piercing flesh.
Apart from the screams at least.
% You pierce through metal, flesh, and bone just as you would ore.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with picks.
\paragraph{RANK 2} All picks have the versatile property for you.
When you wield a pick with two hands, increase its damage die by one (d6 to d8, d8 to d10, etc), and have the heavy property.
\paragraph{RANK 3} You learn the Trip technique.

% ============================================================================== %
\subsubsection{Piercer} \label{feat::piercer}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You have achieved a penetrating precision in combat.
\paragraph{REQUIREMENTS} Proficiency with at least two martial piercing weapon types.
\paragraph{RANK 1} Once per turn, when you hit a creature with an attack that deals piercing damage, you can reroll one of the attack's damage dice, and you must use the new roll.
\paragraph{RANK 2} Increase your Strength or Dexterity by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Armor Puncture technique.

% ============================================================================== %
\subsubsection{Pike Master} \label{feat::pikemaster}
\small{\textcolor{gray}{Strength}}

\normalsize
You prefer to maintain distance from your opponents by wielding an amusingly long pole.
\paragraph{REQUIREMENTS} Spear Adept 2.
\paragraph{RANK 1} When you use a pike, its damage die changes from a d10 to a d12.
\paragraph{RANK 2} When you use the Feint technique you can choose to not attack with advantage.
If you do this and still hit your target, it's a critical hit.
\paragraph{RANK 3} When wielding a pike, its reach property adds 3 meters instead of 1.5 meters to the weapon's range.

% ============================================================================== %
\subsubsection{Pistol Adept} \label{feat::pistoladept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Already a master of the crossbow, it isn't hard for you to adapt your use of the handcrossbow to that of the pistol.
\paragraph{REQUIREMENTS} Crossbow Adept 2.
\paragraph{RANK 1} You are proficient with pistols.
\paragraph{RANK 2} You can stow a firearm, then draw another weapon as a single object interaction on your turn.
\paragraph{RANK 3} When you get a critical hit against a creature on a ranged attack with a firearm, all other attacks against the creature are made with advantage until the start of your next turn.

% ============================================================================== %
\subsubsection{Polearm Master} \label{feat::polerarmmaster} %
\small{\textcolor{gray}{Dexterity}}

\normalsize
You keep your enemies at bay with your long weapons.
\paragraph{REQUIREMENTS} Staff Fighter 2, Spear Adept 2, and Halberd Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with staves, spears, and halberds.
\paragraph{RANK 2} While wielding a stave, spear, or halberd, other creatures provoke an opportunity attack from you when they enter your reach.
\paragraph{RANK 3} You learn the Rondel Hit technique.

% ============================================================================== %
\subsubsection{Precise Thrower} \label{feat::precisethrower}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Either from luck or rigorous training, you have the capacity to hit the hardest of targets when throwing a weapon.
\paragraph{REQUIREMENTS} Dagger Savant 2 and Thrown Weapon Master 2.
\paragraph{RANK 1} Attacking at long range doesn't impose disadvantage on your thrown weapon attack rolls.
\paragraph{RANK 2} Whenever you hit a creature with an thrown slashing or piercing weapon, it has disadvantage on the first melee attack it performs on its next turn.
\paragraph{RANK 3} You learn the Bull's Eye technique.

% ============================================================================== %
\subsubsection{Pugilist} \label{feat::pugilist}
\small{\textcolor{gray}{Strength}}

\normalsize
Your fighting style has only three components:
A fist, another fist, and a face to punch.
\paragraph{RANK 1} Your unarmed strike uses a d4 + your Strength modifier for damage.
\paragraph{RANK 2} When you hit a creature with an unarmed strike, you can use a bonus action to attempt to grapple the target.
\paragraph{RANK 3} You learn the Bonk technique.

% ============================================================================== %
\subsubsection{Revenant Blade} \label{feat::revenantblade}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are a expert of the double-bladed scimitar, and use the technique as proficiently as any master from the ancient Janchu'ut school of hunters.
\paragraph{REQUIREMENTS} Curved Blade Adept 2.
\paragraph{RANK 1} A double-bladed scimitar has the finesse property when you wield it.
\paragraph{RANK 2} While you are holding a double-bladed scimitar with two hands, you gain a +1 bonus to Armor Class.
\paragraph{RANK 3} Instead of dealing 1d4 slashing damage, the extra attack you can do with a double-bladed scimitar deals 2d4 slashing damage.

% ============================================================================== %
\subsubsection{Sharpshooter} \label{feat::sharpshooter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You can strike a foe with an arrow or bullet no matter where they are in the battlefield.
\paragraph{REQUIREMENTS} Bow Adept 2 or Musket Adept 2.
\paragraph{RANK 1} If you do not move during your turn, you can make an additional ranged weapon attack as a bonus action.
\paragraph{RANK 2} Both your normal and long ranges are multiplied by 1.5 for all ranged weapons..
\paragraph{RANK 3} Whenever you have advantage on a ranged attack roll using Dexterity, you can reroll one of the dice once.

% ============================================================================== %
\subsubsection{Shield Master} \label{feat::shieldmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You know that fighting to the death leads to a short life.
You trust your shield with your life, and you are an expert at avoiding death.
\paragraph{REQUIREMENTS} Shield Training 2.
\paragraph{RANK 1} If you aren't incapacitated, you can add your shield's AC bonus to any Dexterity saving throw you make against a spell or other harmful effect that targets only you.
\paragraph{RANK 2} If you are subjected to an effect that allows you to make a Dexterity saving throw to take only half damage, you can use your reaction to take no damage if you succeed on the saving throw, interposing your shield between yourself and the source of the effect.
\paragraph{RANK 3} When you use the Shove action or the Push technique with your shield, you can choose to force the Prone condition on your target instead of pushing it.

% ============================================================================== %
\subsubsection{Shield Training} \label{feat::shieldtraining}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Your prefer to live a long life, and choose to carry your trusty shield with you at all times.
\paragraph{RANK 1} You gain proficiency with medium shields.
\paragraph{RANK 2} In combat, you can don or doff a medium shield as a bonus action instead of an action.
\paragraph{RANK 3} You learn the Push technique.

% ============================================================================== %
\subsubsection{Shooter} \label{feat::shooter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You have mastered ranged weapons and can make shots that others find impossible.
\paragraph{REQUIREMENTS} Proficiency with at least two martial ranged weapon types.
\paragraph{RANK 1} Your ranged attacks ignore half cover and three-quarters covers.
\paragraph{RANK 2} Increase your Dexterity by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Leg Shot technique.

% ============================================================================== %
\subsubsection{Slasher} \label{feat::slasher}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Your experience with blades has taught you where to cut to have the greatest results.
\paragraph{REQUIREMENTS} Proficiency with at least two martial slashing weapon types.
\paragraph{RANK 1} Once per turn when you hit a creature with an attack that deals slashing damage, you can reduce the speed of the target by 3 meters until the start of your next turn.
\paragraph{RANK 2} Increase your Strength or Dexterity by 1, to a maximum of 20.
\paragraph{RANK 3} You learn the Grievous Wound technique.

% ============================================================================== %
\subsubsection{Sniper} \label{feat::sniper}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Learned in the use of most ranged weapons, you are an expert at piercing foes from afar.
\paragraph{REQUIREMENTS} Bow Adept 2, Crossbow Adept 2, and Musket Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with bows, crossbows, pistols, and muskets.
\paragraph{RANK 2} Attacking at long range doesn't impose disadvantage on your ranged weapon attack rolls.
\paragraph{RANK 3} You learn the Hemorrhaging Attack technique.

% ============================================================================== %
\subsubsection{Spear Adept} \label{feat::spearadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Trained in the art of the spear, you know that nothing beats a long pole with a pointy end.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with spears.
\paragraph{RANK 2} Spears have the finesse property for you.
\paragraph{RANK 3} You learn the Feint technique.

% ============================================================================== %
\subsubsection{Staff Fighter} \label{feat::stafffighter}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You have mastered the nuances of fighting with a staff.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} The staff counts as a finesse weapon for you.
\paragraph{RANK 2} While wielding a staff, you can use your bonus action to give yourself advantage on your next Dexterity (Acrobatics) or Strength (Athletics) check related to climbing, jumping, or otherwise bypassing obstacles.
This benefit lasts until the end of your turn.
\paragraph{RANK 3} You learn the Sweep technique.

% ============================================================================== %
\subsubsection{Stone Piercer} \label{feat::stonepiercer}
\small{\textcolor{gray}{Strength}}

\normalsize
You know that the difference between piercing stone and crushing bone lies only in the morals of the aggressor.
\paragraph{REQUIREMENTS} Pick Adept 2 and Athlete 2.
\paragraph{RANK 1} You double your damage dice against objects and structures while attacking with a pick.
Additionally, you have advantage on checks made with a climber's kit and pitons.
\paragraph{RANK 2} When you score a critical hit that deals piercing damage to a creature, you can roll one additional damage die when determining the extra piercing damage the target takes.
\paragraph{RANK 3} You learn the Injure technique.

% ============================================================================== %
\subsubsection{Straight Sword Adept} \label{feat::straightswordadept}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You are proficient with the traditional fighting style of straight swords.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You are proficient with straight swords.
\paragraph{RANK 2} When you are wielding a straight sword in one hand and no other weapons, you gain a +1 to AC.
% As a free action at the start of your turn, you can choose to reduce your chance to hit by 2, while increasing your AC by 1 until the start of your next turn.
\paragraph{RANK 3} You learn the Block technique.

% ============================================================================== %
\subsubsection{Sword Master} \label{feat::swordmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
You have an insight unique to those who master the many types of swords.
Your skill with the long blades is unparalleled, and your resoluteness in combat scares even the bravest of warriors.
\paragraph{REQUIREMENTS} Straight Sword Adept 2, Curved Sword Adept 2, and Light Sword Adept 2.
\paragraph{RANK 1} You gain a +1 bonus to attack rolls you make with swords.
\paragraph{RANK 2} When you make an opportunity attack with a sword, you have advantage on the attack roll.
\paragraph{RANK 3} You learn the Parrying Stance technique.

% ============================================================================== %
\subsubsection{Swashbuckler} \label{feat::swashbuckler}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Like modern fighters, you mix your combat style with both melee and ranged attacks.
However, you gain the upper hand on them by adding a fair share of cheap tactics to this mix.
\paragraph{REQUIREMENTS} Curved Sword Adept 2 and Crossbow Adept 2, or Light Sword Adept 2 and Crossbow Adept 2.
\paragraph{RANK 1} When you use the Attack action and attack with a one-handed weapon, you can use a bonus action to attack with a hand crossbow or a loaded firearm you are holding.
\paragraph{RANK 2} During your turn, if you make a melee attack against a creature, that creature can't make opportunity attacks against you for the rest of your turn.
\paragraph{RANK 3} You learn the Cheap Shot technique.

% ============================================================================== %
\subsubsection{Thrown Weapon Master} \label{feat::thrownweaponmaster}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Born with quick fingers and good aim, you're an expert at piercing your enemies with thrown objects.
\paragraph{REQUIREMENTS} Armed Fighter 1.
\paragraph{RANK 1} Attacking at long range doesn't impose disadvantage on your thrown weapon attack rolls.
\paragraph{RANK 2} When you throw a thrown weapon as an attack roll, you can draw another thrown weapon freely.
\paragraph{RANK 3} You learn the Quick Draw technique.

% ============================================================================== %
\subsubsection{Tree Feller} \label{feat::treefeller}
\small{\textcolor{gray}{Strength}}

\normalsize
Nature is your foe, and you use your broad axe to fell both trees and foes.
\paragraph{REQUIREMENTS} Axe Adept 2.
\paragraph{RANK 1} When you use a broad axe, its damage die changes from a d8 to a d10, and from a d10 to a d12 when wielded with two hands.
\paragraph{RANK 2} While wielding a broad axe, you deal double damage to structures and items.
\paragraph{RANK 3} Whenever you hit a plant or a plant creature with a slashing weapon, the target takes an additional 2 slashing damage.

% ============================================================================== %
\subsubsection{Two-weapon Master} \label{feat::twoweaponmaster}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your ability to wield two weapons is unparalleled, and you can surprise any foe with your quick steps and unrelenting strikes.
\paragraph{REQUIREMENTS} Dexterity 16. Dual Wielder 2.
\paragraph{RANK 1} You can use use two-weapon fighting even when the one-handed melee weapons you are wielding aren't light.
\paragraph{RANK 2} You gain a +1 bonus to AC while you are wielding a separate melee weapon in each hand.
\paragraph{RANK 3} You can add your ability modifier to the damage of the bonus attack of your two-weapon fighting action.

% ============================================================================== %
\subsubsection{Unarmed Artist} \label{feat::unarmedartist}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are a painter.
Your hands are your brush, your opponent your canvas.
\paragraph{RANK 1} Your unarmed strike uses a d4 + your Dexterity modifier for damage.
You can only use this ability if you're not using a fist weapon.
\paragraph{RANK 2} When you use the Attack action, you can make an unarmed strike as a bonus action.
\paragraph{RANK 3} You get access to one Martial Arts technique of your choice.
You may buy this rank again to attain new Martial Arts techniques as long as you have not learned all available techniques.

% ============================================================================== %
\subsubsection{Unarmored} \label{feat::unarmored}
\small{\textcolor{gray}{Dexterity}}

\normalsize
Your extensive physical training allows to forfeit armor when fighting.
Your body is the only armor you need.
\paragraph{REQUIREMENTS} Acrobat 2 and Athlete 2.
\paragraph{RANK 1} As long as you are not wearing any armor, your speed increases by 3 meters.
\paragraph{RANK 2} If you are subjected to an effect that allows you to make a Dexterity saving throw to take only half damage, you can use your reaction to take no damage if you succeed on the saving throw, and half damage if you fail.
You only get this bonus while wearing no armor or light armor.
\paragraph{RANK 3} You learn the Rush technique.

% ============================================================================== %
\subsubsection{Way of the Fist} \label{feat::wayofthefist}
\small{\textcolor{gray}{Strength or Dexterity}}

\normalsize
Either by meditative training or drunken fighting, you are a master with your fists.
\paragraph{REQUIREMENT} Pugilist 2 and Unarmed Artist 2.
\paragraph{RANK 1} Your unarmed strike uses a d6 + your Strength or Dexterity modifier for damage.
\paragraph{RANK 2} When you get a critical hit with an unarmed strike, you can take the Disarm, Disengage, or Shove action as a free action.
\paragraph{RANK 3} You are never unarmed, for your fists are your weapons.
Your unarmed strikes deal double stamina damage.

% ============================================================================== %
\subsubsection{Whip Adept} \label{feat::whipadept}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You are learned in the use of the whip, using your unique weapon for both combat and support.
\paragraph{REQUIREMENTS} Armed Fighter 2.
\paragraph{RANK 1} You can use your bonus action to make one melee attack with an equipped whip.
\paragraph{RANK 2} You can use a whip to extend the range of the Grapple and Shove actions to the range of the weapon.
\paragraph{RANK 3} You can use your whip as an elongated appendage to perform actions that do not require fine motor skills.
This includes object interactions, such as grabbing a sword or pulling a bag towards you, and ability checks, such as an acrobatics roll to grab a nearby support beam to swing from.

% ============================================================================== %
\subsubsection{Wrestler} \label{feat::wrestler}
\small{\textcolor{gray}{Strength}}

\normalsize
Every part of your body is a weapon and you wield it expertly.
\paragraph{REQUIREMENTS} Grappler 2 and Combat Improviser 2.
\paragraph{RANK 1} Once per round, as part of your action, you many deal your Strength modifier in damage to any creature you are grappling.
\paragraph{RANK 2} You can use a grappled creature of a size equal or lower to yours as an improvised weapon.
\paragraph{RANK 3} You learn the Charge technique.

% ============================================================================== %
\subsubsection{Yumi User} \label{feat::yumiuser}
\small{\textcolor{gray}{Dexterity}}

\normalsize
You use the versatility of the yumi to your advantage, improving your aim while kneeling or on horseback.
\paragraph{REQUIREMENTS} Bow Adept 2 and Great Weapon User 1.
\paragraph{RANK 1} You only get disadvantage on ranged attack rolls with a yumi when your target is within 3 meters instead of 6.
\paragraph{RANK 2} At the beginning of your turn, you can reduce your movement to 0 and get advantage on one ranged weapon attack you make during the same turn.
\paragraph{RANK 3} You get a +2 to damage rolls with a yumi if you don't move during your turn or are riding on a mount.

% ============================================================================== %

% TODO: Raise a shield as an action/reaction, increasing its AC bonus by +2.
% TODO: Take cover behind a heavy shield, giving 1/2 or 3/4 cover.
