% !TEX root = ../main.tex
\section{Lists} % TODO: This needs a better name urgently.
% FIGHTING STYLES
\subsection*{Fighting Styles} \label{ssec::fightingstyles}
\subsubsection{Archery 1}
    You gain a +2 bonus to attack rolls you make with ranged weapons.
\subsubsection{Archery 2}
    Both your normal and long ranges are multiplied by 1.5 for all ranged weapons.
\subsubsection{Battle Mastery 1}
    You gain a number a Maneuver Dice equal to half your level (rounded down).
    Your Maneuver Dice are d6s, and are special dice that you can use to enhance the effect of certain actions.
    You regain all expended Maneuver Dice at the end of a short rest.

    Whenever you take an action that involves a d20 roll which isn't the Attack or Cast a Spell action, you can choose to roll a Maneuver Die, adding the result of the die to the d20.
\subsubsection{Battle Mastery 2}
    You increase the die associated to your Maneuver Dice from a d6 to a d8.

    In addition, when you roll for initiative and have no Maneuver Dice remaining, you regain 4 Maneuver Dice.
\subsubsection{Dueling 1}
    When you are wielding a melee weapon in one hand and no other weapons, you gain a +2 bonus to damage rolls with that weapon.
\subsubsection{Dueling 2}
    When you are wielding a melee weapon in one hand and no other weapons, you gain a +1 bonus to AC.
\subsubsection{Great Weapon Fighting 1}
    When you roll a 1 or 2 on a damage die for an attack you make with a melee weapon that you are wielding with two hands, you can reroll the die and must use the new roll, even if the new roll is a 1 or a 2.
    The weapon must have the two-handed or versatile property for you to gain this benefit.
\subsubsection{Great Weapon Fighting 2}
    You gain a +1 bonus to attack rolls you make with weapons with the two-handed or versatile property.

    In addition, you gain a +1 bonus to attack rolls you make with weapons with the heavy property.
\subsubsection{Monastic Fighting 1}
    You gain a number of monastic dice equal to half your level (rounded down).
    Your monastic dice are d6s, and are special dice you can spend to use special abilities related to this fighting style.
    You regain all expended monastic dice at the end of a short rest.

    In addition, you learn three abilities when you learn this fighting style:
    \subparagraph{Concentrated Attack} After you hit a creature with an unarmed attack but before you roll damage for the attack, you can spend one monastic die and add the number rolled to the damage done.
    \subparagraph{Patient Defense} You can spend one monastic die and take the Dodge action using only one action.
    When you do this, add the number rolled to your AC until the start of your next turn.
    \subparagraph{Step of the Wind} You can spend one monastic die to take the Disengage action using only one action.
    When you do this, add the 1.5 times the number rolled to your movement speed (in meters) until the end of your turn.
\subsubsection{Monastic Fighting 2}
    You increase the die associated to your monastic dice from a d6 to a d8.

    In addition, when you roll for initiative and have no monastic dice remaining, you regain 4 monastic dice.
\subsubsection{Mounted Fighting 1}
    You have advantage on saving throws made to avoid falling off your mount.
    If you fall off your mount and descend no more than 3 meters, you can land on your feet if you're not incapacitated.

    Finally, mounting or dismounting a creature requires one action rather than two for you.

    To take this fighting style, you must be proficient with land vehicles.
\subsubsection{Mounted Fighting 2}
    Your steed gains a number of hit points equal to half your maximum hit points.
\subsubsection{Protection 1}
    While you are wearing armor, you gain a +1 bonus to AC.
\subsubsection{Protection 2}
    You gain a bonus to all Strength, Dexterity, and Constitution saving throws equal to the AC granted by your shield.
\subsubsection{Thrown Weapon Fighting 1}
    You can draw a weapon that has the thrown property as part of the attack you make with the weapon.
\subsubsection{Thrown Weapon Fighting 2}
    When you hit with a ranged attack using a thrown weapon, you add a +2 bonus to the damage roll.
\subsubsection{Two-Weapon Fighting 1}
    You suffer from the multiple attack penalty for each wielded weapon independently --- Attack rolls made with a weapon held in one hand don't impose a penalty on attack rolls made with a weapon held in your other hand.
\subsubsection{Two-Weapon Fighting 2}
    When you engage in two-weapon fighting, you can add your ability modifier to the damage of the second attack.
\subsubsection{Unarmed Fighting 1}
    Your unarmed strikes can deal bludgeoning damage equal to 1d6 + your Strength modifier on a hit.

    In addition, the multiple attack penalty is reduced by 1 when you make unarmed attacks.
\subsubsection{Unarmed Fighting 2}
    If you aren't wielding any weapons or a shield, the damage die from your unarmed strikes becomes a d8.

    In addition, you can deal 1d4 bludgeoning damage to one creature grappled by you at the start of each of your turns.

% SPELLCASTING STYLES
\subsection*{Spellcasting Styles} \label{ssec::spellcastingstyles}

% MANEUVERS

% METAMAGIC --- metamagic involves using one additional action on the spell to change some effect of it. Same as sorcerer metamagic, but unlimited use.
% ARTIFICER INFUSIONS
\begin{table*}[!ht]%
    \begin{DndTable}[width=\linewidth, header=Artificer Infusions]{ll}
        \textbf{Name} & \textbf{Description} \\
        Armor of Strength &
        \textit{Prerequisite: A suit of armor (requires attunement)}.

        This armor has 6 charges. The wearer can expend the armor's charges in the following ways:
        \begin{itemize}
            \item When the wearer makes a Strength check or a Strength saving throw, it can expend 1 charge to add a bonus to the roll equal to its Intelligence modifier.
            \item If the creature would be knocked prone, it can use its reaction to expend 1 charge to avoid being knocked prone.
        \end{itemize}
        The armor regains 1d6 expended charges daily at dawn. \\

        Enhanced Focus    &
        \textit{Prerequisite: An arcane focus (requires attunement)}.

        While holding this item, a creature gains a +1 bonus to spell attack rolls. In addition, the creature ignores half cover when making a spell attack.

        The bonus increases to +2 when you reach 10th level. \\

        Enhanced Defense  &
        \textit{Prerequisite: A suit of armor or a shield}.

        A creature gains a +1 bonus to Armor Class while wearing (armor) or wielding (shield) the infused item.

        The bonus increases to +2 when you reach 10th level. \\

        Enhanced Weapon   &
        \textit{Prerequisite: A simple or martial weapon}.

        This weapon grants a +1 bonus to attack and damage rolls made with it.

        The bonus increases to +2 when you reach 10th level. \\

        Mind Sharpener    &
        \textit{Prerequisite: A suit of armor or robes}.

        The infused item can send a jolt to the wearer to refocus their mind.
        The item has 4 charges.
        When the wearer fails a Constitution saving throw to maintain concentration on a spell, the wearer can use its reaction to expend 1 of the item's charges to succeed instead.
        The item regains 1d4 expended charges daily at dawn. \\

        Repeating Shot    &
        \textit{Prerequisite: A simple or martial weapon with the ammunition property (requires attunement)}.

        This weapon grants a +1 bonus to attack and damage rolls made with it when it's used to make a ranged attack, and it ignores the loading property if it has it.

        If you load no ammunition in the weapon, it produces its own, automatically creating one piece of ammunition when you make a ranged attack with it.
        The ammunition created by the weapon vanishes the instant after it hits or misses a target. \\

        Returning Weapon  &
        \textit{Prerequisite: A simple or martial weapon with the thrown property}.

        This weapon grants a +1 bonus to attack and damage rolls made with it, and it returns to the wielder's hand immediately after it is used to make a ranged attack.
    \end{DndTable}
\end{table*}
